### 2018-08-05 main.tex
first

\documentset{12pt}
\start{document}
hello,world
\end{document}

### 2018-08-05 TRANS-JOUR/latex/ALL_1x-TIE-2xxx.tex
add style file

%\documentclass[onecolumn]{IEEEtranTIE}
\documentclass[journal]{IEEEtranTIE}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{picinpar}
\usepackage{amsmath}
\usepackage{url}
\usepackage{flushend}
\usepackage[latin1]{inputenc}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{color}
\usepackage{alltt}
\usepackage[hidelinks]{hyperref}
\usepackage{enumerate}
\usepackage{siunitx}
\usepackage{breakurl}
\usepackage{epstopdf}
\usepackage{pbox}

\begin{document}
\title{	Preparation of Papers for IEEE Trans on Industrial Electronics \\ (Jul. 2018)}

\author{
	\vskip 1em
	{\color{red}
	First A. Author1, \emph{Student Membership},
	Second B. Author2, \emph{Membership},
	\\ and Third C. Author3, \emph{Membership}
	}

	\thanks{

		{\color{red}
		Manuscript received Month xx, 2xxx; revised Month xx, xxxx; accepted Month x, xxxx.
		This work was supported in part by the xxx Department of xxx under Grant  (sponsor and financial support acknowledgment goes here).

		(Authors' names and affiliation) First A. Author1 and Second B. Author2 are with the xxx Department, University of xxx, City, State C.P. Country, on leave from the National Institute for xxx, City, Country (e-mail: author@domain.com).

		Third C. Author3 is with the National Institute of xxx, City, State C.P. Country (corresponding author to provide phone: xxx-xxx-xxxx; fax: xxx-xxx-xxxx; e-mail: author@ domain.gov).
		}
	}
}

\maketitle

\begin{abstract}
These instructions give you guidelines for preparing papers for IEEE TRANSACTIONS ON INDUSTRIAL ELECTRONICS. {\color{red} PLEASE NOTE, ALL INFORMATION IN THIS TEMPLATE WRITTEN IN THE \underline{RED TEXT} SHOULD BE OMITTED FOR PEER REVIEW AS TIE PERFORMS A DOUBLE-BLIND REVIEW. IF YOUR PAPER IS ACCEPTED, WE ASK AUTHORS TO INCLUDE THE RED TEXT INFORMATION IN THE FINAL FILES PDF.} Use this document as a template. The electronic file of your paper will be formatted further at IEEE. Paper titles should be written in uppercase and lowercase letters, not all uppercase. Avoid writing long formulas with subscripts in the title; short formulas that identify the elements are fine (e.g., ``Nd-Fe-B''). Do not write ``(Invited)'' in the title. Write full names of authors are required in the author field. Define all symbols used in the abstract. Do not cite references in the abstract. Do not delete the blank line immediately above the abstract; it sets the footnote at the bottom of this column.
\end{abstract}

\begin{IEEEkeywords}
Enter key words or phrases in alphabetical order, separated by commas. For a list of suggested keywords, send a blank e-mail to \href{mailto:keywords@ieee.org}{keywords@ieee.org} or visit \url{http://www.ieee.org/documents/taxonomy_v101.pdf}.
\end{IEEEkeywords}

\markboth{IEEE TRANSACTIONS ON INDUSTRIAL ELECTRONICS}%
{}

\definecolor{limegreen}{rgb}{0.2, 0.8, 0.2}
\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
\definecolor{greenhtml}{rgb}{0.0, 0.5, 0.0}

\section{Introduction}

\IEEEPARstart{T}{his} document is a template for authors. If you are reading a paper or PDF version of this document, please download the electronic file, TRANS-JOUR.zip, from the TIE Web site at \url{http://www.ieee-ies.org/pubs/transactions-on-industrial-electronics} so you can use it to prepare your manuscript.

After unzipping, choose word or LATEX option. Open ALL\_1-TIE-2xxx.docx for Word or ALL\_1-TIE-2xxx.tex for LATEX (highly recommended).

These types of manuscript are accepted in TIE:

\begin{enumerate}[1)]
	\item Regular Papers and Special Section papers - Four to eight pages, including authors' bios and photos. These will be added only on the final submission.
	\item Letters - One to three pages. Authors' bios and photos must not be included.
\end{enumerate}

\section{Submission of a new manuscript for review}

Contributions to the Transactions, Journals, and Letters must be submitted electronically on IEEE's on-line manuscript submission and peer-review system, ScholarOne® Manuscripts (former Manuscript Central).

Before submitting, carefully read the TIE checklist above ``TIE checklist for new manuscript submissions'' and modify your manuscript accordingly. Once your paper is completely suitable to TIE rules, follow this procedure:

\begin{enumerate}[1)]
	\item Open ScholarOne® Manuscripts web \url{http://mc.manuscriptcentral.com/tie-ieee}. If you haven't an existing account, please create it.
	\item Go to your Author Center and click ``Submit First Draft of a New Manuscript''. All IEEE journals require an Open Researcher and Contributor ID (ORCID) for all authors. ORCIDs enable accurate attribution and improved discoverability of an author's published work. The author will need a registered ORCID in order to submit a manuscript or review a proof in this journal.
	\item Along with other information, you will be asked to select the subject from a pull-down list. There are various steps to the submission process; you must complete all steps for a complete submission. At the end of each step you must click ``Save and Continue''.
	\item Just uploading the paper is not sufficient. After the last step, you should see a confirmation that the submission is complete. You should also receive an e-mail confirmation.
	\item More detailed instructions can be found at \url{http://mchelp.manuscriptcentral.com/gethelpnow/training/author/}.
\end{enumerate}

Please notice that in your Author Center you may check the current status of your manuscript such as: In EIC office, Assigned to AE, AE invites reviewers, AE assigns reviewers, Under review, Awaiting AE decision, and Awaiting EIC decision. If you find that your manuscript is not moving in the process for a month or more please contact the Editor-in-Chief.

\subsection{TIE checklist for manuscript submissions}

Authors should consider the following points before submitting a new paper. Otherwise the submission would be automatically rejected.

\begin{enumerate}[1)]
	\item New manuscripts cannot exceed 8 pages (3 for letters). Only a very limited overlength (1/2 page at most) is tolerated. Note that usually in the review process the reviewers tend to ask for more explanations, also note that the maximum allowed length is 8 pages on initial/first submission.  Note that in the final page count, the authors' bios and photos should be included.
	\item In order to secure unbiased review process, we ask that none of the authors be identifiable within the manuscript (do NOT include authors' names, their biographies, affiliation, cover letter, signed copyright form, identifying footnotes, acknowledgments, etc.). We believe this helps ensure that the manuscript will receive a more objective and unbiased review. Please remove any trace that can identify author, editor or reviewers' names, institutions, financing sources, IEEE membership grade, etc. Not applicable to Post Conference Papers. Revealing author identity is a ground for rejection and may cause a long delay in processing your manuscript.
	\item If a significant portion of your manuscript was already published at a conference you must use our ``Post Conference Papers'' template. The manuscript must include the previous work in the references section. 
	\item TIE policy doesn't consider surveys, state of the art papers or project reports. Only Guest Editors of a special section (or submissions allowed by the Editorial Board) are invited to submit such kind of manuscript. Our typical papers propose new methods and demonstrate their effectiveness through experimental results in combination with simulation results.
	\item The only file which has to be submitted (uploaded) is the manuscript in PDF format (WORD files are also possible but please be sure that the file was properly converted by the submission system). In order to make it portable you must embed the not standard fonts or avoid them in the PDF file. This is not an easy process, but often all problems are solved when you are printing PDF file from WORD and you will select in printer properties  ``Press Quality'' instead of ``Standard''.
	\item Manuscripts must be in IEEE double column format and all other IEEE guidelines described in this document, so the length of the paper and readability of figures can be evaluated.
	\item The file maximum size cannot exceed 40MB to make it accessible to our tools. Usually you will get that by adjusting the size of the figures. Note that ``EPS'' figures format only is required on the Final Stage.
	\item Your manuscript must be within the scope of IEEE Trans. on Industrial Electronics. If not, we will not be able to provide adequate review.
	\item All cited papers must be referenced within the text of the manuscript. Be sure that the manuscript is up to date. It is expected that a significant portion of references are to recently published papers.
	\item Your manuscript must have abstract correctly written. In the age of electronic publications it is not easy to be noticed (Industrial Electronics Society alone receives over 15,000 conference and journal papers per year). Authors have to do everything possible so the paper will be noticed and read. Therefore, very careful wording should be used in the title, abstract and index terms. Without those a great paper might never be found and read from IEEE Xplore.
	\item Your paper should describe very clearly your accomplishments so other people can understand what is your original contribution and use it. Notice that usually your technical accomplishments will be evaluated based on the number of citations but not based on the number of papers published.
	\item Write clearly your manuscript. Try to keep your manuscript on the proper level from one section to another. It should be easy to understand by well-qualified professionals, but at the same time please avoid describing well-known facts (use proper references instead). Often manuscripts receive negative reviews because reviewers are not able to understand the manuscript and this is authors' (not reviewers') fault. Notice, that if reviewers have difficulties, then other readers will face the same problem and there is no reason to publish the manuscript.
\end{enumerate}

\section{Submission of a Revised Manuscript for Review}

If an editor decides not to accept your manuscript, they may provide you with a decision that allows for reconsideration. If so, open ScholarOne® Manuscripts web \url{http://mc.manuscriptcentral.com/tie-ieee} and find the paper on your submission dashboard. The ``Actions'' column provides you with links to create a revision (for decision types of Minor Revision or Major Revision) or a resubmission (for decision types of Reject with Resubmit).

The checklist above ``TIE checklist for manuscript submissions'' also applies to the revised stage.

In the revision flow, the reviewers tend to ask for more explanations, also note that the maximum allowed length is 8 pages and exceptionally up to 10 pages may be authorized (paying an overlength fee). Note that in the final page count, the authors' bios and photos will be included.

In the resubmission flow, you have to submit a new paper that it's treated as a new submission (8 pages max. as new papers), this means that a new set of Associate editor and reviewers will take care of the new paper. Therefore your paper should be self-contained. No extra notes are necessary.

\section{Submission of a Final Manuscript}

If an editor decides to accept your manuscript, you will receive via email an ``acceptance'' decision. In ScholarOne® Manuscripts, the status of your paper will be ``Awaiting Final Files'' and you will be able to submit the final manuscript.

The checklist above ``TIE checklist for manuscript submissions'' also applies to the final stage, with some exceptions:

\begin{enumerate}[1)]
	\item The {\color{red} \textbf{RED TEXT}} must be included in this stage (author names list, footnote on the first page, optional acknowledgement section and authors' bios and photos). Letters to editor should not include authors' bios and photos.
	\item Once you add footnotes, acknowledgement, author photos and bios, please tailor your paper so it's length does not exceed the 8 pages limit (up to 10 pages with fees) and the last page is not half empty. If your paper after editing at IEEE HQ will run to a new page the editor may remove your photos and/or bios.
	\item Please notice that there are mandatory overlength charges of \$160 per page, up to 10 pages.
	\item This submission must include the final list of references. Any later change will cause prolonged delays in the publishing process.
\end{enumerate}

Upon acceptance, you will receive an email with specific instructions regarding the submission of your final files.  To avoid any delays in publication, please be sure to follow these instructions. Final submissions should include source files of your accepted manuscript, high quality graphic files, and a formatted PDF file. If you have any questions regarding the final submission process, please contact the administrative contact for the journal.

\subsection{Final files:}

\begin{enumerate}[1)]
	\item Double column version of your Manuscript, saved as PDF. This PDF file must be made following all IEEE and TIE guide styles and will be used for preprinting your paper on IEEE Xplore. When printing to PDF from WORD in printer properties, select  ``Press Quality'' instead of ``Standard'' so the file meets Xplore requirements. Name this file as ALL\_1x-TIE-xxxx.pdf. This double column version of your final paper will be published as it is on the IEEE Xplore as forthcoming articles.
	\item Format the complete document (including text, figures and tables) with single-column double-space (using 12 font size). Save the document as TXT\_1x-TIE-xxxx.doc (whether Word file) or TXT\_1x-TIE-xxxx.tex (whether LaTeX project).
	\item Save all your figures in one or several documents. FIG1\_1x-TIE-xxxx.ext. Proper extensions are PS, EPS, TIFF, Microsoft Word, Microsoft PowerPoint, Microsoft Excel, or PDF.
	\item Letters (up to 3 printed pages) should not have biographies or photos of authors.
	\item For regular papers (4 to 8 pages, up to 10 with fees) include color photos of each author with proper format (TIF, JPEG, EPS, PDF, DOC, or PPT) and proper resolution (300 dpi). Name each photo as ``Author\_Name''.``extension''.
	\item For regular papers include biographies of each author (100-150 words). Name each file as Author\_Name.txt.
	\item In text document ABS\_1x-TIE-xxxx.txt include title, authors, and abstract. Thanks to this file, your paper will be broadcasted before printing. Please do not include authors' IEEE membership or status.
	\item In text document MOD\_1x-TIE-xxxx.txt explain recent changes to the manuscript after acceptance. If no changes have been done, this file should include the sentence ``No changes have been applied to the manuscript''.
	\item Please prepare the text document INF\_1x-TIE-xxxx.txt with key information about your manuscript (download the template from webpage):

	\begin{enumerate}[a.]
		\item Document ID.
		\item Document title.
		\item Document subject (select best fitting subject out of 12 subjects):
			\begin{itemize}
			\item High Power Systems Area: 
			\\Multi-Phase Systems (MPS).
			\\Machines and Drives (M\&D).
			\item Medium Power Systems Area:
			\\Single-Phase Electronics (SPE).
			\\Renewable Energy Systems (RES).
			\item Mechatronics Area:
			\\Robotics and Mechatronics (R\&M).
			\\Actuators and Motors (A\&M).
			\item Control Systems Area:
			\\Control and Signal Processing (C\&SP).
			\\Diagnosis and Monitoring (D\&M).
			\item Low Power Systems Area:
			\\Instrumentation and Sensors (I\&S).
			\\Embedded Systems (ES).
			\\Intelligent Systems (IS).
			\\Networking (Net).
			\end{itemize}
		\item Keywords.
		\item Corresponding author:
		\begin{itemize}
			\item Full name, complete address, email, telephone/fax (where proofs of the manuscript can be sent).				 
		\end{itemize}				
		\item Authors' names and IEEE and IES memberships. For each author:
		\begin{itemize}
			\item First and last name of the author, IEEE membership rank (S/M/SM/F), year, IEEE membership number, IES membership (yes/no).
		\end{itemize}
		\item All color figures will be displayed on Xplore for free, but if you want color figures printed in hardcopies you will have to pay for this extra service. Please indicate here if you want some of your figures to be printed in color.
	\end{enumerate}
\end{enumerate}

Pack everything to one zip file 1x-TIE-xxxx.zip and upload into ScholarOne® Manuscripts.

As a summary, the zip file should include the following files:

\begin{enumerate}[1)]
	\item ALL\_1x-TIE-xxxx.pdf - PDF file of paper in IEEE double column format.
	\item TXT\_1x-TIE-xxxx.doc or TXT\_1x-TIE-xxxx.tex - Manuscript in single column double space to extract text of the manuscript for production.
	\item FIG1\_1x-TIE-xxxx.ext - Figure or figures in the acceptable format.
	\item AUTHOR\_NAME.txt - Short biographies of each author (100-150 words).
	\item AUTHOR\_NAME.ext - Color photos of each author in proper graphical format.
	\item ABS\_1x-TIE-xxxx.txt - Title, authors, and abstract. Please do not include authors' IEEE membership or status here.
	\item MOD\_1x-TIE-xxxx.txt - Recent modifications to the manuscript and response to reviewers' comment
	\item INF\_1x-TIE-xxxx.txt - Key information about manuscript including (\url{http://www.ieee-ies.org/images/files/tie/resources/INF_1x-TIE-xxxx.txt}).
\end{enumerate}

Items 4 and 5 should be provided only if applicable (for papers longer than 3 printing pages).

The zip file 1x-TIE-xxxx.zip should be uploaded into ScholarOne® Manuscripts.

You are strongly encouraged to use TeX, LaTeX or Troff programs for the most accurate and efficient transfer of your manuscript, especially for those containing extensive mathematics.

\section{Guidelines for Manuscript Preparation}
A general IEEE style guide is available at \url{http://www.ieee.org/web/publications/authors/transjnl/index.html}.

\subsection{Abbreviations and Acronyms}
Define abbreviations and acronyms the first time they are used in the text, even after they have already been defined in the abstract. Abbreviations such as IEEE, SI, ac, and dc do not have to be defined. Abbreviations that incorporate periods should not have spaces: write ``C.N.R.S.,'' not ``C. N. R. S.'' Do not use abbreviations in the title unless they are unavoidable (for example, ``IEEE'' in the title of this article).

\subsection{Other Recommendations}
Use one space after periods and colons. Hyphenate complex modifiers: ``zero-field-cooled magnetization.'' Avoid dangling participles, such as, ``Using (1), the potential was calculated.'' [It is not clear who or what used (1).] Write instead, ``The potential was calculated by using (1),'' or ``Using (1), we calculated the potential.''

Use a zero before decimal points: ``0.25,'' not ``.25.'' Use ``cm3,'' not ``cc.'' Indicate sample dimensions as ``0.1 cm x 0.2 cm,'' not ``0.1 x 0.2 cm2.'' The abbreviation for ``seconds'' is ``s,'' not ``sec.'' Use ``Wb/m2'' or ``webers per square meter,'' not ``webers/m2.'' When expressing a range of values, write ``7 to 9'' or ``7-9,'' not ``7~9.''.

\section{Maths}

If you are using Word, use either the Microsoft Equation Editor or the MathType add-on (http://www.mathtype.com) for equations in your paper (Insert | Object | Create New | Microsoft Equation or MathType Equation). ``Float over text'' should not be selected.

\subsection{Equations}
Number equations consecutively with equation numbers in parentheses flush with the right margin, as in (1). First use the equation editor to create the equation. Then select the ``Equation'' markup style. Press the tab key and write the equation number in parentheses. To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents. Use parentheses to avoid ambiguities in denominators. Punctuate equations when they are part of a sentence, as in

\begin{align}
\nonumber\mathbf \int_{0}^{{r}_2} & F(r,\varphi) dr \ d\varphi = [\sigma{r}_2 / (2{\mu}_0)]
\\
& \int_{0}^{\infty} exp(-\lambda|{z}_j - {z}_i|){\lambda}^{-1} {J}_1 (\lambda {r}_2) {J}_0 (\lambda {r}_i) d \lambda .
\end{align}

Be sure that the symbols in your equation have been defined before the equation appears or immediately following. Italicize symbols (T might refer to temperature, but T is the unit tesla). Refer to ``(1),'' not ``Eq. (1)'' or ``equation (1),'' except at the beginning of a sentence: ``Equation (1) is ...'' .

\section{Units}

Use either SI (MKS) or CGS as primary units. (SI units are strongly encouraged.) English units may be used as secondary units (in parentheses). This applies to papers in data storage. For example, write ``15 Gb/cm2 (100 Gb/in2).'' An exception is when English units are used as identifiers in trade, such as ``3½-in disk drive.'' Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity in an equation.

\begin{figure}[!t]\centering
	\includegraphics[width=8.5cm]{FIG1.eps}
	\caption{Magnetization as a function of applied field. Note that ``Fig.'' is abbreviated. There is a period after the figure number, followed by two spaces. It is good practice to explain the significance of the figure in the caption.}\label{FIG_1}
\end{figure}

The SI unit for magnetic field strength H is A/m. However, if you wish to use units of T, either refer to magnetic flux density B or magnetic field strength symbolized as \SI{}{\micro0H}. Use the center dot to separate compound units, e.g., ``A·m2.''

\section{Guidelines for Graphics Preparation and Submission}

\subsection{Types of Graphics}
The following list outlines the different types of graphics published in IEEE journals. They are categorized based on their construction, and use of color / shades of gray.

Such figures may include photographs, illustrations, multicolor graphs, and flowcharts.

Figures that are composed of only black lines and shapes. These figures should have no shades or half-tones of gray. Only black and white.

Head and shoulders shots of authors which appear at the end of our papers.  Data charts which are typically black and white, but sometimes include color.

\subsection{Multipart figures}

Figures compiled of more than one sub-figure presented side-by-side, or stacked. If a multipart figure is made up of multiple figure types (one part is lineart, and another is grayscale or color) the figure should meet the stricter guidelines.

\begin{table}[!t]
	\renewcommand{\arraystretch}{1.3}
	\caption{Units for Magnetic Properties}
	\centering
	\label{table_1}
	%\centering
	\resizebox{\columnwidth}{!}{
		\begin{tabular}{l l l}
			\hline\hline \\[-3mm]
			\multicolumn{1}{c}{Symbol} & \multicolumn{1}{c}{Quantity} & \multicolumn{1}{c}{\pbox{20cm}{Conversion from Gaussian and \\ \hphantom{spaces} CGS EMU to $ SI^{a} $ }}  \\[1.6ex] \hline
			$ \Phi $  & magnetic flux & $ 1Mx \rightarrow 10^8 Wb = 10^8 V \cdot s $ \\
			\pbox{20cm}{$ \emph{B} $ \\\hphantom{1}} & \pbox{20cm}{magnetic flux density, \\ \hphantom{1} magnetic induction} &  \pbox{20cm}{$ 1G \rightarrow 10^4 T = 10^4 Wb/m^2 $ \\ \hphantom{1}} \\ 
			$ \emph{H} $ & magnetic field strength & $ 1Oe \rightarrow 10^3/(4\pi)A/m $ \\
			\pbox{20cm}{$ \emph{m} $ \\ \hphantom{1}} & \pbox{20cm}{magnetic moment \\ \hphantom{1}} & \pbox{20cm}{$ 1 erg/G = 1 emu $ \\ \hphantom{1} $ \rightarrow 10^3 A \cdot m^2 = 10^3 J/T $ } \\ 
			\pbox{20cm}{$ \emph{M} $ \\ \hphantom{1}} & \pbox{20cm}{magnetization \\ \hphantom{1}} & \pbox{20cm}{$ 1 erg/(G \cdot cm^3) = 1 emu/cm^3 $ \\ \hphantom{1} $ \rightarrow 10^3 A/m $ } \\ 
			$ 4\pi\emph{M} $ & magnetization & $ 1G \rightarrow 10^3/(4\pi)A/m $ \\
			$ \sigma $ & specific magnetization & $ 1 erg/(G \cdot g) = 1 emu/g \rightarrow 1 A \cdot m^2/kg $ \\
			\pbox{20cm}{$ \emph{j} $ \\ \hphantom{1}} & \pbox{20cm}{magnetic dipole \\ \hphantom{1} moment } & \pbox{20cm}{$ 1 erg/G = 1 emu $ \\ \hphantom{1} $ \rightarrow 4\pi \times 10^{10} Wb \cdot m $ } \\ [1.4ex]
			\pbox{20cm}{$ \emph{J} $ \\ \hphantom{1}} & \pbox{20cm}{magnetic polarization \\ \hphantom{1}} & \pbox{20cm}{$ 1 erg/(G \cdot cm^3) = 1 emu/cm^3 $ \\ \hphantom{1} $ \rightarrow 4\pi \times 10^{4} T $ } \\ 
			$ \chi \ \kappa $ & susceptibility & $ 1 \rightarrow 4\pi $ \\ 
			$ \chi  $ & mass susceptibility & $ 1 cm^3/g \rightarrow 4\pi \times 10^{3} m^3/kg $ \\ 
			\pbox{20cm}{$ \mu $ \\ \hphantom{1}} & \pbox{20cm}{permeability \\ \hphantom{1}} & \pbox{20cm}{$ 1 \rightarrow 4\pi \times 10^{7} H/m $ \\ \hphantom{1} $ =4\pi \times 10^{7} Wb/(A \cdot m) $ } \\ 
			$ \mu_r $ & relative permeability & $ \mu \rightarrow \mu_r $ \\ 
			$ \omega, \emph{W} $ & energy density & $ 1 erg/cm^3 \rightarrow 10^1 J/m^3 $ \\ 
			$ \emph{N}, \emph{D} $ & demagnetizing factor & $ 1 \rightarrow 1/(4\pi) $ \\ [1.4ex]
			\hline\hline
		\end{tabular}
	}
\end{table}

\subsection{File Formats For Graphics}

Format and save your graphics using a suitable graphics processing program that will allow you to create the images as PostScript (PS), Encapsulated PostScript (.EPS), Tagged Image File Format (.TIFF), Portable Document Format (.PDF), or Portable Network Graphics (.PNG) sizes them, and adjusts the resolution settings. If you created your source files in one of the following programs you will be able to submit the graphics without converting to a PS, EPS, TIFF, PDF, or PNG file: Microsoft Word, Microsoft PowerPoint, or Microsoft Excel. Though it is not required, it is recommended that these files be saved in PDF format rather than DOC, XLS, or PPT. Doing so will protect your figures from common font and arrow stroke issues that occur when working on the files across multiple platforms. When submitting your final paper, your graphics should all be submitted individually in one of these formats along with the manuscript.

\subsection{Sizing of Graphics}

Most charts, graphs, and tables are one column wide (3.5 inches / 88 millimeters / 21 picas) or page wide (7.16 inches / 181 millimeters / 43 picas). The maximum depth a graphic can be is 8.5 inches (216 millimeters / 54 picas). When choosing the depth of a graphic, please allow space for a caption. Figures can be sized between column and page widths if the author chooses, however it is recommended that figures are not sized less than column width unless when necessary.

There is currently one publication with column measurements that don't coincide with those listed above. PROCEEDINGS OF THE IEEE has a column measurement of 3.25 inches (82.5 millimeters / 19.5 picas).

The final printed size of author photographs is exactly
1 inch wide by 1.25 inches tall (25.4 millimeters x 31.75 millimeters / 6 picas x 7.5 picas). Author photos printed in editorials measure 1.59 inches wide by 2 inches tall (40 millimeters  x 50 millimeters  / 9.5 picas x 12 picas).

\subsection{Resolution}

The proper resolution of your figures will depend on the type of figure it is as defined in the ``Types of Figures'' section. Author photographs, color, and grayscale figures should be at least 300dpi. Lineart, including tables should be a minimum of 600dpi.

\subsection{Vector Art}

While IEEE does accept, and even recommends that authors submit artwork in vector format, it is our policy is to rasterize all figures for publication. This is done in order to preserve the figures' integrity across multiple computer platforms.

\subsection{Color Space}

The term color space refers to the entire sum of colors that can be represented within the said medium. For our purposes, the three main color spaces are Grayscale, RGB (red/green/blue) and CMYK (cyan/magenta/yellow/black). RGB is generally used with on-screen graphics, whereas CMYK is used for printing purposes.

All color figures should be generated in RGB or CMYK color space. Grayscale images should be submitted in Grayscale color space. Line art may be provided in grayscale OR bitmap colorspace. Note that ``bitmap colorspace'' and ``bitmap file format'' are not the same thing. When bitmap color space is selected, .TIF/.TIFF is the recommended file format.

\subsection{Accepted Fonts Within Figures}

When preparing your graphics IEEE suggests that you use of one of the following Open Type fonts: Times New Roman, Helvetica, Arial, Cambria, and Symbol. If you are supplying EPS, PS, or PDF files all fonts must be embedded. Some fonts may only be native to your operating system; without the fonts embedded, parts of the graphic may be distorted or missing.

A safe option when finalizing your figures is to strip out the fonts before you save the files, creating ``outline'' type. This converts fonts to artwork what will appear uniformly on any screen.

\subsection{Using Labels Within Figures}

\begin{enumerate}
	\item Figure Axis labels\\
	Figure axis labels are often a source of confusion. Use words rather than symbols. As an example, write the quantity``Magnetization,'' or ``Magnetization M,'' not just ``M.'' Put units in parentheses. Do not label axes only with units. As in \mbox{Fig. \ref{FIG_1}}, for example, write ``Magnetization (A/m)'' or ``Magnetization (A m1),'' not just ``A/m.'' Do not label axes with a ratio of quantities and units. For example, write ``Temperature (K),'' not ``Temperature/K.''. Multipliers can be especially confusing. Write ``Magnetization (kA/m)'' or ``Magnetization (103 A/m).'' Do not write ``Magnetization (A/m) x 1000'' because the reader would not know whether the top axis label in \mbox{Fig. \ref{FIG_1}} meant 16000 A/m or 0.016 A/m. Figure labels should be legible, approximately 8 to 10 point type.	
	\item Subfigure Labels in Multipart Figures and Tables\\
	Multipart figures should be combined and labeled before final submission. Labels should appear centered below each subfigure in 8 point Times New Roman font in the format of (a) (b) (c). 	
\end{enumerate}

\subsection{Referencing a Figure or Table Within Your Paper}
When referencing your figures and tables within your paper, use the abbreviation ``Fig.'' even at the beginning of a sentence. Do not abbreviate ``Table.'' Tables should be numbered with Roman Numerals.

\subsection{Checking Your Figures: The IEEE Graphics Checker}
The IEEE Graphics Checker Tool enables authors to pre-screen their graphics for compliance with IEEE Transactions and Journals standards before submission. The online tool, located at \url{http://graphicsqc.ieee.org/}, allows authors to upload their graphics in order to check that each file is the correct file format, resolution, size and colorspace; that no fonts are missing or corrupt; that figures are not compiled in layers or have transparency, and that they are named according to the IEEE Transactions and Journals naming convention. At the end of this automated process, authors are provided with a detailed report on each graphic within the web applet, as well as by email.

For more information on using the Graphics Checker Tool or any other graphics related topic, contact the IEEE Graphics Help Desk by e-mail at graphics@ieee.org.

\subsection{Submitting Your Graphics}
Because IEEE will do the final formatting of your paper, you do not need to position figures and tables at the top and bottom of each column. In fact, all figures, figure captions, and tables can be placed at the end of your paper. In addition to, or even in lieu of submitting figures within your final manuscript, figures should be submitted individually, separate from the manuscript in one of the file formats listed above in section VI-J. Place figure captions below the figures; place table titles above the tables. Please do not include captions as part of the figures, or put them in ``text boxes'' linked to the figures. Also, do not place borders around the outside of your figures.

\subsection{Color Processing / Printing in IEEE Journals}
All IEEE Transactions, Journals, and Letters allow an author to publish color figures on IEEE Xplore® at no charge, and automatically convert them to grayscale for print versions. In most journals, figures and tables may alternatively be printed in color if an author chooses to do so. Please note that this service comes at an extra expense to the author. If you intend to have print color graphics, include a note with your final paper indicating which figures or tables you would like to be handled that way, and stating that you are willing to pay the additional fee.

\section{Conclusion}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions.

\section*{Appendix}

Appendixes, if needed, appear before the acknowledgment.

{\color{red}
\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in American English out an ``e'' after the ``g.'' Use the singular heading even if you have many acknowledgments. Avoid expressions such as ``One of us (S.B.A.) would like to thank ... .'' Instead, write ``F. A. Author thanks ... .'' In most cases, sponsor and financial support acknowledgments are placed in the unnumbered footnote on the first page, not here.
}

\section*{References and Footnotes}

\subsection{References}
References need to be cited in text. Put the number on the line, in square brackets inside the punctuation.  Multiple references are each numbered with separate brackets. When citing a section in a book, please give the relevant page numbers. In text, refer simply to the reference number. Do not use ``Ref.'' or ``reference'' except at the beginning of a sentence: ``Reference [\#] shows ... .'' Please do not use automatic endnotes in Word, rather, type the reference list at the end of the paper using the ``References'' style.

Reference numbers are set flush left and form a column of their own, hanging out beyond the body of the reference. The reference numbers are on the line, enclosed in square brackets. In all references, the given name of the author or editor is abbreviated to the initial only and precedes the last name. Use them all; use et al. exceptionally if more than 6 author names were listed. Use commas around Jr., Sr., and III in names. Abbreviate conference titles \cite{inproceedings1}.  When citing journals \cite{article1, article2}, provide the issue number, page range, volume number, DOI, year, and/or month if available. When referencing a patent \cite{patent1}, provide the day and the month of issue, or application. References may not include all information; please obtain and include relevant information. Do not combine references. There must be only one reference with each number. If there is a URL included with the print reference, it can be included at the end of the reference \cite{onlinebook1}.

Authors are encouraged to include the DOI number for each reference. It's the most important part of the reference. The DOI is like a digital fingerprint and it's used to identify the article without mistakes.

Other than books \cite{inbook1, book1}, capitalize only the first word in a paper title, except for proper nouns and element symbols. For papers published in translation journals, please give the English citation first, followed by the original foreign-language citation See the end of this document for formats and examples of common references. For a complete discussion of references and their formats, see ``The IEEE Style Manual,'' available as a PDF link off the Author Digital Toolbox main page.

\subsection{Footnotes}
Number footnotes separately in superscripts (Insert | Footnote).\footnote{It is recommended that footnotes be avoided (except for the unnumbered footnote with the receipt date on the first page). Instead, try to integrate the footnote information into the text.}  Place the actual footnote at the bottom of the column in which it is cited; do not put footnotes in the reference list (endnotes). Use letters for table footnotes  (see \mbox{Table \ref{table_1}}).

\section{Editorial Policy}

Do not submit a reworked version of a paper you have submitted or published elsewhere. Do not publish ``preliminary'' data or results. The submitting author is responsible for obtaining agreement of all coauthors and any consent required from sponsors before submitting a paper.

The IEEE Transactions and Journals Department does not publish conference records or proceedings. The department  does publish papers related to conferences that have been recommended for publication on the basis of peer review. As a matter of convenience and service to the technical community, these topical papers are typically collected and published in one special issue of most transactions publications.

At least two reviews are required for every paper submitted. Indecipherable English is a valid reason for rejection. There is a service available that will help you improve your English for a fee, and the link to that service can be found at \url{http://www.ieee.org/web/publications/authors/transjnl/index.html}.

Authors of rejected papers may revise and resubmit them as regular papers, whereupon they will be reviewed by two new referees.

\section{Publication Principles}

The two types of contents of that are published are; 1) peer-reviewed and 2) archival. The Transactions and Journals Department publishes scholarly articles of archival value as well as tutorial expositions and critical reviews of classical subjects and topics of current interest.
Authors should consider the following points:

\begin{enumerate}[1)]
\item Technical papers submitted for publication must advance the state of knowledge and must cite relevant prior work.
\item The length of a submitted paper should be commensurate with the importance, or appropriate to the complexity, of the work. For example, an obvious extension of previously published work might not be appropriate for publication or might be adequately treated in just a few pages.
\item Authors must convince both peer reviewers and the editors of the scientific and technical merit of a paper; the standards of proof are higher when extraordinary or unexpected results are reported.
\item Because replication is required for scientific progress, papers submitted for publication must provide sufficient information to allow readers to perform similar experiments or calculations and use the reported results. Although not everything need be disclosed, a paper must contain new, useable, and fully described information. For example, a specimen's chemical composition need not be reported if the main purpose of a paper is to introduce a new measurement technique. Authors should expect to be challenged by reviewers if the results are not supported by adequate data and critical details.
\item Papers that describe ongoing work or announce the latest technical achievement, which are suitable for presentation at a professional conference, may not be appropriate for publication.
\end{enumerate}

% References

\bibliographystyle{Bibliography/IEEEtranTIE}
\bibliography{Bibliography/IEEEabrv,Bibliography/BIB_1x-TIE-2xxx}\ %IEEEabrv instead of IEEEfull

{\color{red}

\vspace{-1cm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photo-men.eps}}]
{First A. Author1} and the other authors may include biographies at the end of regular papers. The first paragraph may contain a place and/or date of birth (list place, then date). Next, the author's educational background is listed. The degrees should be listed with type of degree in what field, which institution, city, state or country, and year degree was earned. The author's major field of study should be lower-cased.

The second paragraph uses the pronoun of the person (he or she) and not the author's last name. It lists military and work experience, including summer and fellowship jobs. Job titles are capitalized. The current job must have a location; previous positions may be listed without one. Information concerning previous publications may be included.

The third paragraph begins with the author's title and last name (e.g., Dr. Smith, Prof. Jones, Mr. Kajor, Ms. Hunter). List any memberships in professional societies other than the IEEE. Finally, list any awards and work for IEEE committees and publications. If a photograph is provided, the biography will be indented around it. The photograph is placed at the top left of the biography. Personal hobbies will be deleted from the biography.
\end{IEEEbiography}

\vspace{-2cm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photo-men.eps}}]
{Second B. Author2} (M'12) was born in City, Country. He received the M. degree in electrical engineering from University of City, Country in 2012.

The second paragraph uses the pronoun of the person (he or she) and not the author's last name. It lists military and work experience, including similar information to the previous author, including military, work experience, and other jobs. Job titles are capitalized. The current job must have a location; previous positions may be listed without one. Information concerning previous publications may be included.

The third paragraph begins with the author's title and last name (e.g., Dr. Smith, Prof. Jones, Mr. Kajor, Ms. Hunter), including similar information to the previous author, including the list of any awards and work for IEEE committees and publications. The photograph is placed at the top left of the biography. Personal hobbies will be deleted from the 
biography.\\ 
\end{IEEEbiography}

\vspace{-2cm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photo-men.eps}}]
{Third C. Author3} (M'99-SM'04-F'09) was born in City, Country. He received the M. and SM. and F. degrees in electrical engineering from University of City, Country in 1999, 2004 and 2009 respectively.

The second paragraph uses the pronoun of the person (he or she) and not the author's last name. It lists military and work experience, including similar information to the previous author, including military, work experience, and other jobs.

The third paragraph begins with the author's title and last name (e.g., Dr. Smith, Prof. Jones, Mr. Kajor, Ms. Hunter), including similar information to the previous author, including the list of any awards and work for IEEE committees and publications. The photograph is placed at the top left of the biography. Personal hobbies will be deleted from the biography.
\\ \\ 
\end{IEEEbiography}

}

\end{document}

### 2018-08-06 test/main.tex
20180806

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{subcaption}
\usepackage[sorting=none]{biblatex}
\addbibresource{biblio.bib}
\usepackage{amsmath}
\usepackage{esint}
\usepackage{systeme}
\usepackage{algorithm2e}
\usepackage{blindtext}
\usepackage{subcaption}
\usepackage{minted}
\usepackage{stackengine}
\usepackage[a4paper,margin=0.5in]{geometry}
\title{\textbf{Photovoltaic System Reconfiguration strategy for mismatch condition}}%\\
           %\emph{Application to mixed typed of data in lung Adenocarcinoma subtype discovery}}
\date{July 2018}
\author{\textbf{Dafang Zhao}\\Nara Institute of Science and Technology, Depenadble System Lab}

\begin{document}
\maketitle

\section{Introduction}
\\As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human. Photovolatic (PV) energy recived signifcant attention since it has unlimited energy and easy to be scaled up.

\section{Related work}
\subsection{Lung adenocarcinoma papers}

Here, we will mainly discuss 3 previous works about LUAD and some work on Maximum Likelihood clustering techniques.
Starting with the work of Hayes et al.\cite{hayes}, whom put in evidence from DNA microarrays data, a total cohort of 231 LUAD patients and 2,553 reliable genes, the presence of 3 clusters.
These clusters were found using consensus clustering\cite{cons}, the genes used came from centroids comparison and gene enrichment analysis.
Although this study focused on survival rates, which is not our case, it managed to find strong evidences concerning the existence of three distinct LUAD subtypes named Bronchoid, Magnoid and Squamoid having different gene expression profiles and clinical relevance. \cite{hayes} also managed to identify sets of genes strongly related to each found subtypes, these genes will be taken in consideration in our study.
The second important study is Wilkerson et al.\cite{wilk}, aimed to have a better understanding of the LUAD molecular pathogenesis in order to find better targets for chemo-treatments.
The study focused on DNA alteration, DNA methylation and mutation occuring in LUAD.
They also used cohort wise centroids and ConsensusClusterPlus\cite{consensusPlus} for a total of 462 patients (GSE data set).
They confirmed the clinical differences between the molecular subtypes, showing that the survival rate and therapy response was differing according to each subtype.
The last study we will discuss is the one from TCGA\cite{TCGA}.
This study mainly focused on the relation between the morphological classification and the gene expression profiles, renaming the 3 known subtypes as Proximal-Inflammatory (PI, former Squamoid), Proximal-proliferative (PP, former Magnoid)and Terminal Respiratory Unit (TRU, forner Bronchoid).
They used RNA-seq data as well, data that we will use in our study (TCGA data set), 230 patients and 22k+ genes.
They used RNA-seq data to study mutations in LUAD and they compared their results of subtype detection with \cite{wilk}, finding high correlation between respective clusters.

\subsection{Hierarchical Maximum Likelihood algorithms}

We want to present here some existing methods, implementing a maximum likelihood approach. Note that our desire is to implement a fully Bayesian approach, which differs slightly, furthermore we have to deal with different categories of data.
Castro et al.\cite{castro}, described two different algorithms for clustering purpose using maximum likelihood estimation and MCMC chains. The first algorithm, called Agglomerative Likelihood Tree (ALT), looks for the Maximum Likelihood Tree (MLT) after computing a measure of similarity based on maximum likelihood estimates paiwise.
The MLT obtained by this algorithm will be binary structured.
The second algorithm, called MLT estimator, takes a more global approach.
Searching directly for the MLT in the tree's forest, it allows non-binary association in trees and smartly uses the ALT algorithm to reduce the space of research. 
Both models aren't adapted to mixed type data, which means a generalisation should be implemented.
Sharma et al.\cite{sharma}, implemented a new algorithm for clustering purpose (called HML), their algorithm is able to deal with the Small Sample Size problem, occurring when the covariance matrix in small sample size and high dimension (which is the case with gene expression profiles), using a Singular-Value Decomposition (SVD) method.
Although HML gave promising results, the SVD approach should be trade out in order to deal with categorical data, applying Multiple Factor Analysis (MFA)\cite{pages} decomposition method for instance.
We also can cite an interesting paper concerning hierarchical clustering algorithm by D.Müllner\cite{mullner}, which served as inspiration for our own algorithm creation.

\subsection{Bayesian inference related papers}

We will see later that our method considers the Bayes factor to cluster our data or appreciate a given clustering solution, our reference in that regard is the paper of E.Raftery\cite{raftery}, giving a comprehensive approach to it.
The book \emph{Pattern Recognition And Machine Learning}\cite{bishop}, provided us useful insights to Bayesian inference and related techniques.
Finally, an analytically tractable solution in our Gaussian marginal likelihood with conjugate prior theoritical model, we used an unpublished paper from Kevin P.Murphy\cite{murphy}.

\section{Methods}
\subsection{Data pre-processing}\label{sec:preprocess}

Because we are working with 2 different data sets, it is important to take care of the gene annotation. Indeed, the data set GSE\cite{shedden} is annotated with probe names where the TCGA\cite{TCGA} is annotated with gene symbols (HGNC).
The first step is to use different annotation tables and databases available on R (AnnotationDbi)\cite{annot}, and from the sources of the data sets in order to obtain comparable data sets.
After manipulation of different gene annotations, a gene set in TCGA's data were discarded due to the absence of correspondence in the databases (additional file 1). We also only kept the genes that are in common between GSE and TCGA data sets, discarding the others (Additional file 2) for comparison purpose.
Concerning clinical data, The TCGA data set gives us access to a lot of clinical information, but in order to keep a relevant comparing ground with GSE and also to simplify the study we chose to keep only 4 clinical variables (Sex, Age, Race, Smoking history).
Clinical data were arranged by convenience, the "Age" variable was divided in 8 categories according to the distribution frequencies, and "smoking history" was changed to match its description from the GDC data portal concerning clinical data:
\begin{enumerate}
    \item : Lifelong non-smoker
    \item : Current smoker
    \item : Current reformed smoker $>$ 15 years
    \item : Current reformed smoker $\leq$ 15 years
    \item : Current reformed smoker duration unknown
    \item : Smoker at diagnosis
    \item : Unknown
\end{enumerate}

Because the available clinical data for GSE does not make any distinction between categories 3 and 4, we considered them as category 5, the 7\textsuperscript{th} category was considered as missing value (NA under R software).

Among the genes between our two data sets, we decided to explore different gene sets, and study their ability to differentiate molecular sub-types. Indeed, if we can show satisfying results using only a relevant subset of genes it could simplify analyses and diagnosis of new patients.
Hence we considered two gene sets, one containing the genes described in \cite{hayes} but also the centroids of \cite{wilk} and the 100 most mutated genes in LUAD (GDC data portal) which we called "predictors" gene set. The second one is based on a deferentially expressed genes analysis (DEG) using the R package \emph{DEGseq}.
As we had access to the raw count of transcripts from RNA-seq for TCGA, we were able to perform a DEG analysis.
\begin{figure}[th]
    \centering
    \begin{subfigure}[t]{0.20\textwidth}
        \centering
        \includegraphics[height=1.6in]{img/SampleS_box.png}
        \caption{Box plots of diseased patients and healthy ones}
        \label{fig:my_label}
    \end{subfigure}
    \begin{subfigure}[t]{0.20\textwidth}
        \centering
        \includegraphics[height=1.6in]{img/result.png}
        \caption{MA-plot of diseased patients and healthy ones (controls)\\
        red dots represent DEG}
        \label{fig:my_label}
    \end{subfigure}
    \caption{DEG analysis using DEGseq package}
    \label{fig:my_label}
\end{figure}
We also compared each sub-type to our controls, taking the sub-type classification given by the TCGA study\cite{TCGA}, see additional file 3.
Each sub-type showed more than 17000 DEG, but in order to stay on the same scale as the predictors gene set and also to keep the ability to differentiate between at least 3 sub-types, we kept only the DEG unique to each sub-type, obtaining a 2000+ genes gene set with only one gene in common with the predictors gene set, which was discarded.
Finally, and for the following analyses, we split our two data sets into four distinct ones:
\begin{table}[!]
    \centering
    \includegraphics[scale=0.4]{img/adenodatasets.png}
    \caption{Lung Adenocarcinoma data sets}
    \label{tab:adeDt}
\end{table}
In table~\ref{tab:adeDt}, only the "predictors" gene set is kept for the GSE data set because the DEG analysis was performed on the raw counts of the TCGA data set.
Because of some differences in the annotations, the presence of alias in HGNC annotation and absence of some of them in the databases used, the "predictors" gene set gave two possibilities for the TCGA data set, "AsGSE" has exactly the same genes as in GSE, but "diffGSE" gets about a hundred genes different with the GSE data set.

\subsection{Hierarchical clustering}

Clustering analysis has been and still remains an important tool in machine learning oriented research. Clustering methods are not statistical analyses, indeed, the simple fact of clustering
does not grant a final and unique solution. Actually, clustering data randomly will just regroup these data into clusters, but it does not mean that these clusters will have a real meaning, hence our desire to provide here a method assessing this problem and providing statistical significance to clustering results.
Finding the number of clusters (K) that reflects the true classes in the data is an important challenge and can determine the quality of the results. 
Concerning health care purposes, the quality and accuracy of the result represents a great deal, a life saving one.
Indeed, the ability to rightly find cancer sub-types allow researchers and physicians to better adapt to each patient particular case, and find new efficient drugs.
Thus, we developed a Bayesian model comparison method for this purpose.
Our method will be detailed later on, for now lets discuss quickly a certain type of clustering algorithm, and the kind of data we worked on.
The data sets we wish to cluster are comprised of different types of data, indeed, the gene expression profiles (GEP) are of numerical continuous type, where clinical knowledge is of categorical type. By categorical type, we mean variables taking a certain range of values (categories) but lacking a mathematical meaning, having or not an order.
Numerical data can be discrete or continuous, here no problem to understand the continuous form of GEP, on the other hand, categorical data types need some explanations.
There are several types of categorical data in our definition of it:
\begin{itemize}
    \item Binary: A variable which can take only two possible values, i.e: Gender (M/F)
    \item Nominal: Generalisation of the binary case for K categories, i.e: Race (Australoid/Capoid/Caucasoid/Mongoloid/Negroid)
    \item Ordinal: As nominal but with an order, i.e: Age
    \item Interval: similar to ordinal but considering intervals between the values, i.e: also Age
\end{itemize}
It is important to differentiate these data types because the mathematical tools we apply to them are different, their treatment will also be different.
Numerical variables, in our case, will be normalised (log2, $\frac{x-\mu}{\sigma}$...), and categorical ones will be conveniently transformed from characters (MALE/FEMALE), to numbers (1/2), even though it is not absolutely necessary.
When it will come to the Bayesian treatment, numerical variables will be assumed to follow Gaussian distributions (close to a Gaussian distribution when we look at the histogram), and categorical ones multinomial distributions, which change completely their handling.
Our focus in this study is the hierarchical approach of clustering, thus, we give here further information about this popular clustering method with R.
\begin{figure}
    \centering
    \includegraphics[scale=0.2]{img/HC.png}
    \caption{Example of Hierarchical Clustering with R.}
    \label{fig:HC}
\end{figure}
Hierarchical clustering algorithms are a well documented type of algorithm and rely on similarity/dissimilarity matrix produced by distance metrics in order to pair in an agglomerative manner each samples of a given data set.
Furthermore, the hierarchical scheme get along nicely with the Bayesian model comparison method.
A very simple distance metric example would be the Euclidean distance, defined as:\\
$$d(i,j)\ =\ \sqrt{\sum_{d=1}^D(j_d-i_d)^2}$$

where i and j are two samples of a data set of dimension D.
The choice of the metric is primordial and has to reflect the data types and needs of the user, in our case, and because we have both numerical and categorical types, we decided to use the Gower distance:\\
$d(i,j)\ =\ \frac{1}{N}\sum_{n=1}^Nd_{ij}^{(d)}$\\

Where i and j two samples, N the total number of samples in the data set.\\
$d_{ij}^{(d)}$ is given by:\\
$$d_{ij}^{(d)}\ =\ \frac{|x_{id}-x_{jd}|}{R_d}$$

Where $x_{id}\ \text{and}\ x_{jd}$ are the value of the samples i and j for the variable $d$.
$R_d$ is the range for the variable $d$, dividing by the range avoid to give more weight to variables with greater range.
The Gower distance is able to compute the distance between pairs of samples even with variables of different types inside the data set, the results obtained using this metric will act like a benchmark for our own metric.
Under R environment, the package "Cluster"\cite{maechler} is the perfect tool in association with the base package "stat", for hierarchical clustering.
An important part of a hierarchical clustering algorithm is the linkage method, here we will quickly introduce the Ward and Complete linkage methods.
The two samples having the shortest distance separating them are linked together, the definition of this distance is what differentiate the linkage methods.\\
\emph{Complete linkage:}\\
If we consider $A$ and $B$, two different cluster sets, then:
\begin{equation}\label{equ:comp}
    D(A,B)\ =\ \smash{\displaystyle\max_{a\in A,b\in B}}d(a,b)
\end{equation}
This linkage simply takes the two samples in different clusters which share the maximum distance and bind the two respective clusters, so it uses a dissimilarity matrix.\\
\emph{Ward linkage:}\\
The Ward's method looks for minimising the within-cluster variance, so at each step, it merge two clusters which minimise the overall increase in within-cluster variance:
\begin{equation}\label{equ:ward}
    D(A,B)\ =\ \sqrt{\frac{2|A||B|}{|A|+|B|}\cdot \|\overrightarrow{c_A}\ -\ \overrightarrow{c_B}\|^2}
\end{equation}
With $\overrightarrow{c_K}$ is the centroid vector (euclidean space) of the cluster $K$.
As shown in figure~\ref{fig:HC}, the result of a Hierarchical clustering algorithm is a dendogram (tree), which can be considered as an ensemble of possible clustering solutions.
Indeed, if we choose to "cut" the "tree" at a certain height, then we will get the corresponding list of cluster attribution for each sample. Cutting at a high height will give fewer clusters which leads to reduce the sensitivity threshold, maybe regrouping quite different samples together.On the contrary, cutting at low height will give more clusters, threatening the result with over-fitting and considerably complicating the interpretation. So, how to cut that tree in order to have a meaningful number of clusters, combining good sample proximity and simple interpretation?
Some tools like AIC or BIC\cite{burnham} exists for this purpose, but they use maximum likelihood estimation and not likelihood marginalisation over given parameters. Furthermore, we wish to apply it to the biological field and deal with both numerical and categorical types of data as well as the common case of missing values.\\
In the further sections, we will first have a short glance at Bayesian inference, then we will give the general framework of it applied to model comparison and finally show how it fits into our clustering method.

\subsection{Bayesian Inference}

The high popularity of Bayesian inference can be explained by its flexibility and performances in statistical computing and model description. its ability to account for an a priori knowledge, and for uncertainty over statistical parameters, makes the Bayesian approach widely appreciated and implemented into constantly improving tools.
Furthermore, the overall accessibility of Bayesian tools, regarding OS or software platforms (R, Python, Matlab...), is a strong argument in favour of its usage.
This paragraph is heavily inspired by the work of Christopher M.Bishop\cite{bishop}.
Bayesian inference is often opposed to the frequentist approach of statistics, indeed, the main difference resides in the statistical reasoning.
The Bayesian approach considers that even if a true parameter value exists i.e: a mean, such parameter can be given taking into account the uncertainty on its true value, so as a distribution.
The frequentist framework stipulates that, knowing that a true single value of a given parameter exists for the population, it is wrong to assign a probability distribution to it, and relies on parameter estimates from collected population samples.
Thus, Bayesian statistics "play" with probability distributions where the frequentist approach only consider the estimated single value given by the available data.
From this, we can easily understand why Bayesian inference is favoured, because in real world problems, the cases with few available data and/or high amount of noise are common, hence increasing the uncertainty on the parameters, giving the advantage to the Bayesian vision.
So lets discuss further the Bayesian approach on statistics.\\
First of all, Bayesian inference relies on the famous Bayes' theorem, which is given by:
\begin{equation}
    P(A|B)\ =\ \frac{P(B|A)P(A)}{P(B)}
\end{equation}
Where:
\begin{itemize}
    \item $P(A|B)$ is the conditional probability, probability of the event A occurring knowing B to be true.
    \item $P(B|A)$ is the other way around.
    \item $P(A)\ \text{and}\ P(B)$ respectively the probabilities of observing the event A and B, also known as the marginal probabilities.
\end{itemize}
In Bayesian interpretation, the first conditional probability is known as \emph{posterior}, so the updated probability, the second conditional is known as the \emph{Likelihood function} and finally $P(A)$ is, here,the a priori knowledge (prior) on the model.
$P(B)$ would be the normalising factor of the equation, insuring that the probability lies between 0 and 1.
This theorem comes from the product and symmetry rules of probability, stipulated as following:
Product rule:\\
$$P(A,B)\ =\ P(B|A)P(A)$$

Symmetry rule:\\
$$P(B,A)\ =\ P(A|B)P(B)$$

Furthermore, from the sum rule, the denominator (normalising constant) can be expressed:\\
$$P(B)\ =\ \sum_AP(A|B)P(B)$$

Detailing the likelihood function, if we consider a Gaussian distributed random variable $X$ (\emph{Independent and identically distributed}) of $N$ samples with parameters $\mu,\ \sigma^2$, respectively the mean and the variance, it gives:
\begin{equation}
    P(X,\mu,\sigma^2)\ =\ \prod_{n=1}^N\mathcal{N}(x_n|\mu,\sigma^2)
    \label{equ:NormalLikelihood}
\end{equation}
Which correspond, in this case, to the chained application of the joint probability, equal to the product of the marginal probabilities of each events.
In order to have a fully Bayesian approach, we also need to attribute a probability distribution to the parameters, giving them hyper-parameters for their respective distributions.\\
Now that we have established the basics of Bayesian inference, we need to also give some details on a nice application of this kind of statistics, which is the model comparison.

\subsection{Model comparison using the Bayesian framework}

We saw in the previous paragraph how one can determine the posterior distribution using a Bayesian treatment, given data, parameters and priors.
Now we are interested in the comparison between two different models (clustering solutions in our case), on the same data and using the same priors (the parameters varying according to each model), using the Bayesian method, the goal being determining which one of the two considered models fits the data the better.
In order to obtain such comparison, the Bayes factor (BF) provides a really straightforward tool\cite{raftery}, involving easy interpretation, and procuring all the flexibility of the Bayesian inference framework.
The idea is simple, compare two cluster solutions and use the Bayes factor in order to favour a model over another, hence, assisting the decision making for clustering methods where the choice of the number of clusters to keep is always subject to debates.
So if we consider a data set $Dt$, the posterior distribution of a model $M_K$ is given by the Bayes' theorem as following:
\begin{equation}
    P(M_K|Dt)\ \propto\ P(Dt|M_K)P(M_K) 
\end{equation}
Where:
\begin{itemize}
    \item $P(M_K|Dt)$ is the posterior probability of the model $M_K$
    \item $P(Dt|M_K)$ is the likelihood of the model $M_K$
    \item $P(M_K)$ the prior probability
    \item For convenience the normalising factor is not written here.
\end{itemize}
Then, if we wish to compare two models $M_1\ \text{and}\ M_2$, we simply look at the ratio of posteriors:
\begin{equation}
    \frac{P(M_1|Dt)}{P(M_2|Dt)}\ =\ \frac{P(Dt|M_1)P(M_1)}{P(Dt|M_2)P(M_2)}
    \label{equ:BayesRatio}
\end{equation}
Thus, the Bayes factor between the model 1 and 2 is defined as:
\begin{equation}
    B_{12}\ =\ \frac{P(Dt|M_1)}{P(Dt|M_2)}
\end{equation}
Which basically can be described as a likelihood ratio when all parameters are known.
Or, as it is nicely put in \cite{raftery}:\\
$$Posterior\ odds\ =\ Bayes\ Factor\ \cdot\ Prior\ odds$$

Now that we defined how to calculate the Bayes factor, we need to precise the calculation of the likelihood functions which require marginalisation over the model parameters.
Following the Bayesian treatment, the likelihood densities are obtained by integrating over the parameter space, also known as the likelihood marginalisation, accounting for unknown parameters.
So for a given model $H_K$, with distribution's parameter $\theta_K$ (can be a vector) we can write:
\begin{equation}
    P(Dt|M_K)\ =\ \int P(Dt|\theta_K,M_K)P(\theta_K|M_K)d\theta_K
    \label{equ:MargMod}
\end{equation}
where:
\begin{itemize}
    \item $P(Dt|M_K)$ the likelihood density of the model K, how well the model fit the data.
    \item $P(Dt|\theta_K,M_K)$ the likelihood density of the data given the parameter $\theta_K$ depending on the model K, how well the model parameter fit the data.
    \item $P(\theta_K|M_K)$ the parameter's prior distribution
\end{itemize}
The marginalisation step allow us to obtain the likelihood function only in function of the model, it is said that we marginalise out the parameters.
Depending on the data and the choice of prior, this marginalisation integral may very well be intractable, leading to different numerical methods like asymptotic approximation or sampling methods\cite{raftery}.
In some cases, however, the choice of conjugate priors and/or uninformative ones leads to analytically tractable solutions, which is our case.
Once we know this ratio's value, we can draw a conclusion concerning the two models, as given in figure~\ref{fig:compRatio}.
When a small value is obtained, we can't conclude about which one of the models is better, but passing a certain value (greater than 2 in $log_{10}$), then one model is decisively better than the other.
\begin{figure}[!]
    \centering
    \includegraphics[scale=0.6]{img/BFratios.jpg}
    \caption{Model comparison decision base on BF}
    \label{fig:compRatio}
\end{figure}

\subsection{Application of the Bayesian scheme to our clustering problem}

\subsubsection{Likelihood function and priors}

In this section we simply describe and define the expression of the likelihood function for our application. We also give information on the choice of priors and their respective hyper-parameters.
These expressions will be further detailed when we will express the marginal likelihood.
We will start by discussing the assumed probability distributions of the data in hand.
Our data is described as following:
\begin{itemize}
    \item $Dt$ the global notation for our data set, hence representing all data.
    \item $d=\{1\dots D\}$ represents the dimension of numerical conditions (gene expression profiles).
    \item $l=\{1\dots L\}$ represents the dimension of categorical conditions (clinical variables).
    \item $n=\{1\dots N\}$ the number of samples (patients).
    \item $k=\{1\dots K\}$ the number of clusters.
    \item $X$ represent all numerical variables.
    \item $\Sigma\ =\ {\sigma_1^2\cdots\sigma_D^2}$ the vector representing the noise of each numerical variable.
    \item $\Psi=\{\mu_1\cdots \mu_D\}$ is a vector of gene average values.
    \item $Y$ represent all categorical variables.
    \item $\Phi=\{P(Y_{1}^S)\dots P(Y_{L}^S)\}$ vector of probabilities associated with each possible value for each categorical variable.
\end{itemize}

\emph{Numerical data:}\\
The gene expression profiles are numerical continuous variables, with appropriate normalisation, the probability distribution can be assumed to be normal.
\begin{figure}[!]
    \centering
    \begin{subfigure}[t]{0.25\textwidth}
        \centering
        \includegraphics[height=1.2in]{img/gaussDist.jpg}
        \caption{Gaussian distribution, from [bishop]}
    \end{subfigure}%
    \begin{subfigure}[t]{0.25\textwidth}
        \centering
        \includegraphics[height=1.2in]{img/distVar.jpg}
        \caption{Histogram of a gene expression profile}
    \end{subfigure}
    \caption{Gaussian distribution assumption}
\end{figure}
Thanks to that assumption we can write the total likelihood function as in equation~\ref{equ:NormalLikelihood}.
Now, if we account for the high dimensional space (several genes), with the joint probability rule it becomes:
\begin{equation}
    \mathcal{L}\ =\ P(X|\Psi,\Sigma)\ =\ \prod_{n=1}^{N}\prod_{d=1}^{D}\mathcal{N}(X_{nd}|\mu_d,\sigma_d^2)
\end{equation}
Choosing a conjugate prior, leads to  an analytical expression for the marginal likelihood.
Here, we only consider a prior on the mean parameter:\\
$$P(\Psi|m,\sigma_0^2)\sim\mathcal{N}(\mu_d|m,\sigma_0^2)$$

In our case, the hyper-parameters are $m=0$ and $\sigma_0^2$ set as the maximum of $\Sigma$.\\

\emph{Categorical variables:}\\
$Y$ follow multinomial distributions, if we take the case of a binomial distribution, particular case of the multinomial distribution, $Y_l\sim\operatorname{B} \left({N, p}\right)$ taking the values $A\ \text{or}\ B$, then the probability of observing the value A is given by:\\
$$P(Y_l=A) = {N\choose k}p^k(1-p)^{N-k}$$

In our case, we can disregard the possible combinations ${N\choose k}$ thank to the independence of the samples, hence the likelihood can be written:
\begin{equation}
    \mathcal{L}=P(Y|\Phi)=\prod_{n=1}^{N}\prod_{l=1}^{L}\prod_SP_{S}^{\delta(Y_{nl},S)}
\end{equation}
Where:
\begin{itemize}
    \item S represents the set of possible value (states) for a given $Y_l$
    \item $\delta$ is the Dirac delta function defined as followed:\\
    \[ \systeme*{1\ \text{if}\ Y_{nl} = S,0\ \text{else}} \]
\end{itemize}
Lets give an easy example, for a dichotomous categorical variable $Y_l$ taking 2 possible values A and B.
Let $P(Y_{l}^A)\ \text{and}\ (1-P(Y_{l}^A))$ be the probability of the event A and B respectively.
$N_A, N_B$ are respectively the number of instances for each value of the variable $Y_1$ Then the likelihood as described in equation (2) will give:\\

$$\mathcal{L}  =  \prod_{1}^{N_A+N_B}\prod_{A,B}P(Y_{l}^A)\cdotp (1-P(Y_{l}^A))$$

Which gives:
\begin{equation}
    \mathcal{L}  =  P(Y_{l}^A)^{N_A}\cdotp (1-P(Y_{l}^A))^{N_B}
    \label{equ:exCat}
\end{equation}
Concerning the prior for the categorical variables, a conjugate prior would be a prior following a Dirichlet distribution, but in our case we simply use a uniform prior equating 1.\\

\emph{Overall likelihood function:}\\
When we regroup the two previous likelihood function under a single expression, and take in consideration the existence of clusters, we obtain the following:
\begin{equation}
    \mathcal{L} = \prod_{k=1}^K\prod_{n\in N_k}\prod_{d=1}^{D}P(X_{knd}|\mu_{kd})\cdotp \prod_{l=1}^{L}\prod_SP_{S}^{\delta(Y_{knl},S)}
    \label{equ:LwithClus}
\end{equation}
Where $N_k$ is the set of index of sample belonging to the cluster $k$.\\
We now move to the heart of the method, the step of marginalisation in order to acquire the likelihood of a given model, leading to the Bayes factor determination.

\subsubsection{Likelihood marginalisation and Bayes factor}

Our method suppose the equiprobability of each clustering model we wish to compare, hence the priors in equation~\ref{equ:BayesRatio} are simplified and the posterior odds directly equate the marginal likelihood ratio between the two models.
We still have to express the marginal likelihood, because we used a Gaussian conjugate prior for the numerical variables, we can use the analytic expression in \cite{murphy}:
\begin{align}
    \mathcal{L}_{Marg} &= P(Dt|m,\sigma^2,\sigma_0^2) \nonumber \\ 
                     &= \int[\prod_{n=1}^N\mathcal{N}(x_n|\mu,\sigma^2)]\mathcal{N}(\mu|m,\sigma_0^2)d\mu
    \label{equ:postuMarph}
\end{align}
So, in the mixed type case, we add the categorical data with $\phi$ the parameter on it:
\begin{equation}
    \mathcal{L}_{Marg}\ =\ \int\prod_{n=1}^N[\mathcal{N}(x_n|\mu,\sigma^2)]\mathcal{N}(\mu|m,\sigma_0^2)\prod_SP_{S}^{\delta(Y_{n},S)}]d\mu d\phi
    \label{equ:Lmarg}
\end{equation}
Because the numerical and categorical variables don't have any parameter in common we can write equation~\ref{equ:Lmarg} as:
\begin{align}
    \mathcal{L}_{Marg}\ =\ \int\prod_{n=1}^N[\mathcal{N}(x_n|\mu,\sigma^2)]\mathcal{N}(\mu|m,\sigma_0^2)]d\mu\cdots \nonumber \\
                    \cdots\int\prod_{n=1}^N[\prod_SP_{S}^{\delta(Y_{n},S)}]P(\phi)d\phi
    \label{equ:Lmarg}
\end{align}
Thus, dissociating the two integral, according a separated treatment for each part.
We will give now the becoming of each integration separately, and reassemble them to obtain the final expression.\\

\emph{Marginal likelihood for numerical variables:}\\
Because we have a high dimension case, then the likelihood correspond to the constant application of the joint probability rule over all conditions.
The marginal likelihood on numerical variables becomes:
\begin{equation}
    \mathcal{L}_{Marg}^{num}\ =\ \prod_{d=1}^D\int\prod_{n=1}^N[\mathcal{N}(x_{nd}|\mu_d,\sigma_d^2)]\mathcal{N}(\mu_d|m,\sigma_0^2)]d\mu_d
\end{equation}
And by expending the expression for all the parameter values we have:
\begin{align}
    \mathcal{L}_{Marg}^{num} &= \int\prod_{n=1}^N[\mathcal{N}(x_n{1}|\mu_1,\sigma_1^2)]\mathcal{N}(\mu_1|m,\sigma_0^2)]d\mu_1\cdots \nonumber \\
    &\int\prod_{n=1}^N[\mathcal{N}(x_{nD}|\mu_D,\sigma_D^2)]\mathcal{N}(\mu_D|m,\sigma_0^2)]\mu_D
\end{align}
It has been shown in \cite{murphy} that the expression in equation~\ref{equ:postuMarph} can be analytically written:
\begin{align}
\mathcal{L}_{Marg} = \frac{\sigma}{(\sqrt{2\pi}\sigma)^N(\sqrt{N\sigma_0^2+\sigma^2})}\exp(\frac{-\sum_{n=1}^Nx_n^2}{2\sigma^2}\nonumber\\
    -\frac{m^2}{2\sigma_0^2})\exp(\frac{\frac{\sigma_0^2N^2\overline{x}^2}{\sigma^2}+\frac{\sigma^2m^2}{\sigma_0^2}+2N\overline{x}m}{2(N\sigma_0^2+\sigma^2)})
\end{align}
In our case we choose $m=0$, and accounting for the multivariate Gaussian distribution it becomes:
\begin{align}
\mathcal{L}_{Marg}^{num} = \frac{1}{(\sqrt{2\pi}^{DN}\prod_{d=1}^D\sigma_d^{N-1}(\sqrt{N\sigma_0^2+\sigma_d^2})}\nonumber\\
    \exp(-\frac{1}{2}\sum_{d=1}^D\sum_{n=1}^N\frac{x_{dn}^2}{\sigma_d^2})\exp(\frac{\sigma_0^2N^2}{2}\sum_{d=1}^D\frac{\overline{x}_d^2}{(N\sigma_0^2+\sigma_d^2)\sigma_d^2})
    \label{equ:multiLmarg}
\end{align}
Finally, applying the \emph{natural logarithm} to equation~\ref{equ:multiLmarg}, it simplifies as:
\small{
\begin{align}\label{equ:lnLikeNum}
ln(\mathcal{L}_{Marg}^{num})= ln(\frac{1}{(\sqrt{2\pi}^{DN}\prod_{d=1}^D\sigma_d^{N-1}(\sqrt{N\sigma_0^2+\sigma_d^2})})\nonumber \\
-\frac{1}{2}\sum_{d=1}^D\sum_{n=1}^N\frac{x_{dn}^2}{\sigma_d^2}+\frac{\sigma_0^2N^2}{2}\sum_{d=1}^D\frac{\overline{x}_d^2}{(N\sigma_0^2+\sigma_d^2)\sigma_d^2}\nonumber\\
= -\frac{DN}{2}ln(2\pi)+\sum_{d=1}^D[\frac{(N-1)}{2}ln(\sigma_d^2)+\frac{1}{2}ln(N\sigma_0^2+\sigma_d^2)]\nonumber\\
-\frac{1}{2}\sum_{d=1}^D\sum_{n=1}^N\frac{x_{dn}^2}{\sigma_d^2}+\frac{\sigma_0^2N^2}{2}\sum_{d=1}^D\frac{\overline{x}_d^2}{(N\sigma_0^2+\sigma_d^2)\sigma_d^2}
\end{align}
}
Using the \emph{natural logarithm} lower the computational time needed and also simplify conveniently the \emph{exponential} in the expression.\\
\emph{Marginal likelihood for categorical variables:}\\
The integral on one categorical variable, seen in equation~\ref{equ:MargMod} can be expended, once again thanks to the joint probability rule, in the multivariate case as:
\begin{align}
    \mathcal{L}_{Marg}^{cat} = \prod_{l=1}^L\int_0^1\prod_{n=1}^N\prod_SP_{S}^{\delta(Y_{nl},S)}P(\phi_l)d\phi_l\nonumber\\
    = \int_0^1\prod_{n=1}^N\prod_SP_{S}^{\delta(Y_{n1},S)}P(\phi_1)d\phi_1\cdots\int_0^1\prod_{n=1}^N\prod_SP_{S}^{\delta(Y_{nL},S)}P(\phi_L)d\phi_L
    \label{equ:LmargCat}
\end{align}
Here we can integrate between 0 and 1 because we are working with probabilities, so if we ignore the prior which always equates 1, we see that the marginal likelihood of each categorical variable is equivalent to a Beta function.
Beta function:\\
$$\textbf{B}(x,y)\ =\ \int_0^1t^{x-1}(1-t)^{y-1}dt$$

We see here that the Beta function fits the expression of the likelihood in the example of equation~\ref{equ:exCat}.
We can easily make the analogy between $t$ and $1-t$ with $P(Y_{l}^A)$ and $(1-P(Y_{l}^A))$.
The difference resides in the parameters of the function, indeed the Beta function deals with $x$ and $y$, which gives $x-1$ and $y-1$ as power of $t$ and $t-1$. In the example it is $N_A$ and $N_B$ which take this role, so we can easily express them together:
\begin{align}
    x &= N_A\ +\ 1\\
    y &= N_B\ +\ 1
\end{align}
So the integral, if expressed with $N_A$ and $N_B$ becomes:\\
$$\textbf{B}(N_A,N_B)\ =\ \int_0^1t^{N_A}(1-t)^{N_B}dt$$

So it perfectly matches with our example. Even in the case of variables with more than two possible events, the Beta function can be generalised in its calculation, using the other definition of the Beta function, closely related to the Gamma function, given by:\\
$$\textbf{B}(x,y)\ =\ \frac{\Gamma(x)\Gamma(y)}{\Gamma(x\ +\ y)}$$

Gamma function:\\
$$\Gamma(n)\ =\ (n-1)!$$

And with our example:\\
$$\textbf{B}(N_A,N_B)\ =\ \frac{\Gamma(N_A+1)\Gamma(N_B+1)}{\Gamma(N_A+N_B+2)}\ =\ \frac{N_A!N_B!}{(N_A+N_B+2)!}$$

When we generalise the expression, we have:
\begin{equation}
    \textbf{B}(Y_l)\ =\ \frac{\prod_{j=1}^J\Gamma(N_{Y_l=j}+1)}{\Gamma(N+sup(S_l))}\ =\ \frac{\prod_{j=1}^JN_{Y_l=j}!}{(N+sup(S_l))!}
\end{equation}
With $S_l$, the set of possible events of the variable $Y_l$, $N$, the number of samples, $j$ iterating over the set $S_l$.
Thus, from equation~\ref{equ:LmargCat}, we can write the likelihood:
\small{
\begin{equation}
     \mathcal{L}_{Marg}^{cat} = \frac{\prod_{j_1=1}^{J_1}\Gamma(N_{Y_1=j_1}+1)}{\Gamma(N+sup(S_1))}\cdots\frac{\prod_{j_L=1}^{J_L}\Gamma(N_{Y_L=j_L}+1)}{\Gamma(N+sup(S_L))}
     \label{equ:LmargCatfin}
\end{equation}
}
Then, for convenience and for saving computational resources, we apply the \emph{natural logarithm} to equation~\ref{equ:LmargCatfin}:
\small
\begin{align}
    \mathcal{L}_{Marg}^{cat}\ =\ \sum_{j_1=1}^{J_1}ln(\Gamma(N_{Y_1=j_1}+1))-ln(\Gamma(N+sup(S_1)))+\cdots\nonumber\\
 \cdots+\sum_{j_L=1}^{J_L}ln(\Gamma(N_{Y_L=j_L}+1))-ln(\Gamma(N+sup(S_L))) 
\end{align}

\emph{Total marginal likelihood:}\\
So if we bind the two parts together:
\begin{equation}
    ln(\mathcal{L}_{Marg})\ =\  ln(\mathcal{L}_{Marg}^{num})\ +\ ln(\mathcal{L}_{Marg}^{cat})
    \label{equ:finalLmargTot}
\end{equation}
Notice that the marginal likelihood expressions are given considering only one cluster, but as shown in equation~\ref{equ:LwithClus}, accounting for more than one cluster would simply require to add a sum over all clusters and change the total number of sample into the number of sample in each respective cluster.\\

\emph{Bayes Factor:}\\
Now that we have the expression of the marginal likelihood over the respective parameters, which, once marginalised gives the likelihood of a given model, we can simply get the BF by applying the ratio (bocoming a difference with $ln$) between two models 1 and 2:
\begin{equation}
    ln(BF_{12})\ =\ ln(\mathcal{L}_{Marg}^{M1})\ -\ ln(\mathcal{L}_{Marg}^{M2})
    \label{equ:lnLikeBF}
\end{equation}
And from the results and the information given in figure~\ref{fig:compRatio}, we can see which one of the two models fits our data the better.
From this value, we can directly compare clustering results from any algorithm, and we can also create a clustering method based on the behaviour of the BF, hence deciding to merge of samples together or not based on the value of the BF.

\subsection{Proposed Methods}

We want here to present different implementations, based on the BF scheme.
Concerning the algorithms, only one was successfully implemented but the reasoning behind the other ones will be explained as well.

\subsubsection{Bayes Factor calculation from clustering result}

The first, and simplest, implementation reside in the simple calculation of the BF from a list of already clustered and labeled data.
The source code can be found in supplementary file.
Here we simply feed the function with two clustering results, one with 3 clusters and the other with 4 for instance, we also give it the data set it is from and it return the BF after calculation of the numerical and categorical marginal likelihood separately.
This implementation is able to deal with missing values, it basically replace them by zeros when calculation, hence missing values don't participate in the marginal likelihood calculations.

The source code of all implementation is given in supplementary files.

\subsubsection{Hierarchical Bottom-Up clustering Algorithm}

The first hierarchical algorithm takes a bottom-up approach, which means it starts by assuming all the samples as distinct clusters and merge them at each step until all the samples are gathered in a single cluster.
In this algorithm, we consider all possible combinations, meaning that the tree will not be reduced as a binary one, more than two branches association is possible.
At each step of the algorithm, the marginal likelihood ($\mathcal{L}_{Marg}$) between each pair of samples is computed, then the samples maximising $\mathcal{L}_{Marg}$ are taken and merged together into one cluster. That decision comes from the fact that maximising the $\mathcal{L}_{Marg}$ means maximising the fitness to the observed data.
The matrix is then updated to reflect the new assumed model, accounting for the freshly created cluster.
The calculation of such matrix requires the marginal likelihood of the previous assumed model, we show that a mathematical simplification on the likelihood expression can be used for the first algorithm's iteration.
Indeed, a lot of calculation is unnecessary for our purpose, which allows us to simplify the expression, hence simplifying the calculation, reducing the required computational resources.
Lets detail the mathematical simplifications, which will be used in the other implemented methods as well.
First of all, we will use the following notation by convenience:
\begin{itemize}
    \item $a=-\frac{DN_k}{2}ln(2\pi)+\sum_{d=1}^D[\frac{(N_k-1)}{2}ln(\sigma_d^2)+\frac{1}{2}ln(N_k\sigma_0^2+\sigma_d^2)]$
    \item $b=-\frac{1}{2}\sum_{d=1}^D\frac{x_{d}^2}{\sigma_d^2}$
    \item $c=\frac{\sigma_0^2N_k^2}{2}\sum_{d=1}^D\frac{\overline{x}_d^2}{(N_k\sigma_0^2+\sigma_d^2)\sigma_d^2}$
    \item lets call $d$ the categorical part of the marginal likelihood
    \item $d\ =\ \sum_{s=1}^S[ln(\Gamma(N_s))]\ -\ ln(\Gamma(N+sup(S)))$
    \item taking even more liberties, we can note $a(N_k=1)$ corresponding to a but with $N_k$, number of samples in the cluster k, equals 1.
    \item In the same way, $b(x_n),\c(x_n)\ \text{and}\ d(x_n)$ respectively the part b, and d taking the value of the sample $x_n$ for their calculation.
\end{itemize}
a,b and c come from equation~\ref{equ:lnLikeNum}, just without the sum over all samples.
The first step is to calculate the marginal likelihood of the model 0, the model assuming each sample as its own cluster. In such scheme, $N_k$ would equates 1, and the sample mean in c directly equates the sample value by gene. Furthermore, d also gives great simplification because the numerators in equation~\ref{equ:LmargCatfin} becomes 0 with \emph{ln}.
Hence we get:
\begin{equation}
    \mathcal{L}_{Marg}^{M0}\ =\ N\cdotp a(N_k=1)\ +\ \sum_{n=1}^Nb(x_n)\ +\ \sum_{n=1}^Nc(x_n)\ +\ \sum_{n=1}^Nd(x_n)
    \label{equ:M0}
\end{equation}
Now if we desire to have the marginal likelihood of any pair of samples i and j:
\begin{align}
    \mathcal{L}_{Marg}^{ij}\ =\ (N_k-2)a(N_k=1)\ +\ a(N_k=2)\ +\ \sum_{n=1}^Nb(x_n)\nonumber\\
    +\ \sum_{N\setminus{i,j}}c(x_n) +\  c(\overline{x_ix_j})\ +\ \sum_{N\setminus{i,j}}d(x_n)\ +\ d(x_i,x_j)
\end{align}
We then can express it using $\mathcal{L}_{Marg}^{M0}$:
\begin{align}
    \mathcal{L}_{Marg}^{ij}\ =\ \mathcal{L}_{Marg}^{M0}\ -\ 2a(N_k=1)\ +\ a(N_k=2)\ +\ \sum_{n=1}^Nb(x_n)\nonumber\\ +\ c(\overline{x_ix_j}) -\ c(x_i)\ -\ c(x_j)\ +\ d(x_i,x_j)\ -\ d(x_i)\ -\ d(x_j)
\end{align}
So for each sample pairs, the difference resides only in the parts depending on $x_i$ and $x_j$, the rest can be considered constants and ignored, which gives finally:
\begin{align}
    \mathcal{L}_{Marg}^{ij}\ \propto\ c(\overline{x_ix_j})\ -\ c(x_i)\ -\ c(x_j)\ +\ d(x_i,x_j)\nonumber\\ -\ d(x_i)\ -\ d(x_j)
    \label{equ:simplifMath}
\end{align}
The simplification is possible only for the first iteration, after the first merging, it falls due to the unpredictability of possible sample associations.
The lack of such generalised simplification makes the algorithm time complexity too high (exponential), the marginal likelihood matrix having to be updated after the creation of each cluster.
Another version of this algorithm was under development, with main difference a binary tree forcing approach in order to keep the simplification applicable at each step.
Unfortunately, as soon as the number of clusters becomes odd, the simplification falls and complications arise.
\RestyleAlgo{boxruled}
\begin{algorithm}[!]
 \SetKwFunction{UpdateMatrix}{updateMatrix}
 \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 \Input{$Dt = (N,D+L)$, $\sigma^2$, prior hyper-parameters (HP)}
 \Output{A list of cluster solutions associated with respective BF}
 \BlankLine
 $L_M\ \leftarrow L_{Marg}^{M0}$\\
 $Cl \leftarrow$ list of clusters (each sample at first)\\
 $N_k$ $\leftarrow$ vector of number of samples by cluster (only 1s at first)\\
 \tcp{Create the first marginal likelihood matrix}
 $L_{Mat}\ \leftarrow$ call \UpdateMatrix{$Cl,\ N_k,\ Dt,\ \sigma^2$, HP}\\
 $K\ \leftarrow$ N\\
 \BlankLine
 \While{we have more than one cluster}
    {
        Get the samples names of the maximum in $L_{Mat}$\\
        Update Cl by merging the two samples\\
        Update $N_k$ as well\\
        Compute the marginal likelihood of the new model\\
        Calculate the Bayes Factor\\
        Replace $L_M$ by the new model $L_M$\\
        \UpdateMatrix{$Cl,\ N_k,\ Dt,\ \sigma^2$, hyper-parameters}\\
        K = K - 1
        Result $\leftarrow$ Append(Cl,K,BF)\\
    }
    Return Result
 \caption{BF\_HC\_Asc}
\end{algorithm}
\RestyleAlgo{boxruled}
\begin{algorithm}[!]
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 \Input{Cl,$N_k$,$Dt = (N,D)$, $\sigma^2$,HP}
 \KwData{List of clusters, each sample value vector}
 \KwResult{Marginal likelihood matrix}
 \tcp{Create a matrix filled with NAs}
 $L_{Mat}\ \leftarrow matrix(NA)$\\
 \For{i in 1 to the number of clusters-1}
    {
        \For{j in i+1 to the number of cluster}
        {
            $L_{Marg}^{ij}\ \leftarrow$ Compute the the marginal likelihood between clusters i and j\\
            \tcp{Put the value into the corresponding index of the new matrix}
            $L_{Mat}[i,j]\ \leftarrow\ L_{Marg}^{ij}$
        }
    }
    Return $L_{Mat}$
 \caption{UpdateMatrix}
\end{algorithm}
The function updating the matrix return a $N\text{x}N$ matrix with the lower triangle filled with $NAs$.
This algorithm is able to deal with missing values.

\subsubsection{Hierarchical Top-Down clustering Algorithm}

The second implementation is a hierarchical Top-down algorithm, which means, we start with all samples gathered in a single cluster and at each step we divide it in smaller clusters based on some conditions.
The work-flow of this algorithm is pretty straightforward and uses the Gower distance, from the "Cluster" package under R, in addition to marginal likelihood.
This approach allow us to avoid having to re-calculate a huge matrix, hence saving a lot of computation time, but it also presents an imperfection, the choice of the dividing condition.
Indeed, each time we want to split a given cluster in two different ones, we face some troubles like, what will be the rule of division or which cluster to divide first.
Unfortunately it is of great difficulty to predict the behaviour of the marginal likelihood, hence finding a relevant way of splitting a cluster is challenging.
For lack of anything better, the splitting condition was set to simply divide a cluster into two equally, or almost equally (case of odd number of samples), sized clusters. 
This separation relies on two steps:
\begin{enumerate}
    \item Calculate the Gower distance matrix for each cluster and get one of the two samples having the maximum distance, we call that sample the \emph{reference sample}
    \item Compute the marginal likelihood between the \emph{reference sample} and all the remaining samples
\end{enumerate}
Through that method, we get, for each singular cluster, the maximum Gower distance and one of the sample associated with it.
We can then sort by decreasing order these distances, which will give us the order of cluster splitting.
This assumption is simple but logical, indeed, the cluster containing the two most distant samples is the strongest candidate for being split in first.
Once we have that list, we just have to iterate on it and calculate for each respective cluster the marginal likelihood combinations.
We then, once again use a decreasing order sorting to basically obtain on the first position the closest samples and at the latest positions the farthest ones.
Finally, we split in two, taking the $floor(\frac{N_k}{2})$ first samples (so if odd number, take the inferior integer), and associate them with the \emph{reference sample} to create a new cluster, the remaining samples are associated into a second new cluster.
At each new iteration over the ordered list, we compute the marginal likelihood of the changed model (one more cluster to take into consideration), and compute the BF with the former model.
Here the first assumed model is as following (all sample in one cluster):
\begin{align}
    \mathcal{L}_{Marg}^{M0}\ =\ a(N_k=N)\ +\ \sum_{n=1}^Nb(x_n)\nonumber\\ 
    +\ c(\overline{x_1\cdots x_N})\+d(x_1,\cdots,x_N)
\end{align}
And when calculating the marginal likelihood with a \emph{reference sample}, the mathematical simplification can go even further than in equation~\ref{equ:simplifMath}, indeed here $x_i$ will be the same for all, $x_{ref}$, so we can consider it a constant and ignore it, which leads to:
\begin{equation}
    \mathcal{L}_{Marg}^{ref,j}\ \propto\ c(\overline{x_{ref}x_j})\ -\ c(x_j)\ +\ d(x_{ref},x_j)\ -\ d(x_j)
\end{equation}
\RestyleAlgo{boxruled}
\begin{algorithm}[!]
 \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 \Input{$Dt = (N,D+L)$, $\sigma^2$, prior hyper-parameters (HP), number of  maximum desired clusters}
 \Output{A list of cluster solutions associated with respective BF}
 \BlankLine
 $old.L_M\ \leftarrow L_{Marg}^{M0}$\\
 $Cl \leftarrow$ list of clusters (a single cluster with all samples)\\
 \tcp{K accounts for the number of clusters, 1 at first}
 $K\ \leftarrow$ 1\\
 \BlankLine
 \While{We haven't reached the desired number of clusters}
    {
        gower $\leftarrow$ Compute the Gower distance matrix of each cluster\\
        gower.max $\leftarrow$ fetch the reference sample and the distance value for each cluster\\
        \tcp{sort the values by decreasing order}
        gower.max.ord $\leftarrow$ sort(gower.max)\\
        indices $\leftarrow$ clusters indices in the order given by gower.max.ord\\
        \For{i in indices}
        {
            Take the cluster to split in Cl\\
            Compute the marginal likelihood with the reference sample\\
            cl.split $\leftarrow$ newly formed clusters\\
            cl.remaining $\leftarrow$ clusters not split yet\\
            K $\leftarrow$ K+1\\
            \tcp{Marginal likelihood of model k}
            $new.L_M\ \leftarrow$ compute model marginal likelihood\\
            \tcp{$old.L_M$ equates $L_{Marg}^{M_{K-1}}$}
            BF $\leftarrow$ $old.L_M\ -\ new.L_M$\\
            Update Cl\\
            Result $\leftarrow$ append Cl and BF
        }
    }
    Return Result
 \caption{BF\_HC\_Desc}
\end{algorithm}
This algorithm is also able to deal with missing values in the same manner as the first one.

\subsubsection{Simplified hierarchical Bottom-Up clustering Algorithm}

The last implemented algorithm is also a bottom-up one, but in order to minimise the overall time complexity, only the first marginal likelihood matrix is calculated and all clusters are formed from it.
This algorithm is of really simple design, the idea is to feed it with a desired number of cluster and it will stop once this number is reached.
At first, the algorithm calculate the marginal likelihood matrix as in the first step of the first algorithm, using the mathematical simplification shown earlier.
Then, from this matrix it will fetch at each step the maximum and the two samples corresponding to put them together in a single cluster. Once it is done, it puts NA into the index of this maximum, which allows to avoid taking the same samples twice.
Because of the possibility of getting samples already in a cluster formed at a previous step, it is necessary to add a checking task, which behaves differently according to the case we are in:
\begin{itemize}
    \item if the two samples are already in the general cluster solution
        \begin{enumerate}
            \item Get the respective cluster index already comprising these samples.
            \item Merge these two clusters into one.
        \end{enumerate}
    \item if only one of the sample is already in a cluster
        \begin{enumerate}
            \item Identify which of the two is already in a cluster.
            \item Get the index of the corresponding cluster
            \item Add the second sample into that cluster
        \end{enumerate}
    \item if none of the samples are already in an existing cluster, we simply put them together in a new cluster
\end{itemize}
By following this work-flow, and looping it until all samples are put into a unique cluster, we obtain the final cluster solution.
Unfortunately, a flaw in the design made it difficult to get the desired result, being able to both cluster all samples and to put them into a given number of clusters was not as easy as anticipated.
By lack of time some issues were not fully addressed, leading to poor results, the algorithm having tendencies to stop before clustering all samples and creating really unbalanced clusters with generally a big one regrouping most of the samples and the remaining ones having a handful number of samples.
\RestyleAlgo{boxruled}
\begin{algorithm}[!]
 \SetKwFunction{UpdateMatrix}{updateMatrix}
 \SetKwFunction{MergeBoth}{mergeBoth}
 \SetKwFunction{MergeOne}{mergeOne}
 \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 \Input{$Dt = (N,D+L)$, $\sigma^2$, prior hyper-parameters (HP), number of clusters desired}
 \Output{A cluster solution associated with its BF}
 \BlankLine
 $L_M\ \leftarrow L_{Marg}^{M0}$\\
 $Cl \leftarrow$ list of clusters (each sample as cluster)\\
 $N_k$ $\leftarrow$ vector of number of samples by cluster (only 1s)\\
 $L_{mat}\ \leftarrow$ \UpdateMatrix{Cl,$N_k$,Dt,$\sigma^2$,HP}\\
 \tcp{List containing the general cluster solution, will be update at each iteration}
 $Cl.sol\ \leftarrow$ void list\\
 \BlankLine
 \While{We haven't reached the desired number of clusters}
    {
       samp.max $\leftarrow$ samples associated with max($L_{mat}$)\\
       \tcp{if we note i and j indices of the current maximum}
       $L_{mat}[i,j]\ \leftarrow$ NA\\
       \If{both samples already in Cl.sol}
       {
        Cl.sol $\leftarrow$ \MergeBoth{Cl.sol,samples}\\
       }
       \uElseIf{Only one sample already in Cl.sol}
       {
        CL.sol $\leftarrow$ \MergeOne{Cl.sol,samples}\\
       }
       \Else
       {
        \tcp{None of the samples are already in Cl.sol}
        Cl.sol $\leftarrow$ Append in a new index the two samples\\
       }
    }
    $L_{marg}\ \leftarrow$ Compute marginal likelihood of the model\\
    BF $\leftarrow\ L_M\ -\ L_{marg}$\\
    Cl.sol $\leftarrow$ Append Cl.sol with BF\\
    Return CL.sol
 \caption{BF\_HC\_Asc\_s}
\end{algorithm}
\RestyleAlgo{boxruled}
\begin{algorithm}[!]
 \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 \Input{Cluster list, two samples to add}
 \Output{A new list containing all clusters}
 \BlankLine
 \For{loop on each element of the clusters list}
 {
  \If{one of the samples is in the current cluster}
  {
   indices $\leftarrow$ Get the index of this cluster\\
  }
  \Else
  {
   Do nothing\\
  }
 }
 Merge the two clusters corresponding to indices into one\\
 return the new cluster solution
 \caption{MergeBoth}
 \label{algo:merge}
\end{algorithm}
The function \emph{MergeOne()} acts like in algorithm~\ref{algo:merge}, but directly puts the sample not already clustered in the cluster containing the other sample.
These functions avoid getting duplicated samples and clusters.

\section{Results}

\subsection{Method testing}

In order to assess the performance of the methods, we applied them to different data sets found on \cite{source1} and \cite{source2}.
We used them to investigate the computational time required by our methods, and because we know the true classes for some of the data sets, we were also able to appreciate their accuracy.
The list and description for each data set can be seen in table~\ref{tab:testDT}:
\begin{table}[!]
    \centering
    \includegraphics[scale=0.4]{img/dataSets.png}
    \caption{Data sets used for testing our methods}
    \label{tab:testDT}
\end{table}
We chose these data sets in order to consider different possibilities, hence we have data sets with both categorical and numerical variables, but also the Wine data set with only numerical, opposed to the Zoo one having only categorical variables.
They also offer different dimensions, which allow us to explore the time required by the algorithms to perform.

\subsubsection{Bayes Factor induced clustering}

For comparison purpose, we decided to apply another already existing method to the same data sets. As stated before, the Gower distance can be used on mixed type of data, then applying a simple hierarchical clustering algorithm, available under R with the \emph{hclust()} function, with either Ward or Complete method of linkage (equations~\ref{equ:comp},\ref{equ:ward}).
We applied the same linkage method but instead of the Gower distance matrix, we calculated the Marginal likelihood matrix between each possible sample pairs.
We are interested in finding the right number of classes, the accuracy, and the computational time required.
\begin{table}[!]
    \centering
    \includegraphics[scale=0.35]{img/ResultsTable.png}
    \caption{Table of results for Gower and Marginal likelihood metrics}
    \label{tab:ResTab}
\end{table}
In table~\ref{tab:ResTab}, \emph{Candidates} represent the cluster models which represent good candidates for the best cluster model and \emph{\# of classes} is the true number of classes in the data set.
The results obtain in table~\ref{tab:ResTab}, were found by plotting the BFs for each model, determining candidates model, and in the case were several candidates were found, comparing the BFs between candidates to find the best one.
Only the algorithm top-down was used, because the bottom-up ones lacked optimisation or yielded really poor clusters.
As this table shows, all techniques manage to get pretty close or even equalise the true number of classes in the data sets, so we consider that the ability of our implemented methods to discover the right number of clusters is satisfying.
\begin{figure}[!]
    \centering
    \includegraphics[scale=0.3]{img/BFplot.png}
    \caption{Conclusive example of BF plot interpretation}
    \label{fig:BFplotConclusive}
\end{figure}
Figure~\ref{fig:BFplotConclusive} shows how we choose the candidate models. From equation~\ref{equ:lnLikeBF} and because each dot represent the log BF between the previous and the current model, i.e: 2 clusters vs 3 clusters, we concluded that when the dot is below zero, it means that the current model is better than the previous one. Furthermore, when after going below zero the next dot goes in higher values (the current model becomes the former one for this dot), it confirm that the "new" former model is better.
We also noticed that even when not going below zero, but showing the same pattern can also predict a good candidate, as shown in figure~\ref{fig:notbelowzero}, there are two candidates not giving a log BF below zero, but are actually better than the one going below zero.
\begin{figure}[!]
    \centering
    \includegraphics[scale=0.3]{img/BFplotNotBelowZero.png}
    \caption{Conclusive example with less obvious candidates}
    \label{fig:notbelowzero}
\end{figure}
Most of the BF were strong or decisive according to figure~\ref{fig:compRatio}. Only for the data set Abalone we got a substantial result between the 22 cluster model and the 27 one, and a not worth even a bare mention case between 27 clusters and 30 clusters, which is why we considered them both as best candidates.

\subsubsection{Accuracy results}

Some data sets have well defined class identifiers, allowing us to compute the accuracy of the different methods.
In order to determine the accuracy, we simply used the Jaccard's index between the true classes and the clustering results. 
For two sets A and B, the Jaccard's index can be calculated with:
\begin{align}
    Jaccard(A,B)\ =\ \frac{|A\cap B|}{|A\cup B|}
\end{align}
So, this index is merely a similarity measure between two sets.
In table~\ref{tab:accTable}, we put a summary of the results, putting only the maximum Jaccard index found for the respective method used and for each class.
Our results show that the accuracy using the Gower distance matrix and the log marginal likelihood matrix share the lead, depending on the data set considered.
However, our hierarchical top-down clustering method perform poorly and rarely goes over an index value of 0.5.
\begin{table}[!]
    \centering
    \includegraphics[scale=0.4]{img/AccTable.png}
    \caption{Table of maximum Jaccard index by method}
    \label{tab:accTable}
\end{table}
Although our methods are able to find the right number of clusters, we showed here that the accuracy is not really on point, especially for the hierarchical top-down algorithm we implemented.

\subsection{Results on the lung adenocarcinoma data sets}

Even thought the test were not conclusive, and accurate enough, we applied our methods to different data sets to see if we could still find interesting results.
We used the 4 data sets described earlier in section~\ref{sec:preprocess}, and obtain the results shown in table~\ref{tab:resAdeno}.
We can see that in most cases, our methods find a best cluster solution of two clusters, but as it has been previously determined in \cite{hayes}, \cite{wilk} and \cite{TCGA}, the number of sub-types is at least three. From there, we can assume that, unfortunately, our scheme is not sensitive enough, and pushing the investigation further would not really lead to meaningful outcomes.
In the case of the TCGA data sets, because we have access to the classification made in \cite{TCGA}, we just can have a look at the accuracy yielded by the different gene sets taken into consideration, which would, at least, give us which gene set would seem to be a better predictor to lung Adecarcinoma sub-types exploration.
\begin{table}[!]
    \centering
    \includegraphics[scale=0.4]{img/ResultsAdeno.png}
    \caption{Clustering results with the lung Adenocarcinoma data sets}
    \label{tab:resAdeno}
\end{table}
\begin{table}[!]
    \centering
    \includegraphics[scale=0.3]{img/AccAdeno.png}
    \caption{Methods Accuracy on Adenocarcinoma TCGA data sets}
    \label{tab:accadeno}
\end{table}
Our analysis about accuracy, shown in table~\ref{tab:accadeno}, was produced by taking a three clusters solution from our different methods.
Although it yielded poor results, especially the Ward method being often inconclusive due to an aggregation of most of the samples into one cluster, we still can see that the differentially expressed gene set is a decent predictor for the PI sub-type, where the gene set in "AsGSE" is a decent predictor for the TRU sub-type. Unfortunately, none of the considered gene sets were able to be good enough predictor for the PP sub-type.
Further analyses have not been conducted, deemed to be unnecessary given such inconclusive results.
This is why, we consider our methods as a framework, laying the foundations for future research using the same scheme but bringing some tuning to our model.

\subsection{Time Complexity}\label{sec:tps}

Optimisation is a very important feature in computer science, being able to implement an algorithm computing quickly is a great challenge.
We have shown how we could simplify the mathematical model to avoid some unnecessary calculation, and because we used R, we can also talk about some optimisation problem we had.
R software is far from being an optimal environment for algorithmic implementations, especially under Windows. Even if some tools like R open for Windows or the package "Parallel", for Mac OS or Linux distributions, allow parallel computing, not all functions in R profit from it.
Furthermore, the handling of objects is not really practical, often reduced to use lists for simplification purpose.
So, overall, coding an algorithm with R asks additional reflections and adaptations in order to minimise the computational time consumption.
In table~\ref{tab:runTime}, the time required for each case is given, and as we can see, the Marginal likelihood matrix is a quite time consuming process.
For huge data sets, we quickly reach several hours of computational time, which is not desirable.
These results were obtained with an Intel Core i7-3970X 3.50GHz processor, 32GB of RAM under Windows 7 Ultimate 64-bits.
At first glance, we see that the number of samples play a more important role in the time consumption than variables.
Indeed, if we look at the time required for the GSE data set (442 observations, 2249 variables) and for the TCGA DEG one (230, 2858), we notice a huge difference even though the TCGA data set has 600+ variables more than GSE for only 200+ less observations.
We confirmed that idea by varying the number of observations with a constant number of variables and doing the opposite for the marginal likelihood matrix calculation, which is shown in figure~\ref{fig:tpsObs} and \ref{fig:tpsVar}.
Indeed, from these figures, wee observe that the time consumption increase linearly when varying the variable number only, and takes the form of a quadratic equation when varying the observations only.
So, the overall time consumption when varying the number of observations and variables together give the figure~\ref{fig:tpsBoth}.
The time complexity given in function of N (number of samples) for our implementations is:
\begin{itemize}
    \item Marginal likelihood matrix: $O(N^2)$
    \item Top-Down clustering algorithm: $O(N)$
\end{itemize}
\begin{table}[!]
    \centering
    \includegraphics[scale=0.4]{img/runTime.png}
    \caption{Computational time by data set for each method}
    \label{tab:runTime}
\end{table}
\begin{figure}[!]
    \centering
    \includegraphics[scale=0.3]{img/ObsTime.png}
    \caption{Time consumption evolution in function of number of observations}
    \label{fig:tpsObs}
\end{figure}
\begin{figure}[!]
    \centering
    \includegraphics[scale=0.3]{img/VarTime.png}
    \caption{Time consumption evolution in function of number of variables}
    \label{fig:tpsVar}
\end{figure}
\begin{figure}[!]
    \centering
    \includegraphics[scale=0.3]{img/bothTime.png}
    \caption{Time consumption evolution in function of number of observations and variables}
    \label{fig:tpsBoth}
\end{figure}

\section{Discussion}

As our results show, the pairwise $\mathcal{L}_{Marg}$ matrix could represent an interesting alternative to distance matrix calculation for mixed type of data.
Indeed, this method is able to mostly find the right number of classes, or at least a close one, for most of the test data sets.
The Top-down clustering algorithm is also able to find a satisfying number of clusters, close to the true one, but not as good as the other method.
Unfortunately, we also showed that although we find a relevant number of clusters, the accuracy is not on point, the Jaccard index struggling to go over 0.5.
Once again an association between the marginal likelihood matrix and a Ward or complete linkage hierarchical clustering outperform the top-down algorithm and even in some cases the Gower distance usage or equating it, i.e: Credit, Dermatology, Zoo data sets.
The lack of accuracy of the top-down clustering algorithm can be explained by the splitting condition, too simplistic, and maybe the theoretical model, lacking sensitivity.
Hence, we believe that by refining the mathematical expressions, adding for instance a prior on the variance for gene expression profiles and adding an informative prior following a Dirichlet distribution for the clinical knowledge, would improve the accuracy.
Some other techniques could be used to obtain a numerical approximation rather than an analytical expression of the likelihood, like MCMC sampling (Gibbs, Metropolis-Hasting).
Furthermore, finding a relevant splitting scheme at each step of this algorithm, relying on the behaviour of the marginal likelihood, would also lead to better results.
Concerning the marginal likelihood matrix, updating such matrix at each new cluster association should also grants to this method better outcomes, but then, as we highlighted it in section~\ref{sec:tps}, the time complexity would go through the roof.
We strongly believe that a Python or Java implementation rather than R, could provide a significant time consumption improvement, and such languages should also allow a more practical object/data manipulation.
Thus, tuning the mathematical model and working on the optimisation of the algorithms could potentially yield to interesting and attractive new methods for cluster investigation.

\section{Conclusion}

Although further refinements are needed to reach applicable methods, we managed to propose an interesting framework for clustering investigation using Bayesian inference.
The lack of accuracy from our implementations prevented us from moving our analyses forward with adenocarcinoma data sets. Without the ability to cluster accurately our data, we preferred to restrict ourselves concerning any interpretation of the clusters. 
Nonetheless, this paper can provide a good basis for future work, we also gave some hints about possible improvement to such model.
The ability of such model to be applied to any practical use makes it attractive and subject to future enhancement, indeed, the probability distribution can be easily tuned to match the needs and efficiency and readability of hierarchical clustering has already been proven over the years.
Several algorithmic approaches were adopted, hence, we proposed three different hierarchical algorithms, written under R, and a simple model comparison tool, all the source code is available.
On a more personal note, working on Bayesian inference was a great learning opportunity, given the popularity and increasing interest for such statistical scheme, and also represented a challenge given the strong mathematical requirements to understand and implement it.
The occasion to freely develop algorithms was also a first, and gave its fair share of programming challenges as well as a personal opening to unexplored fields of computer sciences.
Concerning Japan, my experience here has been a real pleasure, socially as well as culturally, producing unforgettable memories. It truly represents a chance and a great life experience, the once in a lifetime kind, and I hope to come back in this beautiful and welcoming country as soon as possible.

\printbibliography

\end{document}

### 2018-08-06 test/main.tex
20180806

@@
 \date{July 2018}
-\author{\textbf{Dafang Zhao}\\Nara Institute of Science and Technology, Depenadble System Lab}
+\author{\textbf{Dafang Zhao}\\Nara Institute of Science and Technology, Dependable System Lab}
 
@@
 \\As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human.
-Photovolatic (PV) energy recived signifcant attention since it has unlimited energy and easy to be scaled up.
+Photovoltaic (PV) energy received significant attention since it has unlimited energy and easy to be scaled up.
+Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
 

### 2018-08-08 test/main.tex
20180806-3
20180808

@@
-\documentclass[twocolumn]{article}
+\documentclass[twocolumn,12pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage[a4paper,margin=0.5in]{geometry}
-\title{\textbf{Photovoltaic System Reconfiguration strategy for mismatch condition}}%\\
+\title{\textbf{Photovoltaic System Reconfiguration strategy for mismatch conditions}}%\\
            %\emph{Application to mixed typed of data in lung Adenocarcinoma subtype discovery}}
@@
 Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
-
+But PV arrays are senstive to shading and PV cell's fault or aging.
+That means the interconnection of PV cells or modules which do not have identical properties or which experience different conditions from one another.
 \section{Related work}

### 2018-08-08 main.tex
20180805
rm file
20180806
re-write
write in IEEE trans style

@@
-\documentset{12pt}
-\start{document}
-hello,world
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\begin{document}
+
+\title{Photovoltaic System Reconfiguration strategy for mismatch condition\\
+{\footnotesize \textsuperscript{}}
+\thanks{Identify applicable funding agency here. If none, delete this.}
+}
+
+\author{\IEEEauthorblockN{1\textsuperscript{st} Dafang Zhao}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}}
+}
+
+\maketitle
+
+\begin{abstract}
+This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract.
+\end{abstract}
+
+\begin{IEEEkeywords}
+component, formatting, style, styling, insert
+\end{IEEEkeywords}
+
+\section{Introduction}
+
+\\As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human.
+Photovoltaic (PV) energy received significant attention since it has unlimited energy and easy to be scaled up.
+Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
+But due to PV arrays are senstive to shading and PV cell's fault or aging.
+That means when interconnection of PV cells or modules do no have identical properties or experience different conditions from one another.PV arrays are in mismatch condition.
+In order to avoid mismatch condition damage PV cells, we proposed an algorithm that can re-configurate photovoltaic arrays to minimize mismatch loss.
+\\In this paper, we using non-uniform irradiance levels to represent mismatch condition and analysis the efficiency of a PV system under different shaded working condition is presented.When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maxmimum power points (MPPs) \cite{b1}, which been genearated by turning on bypass diodes.
+
+\section{Ease of Use}
+
+\subsection{Maintaining the Integrity of the Specifications}
+
+The IEEEtran class file is used to format your paper and style the text. All margins, 
+column widths, line spaces, and text fonts are prescribed; please do not 
+alter them. You may note peculiarities. For example, the head margin
+measures proportionately more than is customary. This measurement 
+and others are deliberate, using specifications that anticipate your paper 
+as one part of the entire proceedings, and not as an independent document. 
+Please do not revise any of the current designations.
+
+\section{Prepare Your Paper Before Styling}
+Before you begin to format your paper, first write and save the content as a 
+separate text file. Complete all content and organizational editing before 
+formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
+proofreading, spelling and grammar.
+
+Keep your text and graphic files separate until after the text has been 
+formatted and styled. Do not number text heads---{\LaTeX} will do that 
+for you.
+
+\subsection{Abbreviations and Acronyms}\label{AA}
+Define abbreviations and acronyms the first time they are used in the text, 
+even after they have been defined in the abstract. Abbreviations such as 
+IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
+abbreviations in the title or heads unless they are unavoidable.
+
+\subsection{Units}
+\begin{itemize}
+\item Use either SI (MKS) or CGS as primary units.
+(SI units are encouraged.) English units may be used as secondary units (in parentheses).
+An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
+\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
+This often leads to confusion because equations do not balance dimensionally.
+If you must use mixed units, clearly state the units for each quantity that you use in an equation.
+\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
+Spell out units when they appear in text: ``.
+.
+.
+a few henries'', not ``.
+.
+.
+a few H''.
+\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+\end{itemize}
+
+\subsection{Equations}
+Number equations consecutively. To make your 
+equations more compact, you may use the solidus (~/~), the exp function, or 
+appropriate exponents. Italicize Roman symbols for quantities and variables, 
+but not Greek symbols. Use a long dash rather than a hyphen for a minus 
+sign. Punctuate equations with commas or periods when they are part of a 
+sentence, as in:
+\begin{equation}
+a+b=\gamma\label{eq}
+\end{equation}
+
+Be sure that the 
+symbols in your equation have been defined before or immediately following 
+the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
+the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+
+\subsection{\LaTeX-Specific Advice}
+
+Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
+of ``hard'' references (e.g., \verb|(1)|). That will make it possible
+to combine sections, add equations, or change the order of figures or
+citations without having to go through the file line by line.
+
+Please don't use the \verb|{eqnarray}| equation environment. Use
+\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
+environment leaves unsightly spaces around relation symbols.
+
+Please note that the \verb|{subequations}| environment in {\LaTeX}
+will increment the main equation counter even when there are no
+equation numbers displayed. If you forget that, you might write an
+article in which the equation numbers skip from (17) to (20), causing
+the copy editors to wonder if you've discovered a new method of
+counting.
+
+{\BibTeX} does not work by magic. It doesn't get the bibliographic
+data from thin air but from .bib files. If you use {\BibTeX} to produce a
+bibliography you must send the .bib files.
+
+{\LaTeX} can't read your mind. If you assign the same label to a
+subsubsection and a table, you might find that Table I has been cross
+referenced as Table IV-B3.
+
+{\LaTeX} does not have precognitive abilities. If you put a
+\verb|\label| command before the command that updates the counter it's
+supposed to be using, the label will pick up the last counter to be
+cross referenced instead. In particular, a \verb|\label| command
+should not go before the caption of a figure or a table.
+
+Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
+will not stop equation numbers inside \verb|{array}| (there won't be
+any anyway) and it might stop a wanted equation number in the
+surrounding equation.
+
+\subsection{Some Common Mistakes}\label{SCM}
+\begin{itemize}
+\item The word ``data'' is plural, not singular.
+\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
+\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
+When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
+A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
+(A parenthetical sentence is punctuated within the parentheses.)
+\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
+\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
+\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
+\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
+\item Do not confuse ``imply'' and ``infer''.
+\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
+\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
+\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
+\end{itemize}
+An excellent style manual for science writers is \cite{b7}.
+
+\subsection{Authors and Affiliations}
+\textbf{The class file is designed for, but not limited to, six authors.} A 
+minimum of one author is required for all conference articles. Author names 
+should be listed starting from left to right and then moving down to the 
+next line. This is the author sequence that will be used in future citations 
+and by indexing services. Names should not be listed in columns nor group by 
+affiliation. Please keep your affiliations as succinct as possible (for 
+example, do not differentiate among departments of the same organization).
+
+\subsection{Identify the Headings}
+Headings, or heads, are organizational devices that guide the reader through 
+your paper. There are two types: component heads and text heads.
+
+Component heads identify the different components of your paper and are not 
+topically subordinate to each other. Examples include Acknowledgments and 
+References and, for these, the correct style to use is ``Heading 5''. Use 
+``figure caption'' for your Figure captions, and ``table head'' for your 
+table title. Run-in heads, such as ``Abstract'', will require you to apply a 
+style (in this case, italic) in addition to the style provided by the drop 
+down menu to differentiate the head from the text.
+
+Text heads organize the topics on a relational, hierarchical basis. For 
+example, the paper title is the primary text head because all subsequent 
+material relates and elaborates on this one topic. If there are two or more 
+sub-topics, the next level head (uppercase Roman numerals) should be used 
+and, conversely, if there are not at least two sub-topics, then no subheads 
+should be introduced.
+
+\subsection{Figures and Tables}
+\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
+bottom of columns. Avoid placing them in the middle of columns. Large 
+figures and tables may span across both columns. Figure captions should be 
+below the figures; table heads should appear above the tables. Insert 
+figures and tables after they are cited in the text. Use the abbreviation 
+``Fig.~\ref{fig}'', even at the beginning of a sentence.
+
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+\cline{2-4} 
+\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+\hline
+copy& More table copy$^{\mathrm{a}}$& &  \\
+\hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig1.png}}
+\caption{Example of a figure caption.}
+\label{fig}
+\end{figure}
+
+Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
+rather than symbols or abbreviations when writing Figure axis labels to 
+avoid confusing the reader. As an example, write the quantity 
+``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
+units in the label, present them within parentheses. Do not label axes only 
+with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
+\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
+quantities and units. For example, write ``Temperature (K)'', not 
+``Temperature/K''.
+
+\section*{Acknowledgment}
+
+The preferred spelling of the word ``acknowledgment'' in America is without 
+an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+acknowledgments in the unnumbered footnote on the first page.
+
+\section*{References}
+
+Please number citations consecutively within brackets . The 
+sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
+number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
+the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+
+Number footnotes separately in superscripts. Place the actual footnote at 
+the bottom of the column in which it was cited. Do not put footnotes in the 
+abstract or reference list. Use letters for table footnotes.
+
+Unless there are six authors or more give all authors' names; do not use 
+``et al.''. Papers that have not been published, even if they have been 
+submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
+that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
+Capitalize only the first word in a paper title, except for proper nouns and 
+element symbols.
+
+For papers published in translation journals, please give the English 
+citation first, followed by the original foreign-language citation \cite{b6}.
+
+\begin{thebibliography}{00}
+\bibitem{b1} Koutroulis, Eftichios, and Frede Blaabjerg.
+"A new technique for tracking the global maximum power point of PV arrays operating under partial-shading conditions." IEEE Journal of Photovoltaics 2.2 (2012): 184-190.
+\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+\bibitem{b6} Y.
+Yorozu, M.
+Hirano, K.
+Oka, and Y.
+Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
+J.
+Magn.
+Japan, vol.
+2, pp.
+740--741, August 1987 [Digests 9th Annual Conf.
+Magnetics Japan, p.
+301, 1982].
+\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\end{thebibliography}
+\vspace{12pt}
+\color{red}
+IEEE conference templates contain guidance text for composing and formatting conference papers.
+Please ensure that all template text is removed from your conference paper prior to submission to the conference.
+Failure to remove the template text from your paper may result in your paper not being published.
+
 \end{document}

### 2018-08-08 test/main.tex
re-write
write in IEEE trans style

@@
 \usepackage{stackengine}
+\usepackage{apacite}
 \usepackage[a4paper,margin=0.5in]{geometry}
@@
 But PV arrays are senstive to shading and PV cell's fault or aging.
-That means the interconnection of PV cells or modules which do not have identical properties or which experience different conditions from one another.
+That means when interconnection of PV cells or modules do no have identical properties or experience different conditions from one another.PV arrays are in mismatch condition.
+In order to avoid mismatch condition damage PV cells, we proposed an algorithm that can reconfigurate photovoltaic arrays to minimize mismatch loss.
+\\In this paper, we using non-uniform irradiance levels to represent mismatch condition and analysis the efficiency of a PV system under different shaded working condition is presented.When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maxmimum power points (MPPs) \cite{koutroulis2012new} so
+%\\The basic knowledge of this study is the traditional electrical connection implementation of PV modules on the market and modelling 
 \section{Related work}
@@
 \printbibliography
-
+\bibliographystyle{apacite}
+\bibliography{References}
 \end{document}

### 2018-08-08 main.tex
20180809

@@
 
-\\As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human.
+As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human.
 Photovoltaic (PV) energy received significant attention since it has unlimited energy and easy to be scaled up.
@@
 In order to avoid mismatch condition damage PV cells, we proposed an algorithm that can re-configurate photovoltaic arrays to minimize mismatch loss.
-\\In this paper, we using non-uniform irradiance levels to represent mismatch condition and analysis the efficiency of a PV system under different shaded working condition is presented.When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maxmimum power points (MPPs) \cite{b1}, which been genearated by turning on bypass diodes.
+
+In this paper, we using non-uniform irradiance levels to represent mismatch condition and analysis the efficiency of a PV system under different shaded working condition is presented.
+When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maxmimum power points (MPPs) \cite{b1}, which been genearated by turning on bypass diodes.
+By changing electrical connection among the panels to prevent activate bypass diodes is a recent appealing solution\cite{b2}.
+
+This procedure enables to detect panel's operating conditions, in more than two-strings, receiving different irradiance levels.
+The reconfiguration algorithm will analysis panels' working conditions and reorganizes panels into different strings by different irradiance levels.
+However, in sparse of mismatching conditions, distribution of panels among different irradiance levels are not significant.
+For that, by increasing number of strings in the PV array and using exhaustive search can be a solution\cite{b3}.
+
+The main difficulty facing the reconfiguration problem is
 
@@
 Please number citations consecutively within brackets . The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
+sentence punctuation follows the bracket. Refer simply to the reference 
 number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
@@
 "A new technique for tracking the global maximum power point of PV arrays operating under partial-shading conditions." IEEE Journal of Photovoltaics 2.2 (2012): 184-190.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+\bibitem{b2} La Manna, Damiano, et al. "Reconfigurable electrical interconnection strategies for photovoltaic arrays: A review." Renewable and Sustainable Energy Reviews 33 (2014): 412-426.
+\bibitem{b3}Storey, Jonathan, Peter R. Wilson, and Darren Bagnall. "The optimized-string dynamic photovoltaic array." IEEE Transactions on Power Electronics 29.4 (2014): 1768-1776.
 \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.

### 2018-08-09 main.tex
20180810

@@
 {\footnotesize \textsuperscript{}}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+%\thanks{Identify applicable funding agency here. If none, delete this.}
 }
@@
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}}
+\textit{name of organization (of Aff.)}}As the world of fossil energy constantly exhausted and the
+increasingly serious environmental pollution, the research and
+utilization of renewable energy and green energy have become
+maintain necessary means of survival and development of the
+human. Photovoltaic (PV) energy received significant attention
+since it has unlimited energy and easy to be scaled up. Thanks
+to extensive technology and research on photovoltaic energy
+generation, large scale photovoltaic energy generation system
+have been deployed into many practical application. But due to
+PV arrays are senstive to shading and PV cell’s fault or aging.
+That means when interconnection of PV cells or modules do
+no have identical properties or experience different conditions
+from one another. PV arrays are in mismatch condition. In
+order to avoid mismatch condition damage PV cells, we
+proposed an algorithm that can re-configurate photovoltaic
+arrays to minimize mismatch loss.
+In this paper, we using non-uniform irradiance levels to
+represent mismatch condition and analysis the efficiency of
+a PV system under different shaded working condition is
+presented. When photovoltaic arrays operating in non-uniform
+irradiance levels may present multiple local maxmimum power
+points (MPPs) [1], which been genearated by turning on
+bypass diodes. By changing electrical connection among the
+panels to prevent activate bypass diodes is a recent appealing
+solution [2].
+The main difficulty facing the reconfiguration problem is
+that some or even all panels can be subjected to partial
+shading, so there may be more than one MPP for each
+panel. Reconfiguration strategy need also consider to group
+PV modules which provided high power separately [3] [4].
+This procedure enables to detect panel’s operating con-
+ditions, in more than two-strings, receiving different irradi-
+ance levels. The reconfiguration algorithm will analysis pan-
+els’ working conditions and reorganizes panels into different
+strings by different irradiance levels. However, in sparse of
+mismatching conditions, distribution of panels among different
+irradiance levels are not significant. For that, by increasing
+number of strings in the PV array and using exhaustive
+search can be a solution [3].Another approach to optimize
+photovoltaic arrays is using genetic algorithm [5]. However,
+computing cost is too significant, and this algorithm can’t
+detect best configuration precisely.
 \and
@@
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}}
-}
+\textit{name of organization (of Aff.)}}}
 
@@
 But due to PV arrays are senstive to shading and PV cell's fault or aging.
-That means when interconnection of PV cells or modules do no have identical properties or experience different conditions from one another.PV arrays are in mismatch condition.
+That means when interconnection of PV cells or modules do no have identical properties or experience different conditions from one another.
+PV arrays are in mismatch condition.
 In order to avoid mismatch condition damage PV cells, we proposed an algorithm that can re-configurate photovoltaic arrays to minimize mismatch loss.
@@
 
+The main difficulty facing the reconfiguration problem is that some or even all panels can be subjected to partial shading, so there may be more than one MPP for each panel.
+Reconfiguration strategy need also consider to group PV modules which provided high power separately\cite{b3} \cite{b4}.
+
 This procedure enables to detect panel's operating conditions, in more than two-strings, receiving different irradiance levels.
@@
 However, in sparse of mismatching conditions, distribution of panels among different irradiance levels are not significant.
-For that, by increasing number of strings in the PV array and using exhaustive search can be a solution\cite{b3}.
+For that, by increasing number of strings in the PV array and using exhaustive search can be a solution\cite{b3}.Another approach to optimize photovoltaic arrays is using genetic algorithm\cite{b5}.
+However, computing cost is too significant, and this algorithm can't detect best configuration precisely.
 
-The main difficulty facing the reconfiguration problem is
-
-\section{Ease of Use}
-
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\section{Assumption of a PV array}
 
@@
 \bibitem{b3}Storey, Jonathan, Peter R. Wilson, and Darren Bagnall. "The optimized-string dynamic photovoltaic array." IEEE Transactions on Power Electronics 29.4 (2014): 1768-1776.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+\bibitem{b4} Storey, Jonathan P., Peter R.
+Wilson, and Darren Bagnall.
+"Improved optimization strategy for irradiance equalization in dynamic photovoltaic arrays." IEEE transactions on power electronics 28.6 (2013): 2946-2956.
+\bibitem{b5} P.
+Carotenuto, A.
+D.
+Cioppa, A.
+Marcelli, and G.
+Spagnuolo, “An evolu- tionary approach to the dynamical reconfiguration of photovoltaic fields,” Neurocomputing, vol.
+170, pp.
+393–405, 2015.
 \bibitem{b6} Y.

### 2018-08-09 main.tex
20180809-3

@@
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}}As the world of fossil energy constantly exhausted and the
-increasingly serious environmental pollution, the research and
-utilization of renewable energy and green energy have become
-maintain necessary means of survival and development of the
-human. Photovoltaic (PV) energy received significant attention
-since it has unlimited energy and easy to be scaled up. Thanks
-to extensive technology and research on photovoltaic energy
-generation, large scale photovoltaic energy generation system
-have been deployed into many practical application. But due to
-PV arrays are senstive to shading and PV cell’s fault or aging.
-That means when interconnection of PV cells or modules do
-no have identical properties or experience different conditions
-from one another. PV arrays are in mismatch condition. In
-order to avoid mismatch condition damage PV cells, we
-proposed an algorithm that can re-configurate photovoltaic
-arrays to minimize mismatch loss.
-In this paper, we using non-uniform irradiance levels to
-represent mismatch condition and analysis the efficiency of
-a PV system under different shaded working condition is
-presented. When photovoltaic arrays operating in non-uniform
-irradiance levels may present multiple local maxmimum power
-points (MPPs) [1], which been genearated by turning on
-bypass diodes. By changing electrical connection among the
-panels to prevent activate bypass diodes is a recent appealing
-solution [2].
-The main difficulty facing the reconfiguration problem is
-that some or even all panels can be subjected to partial
-shading, so there may be more than one MPP for each
-panel. Reconfiguration strategy need also consider to group
-PV modules which provided high power separately [3] [4].
-This procedure enables to detect panel’s operating con-
-ditions, in more than two-strings, receiving different irradi-
-ance levels. The reconfiguration algorithm will analysis pan-
-els’ working conditions and reorganizes panels into different
-strings by different irradiance levels. However, in sparse of
-mismatching conditions, distribution of panels among different
-irradiance levels are not significant. For that, by increasing
-number of strings in the PV array and using exhaustive
-search can be a solution [3].Another approach to optimize
-photovoltaic arrays is using genetic algorithm [5]. However,
-computing cost is too significant, and this algorithm can’t
-detect best configuration precisely.
+\textit{name of organization (of Aff.)}}
 \and
@@
 
-In this paper, we using non-uniform irradiance levels to represent mismatch condition and analysis the efficiency of a PV system under different shaded working condition is presented.
+In this paper, we using non-uniform irradiance levels to represent mismatch condition and analyzes the efficiency of a PV system under different shaded working condition is presented.
 When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maxmimum power points (MPPs) \cite{b1}, which been genearated by turning on bypass diodes.
@@
 This procedure enables to detect panel's operating conditions, in more than two-strings, receiving different irradiance levels.
-The reconfiguration algorithm will analysis panels' working conditions and reorganizes panels into different strings by different irradiance levels.
+The reconfiguration algorithm will analyzes panels' working conditions and reorganizes panels into different strings by different irradiance levels.
 However, in sparse of mismatching conditions, distribution of panels among different irradiance levels are not significant.
@@
 \section{Assumption of a PV array}
+In this paper, we using following definitions of PV arrays, modules, strings and panels.
+A PV array formed by several parallel connected PV strings, and string is several series connected PV panels.
+For a PV panel, fromed by two or three PV modules connected in series with bypass diodes.
+An equivalent connection as showd in Fig.
+1.
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig1.png}}
+\caption{Definition of PV array and internal components.}
+\label{fig}
+\end{figure}
+
+The algorithm we proposed based on following assumptions.
+
+\begin{itemize}
+\item The current versus voltage (\textit{I-V}) curve of each panel calculated by algorithm presented in \cite{b6}.
+This algorithm will analyzes panel's \textit{I-V} curve sample and coordinate to maximum or minimum power point in \textit{P-V} curve.
+\item All the panels in PV array have same number (\textit{N}) of modules.
+For particular module, using (\textit{$V_{mppn}$, $I_{mppn}$}) to identify MPP voltage and current by index \textit{n}.
+Those parameter can be directly estimated by the prosess provided in\cite{b7}.
+\end{itemize}
+
+Futhermore, it is also assumed that for each string it has same number of panels in PV array.
+Means every string in PV array have same length.
+String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
 
@@
 301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\bibitem{b7} Orozco-Gutierrez, M. L., et al. "Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on. IEEE, 2015.
+\bibitem{b8}Spagnuolo, Giovanni, et al.
+"Control of photovoltaic arrays: Dynamical reconfiguration for fighting mismatched conditions and meeting load requests." IEEE Industrial Electronics Magazine 9.1 (2015): 62-76.
+
 \end{thebibliography}

### 2018-08-13 main.tex
20180809-4
20180813

@@
 Photovoltaic (PV) energy received significant attention since it has unlimited energy and easy to be scaled up.
-Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
+Thanks to extensive technology and research onn photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
 But due to PV arrays are senstive to shading and PV cell's fault or aging.
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
+\centerline{\includegraphics{fig.png}}
 \caption{Definition of PV array and internal components.}
@@
 
-Futhermore, it is also assumed that for each string it has same number of panels in PV array.
+Furthermore, it is also assumed that for each string it has same number of panels in PV array.
 Means every string in PV array have same length.
 String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig.png}}
+\caption{Flowchart of recongfiguration algorithm.}
+\label{fig}
+\end{figure}
 
-\section{Prepare Your Paper Before Styling}
+\section{Reconfiguration Algorithm}
+The general steps of reconfiguration algorithm are presented in Fig.2.
+The first step is determine each PV modul's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array.
+Afterward, determine real number of working modules per string by applying method in \cite{b10}.
+
 Before you begin to format your paper, first write and save the content as a 
@@
 \bibitem{b7} Orozco-Gutierrez, M. L., et al. "Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on. IEEE, 2015.
-\bibitem{b8}Spagnuolo, Giovanni, et al.
+\bibitem{b8} Spagnuolo, Giovanni, et al.
 "Control of photovoltaic arrays: Dynamical reconfiguration for fighting mismatched conditions and meeting load requests." IEEE Industrial Electronics Magazine 9.1 (2015): 62-76.
+\bibitem{b9} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
+\bibitem{b10} Orozco-Gutierrez, M.
+L., et al.
+"Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on.
+IEEE, 2015.Orozco-Gutierrez, M.
+L., et al.
+"Optimized configuration of mismatched photovoltaic arrays." IEEE J.
+Photovolt 6.5 (2016): 1210-1220.
 

### 2018-08-13 main.tex
20180813-2

@@
 The first step is determine each PV modul's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array.
-Afterward, determine real number of working modules per string by applying method in \cite{b10}.
+Afterward, determine real number of working modules \textit{$Q_{MN}$}  per string by applying method in \cite{b10}.
+Next, find maximum output power by multiplying current candidates and voltage candidates which determine by \textit{$Q_{MN}$}.
 

### 2018-08-13 main.tex
20180813-03

--- 2018-08-09 main.tex
@@
 In this paper, we using non-uniform irradiance levels to represent mismatch condition and analyzes the efficiency of a PV system under different shaded working condition is presented.
-When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maxmimum power points (MPPs) \cite{b1}, which been genearated by turning on bypass diodes.
+When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maximum power points (MPPs) \cite{b1}, which been generated by turning on bypass diodes.
 By changing electrical connection among the panels to prevent activate bypass diodes is a recent appealing solution\cite{b2}.
@@
 A PV array formed by several parallel connected PV strings, and string is several series connected PV panels.
-For a PV panel, fromed by two or three PV modules connected in series with bypass diodes.
-An equivalent connection as showd in Fig.
+For a PV panel, formed by two or three PV modules connected in series with bypass diodes.
+An equivalent connection as showed in Fig.
 1.
@@
 
-Futhermore, it is also assumed that for each string it has same number of panels in PV array.
+Furthermore, it is also assumed that for each string it has same number of panels in PV array.
 Means every string in PV array have same length.
 String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig1.png}}
+\caption{Flowchart of reconfiguration algorithm.}
+\label{fig}
+\end{figure}
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\section{Reconfiguration Algorithm}
+The general steps of reconfiguration algorithm are presented in Fig.2.
+The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array.
+Afterward, determine real number of working modules \textit{$Q_{MN}$}  per string by applying method in \cite{b10}.
+Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{MN}$}.
+Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shadowing distribution among PV array.
+Then grouping panels into different shadow levels.
+Then grouping panels by different irradiance levels.
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+After this procedures is conducted for PV array, all panels will be sorted into many groups that from un-shadowed to fully shadowed group.
+However, if just simply grouping panels by shadow conditions it may cause electrical connection overhead or unable calculate optimal configuration.
+To further reconfigure PV system into a better configuration, the algorithm will proceed as follow:
+\begin{itemize}
+\item Sorting group by different irradiance levels, select panels from first group into a PV string which working on high current level.
+\item If selected panels' working modules ( \textit{$Q_{MN}^{*}$} ) less than \textit{$Q_{MN}$} , select panels from next irradiance level group.
+\item If selected panels' \textit{$Q_{MN}^{*}$} more than \textit{$Q_{MN}$}, re-select panels to adjust \textit{$Q_{MN}^{*}$} equal to \textit{$Q_{MN}$} if it is possible. 
+\end{itemize}
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
+%Before you begin to format your paper, first write and save the content as a 
+%separate text file. Complete all content and organizational editing before 
+%formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
+%proofreading, spelling and grammar.
+%
+%Keep your text and graphic files separate until after the text has been 
+%formatted and styled. Do not number text heads---{\LaTeX} will do that 
+%for you.
+%
+%\subsection{Abbreviations and Acronyms}\label{AA}
+%Define abbreviations and acronyms the first time they are used in the text, 
+%even after they have been defined in the abstract. Abbreviations such as 
+%IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
+%abbreviations in the title or heads unless they are unavoidable.
+%
+%\subsection{Units}
+%\begin{itemize}
+%\item Use either SI (MKS) or CGS as primary units.
 (SI units are encouraged.) English units may be used as secondary units (in parentheses).
 An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
+%\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
 This often leads to confusion because equations do not balance dimensionally.
 If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
+%\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
 Spell out units when they appear in text: ``.
@@
 a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
+%\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+%\end{itemize}
+%
+%\subsection{Equations}
+%Number equations consecutively. To make your 
+%equations more compact, you may use the solidus (~/~), the exp function, or 
+%appropriate exponents. Italicize Roman symbols for quantities and variables, 
+%but not Greek symbols. Use a long dash rather than a hyphen for a minus 
+%sign. Punctuate equations with commas or periods when they are part of a 
+%sentence, as in:
+%\begin{equation}
+%a+b=\gamma\label{eq}
+%\end{equation}
+%
+%Be sure that the 
+%symbols in your equation have been defined before or immediately following 
+%the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
+%the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+%
+%\subsection{\LaTeX-Specific Advice}
+%
+%Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
+%of ``hard'' references (e.g., \verb|(1)|). That will make it possible
+%to combine sections, add equations, or change the order of figures or
+%citations without having to go through the file line by line.
+%
+%Please don't use the \verb|{eqnarray}| equation environment. Use
+%\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
+%environment leaves unsightly spaces around relation symbols.
+%
+%Please note that the \verb|{subequations}| environment in {\LaTeX}
+%will increment the main equation counter even when there are no
+%equation numbers displayed. If you forget that, you might write an
+%article in which the equation numbers skip from (17) to (20), causing
+%the copy editors to wonder if you've discovered a new method of
+%counting.
+%
+%{\BibTeX} does not work by magic. It doesn't get the bibliographic
+%data from thin air but from .bib files. If you use {\BibTeX} to produce a
+%bibliography you must send the .bib files. 
+%
+%{\LaTeX} can't read your mind. If you assign the same label to a
+%subsubsection and a table, you might find that Table I has been cross
+%referenced as Table IV-B3. 
+%
+%{\LaTeX} does not have precognitive abilities. If you put a
+%\verb|\label| command before the command that updates the counter it's
+%supposed to be using, the label will pick up the last counter to be
+%cross referenced instead. In particular, a \verb|\label| command
+%should not go before the caption of a figure or a table.
+%
+%Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
+%will not stop equation numbers inside \verb|{array}| (there won't be
+%any anyway) and it might stop a wanted equation number in the
+%surrounding equation.
+%
+%\subsection{Some Common Mistakes}\label{SCM}
+%\begin{itemize}
+%\item The word ``data'' is plural, not singular.
+%\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
+%\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
 When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
@@
 (A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets . The 
-sentence punctuation follows the bracket. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+%\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
+%\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
+%\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
+%\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
+%\item Do not confuse ``imply'' and ``infer''.
+%\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
+%\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
+%\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
+%\end{itemize}
+%An excellent style manual for science writers is \cite{b7}.
+%
+%\subsection{Authors and Affiliations}
+%\textbf{The class file is designed for, but not limited to, six authors.} A 
+%minimum of one author is required for all conference articles. Author names 
+%should be listed starting from left to right and then moving down to the 
+%next line. This is the author sequence that will be used in future citations 
+%and by indexing services. Names should not be listed in columns nor group by 
+%affiliation. Please keep your affiliations as succinct as possible (for 
+%example, do not differentiate among departments of the same organization).
+%
+%\subsection{Identify the Headings}
+%Headings, or heads, are organizational devices that guide the reader through 
+%your paper. There are two types: component heads and text heads.
+%
+%Component heads identify the different components of your paper and are not 
+%topically subordinate to each other. Examples include Acknowledgments and 
+%References and, for these, the correct style to use is ``Heading 5''. Use 
+%``figure caption'' for your Figure captions, and ``table head'' for your 
+%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
+%style (in this case, italic) in addition to the style provided by the drop 
+%down menu to differentiate the head from the text.
+%
+%Text heads organize the topics on a relational, hierarchical basis. For 
+%example, the paper title is the primary text head because all subsequent 
+%material relates and elaborates on this one topic. If there are two or more 
+%sub-topics, the next level head (uppercase Roman numerals) should be used 
+%and, conversely, if there are not at least two sub-topics, then no subheads 
+%should be introduced.
+%
+%\subsection{Figures and Tables}
+%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
+%bottom of columns. Avoid placing them in the middle of columns. Large 
+%figures and tables may span across both columns. Figure captions should be 
+%below the figures; table heads should appear above the tables. Insert 
+%figures and tables after they are cited in the text. Use the abbreviation 
+%``Fig.~\ref{fig}'', even at the beginning of a sentence.
+%
+%\begin{table}[htbp]
+%\caption{Table Type Styles}
+%\begin{center}
+%\begin{tabular}{|c|c|c|c|}
+%\hline
+%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+%\cline{2-4} 
+%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+%\hline
+%copy& More table copy$^{\mathrm{a}}$& &  \\
+%\hline
+%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+%\end{tabular}
+%\label{tab1}
+%\end{center}
+%\end{table}
+%
+%\begin{figure}[htbp]
+%\centerline{\includegraphics{fig1.png}}
+%\caption{Example of a figure caption.}
+%\label{fig}
+%\end{figure}
+%
+%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
+%rather than symbols or abbreviations when writing Figure axis labels to 
+%avoid confusing the reader. As an example, write the quantity 
+%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
+%units in the label, present them within parentheses. Do not label axes only 
+%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
+%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
+%quantities and units. For example, write ``Temperature (K)'', not 
+%``Temperature/K''.
+%
+%\section*{Acknowledgment}
+%
+%The preferred spelling of the word ``acknowledgment'' in America is without 
+%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+%acknowledgments in the unnumbered footnote on the first page.
+%
+%\section*{References}
+%
+%Please number citations consecutively within brackets . The 
+%sentence punctuation follows the bracket. Refer simply to the reference 
+%number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
+%the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+%
+%Number footnotes separately in superscripts. Place the actual footnote at 
+%the bottom of the column in which it was cited. Do not put footnotes in the 
+%abstract or reference list. Use letters for table footnotes.
+%
+%Unless there are six authors or more give all authors' names; do not use 
+%``et al.''. Papers that have not been published, even if they have been 
+%submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
+%that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
+%Capitalize only the first word in a paper title, except for proper nouns and 
+%element symbols.
+%
+%For papers published in translation journals, please give the English 
+%citation first, followed by the original foreign-language citation \cite{b6}.
 
@@
 \bibitem{b7} Orozco-Gutierrez, M. L., et al. "Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on. IEEE, 2015.
-\bibitem{b8}Spagnuolo, Giovanni, et al.
+\bibitem{b8} Spagnuolo, Giovanni, et al.
 "Control of photovoltaic arrays: Dynamical reconfiguration for fighting mismatched conditions and meeting load requests." IEEE Industrial Electronics Magazine 9.1 (2015): 62-76.
+\bibitem{b9} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
+\bibitem{b10} Orozco-Gutierrez, M. L., et al. "Optimized configuration of mismatched photovoltaic arrays." IEEE J. Photovolt 6.5 (2016): 1210-1220.
 
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
+%\vspace{12pt}
+%\color{red}
+%IEEE conference templates contain guidance text for composing and formatting conference papers.
 Please ensure that all template text is removed from your conference paper prior to submission to the conference.

### 2018-08-14 main.tex
20180814

@@
 \usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsfonts}
 \usepackage{algorithmic}
@@
 \item All the panels in PV array have same number (\textit{N}) of modules.
-For particular module, using (\textit{$V_{mppn}$, $I_{mppn}$}) to identify MPP voltage and current by index \textit{n}.
+For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify MPP voltage and current by index \textit{n}.
 Those parameter can be directly estimated by the prosess provided in\cite{b7}.
@@
 
-When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}.
+When there are more than two panels connected in series, for a string MPPs is not straightforward.
+The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}.
+For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal.
+For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules \textit{$M_a$} by average MPP voltages \textit{$\bar V_{mpp}$} with $\pm$18\% error \cite{b10}.
 

### 2018-08-14 main.tex
201808015

--- 2018-08-13 main.tex
@@
 Photovoltaic (PV) energy received significant attention since it has unlimited energy and easy to be scaled up.
-Thanks to extensive technology and research onn photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
+Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
 But due to PV arrays are senstive to shading and PV cell's fault or aging.
@@
 A PV array formed by several parallel connected PV strings, and string is several series connected PV panels.
-For a PV panel, fromed by two or three PV modules connected in series with bypass diodes.
-An equivalent connection as showd in Fig.
-1.
+For a PV panel, formed by two or three PV modules connected in series with bypass diodes.
+An equivalent connection as showed in Fig.
+\ref{fig1}.
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig.png}}
+\centerline{\includegraphics{fig1.png}}
 \caption{Definition of PV array and internal components.}
-\label{fig}
+\label{fig1}
 \end{figure}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig.png}}
-\caption{Flowchart of recongfiguration algorithm.}
-\label{fig}
+\centerline{\includegraphics{fig1.png}}
+\caption{Flowchart of reconfiguration algorithm.}
+\label{fig2}
 \end{figure}
@@
 \section{Reconfiguration Algorithm}
-The general steps of reconfiguration algorithm are presented in Fig.2.
-The first step is determine each PV modul's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array.
-Afterward, determine real number of working modules \textit{$Q_{MN}$}  per string by applying method in \cite{b10}.
-Next, find maximum output power by multiplying current candidates and voltage candidates which determine by \textit{$Q_{MN}$}.
+The general steps of reconfiguration algorithm are presented in Fig.
+\ref{fig2}.
+The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array.
+When there are more than two panels connected in series, for a string MPPs is not straightforward.
+The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}.
+For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal.
+For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules (\textit{$N_a$}) by average MPP voltages (\textit{$\bar V_{mpp}$}) with $\pm$18\% error \cite{b10}.
+Afterward, determine real number of working modules (\textit{$Q_{M_n}$})  per string by applying method in \cite{b10}.
+Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}.
+Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shadowing distribution among PV array.
+Then grouping panels into different shadow levels.
+Then grouping panels by different irradiance levels.
 
+After this procedures is conducted for PV array, all panels will be sorted into many groups that from un-shadowed to fully shadowed group.
+However, if just simply grouping panels by shadow conditions it may cause electrical connection overhead or unable calculate optimal configuration.
+To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
+\begin{itemize}
+\item Sorting group by different irradiance levels, select panels from first group into a PV string which working on high current level.
+\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
+\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
+\end{itemize}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig1.png}}
+\caption{Flowchart of reconfiguration algorithm.}
+\label{fig3}
+\end{figure}
+
+This algorithm will better understood by applying to shadow condition showed in Fig.
+\ref{fig3}.
+This PV system is composed with 9 PV panels connected into 3 strings as showed in Fig.\ref{fig3}.
+Irradiance levels, \textit{$I_{mpp}$} and \textit{$V_{mpp}$} of each module are given in Table \ref{tab}
+
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+\cline{2-4} 
+\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+\hline
+copy& More table copy$^{\mathrm{a}}$& &  \\
+\hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\end{tabular}
+\label{tab}
+\end{center}
+\end{table}
+The example refer to a three-strings PV array, each string contain with 3 panels, each one made of three identical PV modules (\textit{N}=3).
+In this example, it is assumed that input range of DC-DC converter and MPPT device defined by \textit{$V_{min}$} = 200V and \textit{$V_{max}$} = 500V.
+MPP current candidates and MPP voltage candidates are present in ( \ref{e1} ) and ( \ref{e2} ), respectively.
+Additional, number of real working module at MPP current candidates are given in ( \ref{e3} ).
+\begin{equation}
+\begin{aligned}
+\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
+\end{aligned}
+\end{equation}
+\begin{equation}
+\begin{aligned}
+\textit{$V_{mpp_n}$} = [&12,4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
+\end{aligned}
+\end{equation}
+\begin{equation}
+\begin{aligned}
+\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
+\end{aligned}
+\end{equation}
+
+Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%.
+Though procedure of algorithm, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
+Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead.
+In order to reduce electrical connection simulation time, replacement and feasibility check will be approved.
+
+\vspace{100pt}
 Before you begin to format your paper, first write and save the content as a 
@@
 \bibitem{b9} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
-\bibitem{b10} Orozco-Gutierrez, M.
-L., et al.
-"Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on.
-IEEE, 2015.Orozco-Gutierrez, M.
-L., et al.
-"Optimized configuration of mismatched photovoltaic arrays." IEEE J.
-Photovolt 6.5 (2016): 1210-1220.
+\bibitem{b10} Orozco-Gutierrez, M. L., et al. "Optimized configuration of mismatched photovoltaic arrays." IEEE J. Photovolt 6.5 (2016): 1210-1220.
 
 \end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
+%\vspace{12pt}
+%\color{red}
+%IEEE conference templates contain guidance text for composing and formatting conference papers.
 Please ensure that all template text is removed from your conference paper prior to submission to the conference.

### 2018-08-15 main.tex
20180815-01

@@
 Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shadowing distribution among PV array.
-Then grouping panels into different shadow levels.
-Then grouping panels by different irradiance levels.
+Then grouping panels into different shadow distribution.
 
-After this procedures is conducted for PV array, all panels will be sorted into many groups that from un-shadowed to fully shadowed group.
-However, if just simply grouping panels by shadow conditions it may cause electrical connection overhead or unable calculate optimal configuration.
+After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group.
+However, if just simply grouping panels by shadow distribution conditions it may cause electrical connection overhead or unable calculate optimal configuration.
 To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
 \begin{itemize}
-\item Sorting group by different irradiance levels, select panels from first group into a PV string which working on high current level.
+\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
 \item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
@@
 
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig1.png}}
+\caption{Flowchart of reconfiguration algorithm.}
+\label{fig4}
+\end{figure}
+
 Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%.
 Though procedure of algorithm, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
+And PV array are organized as Fig \ref{fig4}
 Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead.
 In order to reduce electrical connection simulation time, replacement and feasibility check will be approved.
+
+Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string.
+Firstly, selecting panels for high current string, string three.
+According to Table \ref{tab}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A.
+Those four panel can provide 4 PV module working at 3A and meet requirement of \textit{$Q_{M_n}$}.
+Because on extra panel can provide module  working on 3A, no replacement will be approved.
+Means no further improvement for configuration of string three.
+Then select panel for string two, Panel 4 and Panel 8 will be selected, but this configuration is not optimized.
+Selected panels provide 5 modules able to work at 2A, satisfy requirement of \textit{$Q_{M_n}$} $\ge$ 4, but one module more than requirement.
+The process will replace Panel 4 by Panel 1 that provide just 4 modules working at 2A.
+Configuration for string two are Panel 8 and Panel 1.
+At last, select panels for string one.
+Panel 4 to Panel 6 are selected, they can provide 5 modules working at 2A satisfy requirement.
 

### 2018-08-15 main.tex
20180815-2

--- 2018-08-14 main.tex
@@
 \usepackage{xcolor}
+\usepackage{graphicx}
+\usepackage{subfigure}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\section{Assumption of a PV array}
+\section{Assumption of a PV array} \label{assum}
 In this paper, we using following definitions of PV arrays, modules, strings and panels.
@@
 An equivalent connection as showed in Fig.
-1.
+\ref{fig2}.
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
+\centerline{\includegraphics{fig2.png}}
 \caption{Definition of PV array and internal components.}
-\label{fig}
+\label{fig2}
 \end{figure}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
+\centerline{\includegraphics{fig2.png}}
 \caption{Flowchart of reconfiguration algorithm.}
-\label{fig}
+\label{fig2}
 \end{figure}
@@
 \section{Reconfiguration Algorithm}
-The general steps of reconfiguration algorithm are presented in Fig.2.
+The general steps of reconfiguration algorithm are presented in Fig.
+\ref{fig2}.
 The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array.
-Afterward, determine real number of working modules \textit{$Q_{MN}$}  per string by applying method in \cite{b10}.
-Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{MN}$}.
-Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shadowing distribution among PV array.
-Then grouping panels into different shadow levels.
-Then grouping panels by different irradiance levels.
-
-After this procedures is conducted for PV array, all panels will be sorted into many groups that from un-shadowed to fully shadowed group.
-However, if just simply grouping panels by shadow conditions it may cause electrical connection overhead or unable calculate optimal configuration.
-To further reconfigure PV system into a better configuration, the algorithm will proceed as follow:
-\begin{itemize}
-\item Sorting group by different irradiance levels, select panels from first group into a PV string which working on high current level.
-\item If selected panels' working modules ( \textit{$Q_{MN}^{*}$} ) less than \textit{$Q_{MN}$} , select panels from next irradiance level group.
-\item If selected panels' \textit{$Q_{MN}^{*}$} more than \textit{$Q_{MN}$}, re-select panels to adjust \textit{$Q_{MN}^{*}$} equal to \textit{$Q_{MN}$} if it is possible. 
-\end{itemize}
-
 When there are more than two panels connected in series, for a string MPPs is not straightforward.
@@
 For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal.
-For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules \textit{$M_a$} by average MPP voltages \textit{$\bar V_{mpp}$} with $\pm$18\% error \cite{b10}.
+For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules (\textit{$N_a$}) by average MPP voltages (\textit{$\bar V_{mpp}$}) with $\pm$18\% error \cite{b10}.
+Afterward, determine real number of working modules (\textit{$Q_{M_n}$})  per string by applying method in \cite{b10}.
+Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}.
+Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shadowing distribution among PV array.
+Then grouping panels into different shadow distribution.
 
+After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group.
+However, if just simply grouping panels by shadow distribution conditions it may cause electrical connection overhead or unable calculate optimal configuration.
+To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
+\begin{itemize}
+\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
+\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
+\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
+\end{itemize}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig2.png}}
+\caption{Flowchart of reconfiguration algorithm.}
+\label{fig3}
+\end{figure}
+
+This algorithm will better understood by applying to shadow condition showed in Fig.
+\ref{fig3}.
+This PV system is composed with 9 PV panels connected into 3 strings as showed in Fig.\ref{fig3}.
+Irradiance levels, \textit{$I_{mpp}$} and \textit{$V_{mpp}$} of each module are given in Table \ref{tab}
+
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+\cline{2-4} 
+\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+\hline
+copy& More table copy$^{\mathrm{a}}$& &  \\
+\hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\end{tabular}
+\label{tab}
+\end{center}
+\end{table}
+The example refer to a three-strings PV array, each string contain with 3 panels, each one made of three identical PV modules (\textit{N}=3).
+In this example, it is assumed that input range of DC-DC converter and MPPT device defined by \textit{$V_{min}$} = 200V and \textit{$V_{max}$} = 500V.
+MPP current candidates and MPP voltage candidates are present in ( \ref{e1} ) and ( \ref{e2} ), respectively.
+Additional, number of real working module at MPP current candidates are given in ( \ref{e3} ).
+\begin{equation}
+\begin{aligned}
+\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
+\end{aligned}
+\end{equation}
+\begin{equation}
+\begin{aligned}
+\textit{$V_{mpp_n}$} = [&12,4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
+\end{aligned}
+\end{equation}
+\begin{equation}
+\begin{aligned}
+\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
+\end{aligned}
+\end{equation}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig2.png}}
+\caption{Flowchart of reconfiguration algorithm.}
+\label{fig4}
+\end{figure}
+
+Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%.
+Though procedure of algorithm, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
+And PV array are organized as Fig \ref{fig4}
+Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead.
+In order to reduce electrical connection simulation time, replacement and feasibility check will be approved.
+
+Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string.
+Firstly, selecting panels for high current string, string three.
+According to Table \ref{tab}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A.
+Those four panel can provide 4 PV module working at 3A and meet requirement of \textit{$Q_{M_n}$}.
+Because on extra panel can provide module  working on 3A, no replacement will be approved.
+Means no further improvement for configuration of string three.
+Then select panel for string two, Panel 4 and Panel 8 will be selected, but this configuration is not optimized.
+Selected panels provide 5 modules able to work at 2A, satisfy requirement of \textit{$Q_{M_n}$} $\ge$ 4, but one module more than requirement.
+The process will replace Panel 4 by Panel 1 that provide just 4 modules working at 2A.
+Configuration for string two are Panel 8 and Panel 1.
+At last, select panels for string one.
+Panel 4, Panel 5, Panel 6 are selected, they can provide 5 modules working at 2A that satisfy requirement.
+For configuration on string one due to it is the last string to process and meet requirement, in order to reduce computing time replacement will not be approved.
+Configuration of MPP candidate \{2, 2, 3\} are \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}.
+As described in section \ref{assum}, each string have identical length and Panel 3 not been used in any configuration.
+So optimized configuration for this MPP candidate are: \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8, Panel 3\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}.
+The MPP values of this configuration calculated by multiplay string voltage and current equal to 347.2W are put into evidence.
+
+For the third MPP candidate, as same calculating procedure as fourth MPP candidate, optimized configuration for MPP candidate \{2, 2, 2\} are: \textit{St} 1:\{Panel 4,Panel 8, Panel 3\}, \textit{St} 2: \{Panel 1, Panel 2, Panel 6\}, \textit{St} 3: \{Panel 5, Panel 7, Panel 9\}.
+
+The first MPP candidate \{0.5, 0.5, 2\}, after replacement string three contain four panels, \{Panel 4, Panel 8, Panel 1, Panel 2\} but it is over maximum string length of this PV array.
+Also for MPP candidate \{0.5, 2, 2\}, there are no configuration can't provide 7 modules working 
+on three different string at 0.5A, 2A, 2A, respectively.
+
+\section{evaluation of optimization algorithm}
+%\subsection{Verification of the Proposed algorithm}
+This section verifies the effectiveness of proposed algorithm using LTspice simulation.
+With pilot example presented in last section, first shading scenario as showed in Fig.\ref{fig5a}.
+To minimize power loss, the proposed algorithm, as described, is applied to reconfigure the system.
+The resulting configuration is depicted in Fig.\ref{fig5b}.
+
+\begin{figure}[htbp]
+\begin{minipage}[t]{0.5\linewidth}
+\centerline{\includegraphics{fig2.png}}
+\caption{(a)}
+\label{fig5a}
+%\end{minipage}%
+%\begin{minipage}[t]{0.5\linewidth}
+\centerline{\includegraphics{fig2.png}}
+\caption{(b)}
+\label{fig5b}
+\end{minipage}
+\end{figure}
+
+As shown, working module on each string are large or equal than required \textit{$Q_{M_n}$}, which means mismatched power loss are minimized.
+The \textit{P-V} curve for this PV array before and after reconfiguration are showed in Fig.\ref{fig6}.
+It can be seen that after reconfiguration maximum power (!!!!!!!!!!
+W) are significantly higher than before reconfiguration maximum power (!!!!!!!!W).
+
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig2.png}}
+\caption{Flowchart of reconfiguration algorithm.}
+\label{fig6}
+\end{figure}
+The simulations were performed using an Intel i7-4770 3.2-Ghz processor and 32.0 GB of RAM memory.
+The calculation time used by the proposed estimation method was 165.2 ms, which is significantly lower than the 57 h, 57 m, and 55 s needed by the exhaustive search algorithm.
+\section{conclusions}
+
+%\begin{figure}
+%\centering
+%\subfigure[the first subfigure]{
+%\begin{minipage}[b]{0.2\textwidth}
+%\includegraphics[width=1\textwidth]{fig2.png} \\
+%\includegraphics[width=1\textwidth]{fig2.png}
+%\end{minipage}
+%}
+%\subfigure[the second subfigure]{
+%\begin{minipage}[b]{0.2\textwidth}fig2
+%\includegraphics[width=1\textwidth]{fig2.png} \\
+%\includegraphics[width=1\textwidth]{fig2.png}
+%\end{minipage}
+%}
+%\end{figure}
+
+%\vspace{100pt}
 %Before you begin to format your paper, first write and save the content as a 
@@
 %\begin{figure}[htbp]
-%\centerline{\includegraphics{fig1.png}}
+%\centerline{\includegraphics{fig2.png}}
 %\caption{Example of a figure caption.}

### 2018-08-16 main.tex
20180816
almost finished
missing abstract, figure, table, author

@@
 
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+\cline{2-4} 
+\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+\hline
+copy& More table copy$^{\mathrm{a}}$& &  \\
+\hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\end{tabular}
+\label{tab2}
+\end{center}
+\end{table}
+
 Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string.
 Firstly, selecting panels for high current string, string three.
-According to Table \ref{tab}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A.
+According to Table \ref{tab2}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A.
 Those four panel can provide 4 PV module working at 3A and meet requirement of \textit{$Q_{M_n}$}.
@@
 \end{figure}
+The computational time required to find the best configuration in the proposed and existed method is also compared and summarized in Table \ref{tab3}.
+As shown in Table \ref{tab3}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm and methods described in \cite{b10} \cite{b11} \cite{b12}.
+
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+\cline{2-4} 
+\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+\hline
+copy& More table copy$^{\mathrm{a}}$& &  \\
+\hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\end{tabular}
+\label{tab3}
+\end{center}
+\end{table}
+
 The simulations were performed using an Intel i7-4770 3.2-Ghz processor and 32.0 GB of RAM memory.
@@
 \section{conclusions}
-
+The existing PV reconfiguration methods either have high accuracy but suffer from long computational time such as exhausted searching algorithm or GA, or they have short computational time but do not guarantee the best configuration as described in \cite{b10} \cite{b11} \cite{b12}.
+This paper proposed a new PV system reconfiguration algorithm with high accuracy and less computational time.
+Proposed algorithm's effectiveness has been validated using LTspice simulation.
+The algorithm was tested though un-uniform shadow distribution among PV array and shows its effectiveness in finding optimal configuration.
+The proposed algorithm also compared with existed method in terms of accuracy and computational time.
+The result shows that proposed algorithm has high accuracy and less computational time.
 %\begin{figure}
@@
 \bibitem{b10} Orozco-Gutierrez, M. L., et al. "Optimized configuration of mismatched photovoltaic arrays." IEEE J. Photovolt 6.5 (2016): 1210-1220.
+\bibitem{b11} El-Dein, MZ Shams, Mehrdad Kazerani, and M. M. A. Salama. "Optimal photovoltaic array reconfiguration to reduce partial shading losses." IEEE Trans. Sustain. Energy 4.1 (2013): 145-153.
+\bibitem{b12} Storey, Jonathan P., Peter R.
+Wilson, and Darren Bagnall.
+"Improved optimization strategy for irradiance equalization in dynamic photovoltaic arrays." IEEE transactions on power electronics 28.6 (2013): 2946-2956.
 

### 2018-08-16 main.tex
20180816

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+%% \usepackage{subfigure}
+\usepackage{subfig}
+%% \usepackage{subcaption}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{document}
-
-\title{Photovoltaic System Reconfiguration strategy for mismatch condition\\
+\title{Photovoltaic System Reconfiguration strategy foer mismatch condition\\
 {\footnotesize \textsuperscript{}}
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+  Power generation efficiency of photovoltaic(PV) system reduced significantly under partial shading or solar cell damage etc.
+conditions.
+Which affected of turned on bypass diode.
+These efficiency loss in the form of mismatch losses.
+Using reconfiguration technology to reconfigure electrical connection, which, changing series or parallel connetion among PV panel can minimize mismatch losses.
+However existed reconfiguration methods such as exhaustive search or GA need very long computing time to find best configuration.
+This paper proposed an reconfiguration strategy that find optimal configuration among mismatched PV array in a very less computational time.
+This algorithm is very light and suitble for embedded device.
+The results show that compare with existed reconfiguration method under non-uniform shadow scenario proposed algorithm computes an optimized configuration with less computational time and very high accuracy.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+  Photovoltaic system, mismathed power loss, reconfiguration, dynamical reconfiguration.
 \end{IEEEkeywords}
@@
 An equivalent connection as showed in Fig.
-\ref{fig2}.
+\ref{fig1}.
 \begin{figure}[htbp]
@@
 \caption{Definition of PV array and internal components.}
-\label{fig2}
+\label{fig1}
 \end{figure}
@@
 Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}.
-Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shadowing distribution among PV array.
+Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shading distribution among PV array.
 Then grouping panels into different shadow distribution.
@@
 \centerline{\includegraphics{fig2.png}}
-\caption{Flowchart of reconfiguration algorithm.}
+\caption{An example of un-uniform shadowed PV array.}
 \label{fig3}
@@
 This PV system is composed with 9 PV panels connected into 3 strings as showed in Fig.\ref{fig3}.
-Irradiance levels, \textit{$I_{mpp}$} and \textit{$V_{mpp}$} of each module are given in Table \ref{tab}
+Irradiance levels, \textit{$I_{mpp}$} and \textit{$V_{mpp}$} of each module are given in Table \ref{tab1}.
 
@@
 \end{tabular}
-\label{tab}
+\label{tab1}
 \end{center}
@@
 \centerline{\includegraphics{fig2.png}}
-\caption{Flowchart of reconfiguration algorithm.}
+\caption{Organized PV array after first part of Algorithm.}
 \label{fig4}
@@
 Though procedure of algorithm, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
-And PV array are organized as Fig \ref{fig4}
+And PV array are organized as Fig.\ref{fig4}
 Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead.
@@
 
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab2}
-\end{center}
-\end{table}
+%% \begin{table}[htbp]
+%% \caption{Table Type Styles}
+%% \begin{center}
+%% \begin{tabular}{|c|c|c|c|}
+%% \hline
+%% \textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+%% \cline{2-4} 
+%% \textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+%% \hline
+%% copy& More table copy$^{\mathrm{a}}$& &  \\
+%% \hline
+%% \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+%% \end{tabular}
+%% \label{tab2}
+%% \end{center}
+%% \end{table}
 
@@
 Firstly, selecting panels for high current string, string three.
-According to Table \ref{tab2}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A.
+According to Table \ref{tab1}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A.
 Those four panel can provide 4 PV module working at 3A and meet requirement of \textit{$Q_{M_n}$}.
@@
 This section verifies the effectiveness of proposed algorithm using LTspice simulation.
-With pilot example presented in last section, first shading scenario as showed in Fig.\ref{fig5a}.
+With pilot example presented in last section, shading scenario as showed in Fig.\ref{fig5a}.
 To minimize power loss, the proposed algorithm, as described, is applied to reconfigure the system.
-The resulting configuration is depicted in Fig.\ref{fig5b}.
+The resulting configuration is depicted in Fig.\ref{fig5b} and Fig.\ref{fig5c}.
+\begin{figure}[H]
+\centering
 
-\begin{figure}[htbp]
-\begin{minipage}[t]{0.5\linewidth}
-\centerline{\includegraphics{fig2.png}}
-\caption{(a)}
+\subfloat[]{
 	\label{fig5a}
-%\end{minipage}%
-%\begin{minipage}[t]{0.5\linewidth}
-\centerline{\includegraphics{fig2.png}}
-\caption{(b)}
+	\includegraphics{fig2.png} }
+
+\subfloat[]{
 	\label{fig5b}
-\end{minipage}
+	\includegraphics{fig2.png} }
+
+\subfloat[]{
+	\label{fig5c}
+	\includegraphics{fig2.png}}
+
+\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfigurationfor MPP candidate \{2, 2, 3\} and (c) MPP candidate \{2, 2, 2\}} 
 \end{figure}
+
+%% \begin{figure}[htbp]            
+%% \begin{minipage}[t]{0.5\linewidth}
+%% \centerline{\includegraphics{fig2.png}}
+%% \caption{(a)}
+%% \label{fig5a}
+%% %\end{minipage}%
+%% %\begin{minipage}[t]{0.5\linewidth}
+%% \centerline{\includegraphics{fig2.png}}
+%% \caption{(b)}
+%% \label{fig5b}
+%% \end{minipage}
+%% \end{figure}
 
@@
 \centerline{\includegraphics{fig2.png}}
-\caption{Flowchart of reconfiguration algorithm.}
+\caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}
 \label{fig6}

### 2018-08-16 main.tex
some modify
missing figure, author
Unlayout version

@@
 Using reconfiguration technology to reconfigure electrical connection, which, changing series or parallel connetion among PV panel can minimize mismatch losses.
-However existed reconfiguration methods such as exhaustive search or GA need very long computing time to find best configuration.
+However existed reconfiguration methods such as exhaustive search or Genetic algorithm(GA) need very long computing time to find best configuration.
 This paper proposed an reconfiguration strategy that find optimal configuration among mismatched PV array in a very less computational time.
@@
 For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules (\textit{$N_a$}) by average MPP voltages (\textit{$\bar V_{mpp}$}) with $\pm$18\% error \cite{b10}.
-Afterward, determine real number of working modules (\textit{$Q_{M_n}$})  per string by applying method in \cite{b10}.
+Afterward, determine real number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates by applying method in \cite{b10}.
 Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}.

### 2018-08-16 main.tex
20180816

@@
 \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{cite}
@@
 \title{Photovoltaic System Reconfiguration strategy foer mismatch condition\\
-{\footnotesize \textsuperscript{}}
-%\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+{\footnotesize \textsuperscript{}}}
 
@@
 
-%% \begin{table}[htbp]
-%% \caption{Table Type Styles}
-%% \begin{center}
-%% \begin{tabular}{|c|c|c|c|}
-%% \hline
-%% \textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-%% \cline{2-4} 
-%% \textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-%% \hline
-%% copy& More table copy$^{\mathrm{a}}$& &  \\
-%% \hline
-%% \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-%% \end{tabular}
-%% \label{tab2}
-%% \end{center}
-%% \end{table}
-
 Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string.
@@
 It can be seen that after reconfiguration maximum power (!!!!!!!!!!
-W) are significantly higher than before reconfiguration maximum power (!!!!!!!!W).
+W and !!!!!!W) are significantly higher than before reconfiguration maximum power (!!!!!!!!W).
 
@@
 
-The simulations were performed using an Intel i7-4770 3.2-Ghz processor and 32.0 GB of RAM memory.
-The calculation time used by the proposed estimation method was 165.2 ms, which is significantly lower than the 57 h, 57 m, and 55 s needed by the exhaustive search algorithm.
+%The simulations were performed using an Intel i7-4770 3.2-Ghz processor with 32.0 GB of RAM memory. 
+The calculation time used by the proposed algorithm was !!!!!
+ms, which is significantly lower compared with exhaustive search (!!!!!!!time) and accuracy are much higher than methods proposed in \cite{b11} \cite{b12}.
 \section{conclusions}
@@
 The result shows that proposed algorithm has high accuracy and less computational time.
-%\begin{figure}
-%\centering
-%\subfigure[the first subfigure]{
-%\begin{minipage}[b]{0.2\textwidth}
-%\includegraphics[width=1\textwidth]{fig2.png} \\
-%\includegraphics[width=1\textwidth]{fig2.png}
-%\end{minipage}
-%}
-%\subfigure[the second subfigure]{
-%\begin{minipage}[b]{0.2\textwidth}fig2
-%\includegraphics[width=1\textwidth]{fig2.png} \\
-%\includegraphics[width=1\textwidth]{fig2.png}
-%\end{minipage}
-%}
-%\end{figure}
-
-%\vspace{100pt}
-%Before you begin to format your paper, first write and save the content as a 
-%separate text file. Complete all content and organizational editing before 
-%formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-%proofreading, spelling and grammar.
-%
-%Keep your text and graphic files separate until after the text has been 
-%formatted and styled. Do not number text heads---{\LaTeX} will do that 
-%for you.
-%
-%\subsection{Abbreviations and Acronyms}\label{AA}
-%Define abbreviations and acronyms the first time they are used in the text, 
-%even after they have been defined in the abstract. Abbreviations such as 
-%IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-%abbreviations in the title or heads unless they are unavoidable.
-%
-%\subsection{Units}
-%\begin{itemize}
-%\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-%\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-%\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-%\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-%\end{itemize}
-%
-%\subsection{Equations}
-%Number equations consecutively. To make your 
-%equations more compact, you may use the solidus (~/~), the exp function, or 
-%appropriate exponents. Italicize Roman symbols for quantities and variables, 
-%but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-%sign. Punctuate equations with commas or periods when they are part of a 
-%sentence, as in:
-%\begin{equation}
-%a+b=\gamma\label{eq}
-%\end{equation}
-%
-%Be sure that the 
-%symbols in your equation have been defined before or immediately following 
-%the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-%the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-%
-%\subsection{\LaTeX-Specific Advice}
-%
-%Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-%of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-%to combine sections, add equations, or change the order of figures or
-%citations without having to go through the file line by line.
-%
-%Please don't use the \verb|{eqnarray}| equation environment. Use
-%\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-%environment leaves unsightly spaces around relation symbols.
-%
-%Please note that the \verb|{subequations}| environment in {\LaTeX}
-%will increment the main equation counter even when there are no
-%equation numbers displayed. If you forget that, you might write an
-%article in which the equation numbers skip from (17) to (20), causing
-%the copy editors to wonder if you've discovered a new method of
-%counting.
-%
-%{\BibTeX} does not work by magic. It doesn't get the bibliographic
-%data from thin air but from .bib files. If you use {\BibTeX} to produce a
-%bibliography you must send the .bib files. 
-%
-%{\LaTeX} can't read your mind. If you assign the same label to a
-%subsubsection and a table, you might find that Table I has been cross
-%referenced as Table IV-B3. 
-%
-%{\LaTeX} does not have precognitive abilities. If you put a
-%\verb|\label| command before the command that updates the counter it's
-%supposed to be using, the label will pick up the last counter to be
-%cross referenced instead. In particular, a \verb|\label| command
-%should not go before the caption of a figure or a table.
-%
-%Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-%will not stop equation numbers inside \verb|{array}| (there won't be
-%any anyway) and it might stop a wanted equation number in the
-%surrounding equation.
-%
-%\subsection{Some Common Mistakes}\label{SCM}
-%\begin{itemize}
-%\item The word ``data'' is plural, not singular.
-%\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-%\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-%\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-%\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-%\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-%\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-%\item Do not confuse ``imply'' and ``infer''.
-%\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-%\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-%\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-%\end{itemize}
-%An excellent style manual for science writers is \cite{b7}.
-%
-%\subsection{Authors and Affiliations}
-%\textbf{The class file is designed for, but not limited to, six authors.} A 
-%minimum of one author is required for all conference articles. Author names 
-%should be listed starting from left to right and then moving down to the 
-%next line. This is the author sequence that will be used in future citations 
-%and by indexing services. Names should not be listed in columns nor group by 
-%affiliation. Please keep your affiliations as succinct as possible (for 
-%example, do not differentiate among departments of the same organization).
-%
-%\subsection{Identify the Headings}
-%Headings, or heads, are organizational devices that guide the reader through 
-%your paper. There are two types: component heads and text heads.
-%
-%Component heads identify the different components of your paper and are not 
-%topically subordinate to each other. Examples include Acknowledgments and 
-%References and, for these, the correct style to use is ``Heading 5''. Use 
-%``figure caption'' for your Figure captions, and ``table head'' for your 
-%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-%style (in this case, italic) in addition to the style provided by the drop 
-%down menu to differentiate the head from the text.
-%
-%Text heads organize the topics on a relational, hierarchical basis. For 
-%example, the paper title is the primary text head because all subsequent 
-%material relates and elaborates on this one topic. If there are two or more 
-%sub-topics, the next level head (uppercase Roman numerals) should be used 
-%and, conversely, if there are not at least two sub-topics, then no subheads 
-%should be introduced.
-%
-%\subsection{Figures and Tables}
-%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-%bottom of columns. Avoid placing them in the middle of columns. Large 
-%figures and tables may span across both columns. Figure captions should be 
-%below the figures; table heads should appear above the tables. Insert 
-%figures and tables after they are cited in the text. Use the abbreviation 
-%``Fig.~\ref{fig}'', even at the beginning of a sentence.
-%
-%\begin{table}[htbp]
-%\caption{Table Type Styles}
-%\begin{center}
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-%\cline{2-4} 
-%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-%\hline
-%copy& More table copy$^{\mathrm{a}}$& &  \\
-%\hline
-%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-%\end{tabular}
-%\label{tab1}
-%\end{center}
-%\end{table}
-%
-%\begin{figure}[htbp]
-%\centerline{\includegraphics{fig2.png}}
-%\caption{Example of a figure caption.}
-%\label{fig}
-%\end{figure}
-%
-%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-%rather than symbols or abbreviations when writing Figure axis labels to 
-%avoid confusing the reader. As an example, write the quantity 
-%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-%units in the label, present them within parentheses. Do not label axes only 
-%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-%quantities and units. For example, write ``Temperature (K)'', not 
-%``Temperature/K''.
-%
-%\section*{Acknowledgment}
-%
-%The preferred spelling of the word ``acknowledgment'' in America is without 
-%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-%acknowledgments in the unnumbered footnote on the first page.
-%
-%\section*{References}
-%
-%Please number citations consecutively within brackets . The 
-%sentence punctuation follows the bracket. Refer simply to the reference 
-%number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-%the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-%
-%Number footnotes separately in superscripts. Place the actual footnote at 
-%the bottom of the column in which it was cited. Do not put footnotes in the 
-%abstract or reference list. Use letters for table footnotes.
-%
-%Unless there are six authors or more give all authors' names; do not use 
-%``et al.''. Papers that have not been published, even if they have been 
-%submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-%that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-%Capitalize only the first word in a paper title, except for proper nouns and 
-%element symbols.
-%
-%For papers published in translation journals, please give the English 
-%citation first, followed by the original foreign-language citation \cite{b6}.
 
@@
 \end{thebibliography}
-%\vspace{12pt}
-%\color{red}
-%IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
 \end{document}

### 2018-08-20 main.tex
add figure
add fig 2

@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig2.png}}
+\centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
 \caption{Definition of PV array and internal components.}
@@
 The algorithm we proposed based on following assumptions.
-
 \begin{itemize}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig2.png}}
+\centerline{\includegraphics[width=8cm]{paper-fig2.png}}
 \caption{Flowchart of reconfiguration algorithm.}
@@
 \end{itemize}
-
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig2.png}}
+\centerline{\includegraphics[width=6.2cm]{paper-fig3.png}}
 \caption{An example of un-uniform shadowed PV array.}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig2.png}}
+\centerline{\includegraphics[width=8cm]{paper-fig4.png}}
 \caption{Organized PV array after first part of Algorithm.}
@@
 The resulting configuration is depicted in Fig.\ref{fig5b} and Fig.\ref{fig5c}.
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 	\label{fig5a}
-	\includegraphics{fig2.png} }
+	\includegraphics[width=5cm]{paper-fig5(a).png} }
 
@@
 	\label{fig5b}
-	\includegraphics{fig2.png} }
+	\includegraphics[width=5cm]{paper-fig5(b).png} }
 
@@
 	\label{fig5c}
-	\includegraphics{fig2.png}}
+	\includegraphics[width=5cm]{paper-fig5(c).png}}
 
-\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfigurationfor MPP candidate \{2, 2, 3\} and (c) MPP candidate \{2, 2, 2\}} 
+\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 3\} and (c) MPP candidate \{2, 2, 2\}} 
 \end{figure}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig2.png}}
+\centerline{\includegraphics[width=6.2cm]{fig2.png}}
 \caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}

### 2018-08-21 main.tex
add figure
only missing test data

@@
 
+%\begin{table}[]
+%\begin{tabular}{cccc}
+%\multicolumn{4}{c}{Data of partial-shading PV array} \\
+%\\ \hline \hline
+%Panels   & Vmpp(V)  & Impp (A)             & MPP(w)  \\ \hline
+%P1       &          & {[}0, 0.5, 2{]}      &         \\
+%P2       &          & {[}0.5, 3, 3{]}      &         \\
+%P3       &          & {[}0.5, 0.5, 0.5{]}  &         \\
+%P4       &          & {[}0, 2, 2{]}        &         \\
+%P5       &          & {[}0, 0.5, 2{]}      &         \\
+%P6       &          & {[}0.5, 2, 2{]}      &         \\
+%P7       &          & {[}0.5, 2, 3{]}      &         \\
+%P8       &          & {[}2, 2, 2{]}        &         \\
+%P9       &          & {[}0.5, 2, 3{]}      &        
+%\end{tabular}
+%\end{table}
+
 \begin{table}[htbp]
-\caption{Table Type Styles}
+\caption{}
 \begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\begin{tabular}{cccc}
+\multicolumn{4}{c}{DATA OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
+Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
+P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
+P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
+P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
+P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}0, 22.8, 22.8{]}    \\
+P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
+P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
+P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
+P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
+P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
 \end{tabular}
@@
 \end{table}
+
 The example refer to a three-strings PV array, each string contain with 3 panels, each one made of three identical PV modules (\textit{N}=3).
@@
 \begin{aligned}
-\textit{$V_{mpp_n}$} = [&12,4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
+\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
 \end{aligned}
@@
 	\label{fig5a}
-	\includegraphics[width=5cm]{paper-fig5(a).png} }
-
+	\includegraphics[width=5cm]{paper-fig5(a).png} } \\
 \subfloat[]{
 	\label{fig5b}
-	\includegraphics[width=5cm]{paper-fig5(b).png} }
-
+	\includegraphics[width=5cm]{paper-fig5(b).png} } \\
 \subfloat[]{
 	\label{fig5c}
-	\includegraphics[width=5cm]{paper-fig5(c).png}}
-
+	\includegraphics[width=5cm]{paper-fig5(c).png}} \\
 \caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 3\} and (c) MPP candidate \{2, 2, 2\}} 
@@
 \end{figure}
-The computational time required to find the best configuration in the proposed and existed method is also compared and summarized in Table \ref{tab3}.
+The computational time required to find the best configuration in the proposed and existed method is also compared and summarized in Table \ref{tab2}.
 As shown in Table \ref{tab3}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm and methods described in \cite{b10} \cite{b11} \cite{b12}.
@@
 \begin{table}[htbp]
-\caption{Table Type Styles}
+\caption{}
 \begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\begin{tabular}{ccc}
+\multicolumn{3}{c}{\begin{tabular}[c]{@{}c@{}}COMPARISON BETWEEN EXISTED METHODS \\ AND PROPOSED ALGORITHM\end{tabular}} \\ \hline
+Methods                                     & Computational time  & Accuracy  \\ \hline
+The method in \cite{b10}   &                     &           \\
+The method in \cite{b11}   &                     &           \\
+The method in \cite{b12}   &                     &           \\
+Exhaustive search Algorithm                 &                     &           \\
+Proposed Algorithm                          &                     &          
 \end{tabular}
-\label{tab3}
+\label{tab2}
 \end{center}

### 2018-08-23 main.tex
modify-ver1

@@
 \begin{document}
-\title{Photovoltaic System Reconfiguration strategy foer mismatch condition\\
+\title{Photovoltaic System Reconfiguration strategy for mismatch condition\\
 {\footnotesize \textsuperscript{}}}
@@
 \begin{abstract}
-  Power generation efficiency of photovoltaic(PV) system reduced significantly under partial shading or solar cell damage etc.
-conditions.
-Which affected of turned on bypass diode.
-These efficiency loss in the form of mismatch losses.
-Using reconfiguration technology to reconfigure electrical connection, which, changing series or parallel connetion among PV panel can minimize mismatch losses.
-However existed reconfiguration methods such as exhaustive search or Genetic algorithm(GA) need very long computing time to find best configuration.
-This paper proposed an reconfiguration strategy that find optimal configuration among mismatched PV array in a very less computational time.
-This algorithm is very light and suitble for embedded device.
+  Power generation efficiency of photovoltaic(PV) system is reduced significantly under partial shading or solar cell damage  conditions.
+This efficiency losses affected by truing on bypass diode of PV panels, which called mismatch losses.
+Reconfiguration technology to reconfigure electrical series or parallel connection among PV panel can maximize generate power.
+This paper proposes a reconfiguration strategy that finds an optimal configuration among mismatched PV array in a less computational time.
+This algorithm is very light and suitable for embedded device.
 The results show that compare with existed reconfiguration method under non-uniform shadow scenario proposed algorithm computes an optimized configuration with less computational time and very high accuracy.
@@
 
-\section{Introduction}
+\section{Introduction} \label{intro}
 
-As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable energy and green energy have become maintain necessary means of survival and development of the human.
-Photovoltaic (PV) energy received significant attention since it has unlimited energy and easy to be scaled up.
-Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation system have been deployed into many practical application.
-But due to PV arrays are senstive to shading and PV cell's fault or aging.
-That means when interconnection of PV cells or modules do no have identical properties or experience different conditions from one another.
-PV arrays are in mismatch condition.
-In order to avoid mismatch condition damage PV cells, we proposed an algorithm that can re-configurate photovoltaic arrays to minimize mismatch loss.
+As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable and green energy have become necessary means of survival and development of human being.
+Photovoltaic (PV) energy has received a significant attention since it is unlimited and easy to be scaled up.
+Thanks to extensive technology and research on photovoltaic energy generation, large scale photovoltaic energy generation systems have been deployed into many practical applications.
+However, PV arrays are sensitive to shading and PV cell's fault or aging.
+This implies that when interconnection of PV cells or modules do not have identical properties or experience different conditions from one another.
+the PV array is in mismatch condition.
+The photovoltaic arrays under mismatched conditions will accelerate the aging and heating of PV cells and cause a short circuit of photovoltaic cells to further damage the PV array.
+In order to avoid mismatch condition damage PV cells, we propose an algorithm that can reconfigure photovoltaic arrays to avoid mismatch damage and maximize generated power.
 
-In this paper, we using non-uniform irradiance levels to represent mismatch condition and analyzes the efficiency of a PV system under different shaded working condition is presented.
-When photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maximum power points (MPPs) \cite{b1}, which been generated by turning on bypass diodes.
+In this paper, we use non-uniform irradiance levels to represent mismatch condition and analyze the efficiency of a PV system under different shaded working condition.
+Photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maximum power points (MPPs) \cite{b1}, which are generated by turning on bypass diodes.
 By changing electrical connection among the panels to prevent activate bypass diodes is a recent appealing solution\cite{b2}.
 
-The main difficulty facing the reconfiguration problem is that some or even all panels can be subjected to partial shading, so there may be more than one MPP for each panel.
-Reconfiguration strategy need also consider to group PV modules which provided high power separately\cite{b3} \cite{b4}.
+The main difficulty facing the reconfiguration problem is that some or even all panels can be subjected to partial shading and there may be more than one MPP for each panel.
+Moreover, the panels, and not modules, reconfiguration strategy has to be realized so that modules providing the highest power could be grouped separately\cite{b3} \cite{b4}.
 
@@
 However, in sparse of mismatching conditions, distribution of panels among different irradiance levels are not significant.
-For that, by increasing number of strings in the PV array and using exhaustive search can be a solution\cite{b3}.Another approach to optimize photovoltaic arrays is using genetic algorithm\cite{b5}.
+For that, by increasing number of strings in the PV array and using exhaustive search can be a solution\cite{b3}.
+Another approach to optimize photovoltaic arrays is using genetic algorithm\cite{b5}.
 However, computing cost is too significant, and this algorithm can't detect best configuration precisely.
+A simplest reconfiguration strategy for minimizing mismatch losses is presented in \cite{b10}.
+In this strategy, an algorithm gives candidates for PV array reconfiguration, for each candidates we have conduct power simulations.
+But some candidates are not feasible, which means there isn't any configuration for PV array can be realized.
+Since the power simulation is very time consuming, based on existed work we want to reduce number of candidates to accelerate overall reconfiguration algorithm.
+In this paper we propose an algorithm can give optimal configuration and check feasibility with less computational time and high accuracy.
 
 \section{Assumption of a PV array} \label{assum}
-In this paper, we using following definitions of PV arrays, modules, strings and panels.
-A PV array formed by several parallel connected PV strings, and string is several series connected PV panels.
-For a PV panel, formed by two or three PV modules connected in series with bypass diodes.
-An equivalent connection as showed in Fig.
+In this paper, we use the following definitions of PV arrays, modules, strings and panels as showed in Fig.
 \ref{fig1}.
+A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels.
+For a PV panel, formed by three PV modules connected in series with bypass diodes.
 \begin{figure}[htbp]
 \centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
-\caption{Definition of PV array and internal components.}
+\caption{PV arrays, strings, and panels.}
 \label{fig1}
@@
 
-The algorithm we proposed based on following assumptions.
-\begin{itemize}
-\item The current versus voltage (\textit{I-V}) curve of each panel calculated by algorithm presented in \cite{b6}.
-This algorithm will analyzes panel's \textit{I-V} curve sample and coordinate to maximum or minimum power point in \textit{P-V} curve.
-\item All the panels in PV array have same number (\textit{N}) of modules.
-For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify MPP voltage and current by index \textit{n}.
-Those parameter can be directly estimated by the prosess provided in\cite{b7}.
-\end{itemize}
+We assume that each panel follows: The current versus voltage (\textit{I-V}) curve is acquired and calculated by algorithm presented in \cite{b6}.
+That algorithm will analyzes the panel \textit{I-V} curve sample by finding almost-constant-current and voltage regions and coordinate multiple maximum or minimum power point in the \textit{P-V} curve if PV array is working in mismatched conditions or not.
 
-Furthermore, it is also assumed that for each string it has same number of panels in PV array.
+All the panels in PV array have the same number (\textit{N}) of modules.
+For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify voltage and current values on different maximum power point by index \textit{n}.
+Those parameters can be directly estimated by the prosess provided in\cite{b7}.
+
+Furthermore, it is also assumed that for each string it has same number of panels.
 Means every string in PV array have same length.
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=8cm]{paper-fig2.png}}
-\caption{Flowchart of reconfiguration algorithm.}
-\label{fig2}
+\centerline{\includegraphics[width=8cm]{flowchart.png}}
+\caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
+\label{flowchart}
 \end{figure}
 
-\section{Reconfiguration Algorithm}
-The general steps of reconfiguration algorithm are presented in Fig.
+\section{Reconfiguration Algorithm} \label{algo}
+As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}.
+Then determine MPP current and voltage candidates among PV array.
+Calculate MPP candidates matrix by multiplying the current and voltage candidates.
+Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates.
+Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array.
+Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations.
+The general steps of Fast reconfiguration strategy as showed in Fig.
+\ref{flowchart}.
+
+\subsection{Feasibility}
+The feasibility of configuration based on the assumption of section \ref{assum}, each string in PV array must have same number of panels.
+Definition of feasibility in (\ref{feas}).
+When a configuration needs panels in a string (\textit{$NP_n$}) are over mean value for number of panels per-string this configuration is unfeasible.
+\begin{equation}
+\left\{\begin{matrix}
+NP_n > NP\div N_{st}& & \text{Unfeasible}\\ 
+NP_n \leq NP\div N_{st} & & \text{Feasible} 
+\label{feas}
+\end{matrix}\right. 
+\end{equation}
+
+\begin{table}[htbp]
+\caption{}
+\begin{center}
+\begin{tabular}{cccc}
+\multicolumn{4}{c}{DATA OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
+Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
+P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
+P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
+P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
+P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}0, 22.8, 22.8{]}    \\
+P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
+P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
+P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
+P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
+P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+
+\subsection{Reconfiguration strategy}
+Based on existed reconfiguration
+%The general steps of reconfiguration algorithm are presented in Fig.
 \ref{fig2}.
@@
 %\end{table}
-
-\begin{table}[htbp]
-\caption{}
-\begin{center}
-\begin{tabular}{cccc}
-\multicolumn{4}{c}{DATA OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
-Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
-P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
-P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
-P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
-P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}0, 22.8, 22.8{]}    \\
-P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
-P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
-P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
-P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
-P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
 
@@
 393–405, 2015.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
+\bibitem{b6} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
 \bibitem{b7} Orozco-Gutierrez, M. L., et al. "Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on. IEEE, 2015.

### 2018-08-26 main.tex
Modify Version - 1.0
modify paper
add figure
missing test data, last figure

@@
 \usepackage{algorithmic}
+\usepackage{enumerate}
 \usepackage{graphicx}
@@
 \usepackage{graphicx}
-%% \usepackage{subfigure}
+%\usepackage{subfigure}
+\usepackage{caption}
 \usepackage{subfig}
-%% \usepackage{subcaption}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels.
-For a PV panel, formed by three PV modules connected in series with bypass diodes.
+For a PV panel, formed by three PV modules (\textit{$N_M=3$}) connected in series with bypass diodes.
 \begin{figure}[htbp]
@@
 \section{Reconfiguration Algorithm} \label{algo}
+To reconfigure a large scale partial shading PV array, an example refers to 9 panels which have been connected in 3 strings.
+In this example, mismatching conditions presented in Table \ref{tab1}.
+Each panel made of 3 identical PV modules (\textit{N=3}), dataset in Table \ref{tab1} are provide by method in \cite{b6} \cite{b7}.
 As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}.
@@
 Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array.
-Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations.
 The general steps of Fast reconfiguration strategy as showed in Fig.
 \ref{flowchart}.
+Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations.
+Our proposed algorithm based on the method in \cite{b10} to calculate MPP candidates and using unique panel selection technology to give optimal reconfiguration solution among partial-shading PV array.
 
-\subsection{Feasibility}
-The feasibility of configuration based on the assumption of section \ref{assum}, each string in PV array must have same number of panels.
-Definition of feasibility in (\ref{feas}).
-When a configuration needs panels in a string (\textit{$NP_n$}) are over mean value for number of panels per-string this configuration is unfeasible.
-\begin{equation}
-\left\{\begin{matrix}
-NP_n > NP\div N_{st}& & \text{Unfeasible}\\ 
-NP_n \leq NP\div N_{st} & & \text{Feasible} 
-\label{feas}
-\end{matrix}\right. 
-\end{equation}
+In this example, though the procedure in Fast reconfiguration strategy, MPP candidates are presented in (\ref{mpp}) and number of working modules in MPP candidates are presented in (\ref{qmn}), respectively.
 
@@
 \begin{tabular}{cccc}
-\multicolumn{4}{c}{DATA OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
+\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
 Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
@@
 
-\subsection{Reconfiguration strategy}
-Based on existed reconfiguration
+\begin{equation}
+\begin{aligned}
+\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
+\end{aligned}\label{mpp}
+\end{equation}
+\begin{equation}
+\begin{aligned}
+\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
+\end{aligned}
+\label{qmn}
+\end{equation}
+
+\subsection{Feasibility}
+The feasibility of configuration based on the assumption of section \ref{assum}, each string in PV array must have same number of panels.
+Definition of feasibility in (\ref{feas}).
+When a configuration needs panels in a string (\textit{$NP_n$}) are over maximum number of panels per-string(\textit{$NP_{stMAX}$}) this configuration is unfeasible.
+\begin{equation}
+\left\{\begin{matrix}
+NP_n > NP_{stMAX}& & \text{Unfeasible}\\ 
+NP_n \leq NP_{stMAX} & & \text{Feasible} 
+\label{feas}
+\end{matrix}\right. 
+\end{equation}
+For the first MPP candidate \{0.5, 0.5, 2\} need 8 modules for each string.
+According to Table \ref{tab1}, for a string current on 2A at least need 4 panels and didn't meet feasible requirement, thus, algorithm terminate.
+The second MPP candidate \{0.5, 2, 2\} as same as previous one also not feasible.
+
+\subsection{Panel Selection Strategy} \label{selection strategy}
+%Calculate MPP candidates based on existed reconfiguration method in \cite{b10}.
+MPP current candidates and MPP voltage candidates are present in (\ref{e1}) and (\ref{e2}), respectively.
+Additional, number of real working module at MPP current candidates are given in (\ref{e3}).
+Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%.
+Though procedure of algorithm in \cite{b10}, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
+%\begin{equation}
+%\begin{aligned}
+%\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
+%\end{aligned}
+%\end{equation}
+%\begin{equation}
+%\begin{aligned}
+%\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
+%\end{aligned}
+%\end{equation}
+%\begin{equation}
+%\begin{aligned}
+%\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
+%\end{aligned}
+%\end{equation}
+
+ In order to give more precise reconfiguration strategy.
+Our proposed algorithm firstly sort panels in a particular order for MPP candidates.
+For the example of fourth MPP candidate \{2, 2, 3\}, by giving dataset in Table \ref{tab1} generate a selection matrix in (\ref{mpp3-1}) that each column indicate panel's number and  each row indicate to string number.
+Element in the matrix corresponding to number of module which be able to working on string current.
+\begin{equation}
+%\begin{center}
+\begin{tabular}{l|lllllllll}
+    & P1 & P2 & P3 & P4 & P5 & P6 & P7 & P8 & P9 \\ \hline
+St1 & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
+St2 & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
+St3 & 0  & 2  & 0  & 0  & 0  & 0  & 1  & 0  & 1 
+\end{tabular}\label{mpp3-1}
+%\end{center}
+\end{equation}
+Then calculate number of module difference among string currents.
+For panel 1, difference between string 3 and string 2 is 1 (\textit{$Diff_1=1$}) and difference between string 2 and string 1 is 0 (\textit{$Diff_2=0$}).
+Sort panels in lexicographic order by \textit{$Diff_1$} and \textit{$Diff_2$}.
+As showed in matrix (\ref{sorted}).
+\begin{equation}
+\begin{tabular}{l|lllllllll}
+        & P2 & P3 & P1 & P5 & P7 & P9 & P4 & P6 & P8 \\ \hline 
+St1     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
+St2     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
+St3     & 2  & 0  & 0  & 0  & 1  & 1  & 0  & 0  & 0  \\
+\textit{$Diff_1$} & 0  & 0  & 1  & 1  & 1  & 1  & 2  & 2  & 3  \\
+\textit{$Diff_2$} & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0 
+\end{tabular}\label{sorted}
+\end{equation}
+To find the best PV configuration, following steps are required:
+\begin{enumerate} [1-]
+\item Select panels in matrix (\ref{sorted}) from left side to right.
+\item If the element in matrix is 0, release corresponding panel
+\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel.
+As the example of string 2, selected panels are [Panel 1, Panel 5], these panels contain modules are equal to next unselect panel [Panel 4].
+Then swap [Panel 1, Panel 5] and [Panel4], release [Panel 1, Panel 5].
+\label{replace}
+%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
+\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
+\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
+\item If there remain any unselect panel, set unselect panel to a string with minimum length. 
+\end{enumerate}
+\subsection{Panel Replace Strategy}
+In the section \ref{selection strategy}, to obtain optimal panel selection need swap undesired panel.
+Based on section \ref{assum}, each panel only contain three identical PV modules.
+So the element in selection matrix in the range of 0 to 3.
+The replacement policy follows priorities are:
+\begin{enumerate} [ (1) ]
+\item Swap a panel contain 3 working modules to \textbf{three} panels each contain 1 working module.
+\item Swap a panel contain 3 working modules to \textbf{one} panel contain 1 working module and \textbf{one} contain 2 working modules.
+\item Swap a panel contain 2 working modules to \textbf{two} panels each contain 1 working module.
+\end{enumerate}
+
+By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate 1 and MPP candidate 2.
+Configuration for MPP candidate 3 is that first string include Panel 1, Panel 2 and Panel 4; the second string include Panel 5, Panel 6 and Panel 7; the third string include Panel 3, Panel 8 and Panel 9.
+Configuration for MPP candidate 4 is that first string include Panel 1, Panel 5 and Panel 8; the second string include Panel 3, Panel 4 and Panel 6; the third string include Panel 2, Panel 7 and Panel 9.
+Optimal configuration for this partial-shading PV array as showed in Fig.
+\ref{reconfiguration}.
+
+\begin{figure}%
+    \centering
+    \subfloat[MPP candidate 3]{{\includegraphics[width=4cm]{mpp3.png} }}%
+%    \qquad
+    \subfloat[MPP candidate 4]{{\includegraphics[width=4cm]{mpp4.png} }}%
+    \caption{Configuration of partial-shading PV array}%
+    \label{reconfiguration}%
+\end{figure}
+
 %The general steps of reconfiguration algorithm are presented in Fig.
@@
 
-After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group.
+%After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group.
 However, if just simply grouping panels by shadow distribution conditions it may cause electrical connection overhead or unable calculate optimal configuration.
 To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
-\begin{itemize}
-\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
-\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
-\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
-\end{itemize}
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=6.2cm]{paper-fig3.png}}
-\caption{An example of un-uniform shadowed PV array.}
-\label{fig3}
-\end{figure}
+%\begin{itemize}
+%\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
+%\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
+%\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
+%\end{itemize}
+%\begin{figure}[htbp]
+%\centerline{\includegraphics[width=6.2cm]{paper-fig3.png}}
+%\caption{An example of un-uniform shadowed PV array.}
+%\label{fig3}
+%\end{figure}
 
-This algorithm will better understood by applying to shadow condition showed in Fig.
+%This algorithm will better understood by applying to shadow condition showed in Fig.
 \ref{fig3}.
@@
 %\end{table}
-
-The example refer to a three-strings PV array, each string contain with 3 panels, each one made of three identical PV modules (\textit{N}=3).
+%The example refer to a three-strings PV array, each string contain with 3 panels, each one made of three identical PV modules (\textit{N}=3).
 In this example, it is assumed that input range of DC-DC converter and MPPT device defined by \textit{$V_{min}$} = 200V and \textit{$V_{max}$} = 500V.
-MPP current candidates and MPP voltage candidates are present in ( \ref{e1} ) and ( \ref{e2} ), respectively.
-Additional, number of real working module at MPP current candidates are given in ( \ref{e3} ).
-\begin{equation}
-\begin{aligned}
-\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
-\end{aligned}
-\end{equation}
-\begin{equation}
-\begin{aligned}
-\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
-\end{aligned}
-\end{equation}
-\begin{equation}
-\begin{aligned}
-\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
-\end{aligned}
-\end{equation}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=8cm]{paper-fig4.png}}
-\caption{Organized PV array after first part of Algorithm.}
-\label{fig4}
-\end{figure}
-
-Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%.
+%\begin{figure}[htbp]
+%\centerline{\includegraphics[width=8cm]{paper-fig4.png}}
+%\caption{Organized PV array after first part of Algorithm.}
+%\label{fig4}
+%\end{figure}
+%Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%.
 Though procedure of algorithm, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
 And PV array are organized as Fig.\ref{fig4}
-Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead.
+%Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead.
 In order to reduce electrical connection simulation time, replacement and feasibility check will be approved.
-
-Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string.
+%Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string.
 Firstly, selecting panels for high current string, string three.
@@
 Means no further improvement for configuration of string three.
-Then select panel for string two, Panel 4 and Panel 8 will be selected, but this configuration is not optimized.
+%Then select panel for string two, Panel 4 and Panel 8 will be selected, but this configuration is not optimized.
 Selected panels provide 5 modules able to work at 2A, satisfy requirement of \textit{$Q_{M_n}$} $\ge$ 4, but one module more than requirement.
@@
 
-For the third MPP candidate, as same calculating procedure as fourth MPP candidate, optimized configuration for MPP candidate \{2, 2, 2\} are: \textit{St} 1:\{Panel 4,Panel 8, Panel 3\}, \textit{St} 2: \{Panel 1, Panel 2, Panel 6\}, \textit{St} 3: \{Panel 5, Panel 7, Panel 9\}.
-
-The first MPP candidate \{0.5, 0.5, 2\}, after replacement string three contain four panels, \{Panel 4, Panel 8, Panel 1, Panel 2\} but it is over maximum string length of this PV array.
-Also for MPP candidate \{0.5, 2, 2\}, there are no configuration can't provide 7 modules working 
-on three different string at 0.5A, 2A, 2A, respectively.
+%For the third MPP candidate, as same calculating procedure as fourth MPP candidate, optimized configuration for MPP candidate \{2, 2, 2\} are: \textit{St} 1:\{Panel 4,Panel 8, Panel 3\}, \textit{St} 2: \{Panel 1, Panel 2, Panel 6\}, \textit{St} 3: \{Panel 5, Panel 7, Panel 9\}.
+%
+%The first MPP candidate \{0.5, 0.5, 2\}, after replacement string three contain four panels, \{Panel 4, Panel 8, Panel 1, Panel 2\} but it is over maximum string length of this PV array.
+%Also for MPP candidate \{0.5, 2, 2\}, there are no configuration can't provide 7 modules working 
+%on three different string at 0.5A, 2A, 2A, respectively.
 
@@
 %\subsection{Verification of the Proposed algorithm}
-This section verifies the effectiveness of proposed algorithm using LTspice simulation.
+Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected strings is the same.
+This section verifies the effectiveness of proposed algorithm using Matlab simulation.
 With pilot example presented in last section, shading scenario as showed in Fig.\ref{fig5a}.
@@
 The resulting configuration is depicted in Fig.\ref{fig5b} and Fig.\ref{fig5c}.
+%\begin{figure}%
+%    \centering
+%    \subfloat[label 1]{{\includegraphics[width=5cm]{paper-fig5(a).png} }}
+%    \label{fig5a}
+%    \qquad
+%    \subfloat[label 2]{{\includegraphics[width=5cm]{paper-fig5(b).png} }}%
+%    \qquad
+%    \subfloat[label 3]{{\includegraphics[width=5cm]{paper-fig5(c).png} }}
+%    \caption{3 Figures side by side}%
+%    \label{fig5c}%
+%\end{figure}
+
 \begin{figure}
 \centering 
-
 \subfloat[]{
@@
 	\label{fig5b}
-	\includegraphics[width=5cm]{paper-fig5(b).png} } \\
+	\includegraphics[width=4cm]{mpp3.png} }
 \subfloat[]{
 	\label{fig5c}
-	\includegraphics[width=5cm]{paper-fig5(c).png}} \\
-\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 3\} and (c) MPP candidate \{2, 2, 2\}} 
+	\includegraphics[width=4cm]{mpp4.png}} \\
+\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 2\} and (c) MPP candidate \{2, 2, 3\}} 
 \end{figure}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=6.2cm]{fig2.png}}
+\centerline{\includegraphics[width=5cm]{fig2.png}}
 \caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}
@@
 \end{figure}
-The computational time required to find the best configuration in the proposed and existed method is also compared and summarized in Table \ref{tab2}.
-As shown in Table \ref{tab3}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm and methods described in \cite{b10} \cite{b11} \cite{b12}.
+
+To evaluate the performance of proposed algorithm, we compare the propose algorithm with exhaustive search algorithm for 300 different partial-shading PV arrays.
+For each PV array, contain 2$\sim$15 PV panels connected into 2$\sim$5 strings.
+The PV panels will have contain 2$\sim$20 different current candidates.
+
+The computational time required to find the best configuration and accuracy of configuration in the proposed and exhaustive search algorithm are compared and summarized in Table \ref{tab2}.
+As shown in Table \ref{tab2}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm and methods described in \cite{b10}.
+%\cite{b11} \cite{b12}.
 
@@
 The method in \cite{b10}   &                     &           \\
-The method in \cite{b11}   &                     &           \\
-The method in \cite{b12}   &                     &           \\
+%The method in \cite{b11}   &                     &           \\
+%The method in \cite{b12}   &                     &           \\
 Exhaustive search Algorithm                 &                     &           \\
@@
 %The simulations were performed using an Intel i7-4770 3.2-Ghz processor with 32.0 GB of RAM memory. 
-The calculation time used by the proposed algorithm was !!!!!
-ms, which is significantly lower compared with exhaustive search (!!!!!!!time) and accuracy are much higher than methods proposed in \cite{b11} \cite{b12}.
+The calculation time used by the proposed algorithm for one MPP candidate was !!!!!
+ms, which is significantly lower compared with exhaustive search (!!!!!!!time) and accuracy are higher than methods proposed in \cite{b10} \cite{b12}.
 \section{conclusions}
 The existing PV reconfiguration methods either have high accuracy but suffer from long computational time such as exhausted searching algorithm or GA, or they have short computational time but do not guarantee the best configuration as described in \cite{b10} \cite{b11} \cite{b12}.
-This paper proposed a new PV system reconfiguration algorithm with high accuracy and less computational time.
-Proposed algorithm's effectiveness has been validated using LTspice simulation.
+This paper proposed a new PV system reconfiguration algorithm with feasibility check function and have high accuracy and less computational time.
+Proposed algorithm's effectiveness has been validated using Matlab simulation.
 The algorithm was tested though un-uniform shadow distribution among PV array and shows its effectiveness in finding optimal configuration.

### 2018-08-26 main.tex
20180826

@@
 \section{Introduction} \label{intro}
-
-As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable and green energy have become necessary means of survival and development of human being.
+As fossil energy is constantly depleted and increasing a serious pollution problem for the environment, research and utilization on a green and renewable energy have become necessary to support human existence and guarantee a sustainable human development.
+%As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable and green energy have become necessary means of survival and development of human being.
 Photovoltaic (PV) energy has received a significant attention since it is unlimited and easy to be scaled up.

### 2018-08-31 main.tex
20180831

@@
   Power generation efficiency of photovoltaic(PV) system is reduced significantly under partial shading or solar cell damage  conditions.
-This efficiency losses affected by truing on bypass diode of PV panels, which called mismatch losses.
-Reconfiguration technology to reconfigure electrical series or parallel connection among PV panel can maximize generate power.
-This paper proposes a reconfiguration strategy that finds an optimal configuration among mismatched PV array in a less computational time.
+This efficiency losses affected by turning on bypass diode of PV panels, which called mismatch losses.
+Reconfiguration technology to reconfigure electrical series or parallel connection among PV panels can maximize power generation.
+Recently, an efficient reconfiguration method of PV panel connection to optimize power generation is proposed.
+The method first list candidate configurations and applies precise power simulations to the candidates.
+However, some of candidates might not be realized by given PV panels and the paper does not show any systematic way to identify such a feasibility.
+In this paper, we propose a very fast algorithm to check the feasibility with high accuracy.
+%This paper proposes a reconfiguration strategy that finds an optimal configuration among mismatched PV array in a less computational time.
 This algorithm is very light and suitable for embedded device.
@@
 \section{Introduction} \label{intro}
-As fossil energy is constantly depleted and increasing a serious pollution problem for the environment, research and utilization on a green and renewable energy have become necessary to support human existence and guarantee a sustainable human development.
+As constant fossil energy generation is increasing the crisis of fossil fuel depletion and serious pollution problems for the environment, 
+%As fossil energy is constantly depleted and increasing a serious pollution problem for the environment, 
+research and utilization on a green and renewable energy have become necessary for sustainable society and environment.
+%to support human existence and guarantee a sustainable human development.
 %As the world of fossil energy constantly exhausted and the increasingly serious environmental pollution, the research and utilization of renewable and green energy have become necessary means of survival and development of human being.
@@
 However, PV arrays are sensitive to shading and PV cell's fault or aging.
-This implies that when interconnection of PV cells or modules do not have identical properties or experience different conditions from one another.
-the PV array is in mismatch condition.
-The photovoltaic arrays under mismatched conditions will accelerate the aging and heating of PV cells and cause a short circuit of photovoltaic cells to further damage the PV array.
-In order to avoid mismatch condition damage PV cells, we propose an algorithm that can reconfigure photovoltaic arrays to avoid mismatch damage and maximize generated power.
+This means that when
+%interconnection of 
+PV cells or modules do not uniformly generate power
+%have identical properties
+ or experience different irradiance conditions from one another, the PV array is in mismatch condition and could not efficiently generate power.
+In addition, the photovoltaic arrays under mismatched conditions will accelerate the aging and heating of PV cells and cause a short circuit of photovoltaic cells to further damage the PV array.
+In order to maximize power generation and also avoid damaging PV cells, we propose an algorithm that can reconfigure photovoltaic arrays.
 
-In this paper, we use non-uniform irradiance levels to represent mismatch condition and analyze the efficiency of a PV system under different shaded working condition.
-Photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maximum power points (MPPs) \cite{b1}, which are generated by turning on bypass diodes.
+In this paper, we use non-uniform irradiance levels to represent mismatch condition and analyze the efficiency of a PV system.
+% under different shaded working condition. 
+% Photovoltaic arrays operating in non-uniform irradiance levels may present multiple local maximum power points (MPPs) \cite{b1}, which are generated by turning on bypass diodes.
 By changing electrical connection among the panels to prevent activate bypass diodes is a recent appealing solution\cite{b2}.
+Photovoltaic arrays operating in mismatch conditions could not efficiently generate power, and reconfiguration of  panel connection has been widely investigated to solve this problem \cite{b2}.
 
-The main difficulty facing the reconfiguration problem is that some or even all panels can be subjected to partial shading and there may be more than one MPP for each panel.
+Some of works proposed optimized or efficient algorithms to reconfigure the connection of PV cells \cite{b3}\cite{b4}.
+However, these works assume a full reconfiguration ability among PV cells.
+In general, a PV array is a connection of multiple PV panels, each PV panel has multiple PV modules, and each PV module consists of multiple PV cells.
+One typical PV panel has 3 PV modules with 24 PV cells.
+To realize reconfiguration in PV cell level, a new PV panel architecture is required.
+
+Recently, as practical solutions, reconfiguration in PV panels have been investigated \cite{b5}\cite{b10}.
+One PV panel typically has two (plus and minus) terminals, and a PV array is configured by connecting PV panels in series and/or parallel.
+Such a configuration is also realized using a switch among PV panels, and reconfigurations in PV panel level can be regarded as  practical solutions.
+However, the reconfiguration in PV panel level is more difficult than that in PV cell level.
+PV modules in the same PV panel can be individually bypassed by bypass diodes when some mismatch condition occurs, and it causes multiple maximal power points (MPPs) for one PV panel.
+
+A PV panel level reconfiguration using genetic algorithm is proposed in\cite{b5}. Though this can generate a new configuration, 
+computing cost is too significant and the algorithm cannot generate the best configuration precisely. A fast reconfiguration
+strategy for minimizing power losses is presented in \cite{b10}.
+In this strategy, candidates for PV array configurations are first listed by some fast estimation method, and, for each candidates, precise power simulations are applied.
+However, some candidate configurations might not be feasible, that is, it is impossible to realize a designated PV array configuration with given PV panels, and there is no description of a systematic way to identify the feasibility.
+
+In this paper,  we propose an algorithm to identify feasibility for a given configuration with less computational time and high
+accuracy.
+%The main difficulty facing the reconfiguration problem is that some or even all panels can be subjected to partial shading and there may be more than one MPP for each panel.
 Moreover, the panels, and not modules, reconfiguration strategy has to be realized so that modules providing the highest power could be grouped separately\cite{b3} \cite{b4}.
-
-This procedure enables to detect panel's operating conditions, in more than two-strings, receiving different irradiance levels.
+%
+%This procedure enables to detect panel's operating conditions, in more than two-strings, receiving different irradiance levels.
 The reconfiguration algorithm will analyzes panels' working conditions and reorganizes panels into different strings by different irradiance levels.
@@
 
-\section{Assumption of a PV array} \label{assum}
-In this paper, we use the following definitions of PV arrays, modules, strings and panels as showed in Fig.
+\section{Photovoltaic Array} \label{array}
+In this paper, we use the following model of PV arrays, modules, strings and panels as showed in Fig.
 \ref{fig1}.
 A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels.
-For a PV panel, formed by three PV modules (\textit{$N_M=3$}) connected in series with bypass diodes.
+A PV panel is formed by three PV modules (\textit{$N_M=3$}).
+% connected in series with bypass diodes. 
+And each bypass diode is connected in parallel with a module.
 \begin{figure}[htbp]
@@
 \label{fig1}
+\end{figure}
+
+Fig.\ref{fig2a} shows  I-V curves for PV panels. PV panel generates a currents according to a provided control voltage within some range.
+PV cells in a PV panel may have different conditions (irradiance or fault) and hence have different upper limits for their generated currents.
+Therefore, for lower control voltage, only PV cells that can generate higher currents can work and the other PV cells do not generate current with their bypass diodes switching on.
+As a result, PV panel might have multiple maximal power points (MPPs, points where power curve has extreme values).
+Fig.\ref{fig2b} and \ref{fig2c} show I-V curves for series and parallel connections of two PV panels.
+The series connection accepts wider range of control voltage, and the parallel connection can generate higher current.
+
+When understanding complete I-V characteristics of some parallel and/or series connection of PV panels, we may need I-V characteristics of the PV panels.
+However, to find out the (near)  maximum generated power, it is enough to considers some restricted information including maximal power points (MPPs), a short circuit current, an open circuit voltage.
+These values form a fingerprint of the connection.
+
+\begin{figure}
+\centering 
+\subfloat[]{
+	\label{fig2a}
+	\includegraphics[width=4cm]{fig2.png} } \\
+\subfloat[]{
+	\label{fig2b}
+	\includegraphics[width=4cm]{fig2.png} }
+\subfloat[]{
+	\label{fig2c}
+	\includegraphics[width=4cm]{fig2.png}} \\
+\caption{} 
 \end{figure}
@@
 String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
+
+\section{Reconfiguration Algorithm} \label{algo}
+\subsection{Overview of the algorithm}
+In this section, we describe the overview of the reconfiguration algorithm in \cite{b10}.
+First, the reconfiguration algorithm determines MPPs for PV modules in the mismatched condition by using algorithms in \cite{b6}\cite{b7}\cite{b9}.
+As an example, we consider a PV panel where nine panels are connected in three strings.
+We assume that, in this example, the reconfiguration algorithm finds MPPs given in Table \ref{tab1}.
+%To reconfigure a large scale partial shading PV array, an example refers to 9 panels which have been connected in 3 strings. In this example, mismatching conditions presented in Table \ref{tab1}. 
+%Each panel made of 3 identical PV modules (\textit{N=3}), dataset in Table \ref{tab1} are provide by method in \cite{b6} \cite{b7}.
+As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}.
+After that, the reconfiguration algorithm generates candidates of current assignments, where the current assignment specifies a current of each string.
+The reconfiguration algorithm treats the current of each MPP as a current candidate for string, and constructs a current assignment by assigning a current candidate to each string.
+The reconfiguration algorithm generates current assignments by considering all combinations of current candidates for string.
+%Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. 
+Then, for each current assignment, the reconfiguration algorithm computes the number of working modules in each string.
+We define a configuration as a combination of a current assignment and the number of working modules in each string.
+By this algorithm, we obtain a set of candidate configurations.
+Since we can estimate the generated power of each candidate configuration, we can select the candidate configuration that maximizes the generated power.
+%\vspace{10cm}
+%Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates.
+Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array.
+The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}. 
 \begin{figure}[htbp]
@@
 \end{figure}
-
-\section{Reconfiguration Algorithm} \label{algo}
-To reconfigure a large scale partial shading PV array, an example refers to 9 panels which have been connected in 3 strings.
-In this example, mismatching conditions presented in Table \ref{tab1}.
-Each panel made of 3 identical PV modules (\textit{N=3}), dataset in Table \ref{tab1} are provide by method in \cite{b6} \cite{b7}.
-As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}.
-Then determine MPP current and voltage candidates among PV array.
-Calculate MPP candidates matrix by multiplying the current and voltage candidates.
-Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates.
-Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array.
-The general steps of Fast reconfiguration strategy as showed in Fig.
-\ref{flowchart}.
+The previous estimation can not give precise 
+\subsection{Feasibility Problem}
 Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations.
@@
 \subsection{Feasibility}
-The feasibility of configuration based on the assumption of section \ref{assum}, each string in PV array must have same number of panels.
+The feasibility of configuration based on the assumption of section \ref{array}, each string in PV array must have same number of panels.
 Definition of feasibility in (\ref{feas}).
@@
 In the section \ref{selection strategy}, to obtain optimal panel selection need swap undesired panel.
-Based on section \ref{assum}, each panel only contain three identical PV modules.
+Based on section \ref{array}, each panel only contain three identical PV modules.
 So the element in selection matrix in the range of 0 to 3.
@@
 Configuration of MPP candidate \{2, 2, 3\} are \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}.
-As described in section \ref{assum}, each string have identical length and Panel 3 not been used in any configuration.
+As described in section \ref{array}, each string have identical length and Panel 3 not been used in any configuration.
 So optimized configuration for this MPP candidate are: \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8, Panel 3\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}.
@@
 \begin{tabular}{ccc}
-\multicolumn{3}{c}{\begin{tabular}[c]{@{}c@{}}COMPARISON BETWEEN EXISTED METHODS \\ AND PROPOSED ALGORITHM\end{tabular}} \\ \hline
-Methods                                     & Computational time  & Accuracy  \\ \hline
-The method in \cite{b10}   &                     &           \\
-%The method in \cite{b11}   &                     &           \\
-%The method in \cite{b12}   &                     &           \\
-Exhaustive search Algorithm                 &                     &           \\
-Proposed Algorithm                          &                     &          
+\multicolumn{3}{c}{\begin{tabular}[c]{@{}c@{}}COMPARISON BETWEEN EXISTED METHODS\\ AND PROPOSED ALGORITHM\end{tabular}}                                         \\ \hline \hline
+\multicolumn{1}{c|}{}                         & \multicolumn{1}{c|}{Propose Algorithm} & \begin{tabular}[c]{@{}c@{}}Exhaustive search \\ Algorithm\end{tabular} \\ \hline
+\multicolumn{1}{c|}{Number of PV Array}       & \multicolumn{2}{c}{300}                                                                                         \\ \hline
+\multicolumn{1}{c|}{Number of MPP candidates} & \multicolumn{2}{c}{10961}                                                                                       \\ \hline
+\multicolumn{1}{c|}{Feasible Candidates}      & \multicolumn{1}{c|}{1180}              & 1278                                                                   \\ \hline
+\multicolumn{1}{c|}{Unfeasible Candidates}    & \multicolumn{1}{c|}{9781}              & 9683                                                                   \\ \hline
+\multicolumn{1}{c|}{Error Rate}               & \multicolumn{1}{c|}{0.89\%}            & 0\%                                                                    \\ \hline
+\multicolumn{1}{c|}{Ave. times per Array}     & \multicolumn{1}{c|}{0.157s}            & 4370s                                                                 
 \end{tabular}
@@
 %The simulations were performed using an Intel i7-4770 3.2-Ghz processor with 32.0 GB of RAM memory. 
-The calculation time used by the proposed algorithm for one MPP candidate was !!!!!
-ms, which is significantly lower compared with exhaustive search (!!!!!!!time) and accuracy are higher than methods proposed in \cite{b10} \cite{b12}.
+The calculation time used by the proposed algorithm for one MPP candidate was 157 ms, which is significantly lower compared with exhaustive search 1hour 12min 50s and accuracy are higher than methods proposed in \cite{b10} \cite{b12}.
 \section{conclusions}

### 2018-08-31 main.tex
20180831-02

@@
 A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels.
-A PV panel is formed by three PV modules (\textit{$N_M=3$}).
+A PV panel is formed by three PV modules.
 % connected in series with bypass diodes. 
@@
 
-We assume that each panel follows: The current versus voltage (\textit{I-V}) curve is acquired and calculated by algorithm presented in \cite{b6}.
+%We assume that each panel follows: The current versus voltage (\textit{I-V}) curve is acquired and calculated by algorithm presented in \cite{b6}.
 That algorithm will analyzes the panel \textit{I-V} curve sample by finding almost-constant-current and voltage regions and coordinate multiple maximum or minimum power point in the \textit{P-V} curve if PV array is working in mismatched conditions or not.
-
-All the panels in PV array have the same number (\textit{N}) of modules.
+In mismatched conditions, the power versus voltage (P-V) curve of each panel shows multiple MPPs (maximal power points).
+We refer to a MPP by a pair $(V_{mpp},I_{mpp})$ where $V_{mpp}$ and $I_{mpp}$ are the voltage and the current that give a maximal power, respectively.
+The algorithm in \cite{b6} analyzes the current versus voltage (I-V) curves of panels and finds MPPs of each panel in mismatched conditions.
+%All the panels in PV array have the same number (\textit{N}) of modules.
 For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify voltage and current values on different maximum power point by index \textit{n}.
@@
 
-Furthermore, it is also assumed that for each string it has same number of panels.
+%Furthermore, it is also assumed that for each string it has same number of panels.
 Means every string in PV array have same length.
@@
 \section{Reconfiguration Algorithm} \label{algo}
+
 \subsection{Overview of the algorithm}
-In this section, we describe the overview of the reconfiguration algorithm in \cite{b10}.
+In this section, we describe the overview of the Fast reconfiguration algorithm in \cite{b10}.
 First, the reconfiguration algorithm determines MPPs for PV modules in the mismatched condition by using algorithms in \cite{b6}\cite{b7}\cite{b9}.
@@
 Then, for each current assignment, the reconfiguration algorithm computes the number of working modules in each string.
-We define a configuration as a combination of a current assignment and the number of working modules in each string.
-By this algorithm, we obtain a set of candidate configurations.
-Since we can estimate the generated power of each candidate configuration, we can select the candidate configuration that maximizes the generated power.
-%\vspace{10cm}
-%Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates.
-Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array.
-The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}. 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=8cm]{flowchart.png}}
-\caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
-\label{flowchart}
-\end{figure}
-The previous estimation can not give precise 
-\subsection{Feasibility Problem}
-Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations.
-Our proposed algorithm based on the method in \cite{b10} to calculate MPP candidates and using unique panel selection technology to give optimal reconfiguration solution among partial-shading PV array.
-
-In this example, though the procedure in Fast reconfiguration strategy, MPP candidates are presented in (\ref{mpp}) and number of working modules in MPP candidates are presented in (\ref{qmn}), respectively.
-
-\begin{table}[htbp]
-\caption{}
-\begin{center}
-\begin{tabular}{cccc}
-\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
-Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
-P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
-P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
-P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
-P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}0, 22.8, 22.8{]}    \\
-P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
-P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
-P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
-P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
-P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
+We define a configuration as a combination of a current assignment and the number of working modules (\textit{$Q_{M_n}$}) in each string.
+MPP candidates are presented in (\ref{mpp}) and number of working modules of MPP candidates are presented in (\ref{qmn}), respectively.
 
@@
 \end{equation}
+By this algorithm, we obtain a set of candidate configurations.
+Since we can estimate the generated power of each candidate configuration, we can select the candidate configuration that maximizes the generated power.
+%\vspace{10cm}
+%Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates.
+Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array.
+The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}. 
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=8cm]{flowchart.png}}
+\caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
+\label{flowchart}
+\end{figure}
+The previous estimation can not give precise reconfiguration answer.
+This algorithm lists some candidate configurations ( in addition to the maximum one ) and for each candidate configuration it will executes a time consuming and precise power simulation.
+Considering there are some errors in previous estimation, this algorithm is not efficient for finding the best configuration.
+\begin{table}[htbp]
+\caption{}
+\begin{center}
+\begin{tabular}{cccc}
+\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
+Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
+P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
+P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
+P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
+P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}None, 22.8, 22.8{]}    \\
+P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
+P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
+P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
+P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
+P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
 
-\subsection{Feasibility}
-The feasibility of configuration based on the assumption of section \ref{array}, each string in PV array must have same number of panels.
+\subsection{Feasibility Problem}
+To execute a power simulation, we have to assign panels to each string to realize a candidate configuration.
+However, the way is not given in \cite{b10} and some candidate configurations are infeasible.
+For an configuration example \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string.
+According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings.Of course we can compute it by using an exhaustive search.
+However, it is time-consuming.
+So, we need an algorithm to efficiently identify feasibility of a configuration and realize the configuration if it is feasible.
+
+%Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations.
+Our proposed algorithm based on the method in \cite{b10} to calculate MPP candidates and using unique panel selection technology to give optimal reconfiguration solution among partial-shading PV array.
+
+%In this example, though the procedure in Fast reconfiguration strategy, MPP candidates are presented in (\ref{mpp}) and number of working modules in MPP candidates are presented in (\ref{qmn}), respectively.
+
+%\begin{equation}
+%\begin{aligned}
+%\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
+%\end{aligned}\label{mpp}
+%\end{equation}
+%\begin{equation}
+%\begin{aligned}
+%\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
+%\end{aligned}
+%\label{qmn}
+%\end{equation}
+\section{An Algorithm to Identify Feasibility}
+In this section, we propose an algorithm to identify feasibility.
+\subsection{The Input And Output Of Algorithm}
+First, we summarize the input and output of our algorithm.
+The input of our algorithm is information of a PV array and a configuration.
+The information of a PV array is given as a set of panels and the number of working modules in each panel for each current candidate.
+Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}.
+For example, this table shows panel P2 includes three, two, and two modules that work in current 0.5A, 2A, and 3A, respectively.
+Recall that a configuration is a combination of a current assignment and the number of working modules in each string, and a current assignment specifies a current for each string.
+The output of our algorithm is feasibility of the given configuration.
+That is, the algorithm determines whether there exists assignment of panels to strings that realizes the configuration.
+\begin{table}[htbp] 
+\caption{Information of a PV array}
+\begin{center}
+%\begin{equation}
+%\begin{center}
+\begin{tabular}{l|lllllllll}
+    & P1 & P2 & P3 & P4 & P5 & P6 & P7 & P8 & P9 \\ \hline
+0.5A & 2  & 3  & 3  & 2  & 2  & 3  & 3  & 3  & 3  \\
+ 2A & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
+ 3A & 0  & 2  & 0  & 0  & 0  & 0  & 1  & 0  & 1 
+\end{tabular}\label{mpp3-1}
+%\end{center}
+%\end{equation}
+\end{center}
+\end{table}  
+%\subsection{Feasibility}
+%The feasibility of configuration based on the assumption of section \ref{array}, each string in PV array must have same number of panels.
 Definition of feasibility in (\ref{feas}).
 When a configuration needs panels in a string (\textit{$NP_n$}) are over maximum number of panels per-string(\textit{$NP_{stMAX}$}) this configuration is unfeasible.
-\begin{equation}
-\left\{\begin{matrix}
-NP_n > NP_{stMAX}& & \text{Unfeasible}\\ 
-NP_n \leq NP_{stMAX} & & \text{Feasible} 
-\label{feas}
-\end{matrix}\right. 
-\end{equation}
-For the first MPP candidate \{0.5, 0.5, 2\} need 8 modules for each string.
+%\begin{equation}
+%\left\{\begin{matrix}
+%NP_n > NP_{stMAX}& & \text{Unfeasible}\\ 
+%NP_n \leq NP_{stMAX} & & \text{Feasible} 
+%\label{feas}
+%\end{matrix}\right. 
+%\end{equation}
+%For the first MPP candidate \{0.5, 0.5, 2\} need 8 modules for each string.
 According to Table \ref{tab1}, for a string current on 2A at least need 4 panels and didn't meet feasible requirement, thus, algorithm terminate.
 The second MPP candidate \{0.5, 2, 2\} as same as previous one also not feasible.
+Recall that a configuration is a combination of a current assignment and the number of working modules in each string, and a current assignment specifies a current for each string.
+The output of our algorithm is feasibility of the given configuration.
+That is, the algorithm determines whether there exists assignment of panels to strings that realizes the configuration.
+\subsection{Panel Selection Strategy} \label{selection strategy}
+Let $s$ be the number of strings, and $i_h$ ($0\le h<s$) be the current assigned to the $h$-th string.
+Without loss of generality, we assume $i_0\le i_1\le \cdots \le i_{s-1}$ holds.
+In our algorithm, we first determine the assignment of panels for the $(s-1)$-th string (i.e., the string with the biggest current), and then determine assignments for $(s-2)$-th string, $(s-3)$-th string, and so on.
 
-\subsection{Panel Selection Strategy} \label{selection strategy}
+We explain the way to determine the assignment of the $(s-1)$-th string.
+To do this, we consider the number of working modules of each panel for currents less than $i_{s-1}$.
+Let $m_p(i)$ be the number of working modules of Panel $p$ that work in current $i$.
+For each panel $p$, we consider the difference vector $D_p=(m_p(i_{s-2})-m_p(i_{s-1}), m_p(i_{s-3})-m_p(i_{s-2}), \ldots, m_p(i_0)-m_p(1))$.
+The first element $d_1$ of $D_p$ means, if we use panel $p$ in current $i_{s-1}$, we lose $d_1$ working modules in current $i_{s-2}$.
+...
+Sorry, I didn't complete this comment.
+
 %Calculate MPP candidates based on existed reconfiguration method in \cite{b10}.
@@
 Element in the matrix corresponding to number of module which be able to working on string current.
-\begin{equation}
-%\begin{center}
-\begin{tabular}{l|lllllllll}
-    & P1 & P2 & P3 & P4 & P5 & P6 & P7 & P8 & P9 \\ \hline
-St1 & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
-St2 & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
-St3 & 0  & 2  & 0  & 0  & 0  & 0  & 1  & 0  & 1 
-\end{tabular}\label{mpp3-1}
-%\end{center}
-\end{equation}
+
 Then calculate number of module difference among string currents.

### 2018-09-01 main.tex
add fig
only missing P-V curve

@@
 The series connection accepts wider range of control voltage, and the parallel connection can generate higher current.
-
-When understanding complete I-V characteristics of some parallel and/or series connection of PV panels, we may need I-V characteristics of the PV panels.
+%When understanding complete I-V characteristics of some parallel and/or series connection of PV panels, we may need I-V characteristics of the PV panels.
 However, to find out the (near)  maximum generated power, it is enough to considers some restricted information including maximal power points (MPPs), a short circuit current, an open circuit voltage.
 These values form a fingerprint of the connection.
-
+When understanding complete I-V characteristics of some parallel and/or series connection of PV panels, we may need I-V characteristics of the PV panels.
+However, to find out the (near) maximum generated power, it is enough to considers some restricted information including maximal power points (MPPs).
+The algorithm in [6] analyzes the current versus voltage (I-V) curves of panels and finds MPPs, short circuit current, open circuit voltage of each panel in mismatched conditions.These values form a fingerprint of the connection.
 \begin{figure}
@@
 	\label{fig2a}
-	\includegraphics[width=4cm]{fig2.png} } \\
+	\includegraphics[width=8cm]{2panel.png}} \\
 \subfloat[]{
 	\label{fig2b}
-	\includegraphics[width=4cm]{fig2.png} }
+	\includegraphics[width=4cm]{ser.png} }
 \subfloat[]{
 	\label{fig2c}
-	\includegraphics[width=4cm]{fig2.png}} \\
+	\includegraphics[width=4cm]{par.png}} \\
 \caption{} 
 \end{figure}
-
 %We assume that each panel follows: The current versus voltage (\textit{I-V}) curve is acquired and calculated by algorithm presented in \cite{b6}.
 That algorithm will analyzes the panel \textit{I-V} curve sample by finding almost-constant-current and voltage regions and coordinate multiple maximum or minimum power point in the \textit{P-V} curve if PV array is working in mismatched conditions or not.
+
 In mismatched conditions, the power versus voltage (P-V) curve of each panel shows multiple MPPs (maximal power points).
@@
 \subsection{The Input And Output Of Algorithm}
-First, we summarize the input and output of our algorithm.
+%First, we summarize the input and output of our algorithm. 
 The input of our algorithm is information of a PV array and a configuration.
@@
 Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}.
-For example, this table shows panel P2 includes three, two, and two modules that work in current 0.5A, 2A, and 3A, respectively.
+For example, this table shows panel P2 includes three, two, and two modules that work in current 0.5A, 2A and 3A, respectively.
 Recall that a configuration is a combination of a current assignment and the number of working modules in each string, and a current assignment specifies a current for each string.
@@
 The second MPP candidate \{0.5, 2, 2\} as same as previous one also not feasible.
-Recall that a configuration is a combination of a current assignment and the number of working modules in each string, and a current assignment specifies a current for each string.
+%Recall that a configuration is a combination of a current assignment and the number of working modules in each string, and a current assignment specifies a current for each string.
 The output of our algorithm is feasibility of the given configuration.
@@
 Without loss of generality, we assume $i_0\le i_1\le \cdots \le i_{s-1}$ holds.
-In our algorithm, we first determine the assignment of panels for the $(s-1)$-th string (i.e., the string with the biggest current), and then determine assignments for $(s-2)$-th string, $(s-3)$-th string, and so on.
+In our algorithm, we first determine the assignment of panels for the $(s-1)$-th string (i.e., the string with the highest current), and then determine assignments for $(s-2)$-th string, $(s-3)$-th string, and so on.
 
@@
 The first element $d_1$ of $D_p$ means, if we use panel $p$ in current $i_{s-1}$, we lose $d_1$ working modules in current $i_{s-2}$.
-...
-Sorry, I didn't complete this comment.
-
+Then we sort panels in lexicographic order by vector $D_p$.
+This means, a panel with minimum module losses should firstly assign to the string with the highest current.
+%... Sorry, I didn't complete this comment.
+%\vspace{1cm}
 %Calculate MPP candidates based on existed reconfiguration method in \cite{b10}.
@@
 %\end{equation}
-
- In order to give more precise reconfiguration strategy.
+% In order to give more precise reconfiguration strategy.
 Our proposed algorithm firstly sort panels in a particular order for MPP candidates.
@@
 
-Then calculate number of module difference among string currents.
+%Then calculate number of module difference among string currents.
 For panel 1, difference between string 3 and string 2 is 1 (\textit{$Diff_1=1$}) and difference between string 2 and string 1 is 0 (\textit{$Diff_2=0$}).
@@
 As showed in matrix (\ref{sorted}).
-\begin{equation}
+\begin{table}[htbp] 
+\caption{Panel selection order}
+\begin{center}
+%\begin{equation}
 \begin{tabular}{l|lllllllll}
         & P2 & P3 & P1 & P5 & P7 & P9 & P4 & P6 & P8 \\ \hline 
-St1     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
-St2     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
-St3     & 2  & 0  & 0  & 0  & 1  & 1  & 0  & 0  & 0  \\
-\textit{$Diff_1$} & 0  & 0  & 1  & 1  & 1  & 1  & 2  & 2  & 3  \\
-\textit{$Diff_2$} & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0 
+2A     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
+2A     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
+3A     & 2  & 0  & 0  & 0  & 1  & 1  & 0  & 0  & 0  \\
+$d_1$ & 0  & 0  & 1  & 1  & 1  & 1  & 2  & 2  & 3  \\
+$d_2$ & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0 
 \end{tabular}\label{sorted}
-\end{equation}
-To find the best PV configuration, following steps are required:
+%\end{equation}
+\end{center}
+\end{table}
+Table \ref{sorted} shows the panel selection order of MPP candidate \{2A, 2A, 3A\} by given panel information from Table \ref{tab1}.
+For example shows panel P7 includes two, two and one modules that work in current 2A, 2A and 3A, respectively.
+So choosing panel P7 working on 3A will lose one module that can work on 2A.
+To assign panel in the right string, following steps are required:
 \begin{enumerate} [1-]
-\item Select panels in matrix (\ref{sorted}) from left side to right.
-\item If the element in matrix is 0, release corresponding panel
+\item Select panels in Table (\ref{sorted}) from left side to right.
+\item If the element in Table is 0, release corresponding panel
 \item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel.

### 2018-09-02 main.tex
20180901

@@
 \end{figure}
-
+\begin{figure}
+\centering 
+\subfloat[]{
+	\label{fig2a}
+	\includegraphics[width=8.5cm]{2panel.png} }\\
+\subfloat[]{
+	\label{fig2b}
+	\includegraphics[width=4.2cm]{ser.png} }
+\subfloat[]{
+	\label{fig2c}
+	\includegraphics[width=4.2cm]{par.png}} \\
+\caption{I-V curves, (a) 2 panels, (b) strings (series connection of PV panels), and (c) parallel connection of  PV panels}
+\end{figure}
 Fig.\ref{fig2a} shows  I-V curves for PV panels. PV panel generates a currents according to a provided control voltage within some range.
@@
 These values form a fingerprint of the connection.
+
 When understanding complete I-V characteristics of some parallel and/or series connection of PV panels, we may need I-V characteristics of the PV panels.
 However, to find out the (near) maximum generated power, it is enough to considers some restricted information including maximal power points (MPPs).
-The algorithm in [6] analyzes the current versus voltage (I-V) curves of panels and finds MPPs, short circuit current, open circuit voltage of each panel in mismatched conditions.These values form a fingerprint of the connection.
-\begin{figure}
-\centering 
-\subfloat[]{
-	\label{fig2a}
-	\includegraphics[width=8cm]{2panel.png}} \\
-\subfloat[]{
-	\label{fig2b}
-	\includegraphics[width=4cm]{ser.png} }
-\subfloat[]{
-	\label{fig2c}
-	\includegraphics[width=4cm]{par.png}} \\
-\caption{} 
-\end{figure}
+The algorithm in [6] analyzes the current versus voltage (I-V) curves of panels and finds MPPs, short circuit current, open circuit voltage of each panel in mismatched conditions.
+These values form a fingerprint of the connection.
+
 %We assume that each panel follows: The current versus voltage (\textit{I-V}) curve is acquired and calculated by algorithm presented in \cite{b6}.
@@
 String's length are identical based on when they connected in parallel, a string has more panels may cause current back flow into other strings which have less panels\cite{b8}.
+\section{Related Works}
+Carotenuto et al.
+proposed a online recording method of PV module fingerprint \cite{b6}.
+In their method, a fingerprint including the current and voltage at open- and short-circuit points and multiple MPPs are obtained from several samples from a monitored PV panel.
+Orozco-Gutierrez et al.
+proposed a method to estimate multiple MPPs of a PV array from fingerprints of PV panels in the PV array \cite{b7}.
+
+Orozco-Gutierrez et al.
+further proposed a Fast reconfiguration algorithm to optimize power generation by reconfiguring the connection of PV panels \cite{b10}, where the online monitoring \cite{b6} and the power estimation \cite{b7} are utilized.
+In the method in \cite{b10}, first, close values of fingerprints from monitoring of PV panels are grouped with some representative values, and then possible combinations of reconfiguration are enumerated.
+Their power values are estimated by \cite{b7} along with careful estimation of possible errors.
+The method presented a simple feasibility check and obtains estimated power values for all the possible connections for representative values with some error rate \textit{err}, and then select configurations within \textit{err} difference from the largest estimated value as candidates of the optical configurations.
+\begin{table}[htbp]
+\caption{DATASET OF PARTIAL-SHADING PV ARRAY}
+\begin{center}
+\begin{tabular}{cccc}
+%\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
+Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
+P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
+P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
+P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
+P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}None, 22.8, 22.8{]}    \\
+P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
+P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
+P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
+P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
+P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
 
@@
 In this section, we describe the overview of the Fast reconfiguration algorithm in \cite{b10}.
-First, the reconfiguration algorithm determines MPPs for PV modules in the mismatched condition by using algorithms in \cite{b6}\cite{b7}\cite{b9}.
-As an example, we consider a PV panel where nine panels are connected in three strings.
+First, the reconfiguration algorithm determines MPPs for PV modules in the mismatched condition by using algorithms in \cite{b6}\cite{b7}.
+As an example, we consider a PV array where nine panels are connected in three strings.
 We assume that, in this example, the reconfiguration algorithm finds MPPs given in Table \ref{tab1}.
@@
 \begin{aligned}
-\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
+\textit{MPP candidates}& = \\ [\{ 0.5, &0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
 \end{aligned}\label{mpp}
@@
 Considering there are some errors in previous estimation, this algorithm is not efficient for finding the best configuration.
-\begin{table}[htbp]
-\caption{}
-\begin{center}
-\begin{tabular}{cccc}
-\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
-Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
-P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
-P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
-P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
-P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}None, 22.8, 22.8{]}    \\
-P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
-P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
-P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
-P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
-P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
 
-\subsection{Feasibility Problem}
+\subsection{Feasibility Problem}\label{feasPro}
 To execute a power simulation, we have to assign panels to each string to realize a candidate configuration.
 However, the way is not given in \cite{b10} and some candidate configurations are infeasible.
+The definition of feasibility in (\ref{feas}).
+When a configuration needs working modules in a string (\textit{$M_S$}) are less than number of working module per-string (\textit{$Q_{M_{n}}$}), then this configuration is infeasible.
+\begin{equation}
+\left\{\begin{matrix}
+M_S < Q_{M_{n}} & & \text{Infeasible}\\ 
+M_S \geqslant Q_{M_{n}} & & \text{Feasible} 
+\label{feas}
+\end{matrix}\right. 
+\end{equation}
 For an configuration example \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string.
-According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings.Of course we can compute it by using an exhaustive search.
+According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings.
+Of course we can compute it by using an exhaustive search.
 However, it is time-consuming.
@@
 %The feasibility of configuration based on the assumption of section \ref{array}, each string in PV array must have same number of panels. 
-Definition of feasibility in (\ref{feas}).
+%Definition of feasibility in (\ref{feas}).
 When a configuration needs panels in a string (\textit{$NP_n$}) are over maximum number of panels per-string(\textit{$NP_{stMAX}$}) this configuration is unfeasible.
@@
 \begin{tabular}{l|lllllllll}
-        & P2 & P3 & P1 & P5 & P7 & P9 & P4 & P6 & P8 \\ \hline 
-2A     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
-2A     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
-3A     & 2  & 0  & 0  & 0  & 1  & 1  & 0  & 0  & 0  \\
+        & P3 & P2 & P1 & P5 & P7 & P9 & P4 & P6 & P8 \\ \hline 
+2A     & 0  & 2  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
+2A     & 0  & 2  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
+3A     & 0  & 2  & 0  & 0  & 1  & 1  & 0  & 0  & 0  \\
 $d_1$ & 0  & 0  & 1  & 1  & 1  & 1  & 2  & 2  & 3  \\
@@
 Table \ref{sorted} shows the panel selection order of MPP candidate \{2A, 2A, 3A\} by given panel information from Table \ref{tab1}.
-For example shows panel P7 includes two, two and one modules that work in current 2A, 2A and 3A, respectively.
+For this example, this table shows panel P7 includes two, two and one modules that work in current 2A, 2A and 3A, respectively.
 So choosing panel P7 working on 3A will lose one module that can work on 2A.
-To assign panel in the right string, following steps are required:
+To assign panels in the right string, following steps are required:
 \begin{enumerate} [1-]
-\item Select panels in Table (\ref{sorted}) from left side to right.
-\item If the element in Table is 0, release corresponding panel
+\item Select panels in Panel Selection Order Table from left side to right.
+\item If the element in Table is 0, release corresponding panel ,as panel P3.
 \item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel.
-As the example of string 2, selected panels are [Panel 1, Panel 5], these panels contain modules are equal to next unselect panel [Panel 4].
-Then swap [Panel 1, Panel 5] and [Panel4], release [Panel 1, Panel 5].
+As the example of string current on 2A, selected panels are panel P1, panel P5, these panels contain modules are equal to next unselect panel panel P4.
+Then swap (P1, P5) and P4, release P1 and P5.
 \label{replace}
@@
 \item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
-\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
+\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement in \ref{feasPro} equation (\ref{feas}).
+% and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
 \item If there remain any unselect panel, set unselect panel to a string with minimum length. 
 \end{enumerate}
+
 \subsection{Panel Replace Strategy}
 In the section \ref{selection strategy}, to obtain optimal panel selection need swap undesired panel.
-Based on section \ref{array}, each panel only contain three identical PV modules.
-So the element in selection matrix in the range of 0 to 3.
+Based on assumption from section \ref{array}, each panel only contain three identical PV modules.
+So the element in panel selection table in the range of 0 to 3.
 The replacement policy follows priorities are:
@@
 
-By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate 1 and MPP candidate 2.
-Configuration for MPP candidate 3 is that first string include Panel 1, Panel 2 and Panel 4; the second string include Panel 5, Panel 6 and Panel 7; the third string include Panel 3, Panel 8 and Panel 9.
-Configuration for MPP candidate 4 is that first string include Panel 1, Panel 5 and Panel 8; the second string include Panel 3, Panel 4 and Panel 6; the third string include Panel 2, Panel 7 and Panel 9.
+By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate \{0.5A, 0.5A, 2A\} and MPP candidate \{0.5A, 2A, 2A\}.
+Configuration for MPP candidate \{2A, 2A, 2A\} is that first string include Panel P1, P2 and P4; the second string include Panel P5, P6 and P7; the third string include Panel P3, P8 and P9.
+Configuration for MPP candidate \{2A, 2A, 3A\} is that first string include Panel P1, P5 and P8; the second string include Panel P3, P4 and P6; the third string include Panel P2, P7 and P9.
 Optimal configuration for this partial-shading PV array as showed in Fig.
 \ref{reconfiguration}.
-
 \begin{figure}%
@@
 \multicolumn{1}{c|}{Feasible Candidates}      & \multicolumn{1}{c|}{1180}              & 1278                                                                   \\ \hline
-\multicolumn{1}{c|}{Unfeasible Candidates}    & \multicolumn{1}{c|}{9781}              & 9683                                                                   \\ \hline
+\multicolumn{1}{c|}{Infeasible Candidates}    & \multicolumn{1}{c|}{9781}              & 9683                                                                   \\ \hline
 \multicolumn{1}{c|}{Error Rate}               & \multicolumn{1}{c|}{0.89\%}            & 0\%                                                                    \\ \hline
@@
 "Control of photovoltaic arrays: Dynamical reconfiguration for fighting mismatched conditions and meeting load requests." IEEE Industrial Electronics Magazine 9.1 (2015): 62-76.
-\bibitem{b9} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
+%\bibitem{b9} Carotenuto, Pietro Luigi, et al. "Online recording a PV module fingerprint." IEEE Journal of Photovoltaics 4.2 (2014): 659-668.
 \bibitem{b10} Orozco-Gutierrez, M. L., et al. "Optimized configuration of mismatched photovoltaic arrays." IEEE J. Photovolt 6.5 (2016): 1210-1220.

### 2018-09-02 main.tex
add fig

@@
     \centering
-    \subfloat[MPP candidate 3]{{\includegraphics[width=4cm]{mpp3.png} }}%
+    \subfloat[MPP candidate 3]{{\includegraphics[width=4cm]{MPP3.png} }}%
 %    \qquad
-    \subfloat[MPP candidate 4]{{\includegraphics[width=4cm]{mpp4.png} }}%
+    \subfloat[MPP candidate 4]{{\includegraphics[width=4cm]{MPP4.png} }}%
     \caption{Configuration of partial-shading PV array}%
@@
 	\label{fig5b}
-	\includegraphics[width=4cm]{mpp3.png} }
+	\includegraphics[width=4cm]{MPP3.png} }
 \subfloat[]{
 	\label{fig5c}
-	\includegraphics[width=4cm]{mpp4.png}} \\
+	\includegraphics[width=4cm]{MPP4.png}} \\
 \caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 2\} and (c) MPP candidate \{2, 2, 3\}} 
@@
 The \textit{P-V} curve for this PV array before and after reconfiguration are showed in Fig.\ref{fig6}.
-It can be seen that after reconfiguration maximum power (!!!!!!!!!!
-W and !!!!!!W) are significantly higher than before reconfiguration maximum power (!!!!!!!!W).
+It can be seen that after reconfiguration maximum power (283 W and 276W) are higher than before reconfiguration maximum power (277W).
 
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=5cm]{fig2.png}}
+\centerline{\includegraphics[width=8cm]{zhao.pdf}}
 \caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}

### 2018-09-02 main.tex
final version

@@
 {\footnotesize \textsuperscript{}}}
-
 \author{\IEEEauthorblockN{1\textsuperscript{st} Dafang Zhao}
@@
 	\label{fig2a}
-	\includegraphics[width=8.5cm]{2panel.png} }\\
+	\includegraphics[width=4.2cm]{P2.pdf}
+        \includegraphics[width=4.2cm]{P1.pdf}}\\
 \subfloat[]{
 	\label{fig2b}
-	\includegraphics[width=4.2cm]{ser.png} }
+	\includegraphics[width=4.2cm]{ser.pdf} }
 \subfloat[]{
 	\label{fig2c}
-	\includegraphics[width=4.2cm]{par.png}} \\
+	\includegraphics[width=4.2cm]{par.pdf}} \\
 \caption{I-V curves, (a) 2 panels, (b) strings (series connection of PV panels), and (c) parallel connection of  PV panels}
@@
 However, to find out the (near) maximum generated power, it is enough to considers some restricted information including maximal power points (MPPs).
-The algorithm in [6] analyzes the current versus voltage (I-V) curves of panels and finds MPPs, short circuit current, open circuit voltage of each panel in mismatched conditions.
+The algorithm in \cite{b6} analyzes the current versus voltage (I-V) curves of panels and finds MPPs, short circuit current, open circuit voltage of each panel in mismatched conditions.
 These values form a fingerprint of the connection.
@@
 
-In mismatched conditions, the power versus voltage (P-V) curve of each panel shows multiple MPPs (maximal power points).
+%In mismatched conditions, the power versus voltage (P-V) curve of each panel shows multiple MPPs (maximal power points).
 We refer to a MPP by a pair $(V_{mpp},I_{mpp})$ where $V_{mpp}$ and $I_{mpp}$ are the voltage and the current that give a maximal power, respectively.
 The algorithm in \cite{b6} analyzes the current versus voltage (I-V) curves of panels and finds MPPs of each panel in mismatched conditions.
+
 %All the panels in PV array have the same number (\textit{N}) of modules.
@@
 \item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel.
-As the example of string current on 2A, selected panels are panel P1, panel P5, these panels contain modules are equal to next unselect panel panel P4.
+As the example of string current on 2A, selected panels are panel P1 and P5, these panels contain modules are equal to next unselect panel P4.
 Then swap (P1, P5) and P4, release P1 and P5.
@@
 % and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
-\item If there remain any unselect panel, set unselect panel to a string with minimum length. 
+\item If there remain any unselect panel, assign unselect panel to a string with minimum length. 
 \end{enumerate}
@@
 By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate \{0.5A, 0.5A, 2A\} and MPP candidate \{0.5A, 2A, 2A\}.
-Configuration for MPP candidate \{2A, 2A, 2A\} is that first string include Panel P1, P2 and P4; the second string include Panel P5, P6 and P7; the third string include Panel P3, P8 and P9.
-Configuration for MPP candidate \{2A, 2A, 3A\} is that first string include Panel P1, P5 and P8; the second string include Panel P3, P4 and P6; the third string include Panel P2, P7 and P9.
-Optimal configuration for this partial-shading PV array as showed in Fig.
-\ref{reconfiguration}.
-\begin{figure}%
+Configuration for MPP candidate \{2A, 2A, 2A\} as shown in Fig.\ref{recon-a} is that first string include Panel P1, P2 and P4; the second string include Panel P5, P6 and P7; the third string include Panel P3, P8 and P9.
+Configuration for MPP candidate \{2A, 2A, 3A\} as shown in Fig.\ref{recon-b} is that first string include Panel P1, P5 and P8; the second string include Panel P3, P4 and P6; the third string include Panel P2, P7 and P9.
+%% Optimal configuration for this partial-shading PV array as showed in Fig. \ref{reconfiguration}.
+
+\begin{figure}
 \centering 
-    \subfloat[MPP candidate 3]{{\includegraphics[width=4cm]{MPP3.png} }}%
-%    \qquad
-    \subfloat[MPP candidate 4]{{\includegraphics[width=4cm]{MPP4.png} }}%
-    \caption{Configuration of partial-shading PV array}%
-    \label{reconfiguration}%
+\subfloat[]{
+	\label{recon-a}
+	\includegraphics[width=4cm]{MPP3.png} }
+\subfloat[]{
+	\label{recon-b}
+	\includegraphics[width=4cm]{MPP4.png}} \\
+\caption{Configuration of partial-shading PV array}
 \end{figure}
+
+%% \begin{figure}%
+%%     \centering
+%%     \subfloat[MPP candidate 3]{{\includegraphics[width=4cm]{MPP3.png} }}%
+%% %    \qquad
+%%     \subfloat[MPP candidate 4]{{\includegraphics[width=4cm]{MPP4.png} }}%
+%%     \caption{Configuration of partial-shading PV array}%
+%%     \label{reconfiguration}%
+%% \end{figure}
 
@@
 Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected strings is the same.
-This section verifies the effectiveness of proposed algorithm using Matlab simulation.
+%This section verifies the effectiveness of proposed algorithm using Matlab simulation.
 With pilot example presented in last section, shading scenario as showed in Fig.\ref{fig5a}.
@@
 
-\begin{figure}
-\centering 
-\subfloat[]{
-	\label{fig5a}
-	\includegraphics[width=5cm]{paper-fig5(a).png} } \\
-\subfloat[]{
-	\label{fig5b}
-	\includegraphics[width=4cm]{MPP3.png} }
-\subfloat[]{
-	\label{fig5c}
-	\includegraphics[width=4cm]{MPP4.png}} \\
-\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 2\} and (c) MPP candidate \{2, 2, 3\}} 
-\end{figure}
+%% \begin{figure}
+%% \centering 
+%% \subfloat[]{
+%% 	\label{fig5a}
+%% 	\includegraphics[width=5cm]{paper-fig5(a).png} } \\
+%% \subfloat[]{
+%% 	\label{fig5b}
+%% 	\includegraphics[width=4cm]{MPP3.png} }
+%% \subfloat[]{
+%% 	\label{fig5c}
+%% 	\includegraphics[width=4cm]{MPP4.png}} \\
+%% \caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 2\} and (c) MPP candidate \{2, 2, 3\}} 
+%% \end{figure}
 
-%% \begin{figure}[htbp]            
+%%\begin{figure}[htbp]      
 %% \begin{minipage}[t]{0.5\linewidth}
@@
 
-As shown, working module on each string are large or equal than required \textit{$Q_{M_n}$}, which means mismatched power loss are minimized.
+As shown in previous section, working modules on each string are large or equal than required \textit{$Q_{M_n}$}, which means mismatched power loss are minimized.
 The \textit{P-V} curve for this PV array before and after reconfiguration are showed in Fig.\ref{fig6}.
@@
 %The simulations were performed using an Intel i7-4770 3.2-Ghz processor with 32.0 GB of RAM memory. 
-The calculation time used by the proposed algorithm for one MPP candidate was 157 ms, which is significantly lower compared with exhaustive search 1hour 12min 50s and accuracy are higher than methods proposed in \cite{b10} \cite{b12}.
+The calculation time used by the proposed algorithm for one MPP candidate was 157 ms, which is significantly lower compared with exhaustive search 1hour 12min 50s and accuracy are higher than methods proposed in \cite{b10}.
 \section{conclusions}
-The existing PV reconfiguration methods either have high accuracy but suffer from long computational time such as exhausted searching algorithm or GA, or they have short computational time but do not guarantee the best configuration as described in \cite{b10} \cite{b11} \cite{b12}.
+The existing PV reconfiguration methods either have high accuracy but suffer from long computational time such as exhausted searching algorithm or GA, or they have short computational time but do not guarantee the best configuration as described in \cite{b10}.
 This paper proposed a new PV system reconfiguration algorithm with feasibility check function and have high accuracy and less computational time.
@@
 The result shows that proposed algorithm has high accuracy and less computational time.
-
 \begin{thebibliography}{00}
@@
 \bibitem{b7} Orozco-Gutierrez, M. L., et al. "Fast estimation of MPPs in mismatched PV arrays based on lossless model." Clean Electrical Power (ICCEP), 2015 International Conference on. IEEE, 2015.
-\bibitem{b8} Spagnuolo, Giovanni, et al.
+%% \bibitem{b8} Spagnuolo, Giovanni, et al.
 "Control of photovoltaic arrays: Dynamical reconfiguration for fighting mismatched conditions and meeting load requests." IEEE Industrial Electronics Magazine 9.1 (2015): 62-76.
@@
 \bibitem{b10} Orozco-Gutierrez, M. L., et al. "Optimized configuration of mismatched photovoltaic arrays." IEEE J. Photovolt 6.5 (2016): 1210-1220.
-\bibitem{b11} El-Dein, MZ Shams, Mehrdad Kazerani, and M. M. A. Salama. "Optimal photovoltaic array reconfiguration to reduce partial shading losses." IEEE Trans. Sustain. Energy 4.1 (2013): 145-153.
-\bibitem{b12} Storey, Jonathan P., Peter R.
+%% \bibitem{b11} El-Dein, MZ Shams, Mehrdad Kazerani, and M.
+M.
+A.
+Salama.
+"Optimal photovoltaic array reconfiguration to reduce partial shading losses." IEEE Trans.
+Sustain.
+Energy 4.1 (2013): 145-153.
+%% \bibitem{b12} Storey, Jonathan P., Peter R.
 Wilson, and Darren Bagnall.

### 2018-09-03 main.tex
modify figure

@@
 \begin{document}
-\title{Photovoltaic System Reconfiguration strategy for mismatch condition\\
+\title{Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\
 {\footnotesize \textsuperscript{}}}
@@
 As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}.
-After that, the reconfiguration algorithm generates candidates of current assignments, where the current assignment specifies a current of each string.
-The reconfiguration algorithm treats the current of each MPP as a current candidate for string, and constructs a current assignment by assigning a current candidate to each string.
+After that, the Fast reconfiguration algorithm generates candidates of current assignments 
+%% where the current assignment specifies a current of each string. The reconfiguration algorithm
+and treats the current of each MPP as a current candidate for string, constructs a current assignment by assigning a current candidate to each string.
 The reconfiguration algorithm generates current assignments by considering all combinations of current candidates for string.
 %Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. 
-Then, for each current assignment, the reconfiguration algorithm computes the number of working modules in each string.
-We define a configuration as a combination of a current assignment and the number of working modules (\textit{$Q_{M_n}$}) in each string.
-MPP candidates are presented in (\ref{mpp}) and number of working modules of MPP candidates are presented in (\ref{qmn}), respectively.
+Then, for each current assignment, the reconfiguration algorithm computes the number of working modules (\textit{$Q_{M_n}$}) in each string.
+We define a configuration as a combination of a current assignment and the number of working modules in each string.
+MPP candidates are presented in (\ref{mpp}) and number of working modules for each string are presented in (\ref{qmn}), respectively.
 
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=8cm]{flowchart.png}}
+\centerline{\includegraphics[width=8cm]{flowchart(1).png}}
 \caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
@@
 \item Select panels in Panel Selection Order Table from left side to right.
-\item If the element in Table is 0, release corresponding panel ,as panel P3.
+\item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
 \item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel.
@@
 \begin{enumerate} [ (1) ]
-\item Swap a panel contain 3 working modules to \textbf{three} panels each contain 1 working module.
-\item Swap a panel contain 3 working modules to \textbf{one} panel contain 1 working module and \textbf{one} contain 2 working modules.
-\item Swap a panel contain 2 working modules to \textbf{two} panels each contain 1 working module.
+\item Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{three} panels each contain 1 working module ($m_p(i)$ = 1).
+\item Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{one} panel contain 1 working module ($m_p(i)$ = 1) and \textbf{one} contain 2 working modules ($m_p(i)$ = 2).
+\item Swap a panel contain 2 working modules ($m_p(i)$ = 2) to \textbf{two} panels each contain 1 working module ($m_p(i)$ = 1).
 \end{enumerate}
@@
 The computational time required to find the best configuration and accuracy of configuration in the proposed and exhaustive search algorithm are compared and summarized in Table \ref{tab2}.
-As shown in Table \ref{tab2}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm and methods described in \cite{b10}.
-%\cite{b11} \cite{b12}.
+As shown in Table \ref{tab2}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm.
+%% and methods described in \cite{b10}. %\cite{b11} \cite{b12}.
 
@@
 \multicolumn{3}{c}{\begin{tabular}[c]{@{}c@{}}COMPARISON BETWEEN EXISTED METHODS\\ AND PROPOSED ALGORITHM\end{tabular}}                                         \\ \hline \hline
-\multicolumn{1}{c|}{}                         & \multicolumn{1}{c|}{Propose Algorithm} & \begin{tabular}[c]{@{}c@{}}Exhaustive search \\ Algorithm\end{tabular} \\ \hline
+\multicolumn{1}{c|}{}                         & \multicolumn{1}{c|}{Proposed Algorithm} & \begin{tabular}[c]{@{}c@{}}Exhaustive search \\ Algorithm\end{tabular} \\ \hline
 \multicolumn{1}{c|}{Number of PV Array}       & \multicolumn{2}{c}{300}                                                                                         \\ \hline
@@
 %The simulations were performed using an Intel i7-4770 3.2-Ghz processor with 32.0 GB of RAM memory. 
-The calculation time used by the proposed algorithm for one MPP candidate was 157 ms, which is significantly lower compared with exhaustive search 1hour 12min 50s and accuracy are higher than methods proposed in \cite{b10}.
+The calculation time used by the proposed algorithm for one MPP candidate was 157 ms, which is significantly lower compared with exhaustive search 1hour 12min 50s and accuracy are higher than exhaustive search algorithm.
 \section{conclusions}

### 2018-09-03 main.tex
author
dadada

@@
   {\footnotesize \textsuperscript{}}}
-\author{\IEEEauthorblockN{1\textsuperscript{st} Dafang Zhao}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}}
+
+\author{\IEEEauthorblockN{Dafang Zhao, Michiko Inoue, Ooshita Fukuhito}
+  \IEEEauthorblockA{\textit{Graduate School of Science and Technology, Nara Institute of Science and Technology (NAIST) \\8916-5 Takoyama-cho, Ikoma, Nara, 630-0192 Japan}}}
+%%% \IEEEauthorblock\{dafang-z.yu7, kounoe, f-ooshita\}@is.naist.jp}}
+%%% \{dafang-z.yu7, kounoe, f-ooshita\}@is.naist.jp
+
+ \author{\IEEEauthorblockN{Dafang Zhao}
+ \IEEEauthorblockA{\textit{Graduate School of Information Science} \\
+ \textit{Nara Institute of Science and Technology}}
+ \\
+ \IEEEauthorblockN{ Michiko Inoue}
+ \IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
+ \textit{Nara Institute of Science and Technology}}
  \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}}}
+ \IEEEauthorblockN{Fukuhito Ooshita}
+ \IEEEauthorblockA{\textit{Graduate School of Science and Technolog} \\
+ \textit{Nara Institute of Science and Technology}}}
 
 \maketitle
-
 \begin{abstract}
@@
 The method presented a simple feasibility check and obtains estimated power values for all the possible connections for representative values with some error rate \textit{err}, and then select configurations within \textit{err} difference from the largest estimated value as candidates of the optical configurations.
-\begin{table}[htbp]
-\caption{DATASET OF PARTIAL-SHADING PV ARRAY}
-\begin{center}
-\begin{tabular}{cccc}
-%\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
-Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
-P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
-P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
-P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
-P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}None, 22.8, 22.8{]}    \\
-P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
-P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
-P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
-P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
-P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
+
+The method \cite{b10} needs to check feasibility since their method designate a configuration with number of strings, the number of active modules for one string and current value of each string where the active module means a module whose bypass diode is not working and the number of active modules of strings are common for all the strings have the common control voltage.
+For example, if a connection requires two strings with two active modules with 3A and 5A for these strings respectively, we might not find possible combination of PV panels.
+In [10], a simple feasibility check based on the number of active modules for each representative current values.
+However, we found out that the feasibility check proposed in [10] is optimistic and does not always identify infeasible cases.
+
+%\begin{table}[htbp]
+%\caption{DATASET OF PARTIAL-SHADING PV ARRAY}
+%\begin{center}
+%\begin{tabular}{cccc}
+%%\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
+%Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
+%P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
+%P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
+%P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
+%P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}None, 22.8, 22.8{]}    \\
+%P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
+%P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
+%P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
+%P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
+%P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
+%\end{tabular}
+%\label{tab1}
+%\end{center}
+%\end{table}
 

### 2018-09-03 main.tex
final version

@@
 \usepackage{subfig}
+\usepackage{fancyhdr}
+\usepackage{lipsum}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 For example, if a connection requires two strings with two active modules with 3A and 5A for these strings respectively, we might not find possible combination of PV panels.
-In [10], a simple feasibility check based on the number of active modules for each representative current values.
-However, we found out that the feasibility check proposed in [10] is optimistic and does not always identify infeasible cases.
+In \cite{b10}, a simple feasibility check based on the number of active modules for each representative current values.
+However, we found out that the feasibility check proposed in \cite{b10} is optimistic and does not always identify infeasible cases.
 
@@
 
-\section{Reconfiguration Algorithm} \label{algo}
+%% \section{Reconfiguration Algorithm} \label{algo}
 
-\subsection{Overview of the algorithm}
-In this section, we describe the overview of the Fast reconfiguration algorithm in \cite{b10}.
+%% \subsection{Overview of the algorithm}
+%% In this section, we describe the overview of the Fast reconfiguration algorithm in \cite{b10}.
 First, the reconfiguration algorithm determines MPPs for PV modules in the mismatched condition by using algorithms in \cite{b6}\cite{b7}.
@@
 We assume that, in this example, the reconfiguration algorithm finds MPPs given in Table \ref{tab1}.
-%To reconfigure a large scale partial shading PV array, an example refers to 9 panels which have been connected in 3 strings. In this example, mismatching conditions presented in Table \ref{tab1}. 
-%Each panel made of 3 identical PV modules (\textit{N=3}), dataset in Table \ref{tab1} are provide by method in \cite{b6} \cite{b7}.
+%% %To reconfigure a large scale partial shading PV array, an example refers to 9 panels which have been connected in 3 strings. In this example, mismatching conditions presented in Table \ref{tab1}. 
+%% %Each panel made of 3 identical PV modules (\textit{N=3}), dataset in Table \ref{tab1} are provide by method in \cite{b6} \cite{b7}.
 As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}.
-After that, the Fast reconfiguration algorithm generates candidates of current assignments 
-%% where the current assignment specifies a current of each string. The reconfiguration algorithm
-and treats the current of each MPP as a current candidate for string, constructs a current assignment by assigning a current candidate to each string.
+%% After that, the Fast reconfiguration algorithm generates candidates of current assignments 
+%% %% where the current assignment specifies a current of each string. The reconfiguration algorithm
+%% and treats the current of each MPP as a current candidate for string, constructs a current assignment by assigning a current candidate to each string.
 The reconfiguration algorithm generates current assignments by considering all combinations of current candidates for string.
-%Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. 
-Then, for each current assignment, the reconfiguration algorithm computes the number of working modules (\textit{$Q_{M_n}$}) in each string.
+%% %Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. 
+%% Then, for each current assignment, the reconfiguration algorithm computes the number of working modules (\textit{$Q_{M_n}$}) in each string.
 We define a configuration as a combination of a current assignment and the number of working modules in each string.
@@
 
-\begin{equation}
-\begin{aligned}
-\textit{MPP candidates}& = \\ [\{ 0.5, &0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
-\end{aligned}\label{mpp}
-\end{equation}
-\begin{equation}
-\begin{aligned}
-\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
-\end{aligned}
-\label{qmn}
-\end{equation}
-By this algorithm, we obtain a set of candidate configurations.
+%% \begin{equation}
+%% \begin{aligned}
+%% \textit{MPP candidates}& = \\ [\{ 0.5, &0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
+%% \end{aligned}\label{mpp}
+%% \end{equation}
+%% \begin{equation}
+%% \begin{aligned}
+%% \textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
+%% \end{aligned}
+%% \label{qmn}
+%% \end{equation}
+%% By this algorithm, we obtain a set of candidate configurations.
 Since we can estimate the generated power of each candidate configuration, we can select the candidate configuration that maximizes the generated power.
-%\vspace{10cm}
-%Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates.
+%% %\vspace{10cm}
+%% %Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates.
 Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array.
-The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}. 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=8cm]{flowchart(1).png}}
-\caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
-\label{flowchart}
-\end{figure}
-The previous estimation can not give precise reconfiguration answer.
+%% The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}. 
+%% \begin{figure}[htbp]
+%% \centerline{\includegraphics[width=8cm]{flowchart(1).png}}
+%% \caption{Flowchart of reconfiguration algorithm in \cite{b10}.}
+%% \label{flowchart}
+%% \end{figure}
+%% The previous estimation can not give precise reconfiguration answer.
 This algorithm lists some candidate configurations ( in addition to the maximum one ) and for each candidate configuration it will executes a time consuming and precise power simulation.
@@
 
-\subsection{Feasibility Problem}\label{feasPro}
+\begin{table}[htbp]
+\caption{Dataset of Each PV Panel}
+\begin{center}
+\begin{tabular}{c|c|c|c|c|c|c|c|c|c}
+     & P1 & P2  & P3  & P4 & P5 & P6  & P7  & P8  & P9  \\ \hline
+0.5A & ** & *** & *** & ** & ** & *** & *** & *** & *** \\ \hline
+2A   & *  & **  &     & ** & *  & **  & **  & *** & **  \\ \hline
+3A   &    & **  &     &    &    &     & *   &     & *  
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+
+\section{Feasibility}\label{feasPro}
+As an example, we consider a PV array where nine panels are connected in three strings.
+We assume that, in this example, this Fast reconfiguration algorithm estimate number of working module on different current candidate for each panel as shown in Table \ref{tab1}.
+The dot in table in form of a PV module.
+We set $N_C$ as the meaning of not candidate, set infeasible MPPs as zero.
+Though the procedure in Fast reconfiguration algorithm and simple feasibility check, MPPs are presented in matrix below.
+[C1, C2, C3, C4] indicate 4 MPP candidates.
+
 To execute a power simulation, we have to assign panels to each string to realize a candidate configuration.
@@
 \end{equation}
-For an configuration example \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string.
+For an configuration example [C2] \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string.
 According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings.
@@
 \subsection{The Input And Output Of Algorithm}
+
 %First, we summarize the input and output of our algorithm. 
@@
 The information of a PV array is given as a set of panels and the number of working modules in each panel for each current candidate.
-Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}.
+Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}.\\
+\begin{table}[htbp]
+  \begin{center}
+    %% \binom{\begin{pmatrix}
+    \begin{tabular}[]{ccccccccccc}
+ $\frac{Current \rightarrow }{Number\ of\ modules\downarrow}$&\{0.5,0.5,0.5\}&\{0.5,0.5,2\}&\{0.5,0.5,3\}&\{0.5,2,2\}&\{0.5,2,3\}&\{0.5,3,3\}&\{2,2,2\}&\{2,2,3\}&\{2,3,3\}&\{3,3,3\}\\ \hline \hline
+$\geq 1$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  \\
+$\geq 2$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  \\
+$\geq 3$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  &$N_C$  &0      &0 \\
+$\geq 4$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  & C4    &0      &0 \\
+$\geq 5$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &C3     &0      &0      &0  \\
+$\geq 6$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &0      &0      &0      &0 \\
+$\geq 7$ &$N_C$  &$N_C$  &0      &C2     &0     &0      &0      &0      &0      &0 \\
+$\geq 8$ &$N_C$  &C1     &0      &0      &0     &0      &0      &0      &0      &0
+    \end{tabular}\label{mppcandidates}
+    \end{center}
+\end{table}
+
 For example, this table shows panel P2 includes three, two, and two modules that work in current 0.5A, 2A and 3A, respectively.
@@
 That is, the algorithm determines whether there exists assignment of panels to strings that realizes the configuration.
-\subsection{Panel Selection Strategy} \label{selection strategy}
+\subsection{Algorithm} \label{selection strategy}
 Let $s$ be the number of strings, and $i_h$ ($0\le h<s$) be the current assigned to the $h$-th string.
@@
 
-We explain the way to determine the assignment of the $(s-1)$-th string.
+To assign panels in the right string, following steps are required:
+\begin{enumerate} [(1)]
+\item Select panels in Panel Selection Order Table. The detail explanation are described next pargraph.\label{step1}
+\item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
+\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. The replacement will following servious priorities.
+  %% As the example of string current on 2A, selected panels are panel P1 and P5, these panels contain modules are equal to next unselect panel P4. Then swap (P1, P5) and P4, release P1 and P5.
+  \label{replace}
+  %% \subitem  Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{three} panels each contain 1 working module ($m_p(i)$ = 1).
+  %% \subitem Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{one} panel contain 1 working module ($m_p(i)$ = 1) and \textbf{one} contain 2 working modules ($m_p(i)$ = 2).
+  %% \subitem Swap a panel contain 2 working modules ($m_p(i)$ = 2) to \textbf{two} panels each contain 1 working module ($m_p(i)$ = 1).
+%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
+\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
+\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement in \ref{feasPro} equation (\ref{feas}).
+% and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
+\item If there remain any unselect panel, assign unselect panel to a string with minimum length. 
+\end{enumerate}
+\vspace{5.7cm}
+
+\newpage
+We explain step (\ref{step1}) that determine the assignment of the $h$-th string.
 To do this, we consider the number of working modules of each panel for currents less than $i_{s-1}$.
@@
 \begin{table}[htbp] 
-\caption{Panel selection order}
+\caption{Panel selection Table}
 \begin{center}
@@
 So choosing panel P7 working on 3A will lose one module that can work on 2A.
-To assign panels in the right string, following steps are required:
-\begin{enumerate} [1-]
-\item Select panels in Panel Selection Order Table from left side to right.
-\item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
-\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel.
+%% To assign panels in the right string, following steps are required:
+%% \begin{enumerate} [1-]
+%% \item Select panels in Panel Selection Order Table from left side to right.
+%% \item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
+%% \item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel.
 As the example of string current on 2A, selected panels are panel P1 and P5, these panels contain modules are equal to next unselect panel P4.
@@
 \label{replace}
-%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
-\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
-\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement in \ref{feasPro} equation (\ref{feas}).
-% and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
-\item If there remain any unselect panel, assign unselect panel to a string with minimum length. 
-\end{enumerate}
+%% %\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
+%% \item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
+%% \item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement in \ref{feasPro} equation (\ref{feas}).
+%% % and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
+%% \item If there remain any unselect panel, assign unselect panel to a string with minimum length. 
+%% \end{enumerate}
 
-\subsection{Panel Replace Strategy}
-In the section \ref{selection strategy}, to obtain optimal panel selection need swap undesired panel.
-Based on assumption from section \ref{array}, each panel only contain three identical PV modules.
-So the element in panel selection table in the range of 0 to 3.
-The replacement policy follows priorities are:
-\begin{enumerate} [ (1) ]
+In the step (\ref{replace}), to obtain optimal panel selection need swap undesired panel. The replacement policy follows priorities are:
+\begin{enumerate} [1- ]
 \item Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{three} panels each contain 1 working module ($m_p(i)$ = 1).
@@
 
-By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate \{0.5A, 0.5A, 2A\} and MPP candidate \{0.5A, 2A, 2A\}.
+%% By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate \{0.5A, 0.5A, 2A\} and MPP candidate \{0.5A, 2A, 2A\}.
 Configuration for MPP candidate \{2A, 2A, 2A\} as shown in Fig.\ref{recon-a} is that first string include Panel P1, P2 and P4; the second string include Panel P5, P6 and P7; the third string include Panel P3, P8 and P9.
@@
 
-\begin{figure}
-\centering 
-\subfloat[]{
-	\label{recon-a}
-	\includegraphics[width=4cm]{MPP3.png} }
-\subfloat[]{
-	\label{recon-b}
-	\includegraphics[width=4cm]{MPP4.png}} \\
-\caption{Configuration of partial-shading PV array}
-\end{figure}
+%% \begin{figure}
+%% \centering 
+%% \subfloat[]{
+%% 	\label{recon-a}
+%% 	\includegraphics[width=4cm]{MPP3.png} }
+%% \subfloat[]{
+%% 	\label{recon-b}
+%% 	\includegraphics[width=4cm]{MPP4.png}} \\
+%% \caption{Configuration of partial-shading PV array}
+%% \end{figure}
 
@@
 
-As shown in previous section, working modules on each string are large or equal than required \textit{$Q_{M_n}$}, which means mismatched power loss are minimized.
+%% As shown in previous section, working modules on each string are large or equal than required \textit{$Q_{M_n}$}, which means mismatched power loss are minimized.
 The \textit{P-V} curve for this PV array before and after reconfiguration are showed in Fig.\ref{fig6}.
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=8cm]{zhao.pdf}}
-\caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}
-\label{fig6}
-\end{figure}
+%% \begin{figure}[htbp]
+%% \centerline{\includegraphics[width=8cm]{zhao.pdf}}
+%% \caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}
+%% \label{fig6}
+%% \end{figure}
 
-To evaluate the performance of proposed algorithm, we compare the propose algorithm with exhaustive search algorithm for 300 different partial-shading PV arrays.
-For each PV array, contain 2$\sim$15 PV panels connected into 2$\sim$5 strings.
-The PV panels will have contain 2$\sim$20 different current candidates.
+To evaluate the performance of proposed algorithm, we compare the proposed algorithm with exhaustive search algorithm for 300 different partial-shading PV arrays.
+For each PV array, contain 2-15 PV panels connected into 2-5 strings.
+The PV panels will have contain 2-20 different current candidates.
 
 The computational time required to find the best configuration and accuracy of configuration in the proposed and exhaustive search algorithm are compared and summarized in Table \ref{tab2}.
-As shown in Table \ref{tab2}, proposed algorithm achieved high accuracy and less computing time compare with exhaustive search algorithm.
+As shown in Table \ref{tab2}, proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.
 %% and methods described in \cite{b10}. %\cite{b11} \cite{b12}.

### 2018-09-14 main.tex
20180910
grammar check

@@
  \IEEEauthorblockN{Fukuhito Ooshita}
- \IEEEauthorblockA{\textit{Graduate School of Science and Technolog} \\
+ \IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
  \textit{Nara Institute of Science and Technology}}}
@@
 Their power values are estimated by \cite{b7} along with careful estimation of possible errors.
-The method presented a simple feasibility check and obtains estimated power values for all the possible connections for representative values with some error rate \textit{err}, and then select configurations within \textit{err} difference from the largest estimated value as candidates of the optical configurations.
+The method presented a simplify feasibility check and obtains estimated power values for all the possible connections for representative values with some error rate \textit{err}, and then select configurations within \textit{err} difference from the largest estimated value as candidates of the optical configurations.
 
@@
 For example, if a connection requires two strings with two active modules with 3A and 5A for these strings respectively, we might not find possible combination of PV panels.
-In \cite{b10}, a simple feasibility check based on the number of active modules for each representative current values.
+In \cite{b10}, a simplify feasibility check based on the number of active modules for each representative current values.
 However, we found out that the feasibility check proposed in \cite{b10} is optimistic and does not always identify infeasible cases.
@@
 We set $N_C$ as the meaning of not candidate, set infeasible MPPs as zero.
-Though the procedure in Fast reconfiguration algorithm and simple feasibility check, MPPs are presented in matrix below.
+Through the procedure in Fast reconfiguration algorithm and simplify feasibility check, MPPs are presented in matrix below.
 [C1, C2, C3, C4] indicate 4 MPP candidates.
@@
 The information of a PV array is given as a set of panels and the number of working modules in each panel for each current candidate.
-Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}.\\
+Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}.
 \begin{table}[htbp]
@@
     \begin{tabular}[]{ccccccccccc}
- $\frac{Current \rightarrow }{Number\ of\ modules\downarrow}$&\{0.5,0.5,0.5\}&\{0.5,0.5,2\}&\{0.5,0.5,3\}&\{0.5,2,2\}&\{0.5,2,3\}&\{0.5,3,3\}&\{2,2,2\}&\{2,2,3\}&\{2,3,3\}&\{3,3,3\}\\ \hline \hline
+ $\frac{Current\ \rightarrow }{Number\ of\ modules\ \downarrow}$&\{0.5,0.5,0.5\}&\{0.5,0.5,2\}&\{0.5,0.5,3\}&\{0.5,2,2\}&\{0.5,2,3\}&\{0.5,3,3\}&\{2,2,2\}&\{2,2,3\}&\{2,3,3\}&\{3,3,3\}\\  \\ \hline \hline
 $\geq 1$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  \\

### 2018-09-14 main.tex
Updates from ShareLaTeX
grammar check finished

@@
 \begin{IEEEkeywords}
-  Photovoltaic system, mismathed power loss, reconfiguration, dynamical reconfiguration.
+  Photovoltaic system, mismatched power loss, reconfiguration, dynamical reconfiguration.
 \end{IEEEkeywords}
@@
 One PV panel typically has two (plus and minus) terminals, and a PV array is configured by connecting PV panels in series and/or parallel.
-Such a configuration is also realized using a switch among PV panels, and reconfigurations in PV panel level can be regarded as  practical solutions.
+Such a configuration is also realized using a switch among PV panels, and re-configurations in PV panel level can be regarded as  practical solutions.
 However, the reconfiguration in PV panel level is more difficult than that in PV cell level.
@@
 For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify voltage and current values on different maximum power point by index \textit{n}.
-Those parameters can be directly estimated by the prosess provided in\cite{b7}.
+Those parameters can be directly estimated by the process provided in\cite{b7}.
 
@@
 Orozco-Gutierrez et al.
-further proposed a Fast reconfiguration algorithm to optimize power generation by reconfiguring the connection of PV panels \cite{b10}, where the online monitoring \cite{b6} and the power estimation \cite{b7} are utilized.
+further proposed a Fast reconfiguration algorithm to optimize power generation by re-configuring the connection of PV panels \cite{b10}, where the online monitoring \cite{b6} and the power estimation \cite{b7} are utilized.
 In the method in \cite{b10}, first, close values of fingerprints from monitoring of PV panels are grouped with some representative values, and then possible combinations of reconfiguration are enumerated.
@@
 \begin{enumerate} [(1)]
-\item Select panels in Panel Selection Order Table. The detail explanation are described next pargraph.\label{step1}
+\item Select panels in Panel Selection Order Table. The detail explanation are described next paragraph.\label{step1}
 \item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
-\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. The replacement will following servious priorities.
+\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. The replacement will following several priorities.
   %% As the example of string current on 2A, selected panels are panel P1 and P5, these panels contain modules are equal to next unselect panel P4. Then swap (P1, P5) and P4, release P1 and P5.

### 2018-10-09 main.tex
Update main.tex

@@
 
-To execute a power simulation, we have to assign panels to each string to realize a candidate configuration.
-However, the way is not given in \cite{b10} and some candidate configurations are infeasible.
+To execute a power simulation, we need assign panels into different strings to realize a configuration.
+However, the way to assign panels is not given in \cite{b10} and some configuration candidates are infeasible.
 The definition of feasibility in (\ref{feas}).
@@
 \section{An Algorithm to Identify Feasibility}
-In this section, we propose an algorithm to identify feasibility.
+In this section, we propose an algorithm to identify feasibility of configuration candidates.
 \subsection{The Input And Output Of Algorithm}

### 2018-10-09 main.tex
Updates from ShareLaTeX
modify

@@
 \usepackage{lipsum}
+\usepackage{stfloats}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
- \author{\IEEEauthorblockN{Dafang Zhao}
+ \author{\IEEEauthorblockN{Dafantg Zhao}
  \IEEEauthorblockA{\textit{Graduate School of Information Science} \\
@@
   Power generation efficiency of photovoltaic(PV) system is reduced significantly under partial shading or solar cell damage  conditions.
-This efficiency losses affected by turning on bypass diode of PV panels, which called mismatch losses.
+These efficiency losses affected by turning on bypass diode of PV panels, which called mismatch losses.
 Reconfiguration technology to reconfigure electrical series or parallel connection among PV panels can maximize power generation.
@@
 \section{Feasibility}\label{feasPro}
-As an example, we consider a PV array where nine panels are connected in three strings.
-We assume that, in this example, this Fast reconfiguration algorithm estimate number of working module on different current candidate for each panel as shown in Table \ref{tab1}.
-The dot in table in form of a PV module.
-We set $N_C$ as the meaning of not candidate, set infeasible MPPs as zero.
-Through the procedure in Fast reconfiguration algorithm and simplify feasibility check, MPPs are presented in matrix below.
-[C1, C2, C3, C4] indicate 4 MPP candidates.
-
 To execute a power simulation, we need assign panels into different strings to realize a configuration.
@@
 The definition of feasibility in (\ref{feas}).
-When a configuration needs working modules in a string (\textit{$M_S$}) are less than number of working module per-string (\textit{$Q_{M_{n}}$}), then this configuration is infeasible.
+When a configuration needs working modules in \textit{h}-th string (\textit{$M_{Sh}$}) are less than number of working modules per-string (\textit{$Q_{M_{n}}$}), then this configuration is infeasible.
 \begin{equation}
@@
 \end{equation}
-For an configuration example [C2] \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string.
+
+As an example, we consider a PV array where nine panels are connected in three strings.
+We assume that, in this example, this Fast reconfiguration algorithm estimate number of working module on different current candidate for each panel as shown in Table \ref{tab1}.
+The dot in the table in form of a PV module.
+We set $N_C$ as the meaning of not configuration candidate and infeasible MPPs are set as zero.
+Through the procedure in Fast reconfiguration algorithm and simplify feasibility check, MPPs are presented in Table \ref{mppcandidates}.
+[C1, C2, C3, C4] indicate 4 MPP candidates.
+
+For an configuration example [C1] \{0.5A, 0.5A, 2A\}, there are 8 PV modules working on each string.
 According to Table I, for a string current on 2A at least need 4 panels, remaining panels can not provide enough PV module working on 0.5A for another two strings.
+So this configuration is infeasible.
 Of course we can compute it by using an exhaustive search.
@@
 So, we need an algorithm to efficiently identify feasibility of a configuration and realize the configuration if it is feasible.
+
+\begin{table*}[bp]
+\caption{Maximum Power Point Candidates}
+  \begin{center}
+    %% \binom{\begin{pmatrix}
+    \begin{tabular}[]{ccccccccccc}
+ $\frac{Current\ \rightarrow }{Number\ of\ modules\ \downarrow}$&\{0.5,0.5,0.5\}&\{0.5,0.5,2\}&\{0.5,0.5,3\}&\{0.5,2,2\}&\{0.5,2,3\}&\{0.5,3,3\}&\{2,2,2\}&\{2,2,3\}&\{2,3,3\}&\{3,3,3\}\\  \\ \hline \hline
+$\geq 1$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  \\
+$\geq 2$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  \\
+$\geq 3$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  &$N_C$  &0      &0 \\
+$\geq 4$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  & C4    &0      &0 \\
+$\geq 5$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &C3     &0      &0      &0  \\
+$\geq 6$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &0      &0      &0      &0 \\
+$\geq 7$ &$N_C$  &$N_C$  &0      &C2     &0     &0      &0      &0      &0      &0 \\
+$\geq 8$ &$N_C$  &C1     &0      &0      &0     &0      &0      &0      &0      &0
+    \end{tabular}\label{mppcandidates}
+    \end{center}
+\end{table*}
 
@@
 The information of a PV array is given as a set of panels and the number of working modules in each panel for each current candidate.
-Table \ref{mpp3-1} shows the information of a PV panel given in Table \ref{tab1}.
-\begin{table}[htbp]
-  \begin{center}
-    %% \binom{\begin{pmatrix}
-    \begin{tabular}[]{ccccccccccc}
- $\frac{Current\ \rightarrow }{Number\ of\ modules\ \downarrow}$&\{0.5,0.5,0.5\}&\{0.5,0.5,2\}&\{0.5,0.5,3\}&\{0.5,2,2\}&\{0.5,2,3\}&\{0.5,3,3\}&\{2,2,2\}&\{2,2,3\}&\{2,3,3\}&\{3,3,3\}\\  \\ \hline \hline
-$\geq 1$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  \\
-$\geq 2$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  \\
-$\geq 3$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  &$N_C$  &0      &0 \\
-$\geq 4$ &$N_C$  &$N_C$  &$N_C$  &$N_C$  &$N_C$  &0  &$N_C$  & C4    &0      &0 \\
-$\geq 5$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &C3     &0      &0      &0  \\
-$\geq 6$ &$N_C$  &$N_C$  &0      &$N_C$  &0     &0      &0      &0      &0      &0 \\
-$\geq 7$ &$N_C$  &$N_C$  &0      &C2     &0     &0      &0      &0      &0      &0 \\
-$\geq 8$ &$N_C$  &C1     &0      &0      &0     &0      &0      &0      &0      &0
-    \end{tabular}\label{mppcandidates}
-    \end{center}
-\end{table}
+Table \ref{mpp3-1} shows the information of a PV panel be given dataset in Table \ref{tab1}.
 
@@
 \end{enumerate}
-\vspace{5.7cm}
 
-\newpage
 We explain step (\ref{step1}) that determine the assignment of the $h$-th string.

### 2019-04-20 PVSC-46/Manuscript/PVSC_Manuscript.tex
add new sample for manuscript

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%
\documentclass[conference]{./pvsctran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

%\input epsf
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[super]{nth}
\usepackage{multicol}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{\LARGE Manuscript Preparation Guidelines and Template for the 46th IEEE Photovoltaic Specialists Conference (Title in 18-point Times font)}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{ \IEEEauthorblockN{\large William Shockley, Hans Queisser, and William R. Cherry   (List authors on this line using 12 point Times \\font -- use a second line if necessary)} \\
\IEEEauthorblockA{\large Institute Name, City, State/Region, Mail/Zip Code, Country (authors' affiliation(s) listed here in 12 point\\ Times font Ð use a second line if necessary)}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

\setlength{\columnsep}{0.25in}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
An abstract in the two-column format is required for the manuscript. Use 9 point Times New Roman Bold font for the abstract. Set your line spacing to be 10 points rather than single space. Indent the first line by 0.125 inches and type the word ``Abstract'' in 9 point Times New Roman Bold Italic. This should be followed by two spaces, a long dash (option / shift / minus), two spaces, and then the first word of your abstract (as shown above). Please try to keep the length of your abstract to 100 words or less. Times font is an acceptable substitute for Times New Roman font. After the abstract, you should list a few key words that describe your paper. Typically, you should list about 5 to 7 key words, in alphabetical order, using 9 point Times New Roman Bold font.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.
\begin{IEEEkeywords}
amorphous materials, charge carrier lifetime, photovoltaic cells, silicon.
\end{IEEEkeywords}
% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
Please follow these instructions carefully.  Papers not meeting these guidelines may be excluded from the conference proceedings.  These instructions have been formatted in the manner in which you should prepare your manuscript; you may use this TeX document as a template.  Please use this as an example.  For details or clarification, please contact the Publications Chair at \url{Publications@ieee-pvsc.org}.

Please read through this entire template before you start using it to create your paper! This will save you and the PVSC considerable time. A contributor should remember that:
\hfil\break
1) Deadline to submit this paper is \textbf{June 3, 2019!}\\
2) Manuscripts must be submitted electronically to the conference website (\url{http://www.ieee-pvsc.org}).  Manuscripts must be submitted in either Microsoft Word or PDF format.  No hardcopy is required.  If you submit a Microsoft Word document, it will be converted to PDF format.  Be sure to doownload and view this PDF document to ensure proper conversion.  \\
3) If the manuscript is not submitted by the \textbf{June 3, 2019!}\\ deadline, presentation and publication will not be permitted.  In addition, no manuscript will be published without presentation at the conference.  PVSC FOLLOWS A STRICT NO PAPER-NO PODIUM AND NO PODIUM-NO PAPER RULE.  Should you have any difficulty with the electronic submission process, please contact SPLTrak at \url{help@SPLTrak.com}.\\ 
4) All papers are limited to six (8) pages (including all figures) and 2 MB file size.\\
5)	You should employ this format. This document is being made available as a template for your convenience. If you elect not to use this template, please remember that you must still adhere to the general guidelines embodied in this document concerning, but not limited to, font size, margin size, page limits, file size, etc.\\
\begin{table*}
\centerline { TABLE 1  } 
\vskip5pt
\centerline { \normalsize \textsc{Summary of Typographical Settings}}
\vskip2pt
\centerline{
\vbox{\offinterlineskip
\hrule
%\vskip2pt\hrule\vskip2pt
% Leading & means preamble template repeats infinitely. p.241 TeX Book.
\halign{&\vrule#&
\strut\quad#\hfil\quad\cr
%Use either first and third lines following this description, OR the
%second line.  The first choice is used when all vertical rules go to the
%top of the first horizontal line of the table.  The second choice below
%(with the \strut) is used when there are column headings that span
%more than one column.  The \strut in that column line will not have the
%vertical tic marks in the horizontal rule.  Note that a vrule is also
%considered a column, so when using \multispanx, x is the number of
%all columns including the ``vrule.'' 
%height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
&\strut &&\multispan5\hfil {\bf Font Specifics}\hfil&&\multispan9\hfil {\bf Paragraph Description}\hfil &\cr
%&\omit &&\multispan5\hfil {\bf Font Specifics}\hfil&&\multispan9\hfil {\bf Paragraph Description}\hfil &\cr
&{\bf Section}&&\multispan5\hfil (Times Roman unless
specified)\hfil&&\multispan5\hfil spacing (in points)\hfil &&
alignment&&indent&\cr
&\omit&&style&&size&&special&&line&&before&&after&&\omit&&(in inches)&\cr
height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
\noalign{\hrule}
height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
%\noalign{\vskip2pt\hrule\vskip2pt}
%\omit&\omit&\omit&\omit\cr
&Title&&plain&&18&&none&&single&&6&&6&&centered&&none&\cr
&Autohr List&&plain&&12&&none&&single&&6&&6&&centered&&none&\cr
&Affiliations&&plain&&12&&none&&single&&6&&6&&centered&&none&\cr
&Abstract&&bold&&9&&none&&exactly 10&&0&&0&&justified&&0.125 $1^{st}$ line&\cr
&Headings&&plain&&10&&small caps&&exactly 12&&18&&6&&centered&&none&\cr
&Subheadings&&italic&&10&&none&&exactly 12&&6&&6&&left&&none&\cr
&Body Paragraphs&&plain&&10&&none&&exactly 12&&0&&0&&justified&&0.125 $1^{st}$ line&\cr
&Equations&&\multispan5 \hfil Symbol font for special characters
\hfil&&single&&6&&6&&centered&&none&\cr
&Figures&&\multispan5 \hfil 8 to 10 point sans serif (Helvetica)\hfil&&single&&0&&0&&centered&&none&\cr
&Figure Captions&&plain&&9&&none &&10&&0&&0&&justified&&none, tab at 0.5&\cr
&References&&plain&&9&&none&&10&&0&&0&&justified&&0.25 hanging&\cr
height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr}
\hrule}}
\label{table1}
\end{table*}

\section{Detailed Text Formatting}
Use a two column format.  All paragraphs of text, including the abstract, figure captions, and references, should be justified at the left and the right edges.

Please do not include page numbers, headers or footers.  Company logos should not be inserted into a header or footer.  \textbf{YOUR MANUSCRIPT WILL BE REJECTED IF THERE ARE PAGE NUMBERS, HEADERS OR FOOTERS.}  This is to allow IEEE to add their official footer information and allow for IEEE to determine page numbering if appropriate.

For the Title, use 18-point Times (Roman) font. Its paragraph description should be set so that the line spacing is single with 6-point spacing before and 6-point spacing after. The font description for the Author List and Authors' Affiliation(s) should be 12-point Times. The paragraph descriptions should be set so that the line spacing is single with 6-point spacings before and after. Use an additional line spacing of 12 points before the beginning of the double column section, as shown above.

Using 8.5 x 11-inch paper, the top margin is 0.75 inch, the bottom margin is 1 inch, and the left and right margins are
0.625 inch. Except for Title, Authors and Affiliations, use a double column format. The column width is 3.5 inches and the column spacing is 0.25 inch.

Each major section begins with a Heading in 10 point Times font centered within the column and numbered using Roman numerals (except for \textsc{Acknowledgment} and \textsc{References}), followed by a period, a single space, and the title using an initial capital letter for each word. The remaining letters are in \textsc{Small Capitals}. The paragraph description of the section heading line should be set for 18 points before, 6 points after, and the line spacing should be set to exactly 12 points.

For the body of your paper, use 10-point Times font and set your line spacing at ``exactly 12 points'' with 0 points before and after. Indent each paragraph by 0.125 inches.

Further details are provided in the remainder of this paper for specific situations.

\subsection{ Major Subsections}
As shown, denote subsections with left justified 10-point Times Italic. Order them with capitalized alphabetic characters $(A, B,...)$. Follow the letter designation with a period, a single space, and then the subsection title capitalizing the first letter of each word. The paragraph description of the subsection heading is set to "exactly 12-point" line spacing with 6 points before and after.
\subsection{ Equations }
Equations should be centered in the column and numbered sequentially. Place the equation number to the right of the equation within a parenthesis, with right justification within its column. An example would be
\begin{equation}
V_{OC}=\frac{1}{\beta}ln\left(\frac{I_L}{I_S}+1\right)
\end{equation}
\emph{Make sure that any subscripts in your equations are legible and are not too
small to read!} When referring to an equation, use the number within
parenthesis. For example, you would usually refer to the first
equation as (1) rather than equation (1). If possible, use the Symbol
font for all special characters.%, or better yet, use Equation Editor or
%MathType. 
The paragraph description of the line containing the
equation should be set for 6 points before and 6 points after. The
paragraph spacing will need to be set to ``single'' rather than ``exactly
12 point'' so that the height will autoscale to fit the equation.

\section{Figures and Tables}
The use of color in figures and photos is recommended.  Keep in mind that the proceedings will only be produced in electronic format (DVD).  There will not be a hardbound version of the proceedings.  Please consider the use of different line styles (dashes, dots, etc.) in plots to ensure clarity.  See example.  Please use jpg or png format for all images and compress the size.

Most of the following applies to Microsoft Word.  Figures should utilize as much of the column width as possible in order to maximize legibility. Use a sans serif font, such as Helvetica. Helvetica is larger and much easier to read than Times. Using 8- to 10-point Helvetica usually results in a legible figure. \emph{Do not use any font smaller than 8-point!} It must be legible. When referring to a figure, use the abbreviation Fig. followed by its number. Place figure captions directly below each figure. Use
9-point Times with the paragraph spacing set at ``exactly 10 points.'' Set a tab at 0.5 inch. Type ``Fig. \#.'' (\# is the numeral) then tab over to the 0.5 inch mark before beginning the text of the figure caption. Note that figure captions are always (left and right) justified, rather than centered, even if they are less than a single full line in length. See the caption for Fig. 1.

Within \LaTeX, there is basically only one option for placing figures
within your paper.  Often the easiest way is to insert them into the
top of the next column.
%Within Microsoft Word there are several options for placing figures
%within your paper. Often the easiest is to insert them between
%existing paragraphs allowing the figures to remain in that relative
%position. The paragraph description where the figure is inserted must
%be set to ``single'' spacing rather than ``exactly 12 points'' in
%order to allow the line to autoscale in height to display the entire
%figure. Some disadvantages of this approach are that you don't have
%total flexibility in placing figures, and that the figures will move
%as text is inserted or deleted in any part of the document before the
%figure. If you elect to use this approach, it is recommended that you
%nearly complete the editing of your text before inserting any
%figures. Remember to allow room for them, however. Then begin
%inserting figures starting from the beginning of your document. 
Do not lump all figures at the end of the paper!
If you have difficulties with the titles on your figures, you can always elect to add in the titles as separate text boxes, rather than importing the titles with the graph. This is sometimes helpful in getting a lengthy vertically-oriented title to display correctly.

%\begin{figure}
%%\includegraphics {figure_temp.epsi}
%\epsfxsize=3.25in\epsfbox{figure1.eps}
%\caption{ Estimated relationship between the time an author spends reading these instructions and the quality of the author's digest article.}
%\end{figure}

\begin{figure}
\centering
\includegraphics[width=9cm]{image1.png}
\caption{Example of readable plot using different colors and line styles for clarity.}
\end{figure}

Notice that prior to the graph, a single 12-point line is used to
separate the preceding text from the graph. The equivalent of a blank
line should exist between the bottom of the graph (the x-axis caption)
and the figure caption. (In this particular case, there was no need to
add a blank line between the x-axis label and the figure caption,
because there was already adequate spacing provided by the image
border.) After the figure caption, there should be a single 12-point
blank line before the text resumes. 
%\LaTeX accepts encapsulated post script files as figures.  Standard post script figures will not expand and contract to fill the designate area on the page. Encapsulated post script files will.  Thus, encapsulated post script files must obviously be only one page long.  It is often easy to convert a post script file to encapsulated post script.  In Linux this can be done with the command, ``ps2epsi.''
%More flexibility is obtained in inserting figures if you can place
%them exactly where you would like them to be on a page. This can be
%accomplished by inserting the figure, selecting the figure, and then
%choosing ``Format Picture\dots ''. Various settings allow you to place the figure at an absolute position on a page; specify if the text is supposed to flow around the figure or if the figure should move with the text, etc. If you elect to let the text flow around the figure, then remember that you will have to insert a separate text box for the caption, otherwise the figure caption is likely to become separated from the figure.
%When importing a graph from Excel into Word, it is often helpful to
%special-paste it in as a ``Picture (Enhanced Meta-file).'' This saves
%file memory for Word documents. Be aware that the usual Copy
%$\rightarrow $  Paste procedure will copy the entire Excel spreadsheet into your Word file. The Copy $\rightarrow$ Paste Special $\rightarrow$ Picture (Enhanced Metafile) command copies only the graph as a static picture. This is not a concern with PDF file submissions.
If you decide to use color traces in your graphical data, be absolutely certain that there is no ambiguity about your graphical information when printed on a B\&W printer.

Table I on the second page was inserted using ``Insert'', ``Text
Box'', creating the text contained in Table I, and then formatting the
text box using all the settings available under ``Format'', ``Text
Box\dots ''. Table I also serves as an illustration of one of the rare
instances when the double column format requirement can be
violated. Certain figures and tables will require the full-page width
to display. It is usually best to place these figures and tables at
the top, rather than in the middle or bottom of a page. Tables should be entered within a single column if this can be done cleanly, without the entry becoming too crowded.

\section{Citing Previous Work}
When referencing a journal article \cite{Yamaguchi}, a conference
digest article \cite{Hovel} or a book \cite{Fahrenbruch}, place the reference numbers within square
brackets. To simultaneously cite these references \cite{Yamaguchi} - \cite{Fahrenbruch} use the format just demonstrated. The reference list is the last section and references are listed in the order cited. Use 9 point Times. The paragraph description is set for a line spacing of exactly 10 points with 0 point spacing before and after. A 0.25 inch hanging indention should be specified.

Generally speaking, references should be very detailed. For journal articles, list all authors by initials and last name, the title of the paper in quotations (capitalizing only the first letter of the first word, unless it would be capitalized in a sentence, e.g., a proper noun), the journal name in italics, the volume number, the issue number, the page numbers, and the date. Use the examples provided \cite{Yamaguchi} - \cite{Fahrenbruch} as a guide. 
%Further information on LaTeX and TeX can be found in \cite{IEEEhowto:kopka} - \cite{knuth}.

% The following statement makes the two columns on the last page more
% or less of equal length.  Placement of this command is by trial and error.
\vfil\eject

\section{Copyright and Reprint Information}
The IEEE copyright form will be electronically submitted for this conference.  On the conference web site, follow the link in the manuscript submission area.

Reprints may be ordered by checking the appropriate box on the conference registration form.  The reprints will be mailed to you at the address listed on the registration form approximately 3 months after the conference.

\section{Conclusion}
Following these instructions will improve the quality of your paper and the PVSC Proceedings. If you have comments, please contact \url{Publications@ieee-pvsc.org}. Please direct questions regarding the electronic submission process to \url{help@SPLTrak.com}.

% conference papers do not normally have an appendix

% use section* for acknowledgment

% conference papers do not normally have an appendix

% use section* for acknowledgement

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}
\small

\bibitem {Yamaguchi}
M. Yamaguchi, A. Khan, S.J. Taylor, M. Imaizumi, T. Hisamatsu, and S. Matsuda, ``A detailed model to improve the radiation-resistance of Si space solar cells,\emph{Fundamentals of Solar Cells} vol. 46, pp. 2133-2138, 1999.

\bibitem {Hovel}
H. J. Hovel and J. M. Woodall, ``The effect of depletion region recombination currents on the efficiencies of Si and GaAs solar cells'', \emph {in 10th IEEE Photovoltaic Specialist Conference}, p. 25, 1973.

\bibitem {Fahrenbruch}
A. L. Fahrenbruch and R. H. Bube, \emph{Fundamentals of Solar Cells}, New York: Academic Press, 1983.

%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}
%\smallskip
%Note: For the Summary paper submission only, references to the authors own work must be redacted to preserve the new double-blind reviewing requirements.

% that's all folks
\end{document}

### 2019-04-22 PVSC-46/Manuscript/PVSC_Manuscript.tex
edit new template for manuscript PVSC

@@
 %
-\documentclass[conference]{./pvsctran}
+\documentclass[conference]{pvsctran}
 %
@@
 \usepackage{multicol}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
+% Add by Zhao
+\usepackage{cite}
+\usepackage{amsthm,amsfonts}
+\usepackage{xcolor,color}
+\usepackage{graphicx}
+\usepackage{enumerate}
+\usepackage{multirow}
+\usepackage[utf8]{inputenc}
+\usepackage[ruled]{algorithm2e}
+\usepackage[colorinlistoftodos]{todonotes}
 
@@
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{\LARGE Manuscript Preparation Guidelines and Template for the 46th IEEE Photovoltaic Specialists Conference (Title in 18-point Times font)}
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-\author{ \IEEEauthorblockN{\large William Shockley, Hans Queisser, and William R. Cherry   (List authors on this line using 12 point Times \\font -- use a second line if necessary)} \\
-\IEEEauthorblockA{\large Institute Name, City, State/Region, Mail/Zip Code, Country (authors' affiliation(s) listed here in 12 point\\ Times font Ð use a second line if necessary)}}
+\title{ A Rapid Feasibility Checking for Reconfiguration of Mismatched PV Arrays}
 
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
+\author{ \IEEEauthorblockN{\large Dafang Zhao, Fukohito Ooshita, and Michiko Inoue}
+\IEEEauthorblockA{\large Nara Insititute of Science and Technology, Japan \\ Email:\{zhao.dafang.yu7, f-ooshita, kounoe\}@is.naist.jp}}
 
@@
 %\boldmath
-An abstract in the two-column format is required for the manuscript.
-Use 9 point Times New Roman Bold font for the abstract.
-Set your line spacing to be 10 points rather than single space.
-Indent the first line by 0.125 inches and type the word ``Abstract'' in 9 point Times New Roman Bold Italic.
-This should be followed by two spaces, a long dash (option / shift / minus), two spaces, and then the first word of your abstract (as shown above).
-Please try to keep the length of your abstract to 100 words or less.
-Times font is an acceptable substitute for Times New Roman font.
-After the abstract, you should list a few key words that describe your paper.
-Typically, you should list about 5 to 7 key words, in alphabetical order, using 9 point Times New Roman Bold font.
+Power generation efficiency of photovoltaic (PV) arrays is significantly affected by partial shading and PV cell damage.
+Partial shading or PV cell damage induces mismatched power generation among PV panels and causes an efficiency loss of power generation.
+Power generation of mismatched PV arrays can be recovered by reconfiguring connection of PV panels.
+In this paper, we introduce a \textit{feasibility check problem} of PV panel configuration.
+The problem identifies whether a connection among PV panels can be configured from a given PV module level solution. 
+We also propose an algorithm for the feasibility check problem.
+The experimental results demonstrate that the proposed method can identify feasible configurations more than 32,000X faster than the exhaustive search with around 0.6\% errors.
 \end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the conference you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals/conferences frown on
-% math in the abstract anyway.
+
 \begin{IEEEkeywords}
-amorphous materials, charge carrier lifetime, photovoltaic cells, silicon.
+photovoltaic, feasibility, reconfiguration, mismatch
 \end{IEEEkeywords}
-% no keywords
 
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle
@@
 \section{Introduction}
-Please follow these instructions carefully.
-Papers not meeting these guidelines may be excluded from the conference proceedings.
-These instructions have been formatted in the manner in which you should prepare your manuscript; you may use this TeX document as a template.
-Please use this as an example.
-For details or clarification, please contact the Publications Chair at \url{Publications@ieee-pvsc.org}.
+As fossil fuel depletion and environmental pollution become more serious, green and renewable energy has become necessary for a sustainable society and environment. 
+Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
+However, due to the nature of a PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
+PV cells could not uniformly generate power when PV cells experience different irradiances or some of cells have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging.
+To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
+However, it causes a significant loss of power generation.
 
-Please read through this entire template before you start using it to create your paper! This will save you and the PVSC considerable time. A contributor should remember that:
-\hfil\break
-1) Deadline to submit this paper is \textbf{June 3, 2019!}\\
-2) Manuscripts must be submitted electronically to the conference website (\url{http://www.ieee-pvsc.org}).
-Manuscripts must be submitted in either Microsoft Word or PDF format.
-No hardcopy is required.
-If you submit a Microsoft Word document, it will be converted to PDF format.
-Be sure to doownload and view this PDF document to ensure proper conversion.
-\\
-3) If the manuscript is not submitted by the \textbf{June 3, 2019!}\\ deadline, presentation and publication will not be permitted.
-In addition, no manuscript will be published without presentation at the conference.
-PVSC FOLLOWS A STRICT NO PAPER-NO PODIUM AND NO PODIUM-NO PAPER RULE.
-Should you have any difficulty with the electronic submission process, please contact SPLTrak at \url{help@SPLTrak.com}.\\
-4) All papers are limited to six (8) pages (including all figures) and 2 MB file size.\\
-5)	You should employ this format.
-This document is being made available as a template for your convenience.
-If you elect not to use this template, please remember that you must still adhere to the general guidelines embodied in this document concerning, but not limited to, font size, margin size, page limits, file size, etc.\\
-\begin{table*}
-\centerline { TABLE 1  } 
-\vskip5pt
-\centerline { \normalsize \textsc{Summary of Typographical Settings}}
-\vskip2pt
-\centerline{
-\vbox{\offinterlineskip
-\hrule
-%\vskip2pt\hrule\vskip2pt
-% Leading & means preamble template repeats infinitely. p.241 TeX Book.
-\halign{&\vrule#&
-\strut\quad#\hfil\quad\cr
-%Use either first and third lines following this description, OR the
-%second line.  The first choice is used when all vertical rules go to the
-%top of the first horizontal line of the table.  The second choice below
-%(with the \strut) is used when there are column headings that span
-%more than one column.  The \strut in that column line will not have the
-%vertical tic marks in the horizontal rule.  Note that a vrule is also
-%considered a column, so when using \multispanx, x is the number of
-%all columns including the ``vrule.'' 
-%height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
-&\strut &&\multispan5\hfil {\bf Font Specifics}\hfil&&\multispan9\hfil {\bf Paragraph Description}\hfil &\cr
-%&\omit &&\multispan5\hfil {\bf Font Specifics}\hfil&&\multispan9\hfil {\bf Paragraph Description}\hfil &\cr
-&{\bf Section}&&\multispan5\hfil (Times Roman unless
-specified)\hfil&&\multispan5\hfil spacing (in points)\hfil &&
-alignment&&indent&\cr
-&\omit&&style&&size&&special&&line&&before&&after&&\omit&&(in inches)&\cr
-height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
-\noalign{\hrule}
-height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
-%\noalign{\vskip2pt\hrule\vskip2pt}
-%\omit&\omit&\omit&\omit\cr
-&Title&&plain&&18&&none&&single&&6&&6&&centered&&none&\cr
-&Autohr List&&plain&&12&&none&&single&&6&&6&&centered&&none&\cr
-&Affiliations&&plain&&12&&none&&single&&6&&6&&centered&&none&\cr
-&Abstract&&bold&&9&&none&&exactly 10&&0&&0&&justified&&0.125 $1^{st}$ line&\cr
-&Headings&&plain&&10&&small caps&&exactly 12&&18&&6&&centered&&none&\cr
-&Subheadings&&italic&&10&&none&&exactly 12&&6&&6&&left&&none&\cr
-&Body Paragraphs&&plain&&10&&none&&exactly 12&&0&&0&&justified&&0.125 $1^{st}$ line&\cr
-&Equations&&\multispan5 \hfil Symbol font for special characters
-\hfil&&single&&6&&6&&centered&&none&\cr
-&Figures&&\multispan5 \hfil 8 to 10 point sans serif (Helvetica)\hfil&&single&&0&&0&&centered&&none&\cr
-&Figure Captions&&plain&&9&&none &&10&&0&&0&&justified&&none, tab at 0.5&\cr
-&References&&plain&&9&&none&&10&&0&&0&&justified&&0.25 hanging&\cr
-height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr}
-\hrule}}
-\label{table1}
-\end{table*}
+PV arrays are hierarchically constructed such that a group of PV cells form a PV module, a group of PV modules form a PV panel, and a group of PV panels form a PV array. 
+Power generation of mismatched PV arrays can be recovered by reconfiguring connection of these components. 
+Fig.\ref{compare} shows an example of power generations of a PV array with a partial shading. 
+We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
+Before reconfiguration, it has four peaks in power VS voltage curve, while,  if we reconfigure connection among PV panels, it can increase around 35\% power generation.
+
+Though several reconfiguration methods have been proposed, most works consider reconfiguration in PV cell or PV module level \cite{nguyen2008adaptive,wang2014architecture,storey2013improved,storey2014optimized,udenze2018reconfiguration}.
+However, cell level reconfiguration requires a significantly high computation time and a large number of switches for reconfiguration. 
+In addition, they require a special PV panels with capability of switching, and cannot be applied to the system constructed with standard PV panels. 
+From a practical view, reconfiguration of connection among PV panels is a realistic solution since a PV panel is manufactured as a physical one panel with two terminals and PV panels can be flexibly interconnected.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.8\linewidth]{PVSC-46/fig/compare.png}
+    \caption{Power generation before and after reconfiguration}
+    \label{compare}
+\end{figure}
+
+Reconfiguration in PV panel level has been investigated\cite{carotenuto2015evolutionary,hu2017non,orozco2016optimized}. 
+A PV array reconfiguration using genetic algorithm (GA) was proposed in \cite{carotenuto2015evolutionary}.
+Though it can give a new configuration, computing cost is significantly high and the algorithm cannot generate the best configuration precisely.
+Hu et al. also addressed PV panel reconfiguration where they formulate a nonlinear integer programming problem to optimize power generation by reconfiguration \cite{hu2017non}.
+Orozco-Gutierrez et al.
+proposed an efficient and effective reconfiguration method\cite{orozco2016optimized} where it first selects candidates of configurations with approximation and then finds the best one with precise power simulation.
+However, the candidates are specified in a PV module level though PV modules could not be fully reconfigured.
+Actually, we found that some of configuration candidates are not able to be realized.
+However, the paper\cite{orozco2016optimized}  does not show any systematic way to identify such a feasibility.
+
+In this paper, we propose an algorithm to rapidly check feasibility that a given configuration candidate is actually formed by given PV panels. 
+The proposed method can efficiently check the feasibility while identifying most feasible cases accurately. 
+The experimental results demonstrate the effectiveness of the proposed method that 
+% \begin{table*}
+% \centerline { TABLE 1  } 
+% \vskip5pt
+% \centerline { \normalsize \textsc{Summary of Typographical Settings}}
+% \vskip2pt
+% \centerline{
+% \vbox{\offinterlineskip
+% \hrule
+% %\vskip2pt\hrule\vskip2pt
+% % Leading & means preamble template repeats infinitely. p.241 TeX Book.
+% \halign{&\vrule#&
+% \strut\quad#\hfil\quad\cr
+% %Use either first and third lines following this description, OR the
+% %second line.  The first choice is used when all vertical rules go to the
+% %top of the first horizontal line of the table.  The second choice below
+% %(with the \strut) is used when there are column headings that span
+% %more than one column.  The \strut in that column line will not have the
+% %vertical tic marks in the horizontal rule.  Note that a vrule is also
+% %considered a column, so when using \multispanx, x is the number of
+% %all columns including the ``vrule.'' 
+% %height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
+% &\strut &&\multispan5\hfil {\bf Font Specifics}\hfil&&\multispan9\hfil {\bf Paragraph Description}\hfil &\cr
+% %&\omit &&\multispan5\hfil {\bf Font Specifics}\hfil&&\multispan9\hfil {\bf Paragraph Description}\hfil &\cr
+% &{\bf Section}&&\multispan5\hfil (Times Roman unless
+% specified)\hfil&&\multispan5\hfil spacing (in points)\hfil &&
+% alignment&&indent&\cr
+% &\omit&&style&&size&&special&&line&&before&&after&&\omit&&(in inches)&\cr
+% height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
+% \noalign{\hrule}
+% height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
+% %\noalign{\vskip2pt\hrule\vskip2pt}
+% %\omit&\omit&\omit&\omit\cr
+% &Title&&plain&&18&&none&&single&&6&&6&&centered&&none&\cr
+% &Autohr List&&plain&&12&&none&&single&&6&&6&&centered&&none&\cr
+% &Affiliations&&plain&&12&&none&&single&&6&&6&&centered&&none&\cr
+% &Abstract&&bold&&9&&none&&exactly 10&&0&&0&&justified&&0.125 $1^{st}$ line&\cr
+% &Headings&&plain&&10&&small caps&&exactly 12&&18&&6&&centered&&none&\cr
+% &Subheadings&&italic&&10&&none&&exactly 12&&6&&6&&left&&none&\cr
+% &Body Paragraphs&&plain&&10&&none&&exactly 12&&0&&0&&justified&&0.125 $1^{st}$ line&\cr
+% &Equations&&\multispan5 \hfil Symbol font for special characters
+% \hfil&&single&&6&&6&&centered&&none&\cr
+% &Figures&&\multispan5 \hfil 8 to 10 point sans serif (Helvetica)\hfil&&single&&0&&0&&centered&&none&\cr
+% &Figure Captions&&plain&&9&&none &&10&&0&&0&&justified&&none, tab at 0.5&\cr
+% &References&&plain&&9&&none&&10&&0&&0&&justified&&0.25 hanging&\cr
+% height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr}
+% \hrule}}
+% \label{table1}
+% \end{table*}
 
@@
 % references section
-
+\renewcommand\refname{Reference}
+\bibliographystyle{ieeetr}
+\bibliography{reference}
 % can use a bibliography generated by BibTeX as a .bbl file
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
-\small
+% \begin{thebibliography}{1}
+% \small
 
-\bibitem {Yamaguchi}
-M.
+% \bibitem {Yamaguchi}
+% M.
 Yamaguchi, A.
@@
 
-\bibitem {Hovel}
-H.
+% \bibitem {Hovel}
+% H.
 J.
@@
 
-\bibitem {Fahrenbruch}
-A. L. Fahrenbruch and R. H. Bube, \emph{Fundamentals of Solar Cells}, New York: Academic Press, 1983.
+% \bibitem {Fahrenbruch}
+% A. L. Fahrenbruch and R. H. Bube, \emph{Fundamentals of Solar Cells}, New York: Academic Press, 1983.
 
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+% %\bibitem{IEEEhowto:kopka}
+% %H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+% %  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
 
-\end{thebibliography}
+% \end{thebibliography}
 %\smallskip

### 2019-04-24 PVSC-46/Manuscript/PVSC_Manuscript.tex
finish section II

@@
 \usepackage{multirow}
+\usepackage{subcaption}
 \usepackage[utf8]{inputenc}
@@
 The proposed method can efficiently check the feasibility while identifying most feasible cases accurately. 
-The experimental results demonstrate the effectiveness of the proposed method that 
-% \begin{table*}
-% \centerline { TABLE 1  } 
-% \vskip5pt
-% \centerline { \normalsize \textsc{Summary of Typographical Settings}}
-% \vskip2pt
-% \centerline{
-% \vbox{\offinterlineskip
-% \hrule
-% %\vskip2pt\hrule\vskip2pt
-% % Leading & means preamble template repeats infinitely. p.241 TeX Book.
-% \halign{&\vrule#&
-% \strut\quad#\hfil\quad\cr
-% %Use either first and third lines following this description, OR the
-% %second line.  The first choice is used when all vertical rules go to the
-% %top of the first horizontal line of the table.  The second choice below
-% %(with the \strut) is used when there are column headings that span
-% %more than one column.  The \strut in that column line will not have the
-% %vertical tic marks in the horizontal rule.  Note that a vrule is also
-% %considered a column, so when using \multispanx, x is the number of
-% %all columns including the ``vrule.'' 
-% %height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
-% &\strut &&\multispan5\hfil {\bf Font Specifics}\hfil&&\multispan9\hfil {\bf Paragraph Description}\hfil &\cr
-% %&\omit &&\multispan5\hfil {\bf Font Specifics}\hfil&&\multispan9\hfil {\bf Paragraph Description}\hfil &\cr
-% &{\bf Section}&&\multispan5\hfil (Times Roman unless
-% specified)\hfil&&\multispan5\hfil spacing (in points)\hfil &&
-% alignment&&indent&\cr
-% &\omit&&style&&size&&special&&line&&before&&after&&\omit&&(in inches)&\cr
-% height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
-% \noalign{\hrule}
-% height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr
-% %\noalign{\vskip2pt\hrule\vskip2pt}
-% %\omit&\omit&\omit&\omit\cr
-% &Title&&plain&&18&&none&&single&&6&&6&&centered&&none&\cr
-% &Autohr List&&plain&&12&&none&&single&&6&&6&&centered&&none&\cr
-% &Affiliations&&plain&&12&&none&&single&&6&&6&&centered&&none&\cr
-% &Abstract&&bold&&9&&none&&exactly 10&&0&&0&&justified&&0.125 $1^{st}$ line&\cr
-% &Headings&&plain&&10&&small caps&&exactly 12&&18&&6&&centered&&none&\cr
-% &Subheadings&&italic&&10&&none&&exactly 12&&6&&6&&left&&none&\cr
-% &Body Paragraphs&&plain&&10&&none&&exactly 12&&0&&0&&justified&&0.125 $1^{st}$ line&\cr
-% &Equations&&\multispan5 \hfil Symbol font for special characters
-% \hfil&&single&&6&&6&&centered&&none&\cr
-% &Figures&&\multispan5 \hfil 8 to 10 point sans serif (Helvetica)\hfil&&single&&0&&0&&centered&&none&\cr
-% &Figure Captions&&plain&&9&&none &&10&&0&&0&&justified&&none, tab at 0.5&\cr
-% &References&&plain&&9&&none&&10&&0&&0&&justified&&0.25 hanging&\cr
-% height2pt&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&&\omit&\cr}
-% \hrule}}
-% \label{table1}
-% \end{table*}
+The experimental results demonstrate the effectiveness of the proposed method can identify the feasibility of configurations and false negative are less than 1\%.
 
-\section{Detailed Text Formatting}
-Use a two column format.  All paragraphs of text, including the abstract, figure captions, and references, should be justified at the left and the right edges.
+\section{Photovoltaic Array}
 
-Please do not include page numbers, headers or footers.
-Company logos should not be inserted into a header or footer.
-\textbf{YOUR MANUSCRIPT WILL BE REJECTED IF THERE ARE PAGE NUMBERS, HEADERS OR FOOTERS.}  This is to allow IEEE to add their official footer information and allow for IEEE to determine page numbering if appropriate.
+A PV system or PV array is composed of PV panels that have two terminals of plus and minus and can be interconnected.
+There are two common connection styles for PV arrays, \textit{series-parallel} array and \textit{total-cross-tied} array. 
+In a series-parallel array, PV panels are connected in series, and multiple series connections are connected in parallel. 
+In a total-cross-tied array, parallel connections of PV panels are connected in series. 
+In this paper, we focus on series-parallel arrays, however the basic idea of the proposed method can be applied also to total-cross-tied arrays. 
+Hereafter, we simply call a series-parallel array a \textit{PV array}.
 
-For the Title, use 18-point Times (Roman) font.
-Its paragraph description should be set so that the line spacing is single with 6-point spacing before and 6-point spacing after.
-The font description for the Author List and Authors' Affiliation(s) should be 12-point Times.
-The paragraph descriptions should be set so that the line spacing is single with 6-point spacings before and after.
-Use an additional line spacing of 12 points before the beginning of the double column section, as shown above.
+Figure \ref{model} shows an example of a PV array. 
+A PV array is a parallel connection of (PV) strings where a string is a series connection of PV panels. 
+A PV panel is a series connection of PV modules, and a PV module is a parallel connection of a series of PV cells and a bypass diode. 
+A typical PV panel is composed of three PV modules each of which has 12-24 PV cells. 
+A PV module can generate power for a given voltage according to its I-V characteristics as shown in Fig.\ref{fig:IV}(a - c). 
+The I-V characteristics is affected by irradiance level and physical damage of PV cells. 
+Figure \ref{fig:IV}(a) also shows a typical degradation of a I-V characteristics where generated current is reduced with some ratio while keeping the voltage range. 
+When a PV panel has a partial shade, that is its PV modules have different irradiance levels and hence different I-V characteristics, the PV panels might have multiple peaks (maximum power points, MPPs) in power generation as shown in Fig.\ref{fig:IV}(d).
 
-Using 8.5 x 11-inch paper, the top margin is 0.75 inch, the bottom margin is 1 inch, and the left and right margins are
-0.625 inch. Except for Title, Authors and Affiliations, use a double column format. The column width is 3.5 inches and the column spacing is 0.25 inch.
+To find out accurate I-V characteristics of a PV panel, we need a time consuming power simulation. 
+However, we can roughly understand I-V characteristics of a PV panel (and also a string) as follows. 
+When a control voltage is low, PV modules with high irradiance level are active while PV modules with low irradiance level are inactive with turning on their bypass diodes.
+In this case, a high current can flow in the PV panel. When control voltage is high, some of bypass diodes become turning off and the corresponding PV modules become active. 
+In this case, the current level is reduced and generated power sometimes increases and sometimes decreases. 
+The generated power at MPPs can be roughly estimated. 
+In Fig.\ref{fig:IV}(d), one PV panel has three PV modules with different irradiance levels. 
+The peak currents for these modules are 433mA, 307mA, and 155mA, respectively. 
+Voltages at MPPs are roughly 200V, 400V, 600V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 200V in this case). 
+At the first MPP (MPP1), only one PV module with a peak current of 433mA is active at a control voltage of 206V, so the generated power is 89W. 
+At the second MPP (MPP2), two PV modules with peak currents of 433mA and 307mA are active at a control voltage of 420V. 
+In this case, the current level of the PV panel is 307mA since two PV panels are connected in series and they have to have the same current level, and the generated power is 129W.
+At the third MPP (MPP3), the current level of the PV panel is 155mA at a control voltage of 644V, and the generated power is 100W.
 
-Each major section begins with a Heading in 10 point Times font centered within the column and numbered using Roman numerals (except for \textsc{Acknowledgment} and \textsc{References}), followed by a period, a single space, and the title using an initial capital letter for each word.
-The remaining letters are in \textsc{Small Capitals}.
-The paragraph description of the section heading line should be set for 18 points before, 6 points after, and the line spacing should be set to exactly 12 points.
+In a PV array, we have two constraints. 
+PV panels in the same string have the same current level, while all the strings have the same control voltage. 
+When considering reconfiguration of PV panel connection, we should find out the best configuration while considering these constraints.
 
-For the body of your paper, use 10-point Times font and set your line spacing at ``exactly 12 points'' with 0 points before and after. Indent each paragraph by 0.125 inches.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.8\linewidth]{module.png}
+    \caption{PV array, string, module and panel}
+    \label{model}
+\end{figure}
 
-Further details are provided in the remainder of this paper for specific situations.
-
-\subsection{ Major Subsections}
-As shown, denote subsections with left justified 10-point Times Italic.
+\begin{figure}
+     \centering
+    \begin{subfigure}[b]{0.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{PVSC-46/fig/m_1.png}
+        \caption{PV module 1}
+     \end{subfigure}
+     \begin{subfigure}[b]{0.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{PVSC-46/fig/m_2.png}
+        \caption{PV module 2}
+     \end{subfigure}
+     \begin{subfigure}[b]{0.3\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{PVSC-46/fig/m_3.png}
+        \caption{PV module 3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\linewidth}
+        \centering
+        \vspace{3mm}
+        \includegraphics[width=\linewidth]{PVSC-46/fig/panel.png}
+        \caption{PV panel}
+    \end{subfigure}
+    \caption{I-V characteristics}
+    \label{fig:IV}
+\end{figure}
+% \subsection{ Major Subsections}
+% As shown, denote subsections with left justified 10-point Times Italic.
 Order them with capitalized alphabetic characters $(A, B,...)$.
@@
 The paragraph description of the subsection heading is set to "exactly 12-point" line spacing with 6 points before and after.
-\subsection{ Equations }
-Equations should be centered in the column and numbered sequentially.
+% \subsection{ Equations }
+% Equations should be centered in the column and numbered sequentially.
 Place the equation number to the right of the equation within a parenthesis, with right justification within its column.
 An example would be
-\begin{equation}
-V_{OC}=\frac{1}{\beta}ln\left(\frac{I_L}{I_S}+1\right)
-\end{equation}
-\emph{Make sure that any subscripts in your equations are legible and are not too
-small to read!} When referring to an equation, use the number within
-parenthesis. For example, you would usually refer to the first
-equation as (1) rather than equation (1). If possible, use the Symbol
-font for all special characters.%, or better yet, use Equation Editor or
-%MathType. 
-The paragraph description of the line containing the
-equation should be set for 6 points before and 6 points after. The
-paragraph spacing will need to be set to ``single'' rather than ``exactly
-12 point'' so that the height will autoscale to fit the equation.
+% \begin{equation}
+% V_{OC}=\frac{1}{\beta}ln\left(\frac{I_L}{I_S}+1\right)
+% \end{equation}
+% \emph{Make sure that any subscripts in your equations are legible and are not too
+% small to read!} When referring to an equation, use the number within
+% parenthesis. For example, you would usually refer to the first
+% equation as (1) rather than equation (1). If possible, use the Symbol
+% font for all special characters.%, or better yet, use Equation Editor or
+% %MathType. 
+% The paragraph description of the line containing the
+% equation should be set for 6 points before and 6 points after. The
+% paragraph spacing will need to be set to ``single'' rather than ``exactly
+% 12 point'' so that the height will autoscale to fit the equation.
 
-\section{Figures and Tables}
-The use of color in figures and photos is recommended.
+% \section{Figures and Tables}
+% The use of color in figures and photos is recommended.
 Keep in mind that the proceedings will only be produced in electronic format (DVD).
@@
 
-Most of the following applies to Microsoft Word.
+% Most of the following applies to Microsoft Word.
 Figures should utilize as much of the column width as possible in order to maximize legibility.
@@
 Use
-9-point Times with the paragraph spacing set at ``exactly 10 points.'' Set a tab at 0.5 inch.
+% 9-point Times with the paragraph spacing set at ``exactly 10 points.'' Set a tab at 0.5 inch.
 Type ``Fig.
@@
 
-Within \LaTeX, there is basically only one option for placing figures
-within your paper.  Often the easiest way is to insert them into the
-top of the next column.
+% Within \LaTeX, there is basically only one option for placing figures
+% within your paper.  Often the easiest way is to insert them into the
+% top of the next column.
 %Within Microsoft Word there are several options for placing figures
@@
 %inserting figures starting from the beginning of your document. 
-Do not lump all figures at the end of the paper!
-If you have difficulties with the titles on your figures, you can always elect to add in the titles as separate text boxes, rather than importing the titles with the graph.
+% Do not lump all figures at the end of the paper!
+% If you have difficulties with the titles on your figures, you can always elect to add in the titles as separate text boxes, rather than importing the titles with the graph.
 This is sometimes helpful in getting a lengthy vertically-oriented title to display correctly.
 
-%\begin{figure}
-%%\includegraphics {figure_temp.epsi}
-%\epsfxsize=3.25in\epsfbox{figure1.eps}
-%\caption{ Estimated relationship between the time an author spends reading these instructions and the quality of the author's digest article.}
-%\end{figure}
+% %\begin{figure}
+% %%\includegraphics {figure_temp.epsi}
+% %\epsfxsize=3.25in\epsfbox{figure1.eps}
+% %\caption{ Estimated relationship between the time an author spends reading these instructions and the quality of the author's digest article.}
+% %\end{figure}
 
-\begin{figure}
-\centering
-\includegraphics[width=9cm]{image1.png}
-\caption{Example of readable plot using different colors and line styles for clarity.}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=9cm]{image1.png}
+% \caption{Example of readable plot using different colors and line styles for clarity.}
+% \end{figure}
 
-Notice that prior to the graph, a single 12-point line is used to
-separate the preceding text from the graph. The equivalent of a blank
-line should exist between the bottom of the graph (the x-axis caption)
-and the figure caption. (In this particular case, there was no need to
-add a blank line between the x-axis label and the figure caption,
-because there was already adequate spacing provided by the image
-border.) After the figure caption, there should be a single 12-point
-blank line before the text resumes. 
+% Notice that prior to the graph, a single 12-point line is used to
+% separate the preceding text from the graph. The equivalent of a blank
+% line should exist between the bottom of the graph (the x-axis caption)
+% and the figure caption. (In this particular case, there was no need to
+% add a blank line between the x-axis label and the figure caption,
+% because there was already adequate spacing provided by the image
+% border.) After the figure caption, there should be a single 12-point
+% blank line before the text resumes. 
 %\LaTeX accepts encapsulated post script files as figures.
@@
 This is not a concern with PDF file submissions.
-If you decide to use color traces in your graphical data, be absolutely certain that there is no ambiguity about your graphical information when printed on a B\&W printer.
+% If you decide to use color traces in your graphical data, be absolutely certain that there is no ambiguity about your graphical information when printed on a B\&W printer.
 
-Table I on the second page was inserted using ``Insert'', ``Text
-Box'', creating the text contained in Table I, and then formatting the
-text box using all the settings available under ``Format'', ``Text
-Box\dots ''. Table I also serves as an illustration of one of the rare
-instances when the double column format requirement can be
-violated. Certain figures and tables will require the full-page width
-to display. It is usually best to place these figures and tables at
-the top, rather than in the middle or bottom of a page. Tables should be entered within a single column if this can be done cleanly, without the entry becoming too crowded.
+% Table I on the second page was inserted using ``Insert'', ``Text
+% Box'', creating the text contained in Table I, and then formatting the
+% text box using all the settings available under ``Format'', ``Text
+% Box\dots ''. Table I also serves as an illustration of one of the rare
+% instances when the double column format requirement can be
+% violated. Certain figures and tables will require the full-page width
+% to display. It is usually best to place these figures and tables at
+% the top, rather than in the middle or bottom of a page. Tables should be entered within a single column if this can be done cleanly, without the entry becoming too crowded.
 
-\section{Citing Previous Work}
-When referencing a journal article \cite{Yamaguchi}, a conference
-digest article \cite{Hovel} or a book \cite{Fahrenbruch}, place the reference numbers within square
-brackets.
+% \section{Citing Previous Work}
+% When referencing a journal article \cite{Yamaguchi}, a conference
+% digest article \cite{Hovel} or a book \cite{Fahrenbruch}, place the reference numbers within square
+% brackets.
 To simultaneously cite these references \cite{Yamaguchi} - \cite{Fahrenbruch} use the format just demonstrated.
@@
 
-Generally speaking, references should be very detailed.
+% Generally speaking, references should be very detailed.
 For journal articles, list all authors by initials and last name, the title of the paper in quotations (capitalizing only the first letter of the first word, unless it would be capitalized in a sentence, e.g., a proper noun), the journal name in italics, the volume number, the issue number, the page numbers, and the date.
 Use the examples provided \cite{Yamaguchi} - \cite{Fahrenbruch} as a guide.
-%Further information on LaTeX and TeX can be found in \cite{IEEEhowto:kopka} - \cite{knuth}.
+% %Further information on LaTeX and TeX can be found in \cite{IEEEhowto:kopka} - \cite{knuth}.
 
-% The following statement makes the two columns on the last page more
-% or less of equal length.  Placement of this command is by trial and error.
-\vfil\eject
+% % The following statement makes the two columns on the last page more
+% % or less of equal length.  Placement of this command is by trial and error.
+% \vfil\eject
 
-\section{Copyright and Reprint Information}
-The IEEE copyright form will be electronically submitted for this conference.  On the conference web site, follow the link in the manuscript submission area.
+% \section{Copyright and Reprint Information}
+% The IEEE copyright form will be electronically submitted for this conference.  On the conference web site, follow the link in the manuscript submission area.
 
-Reprints may be ordered by checking the appropriate box on the conference registration form.
+% Reprints may be ordered by checking the appropriate box on the conference registration form.
 The reprints will be mailed to you at the address listed on the registration form approximately 3 months after the conference.

### 2019-04-24 PVSC-46/Manuscript/PVSC_Manuscript.tex
finished convert template form

@@
 \usepackage[colorinlistoftodos]{todonotes}
-
+\newtheorem{definition}{Definition}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 % correct bad hyphenation here
@@
 
-\section{Photovoltaic Array}
+\section{Photovoltaic Array}\label{Sec2}
 
@@
 \end{figure}
-% \subsection{ Major Subsections}
-% As shown, denote subsections with left justified 10-point Times Italic.
-Order them with capitalized alphabetic characters $(A, B,...)$.
-Follow the letter designation with a period, a single space, and then the subsection title capitalizing the first letter of each word.
-The paragraph description of the subsection heading is set to "exactly 12-point" line spacing with 6 points before and after.
-% \subsection{ Equations }
-% Equations should be centered in the column and numbered sequentially.
-Place the equation number to the right of the equation within a parenthesis, with right justification within its column.
-An example would be
-% \begin{equation}
-% V_{OC}=\frac{1}{\beta}ln\left(\frac{I_L}{I_S}+1\right)
-% \end{equation}
-% \emph{Make sure that any subscripts in your equations are legible and are not too
-% small to read!} When referring to an equation, use the number within
-% parenthesis. For example, you would usually refer to the first
-% equation as (1) rather than equation (1). If possible, use the Symbol
-% font for all special characters.%, or better yet, use Equation Editor or
-% %MathType. 
-% The paragraph description of the line containing the
-% equation should be set for 6 points before and 6 points after. The
-% paragraph spacing will need to be set to ``single'' rather than ``exactly
-% 12 point'' so that the height will autoscale to fit the equation.
 
-% \section{Figures and Tables}
-% The use of color in figures and photos is recommended.
-Keep in mind that the proceedings will only be produced in electronic format (DVD).
-There will not be a hardbound version of the proceedings.
-Please consider the use of different line styles (dashes, dots, etc.) in plots to ensure clarity.
-See example.
-Please use jpg or png format for all images and compress the size.
+\section{Orozco-Guierrez's method}\label{Sec3}
+In this section, we briefly introduce a method proposed by Orozco-Guierrez et al.\cite{orozco2016optimized} as the most related work to this paper.
+Orozco-Guierrez et al. proposed an efficient reconfiguration algorithm for mismatched PV arrays. 
+The method utilizes information of MPPs of every PV panel that are extracted using an online monitoring \cite{carotenuto2014online} and a power estimation \cite{orozco2015fast}. 
+Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
+For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
+As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
+Table \ref{tab:modules} shows the maximum number of active modules for each current level.
 
-% Most of the following applies to Microsoft Word.
-Figures should utilize as much of the column width as possible in order to maximize legibility.
-Use a sans serif font, such as Helvetica.
-Helvetica is larger and much easier to read than Times.
-Using 8- to 10-point Helvetica usually results in a legible figure.
-\emph{Do not use any font smaller than 8-point!} It must be legible.
-When referring to a figure, use the abbreviation Fig.
-followed by its number.
-Place figure captions directly below each figure.
-Use
-% 9-point Times with the paragraph spacing set at ``exactly 10 points.'' Set a tab at 0.5 inch.
-Type ``Fig.
-\#.'' (\# is the numeral) then tab over to the 0.5 inch mark before beginning the text of the figure caption.
-Note that figure captions are always (left and right) justified, rather than centered, even if they are less than a single full line in length.
-See the caption for Fig.
-1.
+Then power values are approximated for possible configurations. 
+Table \ref{tab:powers} shows an example to form a PV array with two strings where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V). 
+The method has a simple feasibility check as follows. 
+\newline{}
+\textbf{(Feasibility 1)} For the $n$-th highest current level $I_{n}$, the number of active modules in a system is $N(I_{n}) / n$ or less. 
+\newline{}
+Where, $N(I)$ denotes the total number of active modules for a current level $I$. 
+For example, consider a candidate current pair (3A.
+2.5A).
+In this case, the highest and the second highest current levels are 3A and 2.5A, respectively, and the total number of active modules for 3A and 2.5A are 3 and 6, respectively (see Table \ref{tab:modules}).
+Therefore, the number of active modules in the first string is 3 or less, and the number of active modules in the second string is also $ 6/2  = 3$ or less.
+Consequently, the number of active modules per string is at most 3 for a candidate current pair (3A.
+2.5A).
+Table \ref{tab:powers} has values in the cells when Feasibility 1 is satisfied.
 
-% Within \LaTeX, there is basically only one option for placing figures
-% within your paper.  Often the easiest way is to insert them into the
-% top of the next column.
-%Within Microsoft Word there are several options for placing figures
-%within your paper. Often the easiest is to insert them between
-%existing paragraphs allowing the figures to remain in that relative
-%position. The paragraph description where the figure is inserted must
-%be set to ``single'' spacing rather than ``exactly 12 points'' in
-%order to allow the line to autoscale in height to display the entire
-%figure. Some disadvantages of this approach are that you don't have
-%total flexibility in placing figures, and that the figures will move
-%as text is inserted or deleted in any part of the document before the
-%figure. If you elect to use this approach, it is recommended that you
-%nearly complete the editing of your text before inserting any
-%figures. Remember to allow room for them, however. Then begin
-%inserting figures starting from the beginning of your document. 
-% Do not lump all figures at the end of the paper!
-% If you have difficulties with the titles on your figures, you can always elect to add in the titles as separate text boxes, rather than importing the titles with the graph.
-This is sometimes helpful in getting a lengthy vertically-oriented title to display correctly.
+The method finds the largest power value from possible candidate configurations (330W for current pair (3A, 2.5A) with three active modules in this case) and evaluates the case more precisely along with the cases with close values to the best value since the analysis are given with approximated values.
+In the case of Table \ref{tab:powers}, 330W, 320W and 300W are selected for further evaluation.
 
-% %\begin{figure}
-% %%\includegraphics {figure_temp.epsi}
-% %\epsfxsize=3.25in\epsfbox{figure1.eps}
-% %\caption{ Estimated relationship between the time an author spends reading these instructions and the quality of the author's digest article.}
-% %\end{figure}
+\begin{table}[t]
+\caption{Extracted currents of MPPs}
+\label{tab:monitored}
+\centering
+\begin{tabular}{c|rrrr}
+\hline\hline
+       &    	\multicolumn{4}{c}{Panels}								\\
+	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$}	\\ \hline
+MPP1	&	3.10A	&	3.09A	&	0.52A	&	2.47A	\\ \hline
+MPP2	&	2.98A	&	2.55A	&	0.50A	&	1.53A	\\ \hline
+MPP3	&	1.55A	&	2.48A	&	0.46A	&	0.48A	\\ \hline
+\end{tabular}
+\end{table}
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=9cm]{image1.png}
-% \caption{Example of readable plot using different colors and line styles for clarity.}
-% \end{figure}
+\begin{table}[t]
+\caption{Approximated currents of MPPs}
+\label{tab:approximated}
+\centering
+\begin{tabular}{c|rrrr}	
+\hline\hline
+       &    	\multicolumn{4}{c}{Panels}	\\
+	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$}	\\ \hline
+MPP1	&	3A	&	3A	&	0.5A	&	2.5A	\\ \hline
+MPP2	&	3A	&	2.5A	&	0.5A	&	1.5A	\\ \hline
+MPP3	&	1.5A	&	2.5A	&	0.5A	&	0.5A	\\ \hline
+\end{tabular}
+\end{table}
 
-% Notice that prior to the graph, a single 12-point line is used to
-% separate the preceding text from the graph. The equivalent of a blank
-% line should exist between the bottom of the graph (the x-axis caption)
-% and the figure caption. (In this particular case, there was no need to
-% add a blank line between the x-axis label and the figure caption,
-% because there was already adequate spacing provided by the image
-% border.) After the figure caption, there should be a single 12-point
-% blank line before the text resumes. 
-%\LaTeX accepts encapsulated post script files as figures.
-Standard post script figures will not expand and contract to fill the designate area on the page.
-Encapsulated post script files will.
-Thus, encapsulated post script files must obviously be only one page long.
-It is often easy to convert a post script file to encapsulated post script.
-In Linux this can be done with the command, ``ps2epsi.''
-%More flexibility is obtained in inserting figures if you can place
-%them exactly where you would like them to be on a page. This can be
-%accomplished by inserting the figure, selecting the figure, and then
-%choosing ``Format Picture\dots ''.
-Various settings allow you to place the figure at an absolute position on a page; specify if the text is supposed to flow around the figure or if the figure should move with the text, etc.
-If you elect to let the text flow around the figure, then remember that you will have to insert a separate text box for the caption, otherwise the figure caption is likely to become separated from the figure.
-%When importing a graph from Excel into Word, it is often helpful to
-%special-paste it in as a ``Picture (Enhanced Meta-file).'' This saves
-%file memory for Word documents. Be aware that the usual Copy
-%$\rightarrow $  Paste procedure will copy the entire Excel spreadsheet into your Word file.
-The Copy $\rightarrow$ Paste Special $\rightarrow$ Picture (Enhanced Metafile) command copies only the graph as a static picture.
-This is not a concern with PDF file submissions.
-% If you decide to use color traces in your graphical data, be absolutely certain that there is no ambiguity about your graphical information when printed on a B\&W printer.
+\begin{table}[t]
+\caption{Maximum number of active modules}
+\label{tab:modules}
+\centering
+\begin{tabular}{c|rrrr|r}	
+\hline\hline
+       &    	\multicolumn{4}{c|}{Panels}	& \\									
+	&	\multicolumn{1}{c}{$P1$}	&	\multicolumn{1}{c}{$P2$}	&	\multicolumn{1}{c}{$P3$}	&	\multicolumn{1}{c}{$P4$} &	\multicolumn{1}{|c}{total}	\\ \hline
+3A	&	2	&	1	&	0	&	0 & 3	\\ \hline
+2.5A	&	2	&	3	&	0	&	1 & 6	\\ \hline
+1.5A	&	3	&	3	&	0	&	2 & 8	\\ \hline
+0.5A	&	3	&	3	&	3	&	3 & 12	\\ \hline
+\end{tabular}
+\end{table}
 
-% Table I on the second page was inserted using ``Insert'', ``Text
-% Box'', creating the text contained in Table I, and then formatting the
-% text box using all the settings available under ``Format'', ``Text
-% Box\dots ''. Table I also serves as an illustration of one of the rare
-% instances when the double column format requirement can be
-% violated. Certain figures and tables will require the full-page width
-% to display. It is usually best to place these figures and tables at
-% the top, rather than in the middle or bottom of a page. Tables should be entered within a single column if this can be done cleanly, without the entry becoming too crowded.
+\begin{table*}[t]
+\caption{Approximated power}
+\label{tab:powers}
+\centering
+\begin{tabular}{c|rrrrrrrrrrr}
+\hline\hline	
+\# modules & 	\multicolumn{10}{c}{currents sequence for strings (A)} \\ 																
+per string		&	\multicolumn{1}{c}{(3,3)}	&	\multicolumn{1}{c}{(3,2.5)}	&	\multicolumn{1}{c}{(3,1.5)}	&	\multicolumn{1}{c}{(3,0.5)}	&	\multicolumn{1}{c}{(2.5,2.5)}	&	\multicolumn{1}{c}{(2.5,1.5)}	&	\multicolumn{1}{c}{(2.5,0.5)}	&	\multicolumn{1}{c}{(1.5,1.5)}	&	\multicolumn{1}{c}{(1.5,0.5)}	&	\multicolumn{1}{c}{(0.5,0.5)}	\\ \hline
+	1	&	120W	&	110W	&	90W	&	70W	&	100W	&	80W	&	60W	&	60W	&	40W	&	20W	\\ \hline
+	2	&	-	&	220W	&	180W	&	140W	&	200W	&	160W	&	120W	&	120W	&	80W	&	40W	\\ \hline	3	&	-	&\textbf{330W}&	270W	&	210W	&	\textbf{300W}	&	240W	&	180W	&	180W	&	120W	&	60W	\\ \hline
+4	&	-	&	-	&	-	&	-	&	-	&	\textbf{320W}	&	240W	&	240W	&	160W	&	80W	\\ \hline
+	 5	&	-	&	-	&	-	&	-	&	-	&	-	&	\textbf{300W}	&	-	&	200W	&	100W	\\ \hline
+	6	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	240W	&	120W	\\ \hline
+\end{tabular}
+\end{table*}
 
-% \section{Citing Previous Work}
-% When referencing a journal article \cite{Yamaguchi}, a conference
-% digest article \cite{Hovel} or a book \cite{Fahrenbruch}, place the reference numbers within square
-% brackets.
-To simultaneously cite these references \cite{Yamaguchi} - \cite{Fahrenbruch} use the format just demonstrated.
-The reference list is the last section and references are listed in the order cited.
-Use 9 point Times.
-The paragraph description is set for a line spacing of exactly 10 points with 0 point spacing before and after.
-A 0.25 inch hanging indention should be specified.
+\section{Feasibility}
+In the method\cite{orozco2016optimized}, to execute a power simulation for a PV array, we need to assign panels into strings to realize a candidate configuration. 
+For example, a candidate configuration for a current pair (2.5A, 2.5A) with 3 active modules is realized by assign panel P2  to the first string and panels P1 and P4 to the second string as shown in Fig.\ref{fig:feasible-configuration}.
+However, we could not find feasible assignment for a current pair (3A, 2.5A) with 3 active modules or a current pair (2.5A, 1.5A) with 4 active modules though they are expected to generate higher powers 330W or 320W.
+That is, the condition Feasibility 1 is a necessary but not sufficient to check the actual feasibility.
 
-% Generally speaking, references should be very detailed.
-For journal articles, list all authors by initials and last name, the title of the paper in quotations (capitalizing only the first letter of the first word, unless it would be capitalized in a sentence, e.g., a proper noun), the journal name in italics, the volume number, the issue number, the page numbers, and the date.
-Use the examples provided \cite{Yamaguchi} - \cite{Fahrenbruch} as a guide.
-% %Further information on LaTeX and TeX can be found in \cite{IEEEhowto:kopka} - \cite{knuth}.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.8\linewidth]{PVSC-46/fig/feasible-configuration.pdf}
+    \caption{Feasible configuration}
+    \label{fig:feasible-configuration}
+\end{figure}
 
-% % The following statement makes the two columns on the last page more
-% % or less of equal length.  Placement of this command is by trial and error.
-% \vfil\eject
+Now we will define the feasibility. For a PV array $A$ with $s$ strings, let $M_{A,i}(I)$ denote the number of modules that can be active with a current level $I$ in the $i$-th string.
+Let $Q = (Q_{1},Q_{2},\ldots ,Q_{s})$ be a sequence of currents required for strings. 
+A sequence of currents $Q$ is feasible with $m$ modules if and only if it is possible to form a PV array $A$ such that 
+\begin{equation}
+M_{A,i}(Q_{i}) \geq m
+\end{equation}
+holds for each string $i (1 \leq i \leq s)$.
 
-% \section{Copyright and Reprint Information}
-% The IEEE copyright form will be electronically submitted for this conference.  On the conference web site, follow the link in the manuscript submission area.
+\section{An algorithm to identify feasibility}\label{Sec5}
+\subsection{Feasibility Problem}\label{Sec5_1}
+In this section, we propose an algorithm to identify feasibility.
+First we will formulate the feasibility problem that identify the feasibility for given current sequence and the number of active modules per string as follows.
 
-% Reprints may be ordered by checking the appropriate box on the conference registration form.
-The reprints will be mailed to you at the address listed on the registration form approximately 3 months after the conference.
+\textit{Definition 1} (\textit{Feasibility Problem}):\\
+Input: Information of MPPs (approximated values), a current sequence $Q$, the number of $m$ of active modules per-string.\\
+Output: Whether $Q$ with $m$ modules is feasible or not.
+
+\subsection{Outline of the algorithm}
+In the proposed algorithm, we try to configure a PV array and identify the feasibility. 
+For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s}) (Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$. 
+When selecting a panel to a string, we will consider how much we lose an opportunity that the panel is more effectively used for other current level. 
+For example, if we select Panel 1 in Table \ref{tab:modules} for a string with a current level 3A, two modules can be active while the remaining one module becomes inactive. 
+The remaining one module still is not active if $P1$ is used for a current level 2,5A, while it can be active if it is used for current level 1.5A or 0.5A. 
+We will consider that when selecting $P1$ for a current level 3A, we don't have any loss for a current level 2.5A but lose one module for 1.5A and 0.5A. 
+The algorithm select panels so as to minimize such losses.
+
+Let $M_{p}(I)$ denote the number of modules that can be active at current level $I$ in a PV panel $p$. 
+For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s}) (Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, 
+a loss of selecting a panel $p$ at the $k-1$-th string for the $k$-th string is defined as 
+$Loss(p,k) = M_{p}(Q_{k}) - M_{p}(Q_{k-1})$.
+
+To assign panels for the $n$-th string, the following steps are applied. Let $m$ be the required number of active modules.
+\begin{enumerate}
+\item Sort unselected PV panels in a lexicographically ascending order of $Loss(p,n+1)$, $Loss(p,n+2)$,$\ldots$, $Loss(p,s)$ and $M_{p}(Q_{n})$.
+\item Select PV panels until selecting $m$ or more active modules for a current level $Q_{n}$.
+\item Cancel redundant PV panels so that the number of active modules at a current level $Q_{n}$ is minimized.
+\item Swap selected PV panels with unselected PV panels so that the number of selected PV panels is minimized.
+\end{enumerate}
+
+Before explaining more details, we first show an example.
+Table \ref{tab:proposed-example} shows how to select PV panels for the first string where the required number $m$ of active modules is 5. 
+Panels are sorted by $Loss$ and $M_{p}(Q_{1})$ (the number of active modules for the first string) in the order of $P1$, $P2$, $\ldots$, $P7$. 
+In the example, panels $P2$ to $P6$ are at the same loss level $(1,0)$. 
+PV panels are selected for each loss level.
+First, $P1$ is selected, then panels at the second loss level are selected in the order of $P2$, $P3$, $\ldots$.
+After selecting until $P5$, the number of active modules exceed $m (=5)$.
+In this case, if there is some redundant panels, these panels are canceled.
+In the example, $P4$ is canceled.
+Finally, if some of selected PV panels can be swapped with less number of unselected panels, they are swapped.
+In the example, $P2$ and $P3$ are swapped with $P6$.
+Consequently, three panels $P1$, $P5$ and $P6$ are selected.
+
+\begin{table}[t]
+\caption{An example of the proposed method ($m = 5$)}
+\begin{center}
+\begin{tabular}{c|c|ccccc|c}\hline \hline
+                               & \multicolumn{7}{c}{Panels}  \\
+                               &  \multicolumn{1}{c}{$P1$}    & $P2$   & $P3$    & $P4$    & $P5$   & \multicolumn{1}{c}{$P6$}            & $P7$             \\ \hline
+$M_{p}(Q_1)$        & 1     & 1     & 1     & 1     & 2    & 2    & 2              \\ \hline
+$M_{p}(Q_2)$        & 1     & 2     & 2     & 2     & 3    & 3    & 2              \\ \hline
+$M_{p}(Q_3)$        & 1     & 2     & 2     & 2     & 3    & 3    & 3              \\ \hline
+$Loss(p,2)$           & 0     & 1     & 1     & 1     & 1    & 1    & 1    \\ \hline
+$Loss(p,3)$           & 0     & 0     & 0     & 0     & 0    & 0    & 1    \\ \hline\hline
+step 2        & $\surd$ & $\surd$ &$\surd$ &$\surd$ &$\surd$ & & \\ \hline
+step 3      & $\surd$ & $\surd$ &$\surd$ & &$\surd$ & & \\ \hline
+step 4       & $\surd$ &  & & &$\surd$ & $\surd$ & \\ \hline         
+\end{tabular}
+\end{center}
+\label{tab:proposed-example}
+\end{table}
+
+\subsection{Algorithm}
+Step 1 sorts unselected panels (with modules that can be active for the target current), and Step 2 selects panels one by one in the sorted order until reaching the required number of active modules.
+
+Step 3 optimizes the number of active modules. 
+In Step 3, if the number of active modules exceeds the required number $m$, redundant panels are canceled if exist. 
+A panel is \textit{redundant} if the number of active modules is still $m$ or more even if the panel is canceled.  
+Redundant panels are searched at loss level. 
+Starting with a loss level where the last panel is selected, we will check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
+where $Q_{n}$ is a required current level for the current string.
+Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
+If there still exceed $m$ after canceling, we will go to the previous loss level and try to cancel panels.
+This procedure is repeated until selecting an exact $m$ active modules or checking all the loss levels.
+
+Step 4 optimizes the number of selected panels.
+In Step 4, we will swap selected panels and an unselected panel in the same loss level to reduce the number of selected panels.
+There are 3 swap cases as shown in Table \ref{tab:swap}. Algorithm 1 shows a pseudo code of the proposed algorithm.
+
+\begin{table}[t]
+\caption{Swap rule}
+\label{tab:swap}
+\centering
+\begin{tabular}{c|c}
+\hline\hline
+\multicolumn{2}{c}{The numbers of active modules} \\
+selected panels & unselected panels \\ \hline
+1, 1, 1 & 3 \\ \hline
+1, 1 & 2 \\ \hline
+1, 2 & 3 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{algorithm}
+\caption{Feasibility Check}
+\LinesNumbered
+\SetKwInOut{Input}{Input}  
+\Input{
+  \textit{$Q = Q_1, Q_2, \ldots , Q_s$}: required current for each string; 
+  \textit{$m$}: The minimum number of active modules per string;
+  \textit{$M_{p}$}: The number of active modules in each panel \textit{p};
+  %\textit{P}: Number of panels; 
+  \textit{s}: Number of strings;}
+\SetKwInOut{Output}{Output}
+\Output{Feasibility Result;%\\
+        %Conf: Configuration Result;
+        }
+\For{\textup{each string} $ k (2 \leq k \leq s)$ \textup{and panel} $p$}{$Loss(p,k) = M_{p}(Q_{k}) - M_{p}(Q_{k-1})$}
+\For{j = 1 to s}
+    {{\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panes} $< m$}
+       {\textup{\textbf{return :}} Feasibility = NO}}
+     $PS$ = a set of unselected panels with $M_{p}(Q_{j}) > 0$;\\
+     // step 1\\
+     sort $PS$ in a lexicographically ascending order of $Loss(p,j+1)$, $Loss(p,j+2)$, $\ldots$, $Loss(p,s)$, $M_{p}(Q_{j})$;\\
+     // step 2\\
+     select panels in the order in $PS$ until $\sum M_{p}(Q_{j})$ for selected panels $\geq m$;\\
+     //step 3\\
+     group selected panels $LV_{1}$, $LV_{2}$,$\ldots$, $LV_{h}$ with loss level ($LV_{1}$ is the lowest level);\\
+     \For{i = h to 1}
+     {find and cancel redundant panels in $LV_{i}$ in the order in $PS$}
+     //step 4\\
+     \For{i = h to 1}
+     {apply swap rules for selected panels in $LV_{i}$ and an unselected panel in the same loss level}
+    }
+    \textup{\textbf{return :}} Feasibility = YES
+\end{algorithm}
+
+\subsection{Evaluation}
+Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected string is the same
+
+To evaluate the performance of proposed algorithm, we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV array.
+For each PV array, contains 6 - 24 PV panels connected into 3 - 6 PV strings.
+For each PV panel, it will has 3 - 8 working current values.
+
+The computational time required for finding optimal configuration and accuracy of feasibility judgment in the proposed algorithm and exhaustive search algorithm are compared in Table \ref{result_compare}.
+As shown in Table \ref{result_compare}, proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.
+
+\begin{table}[htbp]
+\caption{}
+\begin{center}
+\begin{tabular}{ccc}
+\multicolumn{3}{c}{\begin{tabular}[c]{@{}c@{}}COMPARISON BETWEEN EXISTED METHODS\\ AND PROPOSED ALGORITHM\end{tabular}}                                         \\ \hline \hline
+\multicolumn{1}{c|}{}                         & \multicolumn{1}{c|}{Proposed Algorithm} & \begin{tabular}[c]{@{}c@{}}Exhaustive search \\ Algorithm\end{tabular} \\ \hline
+\multicolumn{1}{c|}{Number of PV Array}       & \multicolumn{2}{c}{100}                                                                                         \\ \hline
+\multicolumn{1}{c|}{Number of MPP candidates} & \multicolumn{2}{c}{486}                                                                                       \\ \hline
+\multicolumn{1}{c|}{Feasible Candidates}      & \multicolumn{1}{c|}{324}              & 327                                                                   \\ \hline
+\multicolumn{1}{c|}{Infeasible Candidates}    & \multicolumn{1}{c|}{162}              & 159                                                                   \\ \hline
+\multicolumn{1}{c|}{Error Rate}               & \multicolumn{1}{c|}{0.62\%}            & 0\%                                                                    \\ \hline
+\multicolumn{1}{c|}{Ave. times per Array}     & \multicolumn{1}{c|}{0.003s}            & 98s                                                                 
+\end{tabular}
+\label{result_compare}
+\end{center}
+\end{table}
+
+\begin{table}[t]
+\caption{PV Cell Parameters}
+\begin{center}
+\begin{tabular}{c|c}
+\hline \hline
+Parameter             & Value  \\ \hline
+Short-Circuit Current & 0.66A  \\
+MPP-Current           & 0.58A  \\
+Open-Circuit Voltage  & 280V   \\
+MPP-Voltage           & 215V  \\
+Max Power Output      & 124.7W 
+\end{tabular}
+\end{center}
+\label{PV_cell_par}
+\end{table}
 
 \section{Conclusion}
-Following these instructions will improve the quality of your paper and the PVSC Proceedings.
+
+Power generation of mismatched PV arrays can be recovered by reconfiguring connection of PV panels.
+In this paper, we introduce a feasibility check problem to configure PV panel connections from PV module connections and proposed an algorithm that efficiently and effectively solve the problem. 
+The experimental results shows that the proposed algorithm can identify feasible configurations more than 32,000X faster than the exhaustive search with around 0.6\% errors. 
+The proposed method is useful to identify or configure actual PV panel connections from PV module level specifications or connections. 
+Since there are many works of PV module level reconfiguration and PV panel level reconfiguration using PV module level optimization as an intermediate solution, the proposed algorithm is useful to actually find PV panel connections from PV module level solutions.
+PV panel level reconfiguration is a practical and realistic solution for PV arrays composed of standard PV panels, 
+and the proposed method contributes to find efficient and effective solution for PV panel level reconfiguration.
+% Following these instructions will improve the quality of your paper and the PVSC Proceedings.
 If you have comments, please contact \url{Publications@ieee-pvsc.org}.

### 2019-05-03 PVSC-46/Manuscript/PVSC_Manuscript.tex
compliar on arch
Updates from Overleaf
Finish the first version 2019/05/04

@@
   Partial shading or PV cell damage induces mismatched power generation among PV panels and causes an efficiency loss of power generation.
-Power generation of mismatched PV arrays can be recovered by reconfiguring connection of PV panels.
+  Power losses of mismatched PV arrays can be recovered by reconfiguring connection of PV panels.
   In this paper, we introduce a \textit{feasibility check problem} of PV panel configuration.
-The problem identifies whether a connection among PV panels can be configured from a given PV module level solution. 
-We also propose an algorithm for the feasibility check problem.
-The experimental results demonstrate that the proposed method can identify feasible configurations more than 32,000X faster than the exhaustive search with around 0.6\% errors.
+  This problem identifies whether a connection among PV panels can be configured from a given PV module level solution.
+  We also propose an algorithm for the \textit{feasibility check problem}.
+  The experimental results demonstrate that the proposed algorithm can identify feasible configurations more than 32,000X faster than the exhaustive search with around 0.6\% errors. 
 \end{abstract}
@@
 Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
-However, due to the nature of a PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
-PV cells could not uniformly generate power when PV cells experience different irradiances or some of cells have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging.
+However, due to the nature of PV cell, which is a basic component of a PV array.
+PV arrays are sensitive to partial shading and PV cell damage. 
+PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging.
 To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
-However, it causes a significant loss of power generation.
+However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, it will also introduce voltage drop which cause PV system generates multi maximum power points.
+% However, it causes a significant loss of power generation.
 
@@
 We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
-Before reconfiguration, it has four peaks in power VS voltage curve, while,  if we reconfigure connection among PV panels, it can increase around 35\% power generation.
+Before reconfiguration, it has four peaks in power VS voltage curve, while, after we reconfigured connection among PV panels, power generation increased by 35\%.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{PVSC-46/fig/compare.png}
+    \includegraphics[width=0.8\linewidth]{../fig/compare.png}
     \caption{Power generation before and after reconfiguration}
@@
 Orozco-Gutierrez et al.
-proposed an efficient and effective reconfiguration method\cite{orozco2016optimized} where it first selects candidates of configurations with approximation and then finds the best one with precise power simulation.
-However, the candidates are specified in a PV module level though PV modules could not be fully reconfigured.
+proposed an efficient and effective reconfiguration method\cite{orozco2016optimized} where it first selects candidates of configurations using the product of approximated currents and voltages,
+then finds the best one with precise power simulation. 
+However, these candidates are specified in a PV module level though PV modules could not be fully reconfigured.
 Actually, we found that some of configuration candidates are not able to be realized.
@@
 
-In this paper, we propose an algorithm to rapidly check feasibility that a given configuration candidate is actually formed by given PV panels. 
+In this paper, we propose an algorithm to rapidly check feasibility that a given configuration candidate is actually able to form by given PV panels. 
 The proposed method can efficiently check the feasibility while identifying most feasible cases accurately. 
@@
 A PV panel is a series connection of PV modules, and a PV module is a parallel connection of a series of PV cells and a bypass diode. 
-A typical PV panel is composed of three PV modules each of which has 12-24 PV cells. 
+A typical commerical PV panel is composed of three PV modules each of which has 12-24 PV cells. 
 A PV module can generate power for a given voltage according to its I-V characteristics as shown in Fig.\ref{fig:IV}(a - c). 
@@
 
-To find out accurate I-V characteristics of a PV panel, we need a time consuming power simulation. 
+To find out accurate I-V characteristics of a PV panel, we need to apply a time consuming power simulation. 
 However, we can roughly understand I-V characteristics of a PV panel (and also a string) as follows. 
 When a control voltage is low, PV modules with high irradiance level are active while PV modules with low irradiance level are inactive with turning on their bypass diodes.
-In this case, a high current can flow in the PV panel. When control voltage is high, some of bypass diodes become turning off and the corresponding PV modules become active. 
-In this case, the current level is reduced and generated power sometimes increases and sometimes decreases. 
+In this case, a high current can flow in the PV panel. When control voltage is increaseing, some of bypass diodes become turning off and the corresponding PV modules become active. 
+In that case, the current flow in the panel is determined by current of module with lowest irradiance level, and generated power sometimes increases and sometimes decreases.
+% the current level is reduced and generated power sometimes increases and sometimes decreases. 
 The generated power at MPPs can be roughly estimated. 
 In Fig.\ref{fig:IV}(d), one PV panel has three PV modules with different irradiance levels. 
-The peak currents for these modules are 433mA, 307mA, and 155mA, respectively. 
-Voltages at MPPs are roughly 200V, 400V, 600V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 200V in this case). 
-At the first MPP (MPP1), only one PV module with a peak current of 433mA is active at a control voltage of 206V, so the generated power is 89W. 
-At the second MPP (MPP2), two PV modules with peak currents of 433mA and 307mA are active at a control voltage of 420V. 
-In this case, the current level of the PV panel is 307mA since two PV panels are connected in series and they have to have the same current level, and the generated power is 129W.
-At the third MPP (MPP3), the current level of the PV panel is 155mA at a control voltage of 644V, and the generated power is 100W.
+The peak currents for these modules are 4.3A, 3.0A, and 1.5A, respectively. 
+Voltages at MPPs are roughly 22V, 44V, 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 22V in this case). 
+At the first MPP (MPP1), only one PV module with a peak current of 4.5A is active at a control voltage of 22V, so the generated power is 94.6W. 
+At the second MPP (MPP2), two PV modules with peak currents of 4.3A and 3.0A are active at a control voltage of 44V. 
+In this case, the current level of the PV panel is 3.0A since two PV panels are connected in series and they have to have the same current level, and the generated power is 132W.
+At the third MPP (MPP3), the current level of the PV panel is 1.5A at a control voltage of 66V, and the generated power is 99W.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{module.png}
+    \includegraphics[width=0.8\linewidth]{../fig/module.png}
     \caption{PV array, string, module and panel}
@@
         \centering
-        \includegraphics[width=\linewidth]{PVSC-46/fig/m_1.png}
+        \includegraphics[width=\linewidth]{../fig/m_1.png}
         \caption{PV module 1}
@@
         \centering
-        \includegraphics[width=\linewidth]{PVSC-46/fig/m_2.png}
+        \includegraphics[width=\linewidth]{../fig/m_2.png}
         \caption{PV module 2}
@@
         \centering
-        \includegraphics[width=\linewidth]{PVSC-46/fig/m_3.png}
+        \includegraphics[width=\linewidth]{../fig/m_3.png}
         \caption{PV module 3}
@@
         \vspace{3mm}
-        \includegraphics[width=\linewidth]{PVSC-46/fig/panel.png}
+        \includegraphics[width=\linewidth]{../fig/panel.png}
         \caption{PV panel}
@@
 The method utilizes information of MPPs of every PV panel that are extracted using an online monitoring \cite{carotenuto2014online} and a power estimation \cite{orozco2015fast}.
-Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
+
+For the method in \cite{orozco2016optimized}, first, close values will be approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
+Then possible combinations of reconfiguration are enumerated.
+For each configuration candidates their generate power value are estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
 For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
+% Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
 As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
 Table \ref{tab:modules} shows the maximum number of active modules for each current level.
-
-Then power values are approximated for possible configurations. 
-Table \ref{tab:powers} shows an example to form a PV array with two strings where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V). 
+Control voltage for one PV model are approximated to 20V.
+Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
+% Then power values are approximated for possible configurations. 
+Table \ref{tab:powers} shows an example to form a PV array with two strings
+where power value is simply multiply PV array current with control voltage for a module and number of active modules per string.
+% where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V). 
 The method has a simple feasibility check as follows. 
@@
 However, we could not find feasible assignment for a current pair (3A, 2.5A) with 3 active modules or a current pair (2.5A, 1.5A) with 4 active modules though they are expected to generate higher powers 330W or 320W.
-That is, the condition Feasibility 1 is a necessary but not sufficient to check the actual feasibility.
+That is, the condition Feasibility 1 is a necessary but not sufficient to give a actual feasibility result.
 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{PVSC-46/fig/feasible-configuration.pdf}
+    \includegraphics[width=0.6\linewidth]{../fig/feasible-configuration-vertical.pdf}
     \caption{Feasible configuration}
@@
 \textit{Definition 1} (\textit{Feasibility Problem}):\\
-Input: Information of MPPs (approximated values), a current sequence $Q$, the number of $m$ of active modules per-string.\\
-Output: Whether $Q$ with $m$ modules is feasible or not.
+\textbf{Input}: Information of MPPs (approximated values), a current sequence $Q$, the number of $m$ of active modules per-string.\\
+\newline
+\textbf{Output}: Whether $Q$ with $m$ modules is feasible or not.
 
 \subsection{Outline of the algorithm}
-In the proposed algorithm, we try to configure a PV array and identify the feasibility. 
+In the proposed algorithm, we try to configure a PV array and identify the feasibility of configuration.
 For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s}) (Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$. 
@@
 \subsection{Algorithm}
-Step 1 sorts unselected panels (with modules that can be active for the target current), and Step 2 selects panels one by one in the sorted order until reaching the required number of active modules.
+This algorithm roughly divided into 4 steps.
+
+Step 1, sort unselected panels in a lexicographically ascending order of index \textit{Loss} and $M_{P}(Q_{n})$.
+This sorting step will give a basic selecting priority for all unselected panels. A panel with uniformly irradiance distribution is perferred over non-uniformly irradiance distributed panel.
+
+Step 2, select panels one by one in the sorted order until reaching the required number of active modules.
+In this selection step, panel with no active modules by high selecting priority will be jumped.
+That will cut the computational space in the step 3 and step 4.
+% Step 1 sorts unselected panels (with modules that can be active for the target current), and Step 2 selects panels one by one in the sorted order until reaching the required number of active modules.
 
@@
 Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
-If there still exceed $m$ after canceling, we will go to the previous loss level and try to cancel panels.
-This procedure is repeated until selecting an exact $m$ active modules or checking all the loss levels.
+If there still exceed $m$ after canceling,
+the same cancel panels procedure will operate on previous loss level.
+% we will go to the previous loss level and try to cancel panels.
+This procedure will repeate until selecting an exact $m$ active modules or checking all the loss levels.
 
@@
 In Step 4, we will swap selected panels and an unselected panel in the same loss level to reduce the number of selected panels.
-There are 3 swap cases as shown in Table \ref{tab:swap}. Algorithm 1 shows a pseudo code of the proposed algorithm.
+There are 3 swap cases as shown in Table \ref{tab:swap}.
+The swap will keep or minimum total module losses and further reduce the number of panels.
+% Pseudo codes are given below to give details to summarize the process of proposed algorithm.
+\textbf{\textit{Algorithm 1}} shows a pseudo code of the proposed algorithm.
 
-\begin{table}[t]
+\begin{table}[ht]
 \caption{Swap rule}
@@
 \begin{algorithm}
-\caption{Feasibility Check}
+\caption{Feasibility Check Problem}
 \LinesNumbered
@@
 \subsection{Evaluation}
-Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected string is the same
+Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected string is the same.
 
-To evaluate the performance of proposed algorithm, we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV array.
+To evaluate the performance of proposed algorithm, we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV arrays.
 For each PV array, contains 6 - 24 PV panels connected into 3 - 6 PV strings.
@@
 The computational time required for finding optimal configuration and accuracy of feasibility judgment in the proposed algorithm and exhaustive search algorithm are compared in Table \ref{result_compare}.
-As shown in Table \ref{result_compare}, proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.
+As shown in Table \ref{result_compare},
+% proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.  
+from 100 PV arrays, 486 configuration candidates are selected where each candidate is specified with a required current sequence for strings and the number of active modules per string.
+Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identify the feasibility of every configuration but that takes a lot of time.
+On the other hand, the proposed algorithm rapidly (more than 32,000X faster) checks feasibility while misidentifying only 3 feasible cases. 
+% Each PV array has 4 or 5 candidates and our algorithm indeed found PV panel connection for each PV array.
 
@@
 
-\begin{table}[t]
-\caption{PV Cell Parameters}
-\begin{center}
-\begin{tabular}{c|c}
-\hline \hline
-Parameter             & Value  \\ \hline
-Short-Circuit Current & 0.66A  \\
-MPP-Current           & 0.58A  \\
-Open-Circuit Voltage  & 280V   \\
-MPP-Voltage           & 215V  \\
-Max Power Output      & 124.7W 
-\end{tabular}
-\end{center}
-\label{PV_cell_par}
-\end{table}
+% \begin{table}[ht]
+% \caption{PV Cell Parameters}
+% \begin{center}
+% \begin{tabular}{c|c}
+% \hline \hline
+% Parameter             & Value  \\ \hline
+% Short-Circuit Current & 0.66A  \\
+% MPP-Current           & 0.58A  \\
+% Open-Circuit Voltage  & 280V   \\
+% MPP-Voltage           & 215V  \\
+% Max Power Output      & 124.7W 
+% \end{tabular}
+% \end{center}
+% \label{PV_cell_par}
+% \end{table}
 

### 2019-05-09 PVSC-46/Manuscript/PVSC_Manuscript.tex
Modify the evaluation part

@@
 %% journal paper.
-%%
+%%。
 %% Support sites:
@@
 
-\section{Introduction}
+\section{Introduction}\label{Sec1}
 As fossil fuel depletion and environmental pollution become more serious, green and renewable energy has become necessary for a sustainable society and environment. 
@@
 
-\subsection{Evaluation}
+\section{Evaluation}\label{Sec6}
 Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected string is the same.
@@
 Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identify the feasibility of every configuration but that takes a lot of time.
-On the other hand, the proposed algorithm rapidly (more than 32,000X faster) checks feasibility while misidentifying only 3 feasible cases. 
+
+The calculation was performed using an Intel i7-4770 Quad-Core processor and 16 GB of RAM memory.
+The time used by the proposed feasibility check method was 3ms, which is significantly lower than the 98s need by the exhaustive search algorithm.
+On the other hand, the proposed algorithm misidentifying only 3 feasible negative cases with rapidly (more than 32,000X faster) feasibility checks speed
+
+In conclusion, the proposed method provides a solution for checking the feasibility of PV configurations with an error lower than 1\% but execution time are significant lower than the one required by exhaustive search algorithm.
 % Each PV array has 4 or 5 candidates and our algorithm indeed found PV panel connection for each PV array.

### 2019-05-24 PVSC-46/Manuscript/PVSC_Manuscript.tex
Modified based on Ooshita-sense's commit

@@
 
-\author{ \IEEEauthorblockN{\large Dafang Zhao, Fukohito Ooshita, and Michiko Inoue}
-\IEEEauthorblockA{\large Nara Insititute of Science and Technology, Japan \\ Email:\{zhao.dafang.yu7, f-ooshita, kounoe\}@is.naist.jp}}
+\author{ \IEEEauthorblockN{\large Dafang Zhao, Fukuhito Ooshita, and Michiko Inoue}
+\IEEEauthorblockA{\large Nara Institute of Science and Technology, Japan \\ Email:\{zhao.dafang.yu7, f-oosita, kounoe\}@is.naist.jp}}
 
@@
 Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
-However, due to the nature of PV cell, which is a basic component of a PV array.
-PV arrays are sensitive to partial shading and PV cell damage. 
+However, due to the nature of PV cell, which is a basic component of a PV array,PV arrays are sensitive to partial shading and PV cell damage. 
 PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging.
@@
 We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
-Before reconfiguration, it has four peaks in power VS voltage curve, while, after we reconfigured connection among PV panels, power generation increased by 35\%.
+Before reconfiguration, it has multiple maximum power points (MPP), while, after we reconfigured connection among PV panels, MPPs has reduced and power generation increased by 35\%.
 
@@
 The proposed method can efficiently check the feasibility while identifying most feasible cases accurately. 
-The experimental results demonstrate the effectiveness of the proposed method can identify the feasibility of configurations and false negative are less than 1\%.
+The experimental results demonstrate the effectiveness of the proposed method that it can identify the feasibility of configurations and false negative are less than 1\%.
 
@@
 The peak currents for these modules are 4.3A, 3.0A, and 1.5A, respectively. 
-Voltages at MPPs are roughly 22V, 44V, 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 22V in this case). 
+Voltages at MPPs are roughly 20V, 44V, 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 22V in this case). 
 At the first MPP (MPP1), only one PV module with a peak current of 4.5A is active at a control voltage of 22V, so the generated power is 94.6W. 
@@
 Orozco-Guierrez et al. proposed an efficient reconfiguration algorithm for mismatched PV arrays. 
-The method utilizes information of MPPs of every PV panel that are extracted using an online monitoring \cite{carotenuto2014online} and a power estimation \cite{orozco2015fast}.
+The method utilizes information of MPPs of every PV panel that is extracted using an online monitoring \cite{carotenuto2014online} and a power estimation \cite{orozco2015fast}.
 
@@
 Then possible combinations of reconfiguration are enumerated.
-For each configuration candidates their generate power value are estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
+For each candidate configuration their generate power value are estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
 For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
@@
 Table \ref{tab:modules} shows the maximum number of active modules for each current level.
-Control voltage for one PV model are approximated to 20V.
+Control voltage for one PV model is approximated to 20V.
 Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
 % Then power values are approximated for possible configurations. 
-Table \ref{tab:powers} shows an example to form a PV array with two strings
-where power value is simply multiply PV array current with control voltage for a module and number of active modules per string.
+Table \ref{tab:powers} shows an example to form a PV array with two strings,
+where power value is simply multiplied PV array current with control voltage .
 % where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V). 
@@
 \newline{}
-\textbf{(Feasibility 1)} For the $n$-th highest current level $I_{n}$, the number of active modules in a system is $N(I_{n}) / n$ or less. 
+\textbf{(Feasibility 1)} For the $n$-th highest current level $I_{n}$, the number of active modules in a configuration candidate is $N(I_{n}) / n$ or less,
 \newline{}
-Where, $N(I)$ denotes the total number of active modules for a current level $I$. 
-For example, consider a candidate current pair (3A.
-2.5A).
+Where $N(I)$ denotes the total number of active modules for a current level $I$. 
+For example, consider a candidate current pair (3A, 2.5A).
 In this case, the highest and the second highest current levels are 3A and 2.5A, respectively, and the total number of active modules for 3A and 2.5A are 3 and 6, respectively (see Table \ref{tab:modules}).
@@
 However, we could not find feasible assignment for a current pair (3A, 2.5A) with 3 active modules or a current pair (2.5A, 1.5A) with 4 active modules though they are expected to generate higher powers 330W or 320W.
-That is, the condition Feasibility 1 is a necessary but not sufficient to give a actual feasibility result.
+That is, the condition Feasibility 1 is necessary but not sufficient to give a actual feasibility result.
 
-\begin{figure}[t]
+\begin{figure}[htp]
     \centering
@@
 In this section, we propose an algorithm to identify feasibility.
-First we will formulate the feasibility problem that identify the feasibility for given current sequence and the number of active modules per string as follows.
+First we will formulate the feasibility problem that identifies the feasibility for given current sequence and the number of active modules per string as follows.
 
@@
 The remaining one module still is not active if $P1$ is used for a current level 2,5A, while it can be active if it is used for current level 1.5A or 0.5A. 
-We will consider that when selecting $P1$ for a current level 3A, we don't have any loss for a current level 2.5A but lose one module for 1.5A and 0.5A. 
+We will consider that when selecting $P1$ for a current level 3A, we do not have any loss for a current level 2.5A but lose one module for 1.5A and 0.5A. 
 The algorithm select panels so as to minimize such losses.
@@
 After selecting until $P5$, the number of active modules exceed $m (=5)$.
-In this case, if there is some redundant panels, these panels are canceled.
+In this case, if some redundant panels, these panels are canceled.
 In the example, $P4$ is canceled.
@@
                                &  \multicolumn{1}{c}{$P1$}    & $P2$   & $P3$    & $P4$    & $P5$   & \multicolumn{1}{c}{$P6$}            & $P7$             \\ \hline
-$M_{p}(Q_1)$        & 1     & 1     & 1     & 1     & 2    & 2    & 2              \\ \hline
+$M_{p}(Q_1)$        & 1     & 1     & 1     & 1     & 2    & 2    & 1              \\ \hline
 $M_{p}(Q_2)$        & 1     & 2     & 2     & 2     & 3    & 3    & 2              \\ \hline
@@
 
-Step 1, sort unselected panels in a lexicographically ascending order of index \textit{Loss} and $M_{P}(Q_{n})$.
+Step 1 sorts unselected panels in a lexicographically ascending order of index \textit{Loss} and $M_{P}(Q_{n})$.
 This sorting step will give a basic selecting priority for all unselected panels. A panel with uniformly irradiance distribution is perferred over non-uniformly irradiance distributed panel.
 
-Step 2, select panels one by one in the sorted order until reaching the required number of active modules.
-In this selection step, panel with no active modules by high selecting priority will be jumped.
-That will cut the computational space in the step 3 and step 4.
+Step 2 selects sorted panels one by one until reaching the required number of active modules.
+In this selection step, panel with no active modules will be skipped.
+% That will cut the computational space in the step 3 and step 4.
 % Step 1 sorts unselected panels (with modules that can be active for the target current), and Step 2 selects panels one by one in the sorted order until reaching the required number of active modules.
@@
 Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
-If there still exceed $m$ after canceling,
-the same cancel panels procedure will operate on previous loss level.
+If they still exceed $m$ after canceling,
+the same procedure will operate on previous loss level.
 % we will go to the previous loss level and try to cancel panels.
-This procedure will repeate until selecting an exact $m$ active modules or checking all the loss levels.
+This procedure is repeated until selecting an exactly $m$ active modules or checking all the loss levels.
 
@@
 There are 3 swap cases as shown in Table \ref{tab:swap}.
-The swap will keep or minimum total module losses and further reduce the number of panels.
+This swap procedure will minimum the total module losses and further more reduce the number of panels.
 % Pseudo codes are given below to give details to summarize the process of proposed algorithm.
@@
 
-\begin{algorithm}
+\begin{algorithm}[htp]
 \caption{Feasibility Check Problem}
@@
 \SetKwInOut{Input}{Input}  
-\Input{
-  \textit{$Q = Q_1, Q_2, \ldots , Q_s$}: required current for each string; 
-  \textit{$m$}: The minimum number of active modules per string;
-  \textit{$M_{p}$}: The number of active modules in each panel \textit{p};
+\Input{\\
+  \textit{$Q = Q_1, Q_2, \ldots , Q_s$}: required current for each string; \\
+  \textit{$m$}: the minimum number of active modules per string;\\
+  \textit{$M_{p}$}: the number of active modules in each panel \textit{p};\\
   %\textit{P}: Number of panels; 
-  \textit{s}: Number of strings;}
+  \textit{s}: the number of strings;}
 \SetKwInOut{Output}{Output}
@@
 \For{j = 1 to s}
-    {{\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panes} $< m$}
+    {{\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panels} $< m$}
        {\textup{\textbf{return :}} Feasibility = NO}}
@@
 To evaluate the performance of proposed algorithm, we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV arrays.
-For each PV array, contains 6 - 24 PV panels connected into 3 - 6 PV strings.
+For each PV array, 6 - 24 PV panels connected into 3 - 6 PV strings.
 For each PV panel, it will has 3 - 8 working current values.
@@
 from 100 PV arrays, 486 configuration candidates are selected where each candidate is specified with a required current sequence for strings and the number of active modules per string.
-Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identify the feasibility of every configuration but that takes a lot of time.
+Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identifies the feasibility of every configuration but that takes a lot of time.
 
 The calculation was performed using an Intel i7-4770 Quad-Core processor and 16 GB of RAM memory.
-The time used by the proposed feasibility check method was 3ms, which is significantly lower than the 98s need by the exhaustive search algorithm.
-On the other hand, the proposed algorithm misidentifying only 3 feasible negative cases with rapidly (more than 32,000X faster) feasibility checks speed
+The time used by the proposed feasibility check method was 3ms, which is significantly lower than the 98s needed by the exhaustive search algorithm.
+On the other hand, the proposed method misidentifying only 3 feasible negative cases, the error rate is less than 1 \%.
+% On the other hand, the proposed algorithm misidentifying only 3 feasible negative cases with rapidly (more than 32,000X faster) feasibility checks speed.
 
-In conclusion, the proposed method provides a solution for checking the feasibility of PV configurations with an error lower than 1\% but execution time are significant lower than the one required by exhaustive search algorithm.
+In conclusion, the proposed method provides a solution for checking the feasibility of PV configurations with an error lower than 1\% but execution time are significantly lower than the one required by exhaustive search algorithm.
 % Each PV array has 4 or 5 candidates and our algorithm indeed found PV panel connection for each PV array.
@@
 Power generation of mismatched PV arrays can be recovered by reconfiguring connection of PV panels.
-In this paper, we introduce a feasibility check problem to configure PV panel connections from PV module connections and proposed an algorithm that efficiently and effectively solve the problem. 
-The experimental results shows that the proposed algorithm can identify feasible configurations more than 32,000X faster than the exhaustive search with around 0.6\% errors. 
+In this paper, we introduced a feasibility check problem to configure PV panel connections from PV module connections and proposed an algorithm that efficiently and effectively solves the problem. 
+The experimental results show that the proposed algorithm can identify feasible configurations more than 32,000X faster than the exhaustive search with around 0.6\% errors. 
 The proposed method is useful to identify or configure actual PV panel connections from PV module level specifications or connections. 

### 2019-05-30 PVSC-46/Manuscript/PVSC_Manuscript.tex
modified in 2019/05/30

@@
 To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
-However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, it will also introduce voltage drop which cause PV system generates multi maximum power points.
+However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, it will introduce voltage drop which cause PV panel mismatched.
 % However, it causes a significant loss of power generation.
@@
 When a control voltage is low, PV modules with high irradiance level are active while PV modules with low irradiance level are inactive with turning on their bypass diodes.
-In this case, a high current can flow in the PV panel. When control voltage is increaseing, some of bypass diodes become turning off and the corresponding PV modules become active. 
+In this case, a high current can flow in the PV panel. When control voltage is increasing, some of bypass diodes become turning off and the corresponding PV modules become active. 
 In that case, the current flow in the panel is determined by current of module with lowest irradiance level, and generated power sometimes increases and sometimes decreases.
@@
 In Fig.\ref{fig:IV}(d), one PV panel has three PV modules with different irradiance levels. 
-The peak currents for these modules are 4.3A, 3.0A, and 1.5A, respectively. 
+The maximum power points currents for these modules are 4.3A, 3.0A, and 1.5A, respectively. 
 Voltages at MPPs are roughly 20V, 44V, 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 22V in this case). 
@@
 In this section, we propose an algorithm to identify feasibility.
-First we will formulate the feasibility problem that identifies the feasibility for given current sequence and the number of active modules per string as follows.
+First we will formulate the feasibility problem that identifies the feasibility for a given current sequence and the number of active modules per string as follows.
 
@@
 The remaining one module still is not active if $P1$ is used for a current level 2,5A, while it can be active if it is used for current level 1.5A or 0.5A. 
-We will consider that when selecting $P1$ for a current level 3A, we do not have any loss for a current level 2.5A but lose one module for 1.5A and 0.5A. 
+We will consider that, when selecting $P1$ for a current level 3A, we do not have any loss for a current level 2.5A but lose one module for 1.5A and 0.5A. 
 The algorithm select panels so as to minimize such losses.
@@
 After selecting until $P5$, the number of active modules exceed $m (=5)$.
-In this case, if some redundant panels, these panels are canceled.
+In this case, if some redundant panels exist, these panels are canceled.
 In the example, $P4$ is canceled.
@@
 \subsection{Algorithm}
-This algorithm roughly divided into 4 steps.
+This algorithm is roughly divided into 4 steps.
 
@@
 To evaluate the performance of proposed algorithm, we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV arrays.
-For each PV array, 6 - 24 PV panels connected into 3 - 6 PV strings.
+For each PV array, 6 - 24 PV panels are connected into 3 - 6 PV strings.
 For each PV panel, it will has 3 - 8 working current values.

### 2019-05-31 PVSC-46/Manuscript/PVSC_Manuscript.tex
camera ready version by Michiko

@@
 \usepackage{graphicx}
+%\usepackage[dvipdfmx]{graphicx} % for michiko
 \usepackage{hyperref} 
-\usepackage{graphicx}
+%\usepackage{graphicx}
 \usepackage{amssymb}
@@
 \usepackage{xcolor,color}
-\usepackage{graphicx}
+%\usepackage{graphicx}
 \usepackage{enumerate}
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+
+%In final version, please replace the following two definitions
+\newcommand{\michiko}{\textcolor{blue}}
+%\newcommand{\michiko}{\textcolor{black}}
 
@@
 Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
-However, due to the nature of PV cell, which is a basic component of a PV array,PV arrays are sensitive to partial shading and PV cell damage. 
+However, due to the nature of PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
 PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging.
 To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
-However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, it will introduce voltage drop which cause PV panel mismatched.
+However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, %
+\michiko{and it will hence result in a significant loss of power generation. }
+
+% it will introduce voltage drop which cause PV panel mismatched.
 % However, it causes a significant loss of power generation.
@@
 We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
-Before reconfiguration, it has multiple maximum power points (MPP), while, after we reconfigured connection among PV panels, MPPs has reduced and power generation increased by 35\%.
+Before reconfiguration, \michiko{there are} multiple \michiko{peaks in a power - voltage curve with similar power levels,} while, after we reconfigured connection among PV panels, 
+\michiko{some peaks exhibit much higher power levels than others and }
+%MPPs has reduced and 
+power generation increased by 35\%.
 
@@
 
-Reconfiguration in PV panel level has been investigated\cite{carotenuto2015evolutionary,hu2017non,orozco2016optimized}. 
-A PV array reconfiguration using genetic algorithm (GA) was proposed in \cite{carotenuto2015evolutionary}.
+Reconfiguration in PV panel level has been investigated~\cite{carotenuto2015evolutionary,hu2017non,orozco2016optimized}. 
+A PV array reconfiguration using genetic algorithm (GA) was proposed in~\cite{carotenuto2015evolutionary}.
 Though it can give a new configuration, computing cost is significantly high and the algorithm cannot generate the best configuration precisely.
-Hu et al. also addressed PV panel reconfiguration where they formulate a nonlinear integer programming problem to optimize power generation by reconfiguration \cite{hu2017non}.
+Hu et al. also addressed PV panel reconfiguration where they formulate a nonlinear integer programming problem to optimize power generation by reconfiguration~\cite{hu2017non}.
 Orozco-Gutierrez et al.
-proposed an efficient and effective reconfiguration method\cite{orozco2016optimized} where it first selects candidates of configurations using the product of approximated currents and voltages,
+proposed an efficient and effective reconfiguration method~\cite{orozco2016optimized} where it first selects candidates of configurations using the product of approximated currents and voltages,
 then finds the best one with precise power simulation. 
@@
 Actually, we found that some of configuration candidates are not able to be realized.
-However, the paper\cite{orozco2016optimized}  does not show any systematic way to identify such a feasibility.
+However, the paper~\cite{orozco2016optimized}  does not show any systematic way to identify such a feasibility.
 
@@
 The proposed method can efficiently check the feasibility while identifying most feasible cases accurately. 
-The experimental results demonstrate the effectiveness of the proposed method that it can identify the feasibility of configurations and false negative are less than 1\%.
+The experimental results demonstrate the effectiveness of the proposed method \michiko{where} it can identify the feasibility of configurations \michiko{with a very small}   false negative \michiko{rate of} less than 1\%.
 
@@
 The I-V characteristics is affected by irradiance level and physical damage of PV cells. 
-Figure \ref{fig:IV}(a) also shows a typical degradation of a I-V characteristics where generated current is reduced with some ratio while keeping the voltage range. 
+\michiko{Figure \ref{fig:IV}(a - c) also show} a typical degradation of a I-V characteristics where generated \michiko{currents are reduced} with some ratio while keeping the voltage range. 
 When a PV panel has a partial shade, that is its PV modules have different irradiance levels and hence different I-V characteristics, the PV panels might have multiple peaks (maximum power points, MPPs) in power generation as shown in Fig.\ref{fig:IV}(d).
@@
 In Fig.\ref{fig:IV}(d), one PV panel has three PV modules with different irradiance levels. 
-The maximum power points currents for these modules are 4.3A, 3.0A, and 1.5A, respectively. 
-Voltages at MPPs are roughly 20V, 44V, 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 22V in this case). 
-At the first MPP (MPP1), only one PV module with a peak current of 4.5A is active at a control voltage of 22V, so the generated power is 94.6W. 
-At the second MPP (MPP2), two PV modules with peak currents of 4.3A and 3.0A are active at a control voltage of 44V. 
+\michiko{Current levels at MPPs} for these modules are 4.3A, 3.0A, and 1.5A, respectively. 
+\michiko{Voltage levels} at MPPs are roughly 20V, 44V, \michiko{and} 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 22V in this case). 
+At the first MPP (MPP1), only one PV module with \michiko{a current of 4.3A} is active at a control voltage of 22V, so the generated power is 94.6W. 
+At the second MPP (MPP2), two PV modules with currents of 4.3A and 3.0A are active at a control voltage of 44V. 
 In this case, the current level of the PV panel is 3.0A since two PV panels are connected in series and they have to have the same current level, and the generated power is 132W.
@@
 
-For the method in \cite{orozco2016optimized}, first, close values will be approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
-Then possible combinations of reconfiguration are enumerated.
-For each candidate configuration their generate power value are estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
-For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
-% Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
-As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
-Table \ref{tab:modules} shows the maximum number of active modules for each current level.
-Control voltage for one PV model is approximated to 20V.
-Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
-% Then power values are approximated for possible configurations. 
-Table \ref{tab:powers} shows an example to form a PV array with two strings,
-where power value is simply multiplied PV array current with control voltage .
-% where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V). 
-The method has a simple feasibility check as follows. 
-\newline{}
-\textbf{(Feasibility 1)} For the $n$-th highest current level $I_{n}$, the number of active modules in a configuration candidate is $N(I_{n}) / n$ or less,
-\newline{}
-Where $N(I)$ denotes the total number of active modules for a current level $I$. 
-For example, consider a candidate current pair (3A, 2.5A).
-In this case, the highest and the second highest current levels are 3A and 2.5A, respectively, and the total number of active modules for 3A and 2.5A are 3 and 6, respectively (see Table \ref{tab:modules}).
-Therefore, the number of active modules in the first string is 3 or less, and the number of active modules in the second string is also $ 6/2  = 3$ or less.
-Consequently, the number of active modules per string is at most 3 for a candidate current pair (3A.
-2.5A).
-Table \ref{tab:powers} has values in the cells when Feasibility 1 is satisfied.
-
-The method finds the largest power value from possible candidate configurations (330W for current pair (3A, 2.5A) with three active modules in this case) and evaluates the case more precisely along with the cases with close values to the best value since the analysis are given with approximated values.
-In the case of Table \ref{tab:powers}, 330W, 320W and 300W are selected for further evaluation.
-
 \begin{table}[t]
@@
 
+For the method in \cite{orozco2016optimized}, first, close values \michiko{of extracted currents or voltages are} approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
+Then possible combinations of reconfiguration are enumerated.
+For each candidate configuration \michiko{its generated} power value \michiko{is} estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
+For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
+% Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
+As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
+Table \ref{tab:modules} shows the maximum number of active modules for each current level.
+Control voltage for one PV model is approximated to 20V.
+Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
+% Then power values are approximated for possible configurations. 
+Table \ref{tab:powers} shows an example to form a PV array with two strings,
+%where power value is simply multiplied PV array current with control voltage .
+\michiko{where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V), and power values of strings are obtained as products of current and voltage values.) For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string is 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is 330W.}
+
+\michiko{When constructing an approximated power matrix like Table~\ref{tab:powers}, the possibility that an array can be formed for given a current sequence and the number of active modules per string (it is called \textit{feasibility}) is examined.}
+The method \michiko{provides} a simple feasibility check as follows.
+
+\textbf{(Feasibility 1)}\footnote{In~\cite{orozco2016optimized}, only the case of $n=2$ is considered, and we extended the condition to general $n$. }%
+For the $n$-th highest current level $I_{n}$ \michiko{in a current sequence for strings}, the number of active modules in a configuration candidate is $N(I_{n}) / n$ or less,
+where $N(I)$ is the total number of active modules for a current level $I$.
+
+For example, consider a candidate current pair (3A, 2.5A).
+In this case, the highest and the second highest current levels are 3A and 2.5A, respectively, and the total number of active modules for 3A and 2.5A are 3 and 6, respectively (see Table \ref{tab:modules}).
+Therefore, the number of active modules in the first string is 3 or less, and the number of active modules in the second string is also $ 6/2  = 3$ or less.
+Consequently, the number of active modules per string is at most 3 for a candidate current pair (3A.
+2.5A).
+Table \ref{tab:powers} has values in the cells when Feasibility 1 is satisfied.
+
+The method finds the largest power value from possible candidate configurations (330W for current pair (3A, 2.5A) with three active modules in this case) and evaluates the case more precisely along with the cases with close values to the best value since the analysis are given with approximated values.
+In the case of Table \ref{tab:powers}, 330W, 320W and 300W are selected for further evaluation.
+
 \begin{table*}[t]
@@
 For example, a candidate configuration for a current pair (2.5A, 2.5A) with 3 active modules is realized by assign panel P2  to the first string and panels P1 and P4 to the second string as shown in Fig.\ref{fig:feasible-configuration}.
-However, we could not find feasible assignment for a current pair (3A, 2.5A) with 3 active modules or a current pair (2.5A, 1.5A) with 4 active modules though they are expected to generate higher powers 330W or 320W.
+However, we could not find \michiko{any} feasible assignment for a current pair (3A, 2.5A) with 3 active modules or a current pair (2.5A, 1.5A) with 4 active modules though they are expected to generate higher powers 330W or 320W.
 That is, the condition Feasibility 1 is necessary but not sufficient to give a actual feasibility result.
 
-\begin{figure}[htp]
+\begin{figure}[b]
     \centering
     \includegraphics[width=0.6\linewidth]{../fig/feasible-configuration-vertical.pdf}
-    \caption{Feasible configuration}
+    \caption{Feasible configuration for a current pair (2.5A, 2.5A) with 3 active modules.}
     \label{fig:feasible-configuration}
@@
 \textbf{Input}: Information of MPPs (approximated values), a current sequence $Q$, the number of $m$ of active modules per-string.\\
-\newline
+%\newline
 \textbf{Output}: Whether $Q$ with $m$ modules is feasible or not.
@@
 When selecting a panel to a string, we will consider how much we lose an opportunity that the panel is more effectively used for other current level. 
-For example, if we select Panel 1 in Table \ref{tab:modules} for a string with a current level 3A, two modules can be active while the remaining one module becomes inactive. 
-The remaining one module still is not active if $P1$ is used for a current level 2,5A, while it can be active if it is used for current level 1.5A or 0.5A. 
+For example, if we select Panel $P1$ in Table \ref{tab:modules} for a string with a current level 3A, two modules can be active while the remaining one module becomes inactive. 
+The remaining one module still is not active if $P1$ is used for a current level 2.5A, while it can be active if it is used for current level 1.5A or 0.5A. 
 We will consider that, when selecting $P1$ for a current level 3A, we do not have any loss for a current level 2.5A but lose one module for 1.5A and 0.5A. 
@@
 \subsection{Algorithm}
-This algorithm is roughly divided into 4 steps.
+\michiko{The proposed algorithm first obtains loss levels for each panel, and assigns panels for strings in the order of $1,2,\ldots ,s$ where $Q_{i} \geq Q_{j} (i \leq j)$ holds for a required current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s})$.
+The pseudo code is given in Algorithm~\ref{alg1}.
+To assign panels to the $n$-th highest current $Q_{n}$, the following 4 steps are applied.}
 
-Step 1 sorts unselected panels in a lexicographically ascending order of index \textit{Loss} and $M_{P}(Q_{n})$.
-This sorting step will give a basic selecting priority for all unselected panels. A panel with uniformly irradiance distribution is perferred over non-uniformly irradiance distributed panel.
+Step 1 sorts unselected panels in a lexicographically ascending order of $Loss(p,n+1)$, $Loss(p,n+2)$,$\ldots$, $Loss(p,s)$ and $M_{p}(Q_{n})$.
+This sorting step \michiko{gives} a basic \michiko{selection} priority for all unselected panels. 
+\michiko{A panel with less losses for higher current levels are preferred.
+For example, a panel $P1$ has $(Loss(P1,2), Loss(P1,3)) = (0,0)$, that is there is no loss for further assignment, and it has the highest priority.
+The last value $M_{p}(Q_{n})$ (the number of active modules at a current level $Q_{n}$ in panel $p$) is used to select the minimum number of modules for a required current level, and it will be described in Step 3.}
+%A panel with uniformly irradiance distribution is preferred over non-uniformly irradiance distributed panel.
 
 Step 2 selects sorted panels one by one until reaching the required number of active modules.
-In this selection step, panel with no active modules will be skipped.
+In this selection step, panel with no active modules are skipped.
 % That will cut the computational space in the step 3 and step 4.
@@
 A panel is \textit{redundant} if the number of active modules is still $m$ or more even if the panel is canceled.  
-Redundant panels are searched at loss level. 
-Starting with a loss level where the last panel is selected, we will check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
+Redundant panels are searched \michiko{for each loss level}. 
+Starting with a loss level where the last panel is selected, we check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
 where $Q_{n}$ is a required current level for the current string.
 Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
-If they still exceed $m$ after canceling,
-the same procedure will operate on previous loss level.
+If \michiko{the number of active modules} still exceeds $m$ after canceling,
+the same procedure is applied to the previous loss level.
 % we will go to the previous loss level and try to cancel panels.
 This procedure is repeated until selecting an exactly $m$ active modules or checking all the loss levels.
+\michiko{This step accurately finds redundant panels if exist in the following reason.
+Since the number of active modules in one panel is 0, 1, 2, or 3 and panels are selected from panels with less active modules in the same loss level, if the number of active modules exceed $m$, the surplus is 1 or 2.
+That means, the last selected panel has 2 or 3 active modules, and panels with 1 or 2 active modules have already selected if exist.}
 
 Step 4 optimizes the number of selected panels.
-In Step 4, we will swap selected panels and an unselected panel in the same loss level to reduce the number of selected panels.
-There are 3 swap cases as shown in Table \ref{tab:swap}.
-This swap procedure will minimum the total module losses and further more reduce the number of panels.
+In Step 4, we swap selected panels and an unselected panel in the same loss level to reduce the number of selected panels.
+There are 3 swap rules as shown in Table \ref{tab:swap}.
+This swap procedure \michiko{keeps the number of active modules while reducing the number of panels.
+The step increases the number of unselected panels and hence increase the flexibility for succeeding selection.}
+%will minimum the total module losses and further more reduce the number of panels.
 % Pseudo codes are given below to give details to summarize the process of proposed algorithm.
-\textbf{\textit{Algorithm 1}} shows a pseudo code of the proposed algorithm.
+%\textbf{\textit{Algorithm 1}} shows a pseudo code of the proposed algorithm.
 
@@
 \caption{Feasibility Check Problem}
+\label{alg1}
 \LinesNumbered
@@
 \section{Evaluation}\label{Sec6}
-Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected string is the same.
+%Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected string is the same.
 
-To evaluate the performance of proposed algorithm, we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV arrays.
+\michiko{To evaluate the proposed method, we prepared MPP informations of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
+MPP information is setup as follows for each PV array. 
+Each PV array has 6 - 24  panels and the number of PV panels is randomly determined. 
+Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array. 
+The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}
+
+\michiko{We first applied the method~\cite{orozco2016optimized} to select configuration candidates.
+Condition \textbf{Feasibility 1} is applied to exclude a part of infeasible configurations, and then configurations that generate more than 77\% of the maximum power are selected from the remainings as candidates as mentioned in~\cite{orozco2016optimized}.
+In our experiments, 486 candidates are selected from 100 PV arrays as shown in Table~\ref{result_compare}.
+That is, for each PV arrays, 4 - 5 candidates are selected in average.}
+
+\michiko{Table~\ref{result_compare} shows the results of feasibility checking by the proposed algorithm and the exhaustive search.} 
+%To evaluate the performance of  proposed algorithm, 
+%we compare the result with exhaustive searching algorithm for 100 random shadow distributed PV arrays.
 For each PV array, 6 - 24 PV panels are connected into 3 - 6 PV strings.
 For each PV panel, it will has 3 - 8 working current values.
-
-The computational time required for finding optimal configuration and accuracy of feasibility judgment in the proposed algorithm and exhaustive search algorithm are compared in Table \ref{result_compare}.
-As shown in Table \ref{result_compare},
+%The computational time required for finding optimal configuration and accuracy of feasibility judgment in the proposed algorithm and exhaustive search algorithm are compared in Table \ref{result_compare}.
+%As shown in Table \ref{result_compare},
 % proposed algorithm achieved less computing time compare with exhaustive search algorithm and with high accuracy.  
-from 100 PV arrays, 486 configuration candidates are selected where each candidate is specified with a required current sequence for strings and the number of active modules per string.
-Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identifies the feasibility of every configuration but that takes a lot of time.
+%from 100 PV arrays, 486 configuration candidates are selected where each candidate is specified with a required current sequence for strings and the number of active modules per string.
+Since the exhaustive search checks all the combinations of panel connections for each configuration candidate, it accurately identifies the feasibility of every configuration.
+% but that takes a lot of time.
+\michiko{Though the exhaustive search identified total 327 feasible configurations, the proposed method identified 324 configurations and 3 configurations are misidentified. 
+The proposed algorthm had a few false negative cases, but its rate was less than 1\%.
+That is, it can correctly identify feasibility for most cases. 
+Indeed, the proposed algorithm found at least one candidate configuration as feasible among 4 - 5 candidates for each PV arrays. }
 
@@
 The time used by the proposed feasibility check method was 3ms, which is significantly lower than the 98s needed by the exhaustive search algorithm.
-On the other hand, the proposed method misidentifying only 3 feasible negative cases, the error rate is less than 1 \%.
+%On the other hand, the proposed method misidentifying only 3 feasible negative cases, the error rate is less than 1 \%.
 % On the other hand, the proposed algorithm misidentifying only 3 feasible negative cases with rapidly (more than 32,000X faster) feasibility checks speed.

### 2019-06-01 PVSC-46/Manuscript/PVSC_Manuscript.tex
Updates from Overleaf

@@
 %where power value is simply multiplied PV array current with control voltage .
-\michiko{where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V), and power values of strings are obtained as products of current and voltage values.) For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string is 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is 330W.}
+\michiko{where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V), and power values of strings are obtained as products of current and voltage values.
+For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string is 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is 330W.}
 
-\michiko{When constructing an approximated power matrix like Table~\ref{tab:powers}, the possibility that an array can be formed for given a current sequence and the number of active modules per string (it is called \textit{feasibility}) is examined.}
+\michiko{When constructing an approximated power matrix like Table~\ref{tab:powers}, the possibility that an array can be formed for a given current sequence and the number of active modules per string (it is called \textit{feasibility}) is examined.}
 The method \michiko{provides} a simple feasibility check as follows.

### 2019-06-01 PVSC-46/Manuscript/PVSC_Manuscript.tex
modified by Prof. Ooshita

@@
 %\newcommand{\michiko}{\textcolor{black}}
+\newcommand{\zhao}{\textcolor{red}}
 
@@
 However, due to the nature of PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
-PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging.
-To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
-However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, %
-\michiko{and it will hence result in a significant loss of power generation. }
-
-% it will introduce voltage drop which cause PV panel mismatched.
-% However, it causes a significant loss of power generation.
-
-PV arrays are hierarchically constructed such that a group of PV cells form a PV module, a group of PV modules form a PV panel, and a group of PV panels form a PV array. 
-Power generation of mismatched PV arrays can be recovered by reconfiguring connection of these components. 
-Fig.\ref{compare} shows an example of power generations of a PV array with a partial shading. 
-We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
-Before reconfiguration, \michiko{there are} multiple \michiko{peaks in a power - voltage curve with similar power levels,} while, after we reconfigured connection among PV panels, 
-\michiko{some peaks exhibit much higher power levels than others and }
-%MPPs has reduced and 
-power generation increased by 35\%.
+PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and % power generation increased by 35\%.
+\zhao{maximum output power increased by 35\%}.
 
@@
 \michiko{where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V), and power values of strings are obtained as products of current and voltage values.
-For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string is 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is 330W.}
+For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string \zhao{are} 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is \zhao{approximated about} 330W.}
 
@@
 Step 3 optimizes the number of active modules. 
-In Step 3, if the number of active modules exceeds the required number $m$, redundant panels are canceled if exist. 
-A panel is \textit{redundant} if the number of active modules is still $m$ or more even if the panel is canceled.  
+In Step 3, if the number of active modules exceeds the required number $m$, redundant panels \zhao{will be} canceled if exist. 
+A panel is \textit{redundant} if the number of active modules is still $m$ or more even if \zhao{this} panel is canceled.  
 Redundant panels are searched \michiko{for each loss level}. 
@@
 \michiko{This step accurately finds redundant panels if exist in the following reason.
-Since the number of active modules in one panel is 0, 1, 2, or 3 and panels are selected from panels with less active modules in the same loss level, if the number of active modules exceed $m$, the surplus is 1 or 2.
+Since the number of active modules in one panel is 0, 1, 2, or 3 \zhao{as assumed in Section \ref{Sec2}} and panels are selected from panels with less active modules in the same loss level, if the number of active modules exceed $m$, the surplus is 1 or 2.
 That means, the last selected panel has 2 or 3 active modules, and panels with 1 or 2 active modules have already selected if exist.}
@@
 Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array.
+\zhao{\large \textbf{Is that means: Current value for PV modules in each PV panel are randomly assigned from 3 - 8 current values.}}
 The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}

### 2019-06-02 PVSC-46/Manuscript/PVSC_Manuscript.tex
Camera ready

--- 2019-06-01 PVSC-46/Manuscript/PVSC_Manuscript.tex
@@
 %In final version, please replace the following two definitions
-\newcommand{\michiko}{\textcolor{blue}}
+\newcommand{\michiko}{\textcolor{black}}
 %\newcommand{\michiko}{\textcolor{black}}
+\newcommand{\zhao}{\textcolor{black}}
 
@@
 To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions.
-However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, %
-\michiko{and it will hence result in a significant loss of power generation. }
+However, the operation of bypass diode will cause a number of PV cells to stop deliver power,
+\michiko{and it will hence result in a significant loss of power generation.}
 
@@
 %MPPs has reduced and 
-power generation increased by 35\%.
+% power generation increased by 35\%.
+% power generation increased by 35\%.
+\zhao{maximum output power increased by 35\%}.
 
@@
 A PV panel is a series connection of PV modules, and a PV module is a parallel connection of a series of PV cells and a bypass diode. 
-A typical commerical PV panel is composed of three PV modules each of which has 12-24 PV cells. 
+A typical commercial PV panel is composed of three PV modules each of which has 12-24 PV cells. 
 A PV module can generate power for a given voltage according to its I-V characteristics as shown in Fig.\ref{fig:IV}(a - c). 
@@
 Step 3 optimizes the number of active modules. 
-In Step 3, if the number of active modules exceeds the required number $m$, redundant panels are canceled if exist. 
-A panel is \textit{redundant} if the number of active modules is still $m$ or more even if the panel is canceled.  
+In Step 3, if the number of active modules exceeds the required number $m$, redundant panels \zhao{are} canceled if exist. 
+A panel is \textit{redundant} if the number of active modules is still $m$ or more even if \zhao{the} panel is canceled.
 Redundant panels are searched \michiko{for each loss level}. 
@@
 Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array.
+% \zhao{\large \textbf{Is that means: Current value for PV modules in each PV panel are randomly assigned from 3 - 8 current values.}}
 The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}
@@
 \michiko{Though the exhaustive search identified total 327 feasible configurations, the proposed method identified 324 configurations and 3 configurations are misidentified. 
-The proposed algorthm had a few false negative cases, but its rate was less than 1\%.
+The proposed algorithm had a few false negative cases, but its rate was less than 1\%.
 That is, it can correctly identify feasibility for most cases. 

### 2019-06-11 PVSC-46/Manuscript/PVSC_Manuscript.tex
finished!
20190611

@@
 Before reconfiguration, \michiko{there are} multiple \michiko{peaks in a power - voltage curve with similar power levels,} while, after we reconfigured connection among PV panels, 
-\michiko{some peaks exhibit much higher power levels than others and }
+\michiko{some peaks exhibit much higher power levels than others and the }%
 %MPPs has reduced and 
@@
 \michiko{Current levels at MPPs} for these modules are 4.3A, 3.0A, and 1.5A, respectively. 
-\michiko{Voltage levels} at MPPs are roughly 20V, 44V, \michiko{and} 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 22V in this case). 
+\michiko{Voltage levels} at MPPs are roughly 20V, 44V, \michiko{and} 66V in Fig.\ref{fig:IV}(d), those are roughly multiples of a voltage of MPP for one PV module (around 20V in this case). 
 At the first MPP (MPP1), only one PV module with \michiko{a current of 4.3A} is active at a control voltage of 22V, so the generated power is 94.6W. 
@@
 \begin{table}[t]
-\caption{Extracted currents of MPPs}
-\label{tab:monitored}
+% \caption{Extracted currents of MPPs}
+% \caption{EXTRACTED CURRENTS OF MPPS}
+% \label{tab:monitored}
 \centering
+\caption{EXTRACTED CURRENTS OF MPPS}
 \begin{tabular}{c|rrrr}
@@
 \end{tabular}
+\label{tab:monitored}
 \end{table}
@@
 \begin{table}[t]
-\caption{Approximated currents of MPPs}
-\label{tab:approximated}
+% \caption{Approximated currents of MPPs}
+% \caption{APPROXIMATED CURRENTS OF MPPS}
+% \label{tab:approximated}
 \centering
+\caption{APPROXIMATED CURRENTS OF MPPS}
 \begin{tabular}{c|rrrr}	
@@
 \end{tabular}
+\label{tab:approximated}
 \end{table}
@@
 \begin{table}[t]
-\caption{Maximum number of active modules}
-\label{tab:modules}
+% \caption{Maximum number of active modules}
+% \caption{MAXIMUM NUMBER OF ACTIVE MODULES}
+% \label{tab:modules}
 \centering
+\caption{MAXIMUM NUMBER OF ACTIVE MODULES}
 \begin{tabular}{c|rrrr|r}	
@@
 \end{tabular}
+\label{tab:modules}
 \end{table}
@@
 \begin{table*}[t]
-\caption{Approximated power}
+% \caption{Approximated power}
+\caption{APPROXIMATED POWER}
 \label{tab:powers}
@@
 \begin{table}[t]
-\caption{An example of the proposed method ($m = 5$)}
+% \caption{An example of the proposed method ($m = 5$)}
+\caption{AN EXAMPLE OF THE PROPOSED METHOD ($ m = 5$)}
 \begin{center}
@@
 \begin{table}[ht]
-\caption{Swap rule}
+% \caption{Swap rule}
+\caption{SWAP RULE}
 \label{tab:swap}

### 2019-11-22 IEEE_CEC_SS/Conference-LaTeX-template_7-9-18/conference_041818.tex
Revert to new OS

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Optimize Configuration For Mismatched PV System}
\author{\IEEEauthorblockN{1\textsuperscript{st} Dafang Zhao}
\IEEEauthorblockA{\textit{Graduate School of Information Science} \\
\textit{Nara Institute of Science and Technology}\\
Ikoma, Japan \\
zhao.dafang.yu7@is.naist.jp}
\\
\IEEEauthorblockN{3\textsuperscript{rd} Michiko Inoue}
\IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
\textit{Nara Institute of Science and Technology}\\
Ikoma, Japan \\
kounoe@is.naist.jp}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Fukuhito Ooshita}
\IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
\textit{Nara Institute of Science and Technology}\\
Ikoma, Japan \\
f-ooshita@is.naist.jp}}

\maketitle

\begin{abstract}
Power generation efficiency of Photovoltaic(PV) system are significantly affected by partial shading and solar cell damage. This efficiency loss caused by turning on bypass diode of PV panels, which we called mismatch loss. 
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-11-25 PVSC-46/Manuscript/PVSC_Manuscript.tex
modified by comment of PVSC publisher
• Table Captions (formatting) - Table captions should be in capital letters, roman numbered and placed above the table. Captions should be fully justified.

• Table Captions (alignment) - Table captions must be centered and fully justified.

• Figure Captions (alignment) - Figure captions must be fully justified and aligned left. Change alignment for Fig 1 ,2 and 3.
fix errors
Updates from Overleaf

@@
 \usepackage{xcolor,color}
+% \usepackage{caption2}
 %\usepackage{graphicx}
@@
 \newcommand{\zhao}{\textcolor{black}}
+
+\captionsetup[subfigure]{justification=justified,singlelinecheck=false}
+\captionsetup[figure]{justification=justified,singlelinecheck=false}
 
@@
 \centering
-    \includegraphics[width=0.8\linewidth]{../fig/compare.png}
+\includegraphics[width=9cm]{../fig/compare.png}
+% \captionstyle{flushleft}
 \caption{Power generation before and after reconfiguration}
@@
 
-\begin{figure}[t]
+\begin{figure}[]
     \centering
-    \includegraphics[width=0.8\linewidth]{../fig/module.png}
+    \includegraphics[width=9cm]{../fig/module.png}
     \caption{PV array, string, module and panel}
@@
      \centering
-    \begin{subfigure}[b]{0.3\linewidth}
+    \begin{subfigure}[b]{2.7cm}
         \centering
@@
      \end{subfigure}
-     \begin{subfigure}[b]{0.3\linewidth}
+     \begin{subfigure}[b]{2.7cm}
         \centering
@@
     \hfill
-    \begin{subfigure}[b]{\linewidth}
+    \begin{subfigure}[b]{9cm}
         \centering
         \vspace{3mm}
-        \includegraphics[width=\linewidth]{../fig/panel.png}
+        \includegraphics[width=9cm]{../fig/panel.png}
         \caption{PV panel}
@@
 \centering
-\caption{EXTRACTED CURRENTS OF MPPS}
+\caption{}
+\centerline{EXTRACTED CURRENTS OF MPPS}
+\vskip5pt
 \begin{tabular}{c|rrrr}
@@
 \centering
-\caption{APPROXIMATED CURRENTS OF MPPS}
+\caption{}
+\centerline{APPROXIMATED CURRENTS OF MPPS}
+\vskip5pt
 \begin{tabular}{c|rrrr}	
@@
 \centering
-\caption{MAXIMUM NUMBER OF ACTIVE MODULES}
+\caption{}
+\centerline{MAXIMUM NUMBER OF ACTIVE MODULES}
+\vskip5pt
 \begin{tabular}{c|rrrr|r}	
@@
 % \caption{Approximated power}
-\caption{APPROXIMATED POWER}
+  \caption{}
+  \centerline{APPROXIMATED POWER}
+  \vskip5pt
 \label{tab:powers}
@@
 % \caption{An example of the proposed method ($m = 5$)}
-\caption{AN EXAMPLE OF THE PROPOSED METHOD ($ m = 5$)}
+  \caption{}
+  \centerline{AN EXAMPLE OF THE PROPOSED METHOD ($ m = 5$)}
+  \vskip5pt
 \begin{center}
@@
 % \caption{Swap rule}
-\caption{SWAP RULE}
+  \caption{}
+  \centerline{SWAP RULE}
+  \vskip5pt
 \label{tab:swap}
@@
 
-\michiko{To evaluate the proposed method, we prepared MPP informations of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
+\michiko{To evaluate the proposed method, we prepared MPP information of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
 MPP information is setup as follows for each PV array. 

### 2019-11-25 Journal-Photovoltaic/manuscript.tex
day 0, init state

\documentclass[journal]{IEEEtran}
% *** CITATION PACKAGES ***
%
\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage[dvips]{graphicx}
\fi

% *** MATH PACKAGES ***
%
\usepackage{amsmath}

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage{algorithmic}

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
 \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
 \usepackage[caption=false,font=footnotesize]{subfig}
\fi

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{url}

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{Bare Demo of IEEEtran.cls\\ for IEEE Journals}

\author{Dafang Zhao,
        Fukohito Ooshita,~\IEEEmembership{Member,~IEEE}
        and~Michiko~Inoue,~\IEEEmembership{Member,~IEEE}}% <-this % stops a space

% \thanks{M. Shell was with the Department
% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
% GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
% \thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!

% The paper headers
% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
% {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  Power generation efficiency of photovoltaic (PV) systems is significantly affected buy partial shading and PV cell damage.
  Partial shading or PV cell damage induces mismatched power generation among PV panels.
  Conducted bypass diodes under mismatch conditions result in loss of efficiency in power generation.

\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEE, IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

\IEEEPARstart{A}{s} fossil fuel depletion and environmental pollution, green and renewable energy become necessary for a sustainable society and environment.

\subsection{Subsection Heading Here}
Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2019-11-26 Journal-Photovoltaic/manuscript.tex
day 1

@@
 \documentclass[journal]{IEEEtran}
-% *** CITATION PACKAGES ***
-%
+
+%%%% Using Latex Packages %%%%
+
 \usepackage{cite}
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-\else
-\usepackage[dvips]{graphicx}
-\fi
-
-% *** MATH PACKAGES ***
-%
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{subcaption}
+\usepackage{color}
+\usepackage{graphicx}
+\usepackage{xcolor}
+\usepackage{enumerate}
+\usepackage{multirow}
 \usepackage{amsmath}
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-\usepackage{algorithmic}
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% *** SUBFIGURE PACKAGES ***
-\ifCLASSOPTIONcompsoc
- \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\else
- \usepackage[caption=false,font=footnotesize]{subfig}
-\fi
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-\usepackage{url}
+\usepackage{amssymb}
+\usepackage[utf8]{inputenc}
+\usepackage[ruled]{algorithm2e}
+\usepackage[colorinlistoftodos]{todonotes}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\newtheorem{definition}{Definition}
+\renewcommand{\topfraction}{1.0}
+\renewcommand{\bottomfraction}{1.0}
+\renewcommand{\dbltopfraction}{1.0}
+\renewcommand{\textfraction}{0.01}
+\renewcommand{\floatpagefraction}{1.0}
+\renewcommand{\dblfloatpagefraction}{1.0}
+\setcounter{topnumber}{5}
+\setcounter{bottomnumber}{5}
+\setcounter{totalnumber}{10}
 
@@
 
-\title{Bare Demo of IEEEtran.cls\\ for IEEE Journals}
+\title{Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration}
 
@@
 
-% The paper headers
-% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-% {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
 % make the title area
@@
   Conducted bypass diodes under mismatch conditions result in loss of efficiency in power generation.
-
+  Mismatched PV array can be recovered by re-configuring electrical connections among PV panels in it.
+  In this paper, a feasibility check problem of PV panel reconfiguration is introduced.
+  This problem identifies whether a connection among PV panels can be configured from a given PV module level solution.
+  Proposed algorithm evaluated by comparison with the exhaustive search through random shading distributed PV array.
+  The experimental results demonstrate that proposed algorithm can identify feasible configurations more than 49,000 times faster than the exhaustive search with around 0.5\% errors.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-IEEE, IEEEtran, journal, \LaTeX, paper, template.
+PV reconfiguration, partial-shading, mismatch, feasibility, heuristic
 \end{IEEEkeywords}
@@
 \section{Introduction}
-
-\IEEEPARstart{A}{s} fossil fuel depletion and environmental pollution, green and renewable energy become necessary for a sustainable society and environment.
-
-\subsection{Subsection Heading Here}
-Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
+\IEEEPARstart{I}{n} recent years, the use of green and renewable energy sources has been increased with the aim to reduce fossil fuel depletion and environment pollution.
+Photovoltaic (PV) energy is one of the most promising emerging technologies.
+PV market growth by improvements of converting unlimited solar energy into electrical energy as well as the cost reductions of PV panels.
 
@@
 The conclusion goes here.
-
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
 
@@
 % by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
+\bibliographystyle{ieeetr}
+\bibliography{library}
 
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiography}{Michael Shell}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
 \end{document}

### 2019-11-26 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-11-26 22-13-09

@@
 
+The use of PV systems for power generation brings many challenges.
+Due to the nature of PV cell, which is the basic component of PV array.
+PV system easily suffers from various forms of system faults, which include physical damage, temperature in-homogeneity, or partial shading.
+Unlike cell damage or other system faults, partial shading sources from cloud, dust or snow are very hard to prevent and predict.
+Thus, when PV cell could not uniformly generate power when they experience different irradiance or been damaged.
+This unbalanced working scenario will lead whole system mismatch.
+Mismatch condition might accelerate heating or aging of PV cells and furthermore hinder operation of maximum power point tracking (MPPT) algorithm, especially when the PV array output P-V curve becomes non-convex\cite{islam2018performance}.
+
+For several series connected PV cells, shaded or damaged cell causing normal cells to produce higher voltages that may reverse bias of ``bad'' cells.
+When a large number of series connected cells cause a huge reverse bias across shaded cells, leading to large dissipation of energy in the ``bad'' cells.
+This huge energy dissipation occurring in a small area might get overheating or burning of PV cells, or ``hot-spots''.
+To protect PV cells from ``hot-spots'', bypass diode is used to circumvent concentrated energy dissipation.
+
 \section{Conclusion}
@@
 % by themselves when using endfloat and the captionsoff option.
+\section*{Temp}
+It is well known that mismatch due to partial shading, soiling, or ageing causes significant losses
+in the energy yield of photovoltaic (PV) systems [1,2]. Furthermore, mismatches may hinder operation
+of maximum power point (MPP) tracking algorithms, especially if the power versus output voltage
+characteristic becomes nonconvex [3]. It has also been shown that, even with commonly used bypass
+diodes, mismatched cells may become reverse-biased and dissipate power, producing an undesired
+cell temperature rise or hot spot [4,5]. This may lead to accelerated ageing and reduced reliability of
+the PV system
 

### 2019-11-26 gitpush.sh

@@ -1,0 +1,6 @@
+time=`date "+%Y-%m-%d %H-%M-%S"`
+who='Zhao'
+git add --all
+git commit -m "${who} push @ ${time}"
+git push origin master
+echo "Finished Push"

### 2019-11-26 gitpush.sh
Zhao push @ 2019-11-26 22-14-44

@@ -1,0 +1,6 @@
+time=`date "+%Y-%m-%d %H-%M-%S"`
+who='Zhao'
+git add --all
+git commit -m "${who} push @ ${time}"
+git push
+echo "Finished Push"

### 2019-11-26 gitpush.sh
Zhao push @ 2019-11-26 22-17-00

@@ -2,5 +2,5 @@ time=`date "+%Y-%m-%d %H-%M-%S"`
 who='Zhao'
 git add --all
 git commit -m "${who} push @ ${time}"
-git push origin master
+git push
 echo "Finished Push"

### 2019-11-27 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-11-27 15-27-31

@@
 To protect PV cells from ``hot-spots'', bypass diode is used to circumvent concentrated energy dissipation.
+However, the operation of bypass diode will cause several stop delivering power and generate multiple local maximum power points\cite{Orozco-Gutierrez2016}.
+Furthermore, strand bypass diode can not complete eliminate hot-spotting\cite{kim2015reexamination}.
+
+In order to improve PV system power generation efficiency and protect PV cells from damage, an efficient and effectively PV system manage method is worth to investigate.
 

### 2019-11-28 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-11-28 16-29-10

@@
 In order to improve PV system power generation efficiency and protect PV cells from damage, an efficient and effectively PV system manage method is worth to investigate.
+The key to improve power generation efficiency is to maintain maximum output power.
+Thus, different maximum power point tracking (MPPT) algorithms have been proposed in this regard.
+In different MPPT algorithms, P\&O\cite{kasa2000maximum,jain2004new,chomsuwan2002photovoltaic,wasynezuk1983dynamic}and hill climbing\cite{koutroulis2001development,teulings1993new,xiao2004modified} methods received many attention due to its low complexity and implement cost.
+Hill climbing and P\&O methods are different ways to implement the same fundamental method.
+Using the approximate linear relationship between $V_{OC}$,$I_{SC}$ and $V_{MPP}$, $I_{MPP}$, fractional voltage-based and current-based MPPT are popular due to their linear dependency of PV panel characteristic and irradiance level\cite{Liu2016,kobayashi2004novel,bekker2004finding,mutoh2002prediction,noguchi2001short}.
+However, under abnormal working condition such as partial shading, it is very hard for conventional MPPT algorithms to find global maximum power point.
+Meanwhile, without any PV module level improvement, it is impossible to protect PV panel against hot-spotting\cite{Olalla2018,ghanbari2016permanent}.
+
+Another attractive direction to improve PV system efficiency under different working condition is PV reconfiguration.
 

### 2019-12-03 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-03 17-28-03

@@
 To protect PV cells from ``hot-spots'', bypass diode is used to circumvent concentrated energy dissipation.
-However, the operation of bypass diode will cause several stop delivering power and generate multiple local maximum power points\cite{Orozco-Gutierrez2016}.
+However, the operation of bypass diode will cause several stop delivering power and generate multiple local maximum power points\cite{Orozco-Gutierrez2016} or the total PV module current are limited by the one of worst ``bad'' cell.
+In both situation, available energy is lost.
 Furthermore, strand bypass diode can not complete eliminate hot-spotting\cite{kim2015reexamination}.
@@
 
-Another attractive direction to improve PV system efficiency under different working condition is PV reconfiguration.
+Another attractive direction to improve PV system efficiency under different working condition is the reconfiguration of PV arrays.
+This concept was first proposed by Salameh $et$ $al.$\cite{Salameh1990} in 1990.
+Then in 2002, Sherif and Boutros $et$ $al.$ proposed a reconfigurable scheme for PV arrays that using transistors as switch network to improve performance\cite{sherif2002solar}.
 

### 2019-12-04 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-04 20-38-43

@@
 Then in 2002, Sherif and Boutros $et$ $al.$ proposed a reconfigurable scheme for PV arrays that using transistors as switch network to improve performance\cite{sherif2002solar}.
+Nguyen $et$ $al.$ proposed a method that divide PV array into two parts as the ``fixed'' part which is static connected PV modules and ``adaptive'' part that can be attached to ``fixed'' part with different configurations\cite{Nguyen2008}.
 
+In this type of ``fixed'' - ``adaptive'' architecture, the mathematical formulation is not clear.
+Moreover, if the partial shading part is large enough to cover ``adaptive'' part, this scheme become ineffective.
 \section{Conclusion}

### 2019-12-06 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-06 16-22-54

@@
 Moreover, if the partial shading part is large enough to cover ``adaptive'' part, this scheme become ineffective.
+Velasco $et$ $al.$\cite{Velasco-Quesada2009,velasco2008grid,velasco2005energy} proposed an principle of operation is referred as ``irradiance equalization''.
+Reconfiguration strategy based on this principle aim to relocate the PV panels on the rows so that ``irradiance equalization'' is achieved.
+However, optimal configuration requires differences between ``row'' irradiance level are minimized as shown in \cite{Velasco-Quesada2009} therefore it can only be realized on fully reconfigurable array.
+They proposed algorithm that calculate all possible configurations and stored as look-up table locally.
+Then, the ``best'' configuration for real-time shading scenario will be chosen from look-up table.
+There is no doubt that the number of possible configurations will increase from the size of the PV array and it will be more difficult to determine the optimal configuration with limited time.
 \section{Conclusion}

### 2019-12-07 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-07 21-19-45

@@
 There is no doubt that the number of possible configurations will increase from the size of the PV array and it will be more difficult to determine the optimal configuration with limited time.
+Though there are several reconfiguration methods have been proposed, most works consider reconfiguration in PV cell or PV module level.
+However, those reconfiguration requires a significantly high computation time or a large number of switches to implement reconfiguration.
+In addition, they require special PV panels with the capability of switching, and cannot be applied to the system constructed with standard PV panels.
+% From a practical view, reconfiguration of connections among PV panels is a realistic solution since a PV panel is manufactured as a physical one panel with two terminals and PV panels can be flexibly interconnected.
+
+% The main challenge in the reconfiguration of PV arrays concerns a large number of possibilities that must be evaluated to find the best solution.
+This paper proposes an optimization algorithm to check possibilities of configurations for reconfiguring PV arrays, which uses an approach that 
 \section{Conclusion}

### 2019-12-08 Journal-Photovoltaic/manuscript.tex
Finish section 1

@@
 % The main challenge in the reconfiguration of PV arrays concerns a large number of possibilities that must be evaluated to find the best solution.
-This paper proposes an optimization algorithm to check possibilities of configurations for reconfiguring PV arrays, which uses an approach that 
+This paper proposes an optimization algorithm to check possibilities of configurations for reconfiguring PV arrays, which uses an approach that limit and sort possible combinations by the index of ``Loss-rate''.
+Proposed feasibility checking algorithm can rapidly check feasibility that a given configuration candidate can be actually formed by given PV panels.
+The experimental results demonstrate the effectiveness of the proposed method where it can identify the feasibility of configurations with a very small false negative rate of less than 1\%.
+
+\section{Photovoltaic Array}
+
 \section{Conclusion}

### 2019-12-09 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-09 16-58-47

@@
 To protect PV cells from ``hot-spots'', bypass diode is used to circumvent concentrated energy dissipation.
-However, the operation of bypass diode will cause several stop delivering power and generate multiple local maximum power points\cite{Orozco-Gutierrez2016} or the total PV module current are limited by the one of worst ``bad'' cell.
+However, the operation of bypass diode will cause several stop delivering power and generate multiple local maximum power points or the total PV module current are limited by the one of worst ``bad'' cell.
 In both situation, available energy is lost.
@@
 % From a practical view, reconfiguration of connections among PV panels is a realistic solution since a PV panel is manufactured as a physical one panel with two terminals and PV panels can be flexibly interconnected.
+Orozco-Gutierrez et al.
+proposed an efficient and effective reconfiguration method~\cite{Orozco-Gutierrez2016} where it first selects candidates of configurations using the product of approximated currents and voltages,
+then finds the best one with precise power simulation. 
+However, these candidates are specified in a PV module level though PV modules could not be fully reconfigured.
+Actually, we found that some of configuration candidates are not able to be realized.
+However, the paper~\cite{Orozco-Gutierrez2016}  does not show any systematic way to identify such a feasibility.
 
@@
 
-\section{Photovoltaic Array}
+\section{PV Array Reconfiguration}
+In this paper, we use following definition for PV array.
+A PV array is formed by several PV panels.
+A PV panel is formed by three series-connected PV modules.
+A PV module consists of several series-connected PV cells with reverse biased bypass diode.
 
+\section{Feasibility Problem}
+\subsection{Problem setting}
+\subsection{Outline of the algorithm}
+\subsection{Algorithm}
+\section{Experiment Results}
 \section{Conclusion}
@@
 \appendices
-\section{Proof of the First Zonklar Equation}
-Appendix one text goes here.
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-\section{}
-Appendix two text goes here.
-
-% use section* for acknowledgment
 \section*{Acknowledgment}

### 2019-12-12 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-09 21-11-42
Zhao push @ 2019-12-12 19-42-19

@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:introduction}
 \IEEEPARstart{I}{n} recent years, the use of green and renewable energy sources has been increased with the aim to reduce fossil fuel depletion and environment pollution.
@@
 In addition, they require special PV panels with the capability of switching, and cannot be applied to the system constructed with standard PV panels.
-% From a practical view, reconfiguration of connections among PV panels is a realistic solution since a PV panel is manufactured as a physical one panel with two terminals and PV panels can be flexibly interconnected.
 Orozco-Gutierrez et al.
@@
 
-% The main challenge in the reconfiguration of PV arrays concerns a large number of possibilities that must be evaluated to find the best solution.
 This paper proposes an optimization algorithm to check possibilities of configurations for reconfiguring PV arrays, which uses an approach that limit and sort possible combinations by the index of ``Loss-rate''.
@@
 
-\section{PV Array Reconfiguration}
+\section{PV Array Reconfiguration}\label{sec:pv-array-reconf}
 In this paper, we use following definition for PV array.
-A PV array is formed by several PV panels.
+A PV array is formed by PV panels.
+Several PV panels connected in series form a $String$.
 A PV panel is formed by three series-connected PV modules.
 A PV module consists of several series-connected PV cells with reverse biased bypass diode.
+Figure~\ref{fig:array} represent the definition are introduced above.
+\begin{figure}[ht]
+\centerline{\includegraphics[width=\linewidth]{fig/module.png}}
+\caption[]{PV array, string, module and panel}
+\label{fig:array}
+\end{figure}
+In a PV array, we have two constraints.
+PV panels in the same string have the same current level, while all the strings have the same control voltage.
+When considering reconfiguration of PV panel, we should find out the best configuration while considering these constraints.
 
-\section{Feasibility Problem}
-\subsection{Problem setting}
-\subsection{Outline of the algorithm}
-\subsection{Algorithm}
-\section{Experiment Results}
-\section{Conclusion}
+As addressed in section~\ref{sec:introduction}, Orozco-Guierrez et al. proposed an efficient reconfiguration algorithm for mismatched PV arrays.
+The method utilizes information of MPPs of every PV panel that is extracted using an online monitoring\cite{Carotenuto2014} and a power estimation\cite{Orozco-Gutierrez2015}.
+Firstly, PV panel characteristics (current values, voltage values) are extracted and closed values are grouped.
+
+\section{Feasibility Problem}\label{sec:feasibility-problem}
+\subsection{Problem setting}\label{sec:problem-setting}
+\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
+\subsection{Algorithm}\label{sec:algorithm}
+\section{Experiment Results}\label{sec:experiment-results}
+\section{Conclusion}\label{sec:conclusion}
 The conclusion goes here.

### 2019-12-16 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-16 16-55-28

@@
 The method utilizes information of MPPs of every PV panel that is extracted using an online monitoring\cite{Carotenuto2014} and a power estimation\cite{Orozco-Gutierrez2015}.
-Firstly, PV panel characteristics (current values, voltage values) are extracted and closed values are grouped.
 
-\section{Feasibility Problem}\label{sec:feasibility-problem}
-\subsection{Problem setting}\label{sec:problem-setting}
+Firstly, maximum power points of PV panels are extracted by using online monitoring from\cite{Carotenuto2014}.
+Then the current and voltage levels of maximum power point for each PV module $s$, $I_{mpp_{s}}$and $V_{mpp_{s}}$, are estimated from maximum power points of PV panels using the method in\cite{Orozco-Gutierrez2015}.
+
+Estimated maximum power point current values ($I_{mpp_s}$) are approximated and close values are grouped into a small number of classes so that the number of possible combinations, in other words, search space is reduced.
+Estimated maximum power point voltage values ($V_{mpp_s}$) are averaged and the mean value $\Bar{V}_{mpp}$ of all PV modules is used to approximate MPP voltage in the string.
+MPP voltage is approximated by $m \times \Bar{V}_{mpp} $ where $m$ is the number of active modules at the MPP.
+Then possible combination of configurations are enumerated.
+
+For furthermore power simulation and configuration implementation, the current sequence and number of activating PV modules pre-string (it is called $feasibility$) are examined for each configuration.
+A simple feasibility checking method provided in \cite{Orozco-Gutierrez2016} are described as follow.
+
+\textbf{(Feasibility 1)}\footnote{In \cite{Orozco-Gutierrez2016}, only the case of $n=2$ is considered, and we extended the condition to general $n$. }
+For each $n$-th highest current level $I_{n}$ in a current sequence for strings,
+it is required that the number of active modules in a configuration is $N(I_{n}) / n$ or less, where $N(I)$ is the total number of active modules for a current level $I$. 
+The maximum number $M$ of active modules for a PV array is given as
+\begin{equation}
+    M=\mbox{min}\begin{Bmatrix}
+N(I),\frac{N(I_2)}{2},\frac{N(I_3)}{3},\cdots,\frac{N(I_{n})}{n}
+\end{Bmatrix}.
+\label{eq:1}
+\end{equation}
+Thus, approximated power $P$ can be calculated as follow.
+\begin{equation}
+\label{eq:2}
+P=\sum{I_{n}}\times M \times \Bar{V}_{mpp}
+\end{equation}
+
+Approximated power values with and only with \textbf{Feasibility 1} is satisfied are listed into a power matrix like Table~\ref{tab:power-matrix}.
+The configuration with  maximum power value and configurations whose powers are more than 77\% of maximum power are selected as configuration candidates\cite{Orozco-Gutierrez2016}.
+
+\section{Feasibility}
+From Orozco $et$ $al.$ method, to complete reconfiguration, we need to assign panels into strings to realize a candidate configuration.
+For example, consider a candidate configuration for a current sequence (2.5A, 2.5A) with 3 active modules per string as shown in Table~\ref{tab:power-matrix}
+
+\begin{table*}[t]
+  \caption{}
+  \centerline{APPROXIMATED POWER}
+  \vskip5pt
+\label{tab:power-matrix}
+\centering
+\begin{tabular}{c|rrrrrrrrrrr}
+\hline\hline	
+\# modules & 	\multicolumn{10}{c}{currents sequence for strings (A)} \\ 																
+per string		&	\multicolumn{1}{c}{(3,3)}	&	\multicolumn{1}{c}{(3,2.5)}	&	\multicolumn{1}{c}{(3,1.5)}	&	\multicolumn{1}{c}{(3,0.5)}	&	\multicolumn{1}{c}{(2.5,2.5)}	&	\multicolumn{1}{c}{(2.5,1.5)}	&	\multicolumn{1}{c}{(2.5,0.5)}	&	\multicolumn{1}{c}{(1.5,1.5)}	&	\multicolumn{1}{c}{(1.5,0.5)}	&	\multicolumn{1}{c}{(0.5,0.5)}	\\ \hline
+	1	&	120W	&	110W	&	90W	&	70W	&	100W	&	80W	&	60W	&	60W	&	40W	&	20W	\\ \hline
+	2	&	-	&	220W	&	180W	&	140W	&	200W	&	160W	&	120W	&	120W	&	80W	&	40W	\\ \hline	3	&	-	&\textbf{330W}&	270W	&	210W	&	\textbf{300W}	&	240W	&	180W	&	180W	&	120W	&	60W	\\ \hline
+4	&	-	&	-	&	-	&	-	&	-	&	\textbf{320W}	&	240W	&	240W	&	160W	&	80W	\\ \hline
+	 5	&	-	&	-	&	-	&	-	&	-	&	-	&	\textbf{300W}	&	-	&	200W	&	100W	\\ \hline
+	6	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	240W	&	120W	\\ \hline
+\end{tabular}
+\end{table*}
+\section{Algorithm to identify feasibility}\label{sec:algor-ident-feas}
+\subsection{Feasibility problem}\label{sec:feasibility-problem}
 \subsection{Outline of the algorithm}\label{sec:outline-algorithm}

### 2019-12-17 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-17 16-59-41

@@
 \textbf{(Feasibility 1)}\footnote{In \cite{Orozco-Gutierrez2016}, only the case of $n=2$ is considered, and we extended the condition to general $n$. }
-For each $n$-th highest current level $I_{n}$ in a current sequence for strings,
+For each $n$-th highest current level $I_{n}$ in a current sequence $Q$ for strings,
 it is required that the number of active modules in a configuration is $N(I_{n}) / n$ or less, where $N(I)$ is the total number of active modules for a current level $I$. 
@@
 \label{eq:2}
-P=\sum{I_{n}}\times M \times \Bar{V}_{mpp}
+P=\sum{Q}\times M \times \Bar{V}_{mpp}
 \end{equation}
@@
 \section{Feasibility}
-From Orozco $et$ $al.$ method, to complete reconfiguration, we need to assign panels into strings to realize a candidate configuration.
-For example, consider a candidate configuration for a current sequence (2.5A, 2.5A) with 3 active modules per string as shown in Table~\ref{tab:power-matrix}
 
@@
 \end{table*}
+
+From Orozco $et$ $al.$ method, to complete reconfiguration, we need to assign panels into strings to realize a candidate configuration.
+For example, consider a candidate configuration for a current sequence (2.5A, 2.5A) with 3 active modules per string as shown in Table~\ref{tab:power-matrix}
+It can be realized by assigning panel P2 to the first string and panel P1 and P4 to the second string as shown in Figure~\ref{fig:feasibleassign}.
+However, for another current sequence (2.5A, 1.5A), there is no feasible assignment for 4 active modules per string, even though this configuration is listed in Table~\ref{tab:power-matrix} by method in\cite{Orozco-Gutierrez2016}.
+It is same for a configuration candidate with current sequence (3A, 2.5A) for 3 active modules per string.
+That is, the condition \textbf{Feasibility 1} is necessary but not sufficient to give an actual feasibility result.
+
+For a PV array $A$ with $s$ strings, let $M_{A,i}(I)$ denotes the number of modules that can be activated with a current level $I$ in the $i$-th string.
+Let $Q = (Q_1,Q_2,\dots,Q_s)$ be the sequence of current required for strings.
+We define the feasibility as follows: A sequence of current $Q$ is feasible with $m$ modules if and only if it is possible to form a PV array $A$ such that
+\begin{equation}
+  M_{A,i}(Q_i)\geq m
+  \label{eq:3}
+\end{equation}
+holds for each string $i$ (1$\leq i \leq s$).
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=\linewidth]{fig/feasible-configuration.pdf}
+    \caption{Feasible configuration for a current sequence (2.5A, 2.5A) with 3 active modules.}
+    \label{fig:feasibleassign}
+\end{figure}
+
 \section{Algorithm to identify feasibility}\label{sec:algor-ident-feas}
 \subsection{Feasibility problem}\label{sec:feasibility-problem}
+In this section, we introduce an algorithm to identify feasibility for a configuration.
+First we will formulate the feasibility problem that identifies the feasibility for a given current sequence and the number of active modules per string as follows.
+
+\textit{Definition 1} (\textit{Feasibility Problem}):\\
+\textbf{Input}: Information of MPPs (approximated values), a current sequence $Q$, the number of $m$ of active modules per-string.\\
+%\newline
+\textbf{Output}: Whether $Q$ with $m$ modules is feasible or not.
+
 \subsection{Outline of the algorithm}\label{sec:outline-algorithm}
@@
 % by themselves when using endfloat and the captionsoff option.
-\section*{Temp}
-It is well known that mismatch due to partial shading, soiling, or ageing causes significant losses
-in the energy yield of photovoltaic (PV) systems [1,2]. Furthermore, mismatches may hinder operation
-of maximum power point (MPP) tracking algorithms, especially if the power versus output voltage
-characteristic becomes nonconvex [3]. It has also been shown that, even with commonly used bypass
-diodes, mismatched cells may become reverse-biased and dissipate power, producing an undesired
-cell temperature rise or hot spot [4,5]. This may lead to accelerated ageing and reduced reliability of
-the PV system
+% \section*{Temp}
+% It is well known that mismatch due to partial shading, soiling, or ageing causes significant losses
+% in the energy yield of photovoltaic (PV) systems [1,2]. Furthermore, mismatches may hinder operation
+% of maximum power point (MPP) tracking algorithms, especially if the power versus output voltage
+% characteristic becomes nonconvex [3]. It has also been shown that, even with commonly used bypass
+% diodes, mismatched cells may become reverse-biased and dissipate power, producing an undesired
+% cell temperature rise or hot spot [4,5]. This may lead to accelerated ageing and reduced reliability of
+% the PV system
 

### 2019-12-18 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-18 09-56-40

@@
 \subsection{Outline of the algorithm}\label{sec:outline-algorithm}
+For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s})$ $(Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign PV panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$.
+In this step, we will consider how much we lose an opportunity that the panel is more effectively used for the next current level.
 \subsection{Algorithm}\label{sec:algorithm}

### 2019-12-19 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-19 17-01-01

--- 2019-12-17 Journal-Photovoltaic/manuscript.tex
@@
 \subsection{Outline of the algorithm}\label{sec:outline-algorithm}
+In a PV array with $s$ PV strings.
+For a given current sequence $Q = (Q_{1},Q_{2},\ldots ,Q_{s})$ $(Q_{i} \geq Q_{j} \mbox{\ if\ } i \leq j)$, we will assign PV panels to strings in the order of $Q_{1},Q_{2},\ldots ,Q_{s}$.
+In this step, we will consider how much we lose an opportunity that the panel is more effectively used for the next current level.
+For example, as the PV panel shown in Table~\ref{tab:NumofModules} which contain three PV modules.
+2 of 3 modules are able to working at current level of $Q_{1}$ and $Q_{2}$.
+All 3 modules are able to activate at current level $Q_{3}$.
+Thus, if this panel been selected working for a PV string at current level $Q_{1 or 2}$ , two-third of modules are able to deliver energy while the remaining one module been bypassed.
+We consider the ``$loss$'' that how many PV modules we fail to use in other current level and the ``$gain$'' that how many PV modules we can activate in the target current level together.
+Since two parameter are considered in the selection process, they can minimize ``$loss$'' while minimizing the number of selected PV panels.
+% In this algorithm, we select PV panels as so to minimize the $loss$ and maximize the $gain$.
+\begin{table}[tbp]
+  \caption[]{}
+  \label{tab:NumofModules} 
+  \centerline{Maximum number of activate PV modules}
+  \vskip5pt
+  \begin{center}
+  \begin{tabular}{c|c|c|c}
+    \hline
+    Current level                 & $Q_{1}$ & $Q_{2}$ & $Q_{3}$  \\ \hline
+    Number of activate PV modules & 2  & 2    & 3        \\ \hline
+  \end{tabular}
+  \end{center}
+\end{table}
+In this algorithm, we choose $Loss-rate$ to give selection priority.
+The $Loss$-$rate$ is the difference of active modules in panel $p$ for the target current level $Q_n$  in current sequence $Q$ with other current levels per module.
+Let $M_{p}(I)$ denote the number of PV modules that can be active at current level $I$ in panel $p$.
+In a $s$ strings PV array, $Loss-rate$ for panel $p$ of target current level $n$ on $k$-th current level $Q_{k}$ ($2 \leq k \leq s$) is shown as follow.
+\begin{equation}\label{eq:4}
+    Loss\mbox{-}rate(p,n,k) =
+    \begin{cases}
+    \frac{M_{p}(Q_{k})-M_{p}(Q_{n})}{M_{p}(Q_{n})} & \mbox{if } M_{p}(Q_{n}) \neq 0 \\
+    \infty & \mbox{if } M_{p}(Q_{n}) = 0
+  \end{cases}
+\end{equation}
+
+For example, as the panel $p$ in Table~\ref{tab:NumofModules} $Loss-rate(p,Q_{1},Q_{2})=0$, $Loss-rate(p,Q_{1},Q_{3})=0.5$, that is, for target current level $Q_{1}$ there is no ``$loss$'' for current level $Q_{2}$ and only loss ``0.5'' active module for current level $Q_{3}$.
+
+To assign panels of target current level $n$ to $n$-th string, the following step are applied.
+Let $m$ be the required number of active modules per-string.
+\begin{enumerate}
+\item\label{step:1} Sort un-selected panels in a lexicographically ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_p(Q_n)$.
+\item\label{step:2} Selects sorted panels one by one until reaching the required number of active modules $m$.
+  In step 2, panel with no active modules is skipped.
+\item\label{step:3} Optimize the number of active modules.
+  In step 3, if the number of selected active modules exceeds the required number $m$, redundant panels will be removed if exist.
+\end{enumerate}
+
 \subsection{Algorithm}\label{sec:algorithm}

### 2019-12-23 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-23 22-26-09

@@
 
-For example, as the panel $p$ in Table~\ref{tab:NumofModules} $Loss-rate(p,Q_{1},Q_{2})=0$, $Loss-rate(p,Q_{1},Q_{3})=0.5$, that is, for target current level $Q_{1}$ there is no ``$loss$'' for current level $Q_{2}$ and only loss ``0.5'' active module for current level $Q_{3}$.
+For example, as the panel $p$ in Table~\ref{tab:NumofModules} $Loss-rate(p,Q_{1},Q_{2})=0$, $Loss-rate(p,Q_{1},Q_{3})=0.5$, that is, for target current level $Q_{1}$ there is no ``$losses$'' for current level $Q_{2}$ and only ``$loss$'' 0.5 active module for current level $Q_{3}$.
 
@@
 \begin{enumerate}
-\item\label{step:1} Sort un-selected panels in a lexicographically ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_p(Q_n)$.
+  \item\label{step:1} Sort un-selected panels with ``$loss$'' and ``$gain$''.
+% \item\label{step:1} Sort un-selected panels in a lexicographically ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_p(Q_n)$.
 \item\label{step:2} Selects sorted panels one by one until reaching the required number of active modules $m$.
-  In step 2, panel with no active modules is skipped.
+  % In step 2, panel with no active modules is skipped.
 \item\label{step:3} Optimize the number of active modules.
@@
 \end{enumerate}
+% \begin{table*}[h]
+%   \caption[]{ \label{tab:Exampleofalgo}}
+%   \centerline{EXAMPLE OF PROPOSED ALGORITHM}
+%   \vskip5pt
+%   \centering
+%   \begin{tabular}{c|c|l|ccccccc}
+%     \hline
+%     \hline
+%     \multicolumn{3}{c|}{\multirow{2}{*}{}}                                    & \multicolumn{7}{c}{Panels}                                                      \\ \cline{4-10} 
+% \multicolumn{3}{c|}{}                                                     & P1  & P4  & P5                       & P2 & P3 & P7                     & P6     \\ \hline
+% \multirow{3}{*}{Current Levels} & Q1 & \multirow{3}{*}{Number of modules} & 2   & 2   & 2                        & 1  & 1  & 1                      & 0      \\ \cline{2-2}
+%                                 & Q2 &                                    & 2   & 2   & 2                        & 1  & 1  & 1                      & 1      \\ \cline{2-2}
+%                                 & Q3 &                                    & 3   & 3   & 3                        & 2  & 2  & 2                      & 2      \\ \hline
+% \multirow{2}{*}{Loss-rate}      & \multicolumn{2}{c|}{Loss-rate(p,Q1,Q2)} & 0   & 0   & \multicolumn{1}{c|}{0}   & 0  & 0  & \multicolumn{1}{c|}{0} & $\infty$ \\ \cline{2-3}
+%                                 & \multicolumn{2}{c|}{Loss-rate(p,Q1,Q3)} & 0.5 & 0.5 & \multicolumn{1}{c|}{0.5} & 1  & 1  & \multicolumn{1}{c|}{1} & 1      \\ \hline
+% \multicolumn{3}{c|}{Algorithm  priority}                                  & 1   & 2   & 3                        & 4  & 5  & 6                      & 7      \\ \hline
+% \end{tabular}
+% \end{table*}
 
+As shown in Table~\ref{tab:exampleofalgo} ,there is an example that demonstrate how to select PV panel for a string on current level $Q_{1}$ where required active module per string $m$ is 4.
+Panels are sorted by $Loss-rate$ which seen as ``$loss$'' and $M_{p}(Q_{1})$ which seen as ``$gain$''.
+In this example, panel P1, P4 and P5 have the same $Loss-rate$ is (0, 0.5) which is smaller than other panels.
+Thus, those three panels are grouped into the \textbf{First} ``$loss$'' level.
+Similarly, panel P2, P3, and P7 are in the \textbf{Second} ``$loss$'' level and panel p6is in the \textbf{last} ``$loss$'' level because it does not contain any module that is able to activate on the target current level.
+Panel selection started from the \textbf{First} ``$loss$'' level, after selected panels active PV modules exceed $m$ ($m=4$ in this example) selection procedure will terminate.
+If some redundant panels exist, those panels are removed.
+In this example, no redundant panel exist and panel P1 and P4 are selected for target current level $Q_{1}$ PV string.
+\begin{table}[htbp]
+  \caption[]{\label{tab:exampleofalgo}}
+  \centerline{EXAMPLE OF PROPOSED ALGORITHM}
+  \vskip5pt
+  \begin{tabular}{c|c|ccccccc}
+  \hline
+  \hline
+\multicolumn{2}{c|}{\multirow{2}{*}{}}  & \multicolumn{7}{c}{Panels}                                                      \\ \cline{3-9} 
+\multicolumn{2}{c|}{}                   & P1  & P4  & P5                       & P2 & P3 & P7                     & P6     \\ \hline
+\multirow{3}{*}{Number of modules} & Q1 & 2   & 2   & 2                        & 1  & 1  & 1                      & 0      \\ \cline{2-2}
+                                   & Q2 & 2   & 2   & 2                        & 1  & 1  & 1                      & 1      \\ \cline{2-2}
+                                   & Q3 & 3   & 3   & 3                        & 2  & 2  & 2                      & 2      \\ \hline
+\multicolumn{2}{c|}{Loss-rate(p,Q1,Q2)} & 0   & 0   & \multicolumn{1}{c|}{0}   & 0  & 0  & \multicolumn{1}{c|}{0} & $\infty$ \\ \cline{1-2}
+\multicolumn{2}{c|}{Loss-rate(p,Q1,Q3)} & 0.5 & 0.5 & \multicolumn{1}{c|}{0.5} & 1  & 1  & \multicolumn{1}{c|}{1} & 1      \\ \hline
+\multicolumn{2}{c|}{Priority}           & 1   & 2   & 3                        & 4  & 5  & 6                      & 7      \\ \hline
+\end{tabular}
+\end{table}
 \subsection{Algorithm}\label{sec:algorithm}
+Proposed algorithm assigns PV panels of given configuration in order of target current level $Q_{1}, Q_{2},\dots, Q_{s}$.
+Where $Q_{i}\geq Q_{j}$ ($i \leq j$) holds for configurations current sequence $Q = (Q_{1},Q_{2},\dots,Q_{s})$.
+Pseudo code of proposed algorithm as shown below.
+
+In the step~\ref{step:1}, un-selected PV panels are sorted  in a lexicographically  ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_{p}(Q_{n})$.
+This sorting procedure gives a basic priority for all un-selected PV panels.
+A panel with less ``$loss$'' and more modules for target current level are preferred.
+The last sorting index $M_{p}(Q_{n})$ aim to minimize the number of selected PV modules for target current level, and it will be described in step~\ref{step:3}.
+Moreover, according to equation~(\ref{eq:4}), the $Loss-rate$ is infinity for those PV panels who have no active modules.
+
+In the step~\ref{step:2}, sorted PV panels are selected one by one until reaching $m$, the required number of active modules per-string.
+
+In the step~\ref{step:3}, the number of active PV modules and the number of selected panels are optimized.
+
+\section{Evaluation}\label{sec:evaluation}
 \section{Experiment Results}\label{sec:experiment-results}

### 2019-12-26 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-26 17-04-14

@@
 Thus, those three panels are grouped into the \textbf{First} ``$loss$'' level.
-Similarly, panel P2, P3, and P7 are in the \textbf{Second} ``$loss$'' level and panel p6is in the \textbf{last} ``$loss$'' level because it does not contain any module that is able to activate on the target current level.
+Similarly, panel P2, P3, and P7 are in the \textbf{Second} ``$loss$'' level and panel P6 is in the \textbf{last} ``$loss$'' level because it does not contain any module that is able to activate on the target current level.
 Panel selection started from the \textbf{First} ``$loss$'' level, after selected panels active PV modules exceed $m$ ($m=4$ in this example) selection procedure will terminate.
@@
 A panel with less ``$loss$'' and more modules for target current level are preferred.
-The last sorting index $M_{p}(Q_{n})$ aim to minimize the number of selected PV modules for target current level, and it will be described in step~\ref{step:3}.
+The last sorting index $M_{p}(Q_{n})$ aim to minimize the number of selected PV modules for target current level $Q_{n}$, and it will be described in step~\ref{step:3}.
 Moreover, according to equation~(\ref{eq:4}), the $Loss-rate$ is infinity for those PV panels who have no active modules.
@@
 In the step~\ref{step:3}, the number of active PV modules and the number of selected panels are optimized.
+As if selected PV panels contain active PV modules exceed required amount $m$, redundant panels will be removed if existed.
+A PV panel is redundant if and only if the number of active PV module still meet requirement or more even if this panel has been removed.
+This remove procedure starting from the last ``$loss$'' level, proposed algorithm will check $M_{p}Q_{n}$ for each panel $p$.
+If the number of active modules still exceed $m$ after panel $p$ is removed, the same procedure will repeat until all redundant panels are removed or every panel have been checked.
+
+\begin{algorithm}[htbp]
+  \caption{Feasibility Problem}
+  \label{sec:algorithm-1}
+  \LinesNumbered
+  \SetKwInOut{Input}{Input}
+  \Input{
+    \textit{$Q = (Q_{1}, Q_{2}, \ldots ,Q_{s}$)}: current sequence for given configuration; \\
+    \textit{$m$}: the number of required active modules per-string;\\
+    \textit{$M_{p}$}: the number of active modules in each panel \textit{p};\\
+    \textit{s}: the number of strings;
+  }
+  \SetKwInOut{Output}{Output}
+  \Output{
+    Feasibility Result;
+  }
+  \For{\textup{each string} $ k (2 \leq k \leq s)$ \textup{and panel} $p$}{$Loss(p,k) = M_{p}(Q_{k}) - M_{p}(Q_{k-1})$}
+  \For{j = 1 to s}
+  {{\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panels} $< m$}
+      {\textup{\textbf{return :}} Feasibility = NO}}
+    $PS$ = a set of unselected panels with $M_{p}(Q_{j}) > 0$;\\
+     // \textbf{step \ref{step3}}\\
+     sort $PS$ in a lexicographically ascending order of $Loss(p,j+1)$, $Loss(p,j+2)$, $\ldots$, $Loss(p,s)$, $M_{p}(Q_{j})$;\\
+     // \textbf{step \ref{step4}}\\
+     select panels in the order in $PS$ until $\sum M_{p}(Q_{j})$ for selected panels $\geq m$;\\
+     // \textbf{step \ref{step5}}\\
+     group selected panels $LV_{1}$, $LV_{2}$,$\ldots$, $LV_{h}$ with loss level ($LV_{1}$ is the lowest level);\\
+     \For{i = h to 1}
+     {find and cancel redundant panels in $LV_{i}$ in the order in $PS$}
+     // \textbf{step \ref{step6}}\\
+     \For{i = h to 1}
+     {apply swap rules for selected panels in $LV_{i}$ and an unselected panel in the same loss level}
+    }
+    \textup{\textbf{return :}} Feasibility = YES
+  \end{algorithm}
 

### 2019-12-28 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-28 19-22-26

@@
 In this algorithm, we choose $Loss-rate$ to give selection priority.
-The $Loss$-$rate$ is the difference of active modules in panel $p$ for the target current level $Q_n$  in current sequence $Q$ with other current levels per module.
+The $Loss$-$rate$ is the difference of active modules in panel $p$ for the target current level $Q_{k^{'}}$  in current sequence $Q$ with other current levels per module.
 Let $M_{p}(I)$ denote the number of PV modules that can be active at current level $I$ in panel $p$.
-In a $s$ strings PV array, $Loss-rate$ for panel $p$ of target current level $n$ on $k$-th current level $Q_{k}$ ($2 \leq k \leq s$) is shown as follow.
+In a $s$ strings PV array, $Loss-rate$ for panel $p$ of target current level $k^{'}$ on $k$-th current level $Q_{k}$ ($2 \leq k \leq s$) is shown as follow.
 \begin{equation}\label{eq:4}
-    Loss\mbox{-}rate(p,n,k) =
+    Loss\mbox{-}rate(p,k^{'},k) =
     \begin{cases}
-    \frac{M_{p}(Q_{k})-M_{p}(Q_{n})}{M_{p}(Q_{n})} & \mbox{if } M_{p}(Q_{n}) \neq 0 \\
-    \infty & \mbox{if } M_{p}(Q_{n}) = 0
+    \frac{M_{p}(Q_{k})-M_{p}(Q_{k^{'}})}{M_{p}(Q_{k^{'}})} & \mbox{if } M_{p}(Q_{k^{'}}) \neq 0 \\
+    \infty & \mbox{if } M_{p}(Q_{k^{'}}) = 0
   \end{cases}
@@
 
-To assign panels of target current level $n$ to $n$-th string, the following step are applied.
+To assign panels of target current level $k^{'}$ to $k^{'}$-th string, the following step are applied.
 Let $m$ be the required number of active modules per-string.
@@
 
-In the step~\ref{step:1}, un-selected PV panels are sorted  in a lexicographically  ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_{p}(Q_{n})$.
+In the step~\ref{step:1}, un-selected PV panels are sorted  in a lexicographically  ascending order of $Loss$-$rate(p,n,n+1)$, $Loss$-$rate(p,n,n+2)$,$\dots,$ $Loss$-$rate(p,n,s)$ and  lexicographically descending order of $M_{p}(Q_{k^{'}})$.
 This sorting procedure gives a basic priority for all un-selected PV panels.
 A panel with less ``$loss$'' and more modules for target current level are preferred.
-The last sorting index $M_{p}(Q_{n})$ aim to minimize the number of selected PV modules for target current level $Q_{n}$, and it will be described in step~\ref{step:3}.
+The last sorting index $M_{p}(Q_{k^{'}})$ aim to minimize the number of selected PV modules for target current level $Q_{k^{'}}$, and it will be described in step~\ref{step:3}.
 Moreover, according to equation~(\ref{eq:4}), the $Loss-rate$ is infinity for those PV panels who have no active modules.
@@
 A PV panel is redundant if and only if the number of active PV module still meet requirement or more even if this panel has been removed.
-This remove procedure starting from the last ``$loss$'' level, proposed algorithm will check $M_{p}Q_{n}$ for each panel $p$.
+This remove procedure starting from the last ``$loss$'' level, proposed algorithm will check $M_{p}Q_{k^{'}}$ for each panel $p$.
 If the number of active modules still exceed $m$ after panel $p$ is removed, the same procedure will repeat until all redundant panels are removed or every panel have been checked.
@@
     \textit{$m$}: the number of required active modules per-string;\\
-    \textit{$M_{p}$}: the number of active modules in each panel \textit{p};\\
+    \textit{$M_{p}$}: the number of active modules in each panel $p$;\\
     \textit{s}: the number of strings;
@@
   }
-  \For{\textup{each string} $ k (2 \leq k \leq s)$ \textup{and panel} $p$}{$Loss(p,k) = M_{p}(Q_{k}) - M_{p}(Q_{k-1})$}
-  \For{j = 1 to s}
-  {{\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panels} $< m$}
-      {\textup{\textbf{return :}} Feasibility = NO}}
-    $PS$ = a set of unselected panels with $M_{p}(Q_{j}) > 0$;\\
-     // \textbf{step \ref{step3}}\\
-     sort $PS$ in a lexicographically ascending order of $Loss(p,j+1)$, $Loss(p,j+2)$, $\ldots$, $Loss(p,s)$, $M_{p}(Q_{j})$;\\
-     // \textbf{step \ref{step4}}\\
+  \For{\textup{each target current level} $Q_{k}$ $(1 \leq k \leq s)$ \textup{and each panel} $p$}
+  {
+    \uIf{$\sum M_{p}(Q_{k})$ $<$ $m$}
+    {\textup{\textbf{return :}} Feasibility = NO\\
+    \tcc{Not enough active modules to meet requirement}}
+    \Else{$Loss-rate(p,k,k+1) = (M_{p}(Q_{k+1}) - M_{p}(Q_{k}))/M_{p}(Q_{k})$}
+  }
+
+  \For{\textup{each} target current level $Q_{k}$}
+  {
+    % {\If{$\sum M_{p}(Q_{j})$ \textup{for unselected panels} $< m$}
+    %   {\textup{\textbf{return :}} Feasibility = NO}}
+    $P$ = a set of un-selected panels with $M_{p}(Q_{k})$;\\
+     \tcp{\textbf{step~\ref{step:1}}}
+     Sort $PS$ in a lexicographically ascending order of $Loss-rate$ and descending order of $M_{P}(Q_{j})$\\
+     % $Loss(p,j+2)$, $\ldots$, $Loss(p,s)$, $M_{p}(Q_{j})$;\\
+     \tcp{\textbf{step~\ref{step:2}}}
      select panels in the order in $PS$ until $\sum M_{p}(Q_{j})$ for selected panels $\geq m$;\\
-     // \textbf{step \ref{step5}}\\
-     group selected panels $LV_{1}$, $LV_{2}$,$\ldots$, $LV_{h}$ with loss level ($LV_{1}$ is the lowest level);\\
+     % \If{$\sum M_{p}(Q_{j})$ \textup{for selected panels} = $m$}
+     % {\textup{\textbf{return :}} Feasibility = YES}
+     \tcp{\textbf{step~\ref{step:3}}}
+     group selected panels into ``$loss$'' levels ($LV_{1}$, $LV_{2}$,$\ldots$, $LV_{h}$) based on $Loss-rate$ ascending order.\\
      \For{i = h to 1}
-     {find and cancel redundant panels in $LV_{i}$ in the order in $PS$}
-     // \textbf{step \ref{step6}}\\
-     \For{i = h to 1}
-     {apply swap rules for selected panels in $LV_{i}$ and an unselected panel in the same loss level}
+     {
+       find and remove redundant panels in ``$loss$'' level $LV_{i}$
+     }
+     % // \textbf{step \ref{step6}}\\b
+     % \For{i = h to 1}
+     % {apply swap rules for selected panels in $LV_{i}$ and an unselected panel in the same loss level}
     }
@@
 \section{Evaluation}\label{sec:evaluation}
+\subsection{Algorithm time complexity}
+In proposed algorithm, first, $Loss-rate(p,k^{'},k)$ is evaluated for all PV panel $p$ and target current level $Q_{k^{'}}$ with other current level $Q_{k}$.
+This step takes $O(sn)$ where is $n$ is the number of panels and $s$ is the number of PV strings.
+Then the algorithm iterate as follows:
+\begin{enumerate}
+\item\label{item:1} Sort panels by $Loss-rate$ and $M_{P}(Q_{k^{'}})$
+\item\label{item:2} Select initial panels
+\item\label{item:3} Remove redundant panels
+\end{enumerate}
+
 \section{Experiment Results}\label{sec:experiment-results}

### 2019-12-30 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-30 14-25-13

@@
 \section{Evaluation}\label{sec:evaluation}
-\subsection{Algorithm time complexity}
+\subsection{Algorithm time complexity}\label{sec:algor-time-compl}
 In proposed algorithm, first, $Loss-rate(p,k^{'},k)$ is evaluated for all PV panel $p$ and target current level $Q_{k^{'}}$ with other current level $Q_{k}$.
@@
 
-\section{Experiment Results}\label{sec:experiment-results}
+When selecting panels for target current level PV string, to sort panels, we use a lexicographically order of $Loss-rate$ and $M_{P}(Q_{k_{'}})$.
+It can be done by sort panels recursively from the first component, that is, we sort panels by $Loss-rate(p,k^{'},k)$, then, sort panels with same level by $Loss-rate(p,k^{'},k+1)$ and so on.
+Since values of $Loss-rate$ and $M_{P}(Q_{k^{'}})$ are related to the number of modules of PV panel and typically there are three PV modules in a commercial PV panel.
+Thus,we can use a bucket sort with 4 buckets.
+Therefore, it takes $O(n)$ for each bucket sort and $O(sn)$ for a lexicographical sorting in total.
+For initial selection, we check the panels in the sorted order, and we check panels again in reverse order to find and remove redundant panels.
+Therefore, these two steps take $Q(n)$.
+Since it takes $O(sn)$ for each PV string in addition to $O(sn)$ to obtain ``$loss$'' levels, the proposed algorithm takes $Q(s^{2}n)$ in total.
+% $\dots$,$Loss-rate(p,k^{'},s)$, M$_{p}(Q_{k^{'}})$.
+\subsection{Experimental setup}\label{sec:experimental-setup}
+To evaluate proposed methods, we prepared MPP information of 100 mismatched PV arrays and applied algorithms.
+Exhaustive searching algorithm is also applied for comparison.
+MPP information is setup as follows for each PV array.
+Each PV array has 4 - 20 PV panels and the number of panels is randomly determined.
+Three current values are randomly assigned to the three PV modules in each panel from 2 - 20 current values, where the number of possible current values are also randomly determined for each PV array.
+The number of strings is 2 - 8 and it is randomly determined for each PV array.
+
+We first applied the method in~\cite{Orozco-Gutierrez2016} to select configuration candidates.
+% as shown in step 1 and step 2.
+Condition \textbf{Feasibility 1} is applied to exclude a part of infeasible configurations, and then configurations that generate more than 77\% of maximum power are selected from the remaining candidates as mentioned in~\cite{Orozco-Gutierrez2016}.
+In the experiments, 384 candidates are selected from 100 PV arrays as shown in Table.
+That is, for each PV array, 3 - 4 candidates are selected in average.
+\subsection{Experimental results}\label{sec:experimental-results}
 \section{Conclusion}\label{sec:conclusion}

### 2020-01-15 Journal-Photovoltaic/manuscript.tex
fix grammar errors

@@
 \begin{abstract}
-  Power generation efficiency of photovoltaic (PV) systems is significantly affected buy partial shading and PV cell damage.
+  Power generation efficiency of photovoltaic (PV) systems are significantly affected by partial shading and PV cell damage.
   Partial shading or PV cell damage induces mismatched power generation among PV panels.
   Conducted bypass diodes under mismatch conditions result in loss of efficiency in power generation.
-  Mismatched PV array can be recovered by re-configuring electrical connections among PV panels in it.
+  Mismatched PV array can be recovered by reconfiguring electrical connections among PV panels in it.
   In this paper, a feasibility check problem of PV panel reconfiguration is introduced.
-  This problem identifies whether a connection among PV panels can be configured from a given PV module level solution.
-  Proposed algorithm evaluated by comparison with the exhaustive search through random shading distributed PV array.
-  The experimental results demonstrate that proposed algorithm can identify feasible configurations more than 49,000 times faster than the exhaustive search with around 0.5\% errors.
+  This problem identifies whether a connection among PV panels can be configured from a given PV module-level solution.
+  The proposed algorithm evaluated by comparison with the exhaustive search through random shading distributed PV array.
+  The experimental results demonstrate that the proposed algorithm can identify feasible configurations more than 49,000 times faster than the exhaustive search with around 0.5\% errors.
 \end{abstract}

### 2020-01-28 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2020-01-28 15-09-24

@@
 Condition \textbf{Feasibility 1} is applied to exclude a part of infeasible configurations, and then configurations that generate more than 77\% of maximum power are selected from the remaining candidates as mentioned in~\cite{Orozco-Gutierrez2016}.
-In the experiments, 384 candidates are selected from 100 PV arrays as shown in Table.
+In the experiments, 384 candidates are selected from 100 PV arrays as shown in Table~\ref{tab:result}.
 That is, for each PV array, 3 - 4 candidates are selected in average.
+
 \subsection{Experimental results}\label{sec:experimental-results}
+Table~\ref{tab:result} shows the results of feasibility checking by proposed algorithm and the exhaustive search algorithm.
+Since the exhaustive search checks all the combinations of panel connections for each configuration candidate.
+Though the exhaustive search identified total 268 feasible configurations, proposed algorithm identified 266 feasible configurations, only 2 configurations are misidentified.
+The proposed algorithms had a few false negative cases, but its rate was less than 1\%.
+That is, it can correctly identify feasibility for most cases. Indeed, the proposed algorithm found at least one candidate configuration as feasible among 3 - 4 candidates for each PV arrays.
+
+The calculation was performed using an Intel i7-4770 Quad-Core processor and 16 GB RAM.
+The time used by proposed algorithm is 1ms, which is significantly lower than 59s needed by the exhaustive search algorithm.
+
+In conclusion, the proposed algorithms provide a solution for checking the feasibility of PV configurations with an error lower than 1\% but execution speed are significantly faster than the one required by exhaustive search algorithm(about 49,000X).
+\begin{table}[htbp]
+\caption[]{\label{tab:result} }
+\centerline{COMPARISON BETWEEN EXHAUSTIVE SEARCH}
+\centerline{AND PROPOSED ALGORITHM}
+  \vskip5pt
+\begin{tabular}{c|c|c}
+  \hline
+  \hline
+                         & Proposed Algorithm & Exhaustive Search \\ \hline
+Number of PV array       & \multicolumn{2}{c}{100}               \\ \hline
+Number of MPP candidates & \multicolumn{2}{c}{384}               \\ \hline
+Feasible candidates      & 266                & 268               \\ \hline
+Infeasible candidates    & 118                & 116               \\ \hline
+Error rate (\%)          & 0.5                & 0                 \\ \hline
+Ave. time pre candidate  & 0.0012s            & 59s               \\ \hline
+\end{tabular}
+\end{table}
 \section{Conclusion}\label{sec:conclusion}
-The conclusion goes here.
+Power generation of mismatched PV arrays can be recovered by reconfiguring connection of PV panels.
+In this paper, a feasibility check problem to configure PV panel connections from PV module connections is introduced and an algorithm that efficiently and effectively solve the problem are proposed.
+The experimental results show that the proposed algorithm can identify feasible configurations more than 49,000X faster than the exhaustive search with around 0.5\% errors.
 
+The proposed algorithm is useful to identify or configure actual PV panel connections from PV module level specifications or connections.
+Since there are many works of PV module level reconfiguration and PV panel level reconfiguration using PV module level optimization as an intermediate solution, the proposed
+algorithm is useful to actually find PV panel connections from PV module level solutions.
+PV panel level reconfiguration is a practical and realistic solution for PV arrays composed of standard PV panels, and the proposed algorithms contribute to finding an efficient and effective solution for PV panel level reconfiguration.
 \appendices
